### 2016-10-27 Alice_Authorlist_2015-Feb-18.tex
first commit v1

% Collaboration: CERN-LHC-ALICE
% Generation Date is 2015/Feb/18

% How to use:
%%%%%%%%% appendix with author list
%\appendix
%\section{The ALICE Collaboration}
%\label{app:collab}
%\input{authors-list.tex}  %%%%%%% get the latest version before submitting

\begingroup
\small
\begin{flushleft}
J.~Adam\Irefn{org39}\And
D.~Adamov\'{a}\Irefn{org82}\And
M.M.~Aggarwal\Irefn{org86}\And
G.~Aglieri Rinella\Irefn{org36}\And
M.~Agnello\Irefn{org110}\And
N.~Agrawal\Irefn{org47}\And
Z.~Ahammed\Irefn{org130}\And
S.U.~Ahn\Irefn{org67}\And
I.~Aimo\Irefn{org93}\textsuperscript{,}\Irefn{org110}\And
S.~Aiola\Irefn{org135}\And
M.~Ajaz\Irefn{org16}\And
A.~Akindinov\Irefn{org57}\And
S.N.~Alam\Irefn{org130}\And
D.~Aleksandrov\Irefn{org99}\And
B.~Alessandro\Irefn{org110}\And
D.~Alexandre\Irefn{org101}\And
R.~Alfaro Molina\Irefn{org63}\And
A.~Alici\Irefn{org104}\textsuperscript{,}\Irefn{org12}\And
A.~Alkin\Irefn{org3}\And
J.~Alme\Irefn{org37}\And
T.~Alt\Irefn{org42}\And
S.~Altinpinar\Irefn{org18}\And
I.~Altsybeev\Irefn{org129}\And
C.~Alves Garcia Prado\Irefn{org118}\And
C.~Andrei\Irefn{org77}\And
A.~Andronic\Irefn{org96}\And
V.~Anguelov\Irefn{org92}\And
J.~Anielski\Irefn{org53}\And
T.~Anti\v{c}i\'{c}\Irefn{org97}\And
F.~Antinori\Irefn{org107}\And
P.~Antonioli\Irefn{org104}\And
L.~Aphecetche\Irefn{org112}\And
H.~Appelsh\"{a}user\Irefn{org52}\And
S.~Arcelli\Irefn{org28}\And
N.~Armesto\Irefn{org17}\And
R.~Arnaldi\Irefn{org110}\And
T.~Aronsson\Irefn{org135}\And
I.C.~Arsene\Irefn{org22}\And
M.~Arslandok\Irefn{org52}\And
A.~Augustinus\Irefn{org36}\And
R.~Averbeck\Irefn{org96}\And
M.D.~Azmi\Irefn{org19}\And
M.~Bach\Irefn{org42}\And
A.~Badal\`{a}\Irefn{org106}\And
Y.W.~Baek\Irefn{org43}\And
S.~Bagnasco\Irefn{org110}\And
R.~Bailhache\Irefn{org52}\And
R.~Bala\Irefn{org89}\And
A.~Baldisseri\Irefn{org15}\And
F.~Baltasar Dos Santos Pedrosa\Irefn{org36}\And
R.C.~Baral\Irefn{org60}\And
A.M.~Barbano\Irefn{org110}\And
R.~Barbera\Irefn{org29}\And
F.~Barile\Irefn{org33}\And
G.G.~Barnaf\"{o}ldi\Irefn{org134}\And
L.S.~Barnby\Irefn{org101}\And
V.~Barret\Irefn{org69}\And
P.~Bartalini\Irefn{org7}\And
J.~Bartke\Irefn{org115}\And
E.~Bartsch\Irefn{org52}\And
M.~Basile\Irefn{org28}\And
N.~Bastid\Irefn{org69}\And
S.~Basu\Irefn{org130}\And
B.~Bathen\Irefn{org53}\And
G.~Batigne\Irefn{org112}\And
A.~Batista Camejo\Irefn{org69}\And
B.~Batyunya\Irefn{org65}\And
P.C.~Batzing\Irefn{org22}\And
I.G.~Bearden\Irefn{org79}\And
H.~Beck\Irefn{org52}\And
C.~Bedda\Irefn{org110}\And
N.K.~Behera\Irefn{org48}\textsuperscript{,}\Irefn{org47}\And
I.~Belikov\Irefn{org54}\And
F.~Bellini\Irefn{org28}\And
H.~Bello Martinez\Irefn{org2}\And
R.~Bellwied\Irefn{org120}\And
R.~Belmont\Irefn{org133}\And
E.~Belmont-Moreno\Irefn{org63}\And
V.~Belyaev\Irefn{org75}\And
G.~Bencedi\Irefn{org134}\And
S.~Beole\Irefn{org27}\And
I.~Berceanu\Irefn{org77}\And
A.~Bercuci\Irefn{org77}\And
Y.~Berdnikov\Irefn{org84}\And
D.~Berenyi\Irefn{org134}\And
R.A.~Bertens\Irefn{org56}\And
D.~Berzano\Irefn{org36}\textsuperscript{,}\Irefn{org27}\And
L.~Betev\Irefn{org36}\And
A.~Bhasin\Irefn{org89}\And
I.R.~Bhat\Irefn{org89}\And
A.K.~Bhati\Irefn{org86}\And
B.~Bhattacharjee\Irefn{org44}\And
J.~Bhom\Irefn{org126}\And
L.~Bianchi\Irefn{org27}\textsuperscript{,}\Irefn{org120}\And
N.~Bianchi\Irefn{org71}\And
C.~Bianchin\Irefn{org133}\textsuperscript{,}\Irefn{org56}\And
J.~Biel\v{c}\'{\i}k\Irefn{org39}\And
J.~Biel\v{c}\'{\i}kov\'{a}\Irefn{org82}\And
A.~Bilandzic\Irefn{org79}\And
S.~Biswas\Irefn{org78}\And
S.~Bjelogrlic\Irefn{org56}\And
F.~Blanco\Irefn{org10}\And
D.~Blau\Irefn{org99}\And
C.~Blume\Irefn{org52}\And
F.~Bock\Irefn{org73}\textsuperscript{,}\Irefn{org92}\And
A.~Bogdanov\Irefn{org75}\And
H.~B{\o}ggild\Irefn{org79}\And
L.~Boldizs\'{a}r\Irefn{org134}\And
M.~Bombara\Irefn{org40}\And
J.~Book\Irefn{org52}\And
H.~Borel\Irefn{org15}\And
A.~Borissov\Irefn{org95}\And
M.~Borri\Irefn{org81}\And
F.~Boss\'u\Irefn{org64}\And
M.~Botje\Irefn{org80}\And
E.~Botta\Irefn{org27}\And
S.~B\"{o}ttger\Irefn{org51}\And
P.~Braun-Munzinger\Irefn{org96}\And
M.~Bregant\Irefn{org118}\And
T.~Breitner\Irefn{org51}\And
T.A.~Broker\Irefn{org52}\And
T.A.~Browning\Irefn{org94}\And
M.~Broz\Irefn{org39}\And
E.J.~Brucken\Irefn{org45}\And
E.~Bruna\Irefn{org110}\And
G.E.~Bruno\Irefn{org33}\And
D.~Budnikov\Irefn{org98}\And
H.~Buesching\Irefn{org52}\And
S.~Bufalino\Irefn{org110}\textsuperscript{,}\Irefn{org36}\And
P.~Buncic\Irefn{org36}\And
O.~Busch\Irefn{org92}\textsuperscript{,}\Irefn{org126}\And
Z.~Buthelezi\Irefn{org64}\And
J.T.~Buxton\Irefn{org20}\And
D.~Caffarri\Irefn{org36}\textsuperscript{,}\Irefn{org30}\And
X.~Cai\Irefn{org7}\And
H.~Caines\Irefn{org135}\And
L.~Calero Diaz\Irefn{org71}\And
A.~Caliva\Irefn{org56}\And
E.~Calvo Villar\Irefn{org102}\And
P.~Camerini\Irefn{org26}\And
F.~Carena\Irefn{org36}\And
W.~Carena\Irefn{org36}\And
J.~Castillo Castellanos\Irefn{org15}\And
A.J.~Castro\Irefn{org123}\And
E.A.R.~Casula\Irefn{org25}\And
C.~Cavicchioli\Irefn{org36}\And
C.~Ceballos Sanchez\Irefn{org9}\And
J.~Cepila\Irefn{org39}\And
P.~Cerello\Irefn{org110}\And
B.~Chang\Irefn{org121}\And
S.~Chapeland\Irefn{org36}\And
M.~Chartier\Irefn{org122}\And
J.L.~Charvet\Irefn{org15}\And
S.~Chattopadhyay\Irefn{org130}\And
S.~Chattopadhyay\Irefn{org100}\And
V.~Chelnokov\Irefn{org3}\And
M.~Cherney\Irefn{org85}\And
C.~Cheshkov\Irefn{org128}\And
B.~Cheynis\Irefn{org128}\And
V.~Chibante Barroso\Irefn{org36}\And
D.D.~Chinellato\Irefn{org119}\And
P.~Chochula\Irefn{org36}\And
K.~Choi\Irefn{org95}\And
M.~Chojnacki\Irefn{org79}\And
S.~Choudhury\Irefn{org130}\And
P.~Christakoglou\Irefn{org80}\And
C.H.~Christensen\Irefn{org79}\And
P.~Christiansen\Irefn{org34}\And
T.~Chujo\Irefn{org126}\And
S.U.~Chung\Irefn{org95}\And
Z.~Chunhui\Irefn{org56}\And
C.~Cicalo\Irefn{org105}\And
L.~Cifarelli\Irefn{org12}\textsuperscript{,}\Irefn{org28}\And
F.~Cindolo\Irefn{org104}\And
J.~Cleymans\Irefn{org88}\And
F.~Colamaria\Irefn{org33}\And
D.~Colella\Irefn{org33}\And
A.~Collu\Irefn{org25}\And
M.~Colocci\Irefn{org28}\And
G.~Conesa Balbastre\Irefn{org70}\And
Z.~Conesa del Valle\Irefn{org50}\And
M.E.~Connors\Irefn{org135}\And
J.G.~Contreras\Irefn{org39}\textsuperscript{,}\Irefn{org11}\And
T.M.~Cormier\Irefn{org83}\And
Y.~Corrales Morales\Irefn{org27}\And
I.~Cort\'{e}s Maldonado\Irefn{org2}\And
P.~Cortese\Irefn{org32}\And
M.R.~Cosentino\Irefn{org118}\And
F.~Costa\Irefn{org36}\And
P.~Crochet\Irefn{org69}\And
R.~Cruz Albino\Irefn{org11}\And
E.~Cuautle\Irefn{org62}\And
L.~Cunqueiro\Irefn{org36}\And
T.~Dahms\Irefn{org91}\And
A.~Dainese\Irefn{org107}\And
A.~Danu\Irefn{org61}\And
D.~Das\Irefn{org100}\And
I.~Das\Irefn{org100}\textsuperscript{,}\Irefn{org50}\And
S.~Das\Irefn{org4}\And
A.~Dash\Irefn{org119}\And
S.~Dash\Irefn{org47}\And
S.~De\Irefn{org118}\And
A.~De Caro\Irefn{org31}\textsuperscript{,}\Irefn{org12}\And
G.~de Cataldo\Irefn{org103}\And
J.~de Cuveland\Irefn{org42}\And
A.~De Falco\Irefn{org25}\And
D.~De Gruttola\Irefn{org12}\textsuperscript{,}\Irefn{org31}\And
N.~De Marco\Irefn{org110}\And
S.~De Pasquale\Irefn{org31}\And
A.~Deisting\Irefn{org96}\textsuperscript{,}\Irefn{org92}\And
A.~Deloff\Irefn{org76}\And
E.~D\'{e}nes\Irefn{org134}\And
G.~D'Erasmo\Irefn{org33}\And
D.~Di Bari\Irefn{org33}\And
A.~Di Mauro\Irefn{org36}\And
P.~Di Nezza\Irefn{org71}\And
M.A.~Diaz Corchero\Irefn{org10}\And
T.~Dietel\Irefn{org88}\And
P.~Dillenseger\Irefn{org52}\And
R.~Divi\`{a}\Irefn{org36}\And
{\O}.~Djuvsland\Irefn{org18}\And
A.~Dobrin\Irefn{org56}\textsuperscript{,}\Irefn{org80}\And
T.~Dobrowolski\Irefn{org76}\Aref{0}\And
D.~Domenicis Gimenez\Irefn{org118}\And
B.~D\"{o}nigus\Irefn{org52}\And
O.~Dordic\Irefn{org22}\And
A.K.~Dubey\Irefn{org130}\And
A.~Dubla\Irefn{org56}\And
L.~Ducroux\Irefn{org128}\And
P.~Dupieux\Irefn{org69}\And
R.J.~Ehlers\Irefn{org135}\And
D.~Elia\Irefn{org103}\And
H.~Engel\Irefn{org51}\And
B.~Erazmus\Irefn{org112}\textsuperscript{,}\Irefn{org36}\And
F.~Erhardt\Irefn{org127}\And
D.~Eschweiler\Irefn{org42}\And
B.~Espagnon\Irefn{org50}\And
M.~Estienne\Irefn{org112}\And
S.~Esumi\Irefn{org126}\And
J.~Eum\Irefn{org95}\And
D.~Evans\Irefn{org101}\And
S.~Evdokimov\Irefn{org111}\And
G.~Eyyubova\Irefn{org39}\And
L.~Fabbietti\Irefn{org91}\And
D.~Fabris\Irefn{org107}\And
J.~Faivre\Irefn{org70}\And
A.~Fantoni\Irefn{org71}\And
M.~Fasel\Irefn{org73}\And
L.~Feldkamp\Irefn{org53}\And
D.~Felea\Irefn{org61}\And
A.~Feliciello\Irefn{org110}\And
G.~Feofilov\Irefn{org129}\And
J.~Ferencei\Irefn{org82}\And
A.~Fern\'{a}ndez T\'{e}llez\Irefn{org2}\And
E.G.~Ferreiro\Irefn{org17}\And
A.~Ferretti\Irefn{org27}\And
A.~Festanti\Irefn{org30}\And
J.~Figiel\Irefn{org115}\And
M.A.S.~Figueredo\Irefn{org122}\And
S.~Filchagin\Irefn{org98}\And
D.~Finogeev\Irefn{org55}\And
F.M.~Fionda\Irefn{org103}\And
E.M.~Fiore\Irefn{org33}\And
M.G.~Fleck\Irefn{org92}\And
M.~Floris\Irefn{org36}\And
S.~Foertsch\Irefn{org64}\And
P.~Foka\Irefn{org96}\And
S.~Fokin\Irefn{org99}\And
E.~Fragiacomo\Irefn{org109}\And
A.~Francescon\Irefn{org36}\textsuperscript{,}\Irefn{org30}\And
U.~Frankenfeld\Irefn{org96}\And
U.~Fuchs\Irefn{org36}\And
C.~Furget\Irefn{org70}\And
A.~Furs\Irefn{org55}\And
M.~Fusco Girard\Irefn{org31}\And
J.J.~Gaardh{\o}je\Irefn{org79}\And
M.~Gagliardi\Irefn{org27}\And
A.M.~Gago\Irefn{org102}\And
M.~Gallio\Irefn{org27}\And
D.R.~Gangadharan\Irefn{org73}\And
P.~Ganoti\Irefn{org87}\And
C.~Gao\Irefn{org7}\And
C.~Garabatos\Irefn{org96}\And
E.~Garcia-Solis\Irefn{org13}\And
C.~Gargiulo\Irefn{org36}\And
P.~Gasik\Irefn{org91}\And
M.~Germain\Irefn{org112}\And
A.~Gheata\Irefn{org36}\And
M.~Gheata\Irefn{org61}\textsuperscript{,}\Irefn{org36}\And
P.~Ghosh\Irefn{org130}\And
S.K.~Ghosh\Irefn{org4}\And
P.~Gianotti\Irefn{org71}\And
P.~Giubellino\Irefn{org36}\And
P.~Giubilato\Irefn{org30}\And
E.~Gladysz-Dziadus\Irefn{org115}\And
P.~Gl\"{a}ssel\Irefn{org92}\And
A.~Gomez Ramirez\Irefn{org51}\And
P.~Gonz\'{a}lez-Zamora\Irefn{org10}\And
S.~Gorbunov\Irefn{org42}\And
L.~G\"{o}rlich\Irefn{org115}\And
S.~Gotovac\Irefn{org114}\And
V.~Grabski\Irefn{org63}\And
L.K.~Graczykowski\Irefn{org132}\And
A.~Grelli\Irefn{org56}\And
A.~Grigoras\Irefn{org36}\And
C.~Grigoras\Irefn{org36}\And
V.~Grigoriev\Irefn{org75}\And
A.~Grigoryan\Irefn{org1}\And
S.~Grigoryan\Irefn{org65}\And
B.~Grinyov\Irefn{org3}\And
N.~Grion\Irefn{org109}\And
J.F.~Grosse-Oetringhaus\Irefn{org36}\And
J.-Y.~Grossiord\Irefn{org128}\And
R.~Grosso\Irefn{org36}\And
F.~Guber\Irefn{org55}\And
R.~Guernane\Irefn{org70}\And
B.~Guerzoni\Irefn{org28}\And
K.~Gulbrandsen\Irefn{org79}\And
H.~Gulkanyan\Irefn{org1}\And
T.~Gunji\Irefn{org125}\And
A.~Gupta\Irefn{org89}\And
R.~Gupta\Irefn{org89}\And
R.~Haake\Irefn{org53}\And
{\O}.~Haaland\Irefn{org18}\And
C.~Hadjidakis\Irefn{org50}\And
M.~Haiduc\Irefn{org61}\And
H.~Hamagaki\Irefn{org125}\And
G.~Hamar\Irefn{org134}\And
L.D.~Hanratty\Irefn{org101}\And
A.~Hansen\Irefn{org79}\And
J.W.~Harris\Irefn{org135}\And
H.~Hartmann\Irefn{org42}\And
A.~Harton\Irefn{org13}\And
D.~Hatzifotiadou\Irefn{org104}\And
S.~Hayashi\Irefn{org125}\And
S.T.~Heckel\Irefn{org52}\And
M.~Heide\Irefn{org53}\And
H.~Helstrup\Irefn{org37}\And
A.~Herghelegiu\Irefn{org77}\And
G.~Herrera Corral\Irefn{org11}\And
B.A.~Hess\Irefn{org35}\And
K.F.~Hetland\Irefn{org37}\And
T.E.~Hilden\Irefn{org45}\And
H.~Hillemanns\Irefn{org36}\And
B.~Hippolyte\Irefn{org54}\And
P.~Hristov\Irefn{org36}\And
M.~Huang\Irefn{org18}\And
T.J.~Humanic\Irefn{org20}\And
N.~Hussain\Irefn{org44}\And
T.~Hussain\Irefn{org19}\And
D.~Hutter\Irefn{org42}\And
D.S.~Hwang\Irefn{org21}\And
R.~Ilkaev\Irefn{org98}\And
I.~Ilkiv\Irefn{org76}\And
M.~Inaba\Irefn{org126}\And
C.~Ionita\Irefn{org36}\And
M.~Ippolitov\Irefn{org75}\textsuperscript{,}\Irefn{org99}\And
M.~Irfan\Irefn{org19}\And
M.~Ivanov\Irefn{org96}\And
V.~Ivanov\Irefn{org84}\And
V.~Izucheev\Irefn{org111}\And
P.M.~Jacobs\Irefn{org73}\And
C.~Jahnke\Irefn{org118}\And
H.J.~Jang\Irefn{org67}\And
M.A.~Janik\Irefn{org132}\And
P.H.S.Y.~Jayarathna\Irefn{org120}\And
C.~Jena\Irefn{org30}\And
S.~Jena\Irefn{org120}\And
R.T.~Jimenez Bustamante\Irefn{org62}\And
P.G.~Jones\Irefn{org101}\And
H.~Jung\Irefn{org43}\And
A.~Jusko\Irefn{org101}\And
P.~Kalinak\Irefn{org58}\And
A.~Kalweit\Irefn{org36}\And
J.~Kamin\Irefn{org52}\And
J.H.~Kang\Irefn{org136}\And
V.~Kaplin\Irefn{org75}\And
S.~Kar\Irefn{org130}\And
A.~Karasu Uysal\Irefn{org68}\And
O.~Karavichev\Irefn{org55}\And
T.~Karavicheva\Irefn{org55}\And
E.~Karpechev\Irefn{org55}\And
U.~Kebschull\Irefn{org51}\And
R.~Keidel\Irefn{org137}\And
D.L.D.~Keijdener\Irefn{org56}\And
M.~Keil\Irefn{org36}\And
K.H.~Khan\Irefn{org16}\And
M.M.~Khan\Irefn{org19}\And
P.~Khan\Irefn{org100}\And
S.A.~Khan\Irefn{org130}\And
A.~Khanzadeev\Irefn{org84}\And
Y.~Kharlov\Irefn{org111}\And
B.~Kileng\Irefn{org37}\And
B.~Kim\Irefn{org136}\And
D.W.~Kim\Irefn{org43}\textsuperscript{,}\Irefn{org67}\And
D.J.~Kim\Irefn{org121}\And
H.~Kim\Irefn{org136}\And
J.S.~Kim\Irefn{org43}\And
M.~Kim\Irefn{org43}\And
M.~Kim\Irefn{org136}\And
S.~Kim\Irefn{org21}\And
T.~Kim\Irefn{org136}\And
S.~Kirsch\Irefn{org42}\And
I.~Kisel\Irefn{org42}\And
S.~Kiselev\Irefn{org57}\And
A.~Kisiel\Irefn{org132}\And
G.~Kiss\Irefn{org134}\And
J.L.~Klay\Irefn{org6}\And
C.~Klein\Irefn{org52}\And
J.~Klein\Irefn{org92}\And
C.~Klein-B\"{o}sing\Irefn{org53}\And
A.~Kluge\Irefn{org36}\And
M.L.~Knichel\Irefn{org92}\And
A.G.~Knospe\Irefn{org116}\And
T.~Kobayashi\Irefn{org126}\And
C.~Kobdaj\Irefn{org113}\And
M.~Kofarago\Irefn{org36}\And
M.K.~K\"{o}hler\Irefn{org96}\And
T.~Kollegger\Irefn{org42}\textsuperscript{,}\Irefn{org96}\And
A.~Kolojvari\Irefn{org129}\And
V.~Kondratiev\Irefn{org129}\And
N.~Kondratyeva\Irefn{org75}\And
E.~Kondratyuk\Irefn{org111}\And
A.~Konevskikh\Irefn{org55}\And
C.~Kouzinopoulos\Irefn{org36}\And
O.~Kovalenko\Irefn{org76}\And
V.~Kovalenko\Irefn{org129}\And
M.~Kowalski\Irefn{org36}\textsuperscript{,}\Irefn{org115}\And
S.~Kox\Irefn{org70}\And
G.~Koyithatta Meethaleveedu\Irefn{org47}\And
J.~Kral\Irefn{org121}\And
I.~Kr\'{a}lik\Irefn{org58}\And
A.~Krav\v{c}\'{a}kov\'{a}\Irefn{org40}\And
M.~Krelina\Irefn{org39}\And
M.~Kretz\Irefn{org42}\And
M.~Krivda\Irefn{org101}\textsuperscript{,}\Irefn{org58}\And
F.~Krizek\Irefn{org82}\And
E.~Kryshen\Irefn{org36}\And
M.~Krzewicki\Irefn{org96}\textsuperscript{,}\Irefn{org42}\And
A.M.~Kubera\Irefn{org20}\And
V.~Ku\v{c}era\Irefn{org82}\And
T.~Kugathasan\Irefn{org36}\And
C.~Kuhn\Irefn{org54}\And
P.G.~Kuijer\Irefn{org80}\And
I.~Kulakov\Irefn{org42}\And
J.~Kumar\Irefn{org47}\And
L.~Kumar\Irefn{org78}\textsuperscript{,}\Irefn{org86}\And
P.~Kurashvili\Irefn{org76}\And
A.~Kurepin\Irefn{org55}\And
A.B.~Kurepin\Irefn{org55}\And
A.~Kuryakin\Irefn{org98}\And
S.~Kushpil\Irefn{org82}\And
M.J.~Kweon\Irefn{org49}\And
Y.~Kwon\Irefn{org136}\And
S.L.~La Pointe\Irefn{org110}\And
P.~La Rocca\Irefn{org29}\And
C.~Lagana Fernandes\Irefn{org118}\And
I.~Lakomov\Irefn{org36}\textsuperscript{,}\Irefn{org50}\And
R.~Langoy\Irefn{org41}\And
C.~Lara\Irefn{org51}\And
A.~Lardeux\Irefn{org15}\And
A.~Lattuca\Irefn{org27}\And
E.~Laudi\Irefn{org36}\And
R.~Lea\Irefn{org26}\And
L.~Leardini\Irefn{org92}\And
G.R.~Lee\Irefn{org101}\And
S.~Lee\Irefn{org136}\And
I.~Legrand\Irefn{org36}\And
R.C.~Lemmon\Irefn{org81}\And
V.~Lenti\Irefn{org103}\And
E.~Leogrande\Irefn{org56}\And
I.~Le\'{o}n Monz\'{o}n\Irefn{org117}\And
M.~Leoncino\Irefn{org27}\And
P.~L\'{e}vai\Irefn{org134}\And
S.~Li\Irefn{org7}\textsuperscript{,}\Irefn{org69}\And
X.~Li\Irefn{org14}\And
J.~Lien\Irefn{org41}\And
R.~Lietava\Irefn{org101}\And
S.~Lindal\Irefn{org22}\And
V.~Lindenstruth\Irefn{org42}\And
C.~Lippmann\Irefn{org96}\And
M.A.~Lisa\Irefn{org20}\And
H.M.~Ljunggren\Irefn{org34}\And
D.F.~Lodato\Irefn{org56}\And
P.I.~Loenne\Irefn{org18}\And
V.R.~Loggins\Irefn{org133}\And
V.~Loginov\Irefn{org75}\And
C.~Loizides\Irefn{org73}\And
X.~Lopez\Irefn{org69}\And
E.~L\'{o}pez Torres\Irefn{org9}\And
A.~Lowe\Irefn{org134}\And
P.~Luettig\Irefn{org52}\And
M.~Lunardon\Irefn{org30}\And
G.~Luparello\Irefn{org26}\textsuperscript{,}\Irefn{org56}\And
P.H.F.N.D.~Luz\Irefn{org118}\And
A.~Maevskaya\Irefn{org55}\And
M.~Mager\Irefn{org36}\And
S.~Mahajan\Irefn{org89}\And
S.M.~Mahmood\Irefn{org22}\And
A.~Maire\Irefn{org54}\And
R.D.~Majka\Irefn{org135}\And
M.~Malaev\Irefn{org84}\And
I.~Maldonado Cervantes\Irefn{org62}\And
L.~Malinina\Irefn{org65}\And
D.~Mal'Kevich\Irefn{org57}\And
P.~Malzacher\Irefn{org96}\And
A.~Mamonov\Irefn{org98}\And
L.~Manceau\Irefn{org110}\And
V.~Manko\Irefn{org99}\And
F.~Manso\Irefn{org69}\And
V.~Manzari\Irefn{org103}\textsuperscript{,}\Irefn{org36}\And
M.~Marchisone\Irefn{org27}\And
J.~Mare\v{s}\Irefn{org59}\And
G.V.~Margagliotti\Irefn{org26}\And
A.~Margotti\Irefn{org104}\And
J.~Margutti\Irefn{org56}\And
A.~Mar\'{\i}n\Irefn{org96}\And
C.~Markert\Irefn{org116}\And
M.~Marquard\Irefn{org52}\And
N.A.~Martin\Irefn{org96}\And
J.~Martin Blanco\Irefn{org112}\And
P.~Martinengo\Irefn{org36}\And
M.I.~Mart\'{\i}nez\Irefn{org2}\And
G.~Mart\'{\i}nez Garc\'{\i}a\Irefn{org112}\And
M.~Martinez Pedreira\Irefn{org36}\And
Y.~Martynov\Irefn{org3}\And
A.~Mas\Irefn{org118}\And
S.~Masciocchi\Irefn{org96}\And
M.~Masera\Irefn{org27}\And
A.~Masoni\Irefn{org105}\And
L.~Massacrier\Irefn{org112}\And
A.~Mastroserio\Irefn{org33}\And
H.~Masui\Irefn{org126}\And
A.~Matyja\Irefn{org115}\And
C.~Mayer\Irefn{org115}\And
J.~Mazer\Irefn{org123}\And
M.A.~Mazzoni\Irefn{org108}\And
D.~Mcdonald\Irefn{org120}\And
F.~Meddi\Irefn{org24}\And
A.~Menchaca-Rocha\Irefn{org63}\And
E.~Meninno\Irefn{org31}\And
J.~Mercado P\'erez\Irefn{org92}\And
M.~Meres\Irefn{org38}\And
Y.~Miake\Irefn{org126}\And
M.M.~Mieskolainen\Irefn{org45}\And
K.~Mikhaylov\Irefn{org57}\textsuperscript{,}\Irefn{org65}\And
L.~Milano\Irefn{org36}\And
J.~Milosevic\Irefn{org22}\textsuperscript{,}\Irefn{org131}\And
L.M.~Minervini\Irefn{org103}\textsuperscript{,}\Irefn{org23}\And
A.~Mischke\Irefn{org56}\And
A.N.~Mishra\Irefn{org48}\And
D.~Mi\'{s}kowiec\Irefn{org96}\And
J.~Mitra\Irefn{org130}\And
C.M.~Mitu\Irefn{org61}\And
N.~Mohammadi\Irefn{org56}\And
B.~Mohanty\Irefn{org130}\textsuperscript{,}\Irefn{org78}\And
L.~Molnar\Irefn{org54}\And
L.~Monta\~{n}o Zetina\Irefn{org11}\And
E.~Montes\Irefn{org10}\And
M.~Morando\Irefn{org30}\And
D.A.~Moreira De Godoy\Irefn{org112}\And
S.~Moretto\Irefn{org30}\And
A.~Morreale\Irefn{org112}\And
A.~Morsch\Irefn{org36}\And
V.~Muccifora\Irefn{org71}\And
E.~Mudnic\Irefn{org114}\And
D.~M{\"u}hlheim\Irefn{org53}\And
S.~Muhuri\Irefn{org130}\And
M.~Mukherjee\Irefn{org130}\And
H.~M\"{u}ller\Irefn{org36}\And
J.D.~Mulligan\Irefn{org135}\And
M.G.~Munhoz\Irefn{org118}\And
S.~Murray\Irefn{org64}\And
L.~Musa\Irefn{org36}\And
J.~Musinsky\Irefn{org58}\And
B.K.~Nandi\Irefn{org47}\And
R.~Nania\Irefn{org104}\And
E.~Nappi\Irefn{org103}\And
M.U.~Naru\Irefn{org16}\And
C.~Nattrass\Irefn{org123}\And
K.~Nayak\Irefn{org78}\And
T.K.~Nayak\Irefn{org130}\And
S.~Nazarenko\Irefn{org98}\And
A.~Nedosekin\Irefn{org57}\And
L.~Nellen\Irefn{org62}\And
F.~Ng\Irefn{org120}\And
M.~Nicassio\Irefn{org96}\And
M.~Niculescu\Irefn{org61}\textsuperscript{,}\Irefn{org36}\And
J.~Niedziela\Irefn{org36}\And
B.S.~Nielsen\Irefn{org79}\And
S.~Nikolaev\Irefn{org99}\And
S.~Nikulin\Irefn{org99}\And
V.~Nikulin\Irefn{org84}\And
F.~Noferini\Irefn{org104}\textsuperscript{,}\Irefn{org12}\And
P.~Nomokonov\Irefn{org65}\And
G.~Nooren\Irefn{org56}\And
J.~Norman\Irefn{org122}\And
A.~Nyanin\Irefn{org99}\And
J.~Nystrand\Irefn{org18}\And
H.~Oeschler\Irefn{org92}\And
S.~Oh\Irefn{org135}\And
S.K.~Oh\Irefn{org66}\And
A.~Ohlson\Irefn{org36}\And
A.~Okatan\Irefn{org68}\And
T.~Okubo\Irefn{org46}\And
L.~Olah\Irefn{org134}\And
J.~Oleniacz\Irefn{org132}\And
A.C.~Oliveira Da Silva\Irefn{org118}\And
M.H.~Oliver\Irefn{org135}\And
J.~Onderwaater\Irefn{org96}\And
C.~Oppedisano\Irefn{org110}\And
A.~Ortiz Velasquez\Irefn{org62}\And
A.~Oskarsson\Irefn{org34}\And
J.~Otwinowski\Irefn{org96}\textsuperscript{,}\Irefn{org115}\And
K.~Oyama\Irefn{org92}\And
M.~Ozdemir\Irefn{org52}\And
Y.~Pachmayer\Irefn{org92}\And
P.~Pagano\Irefn{org31}\And
G.~Pai\'{c}\Irefn{org62}\And
C.~Pajares\Irefn{org17}\And
S.K.~Pal\Irefn{org130}\And
J.~Pan\Irefn{org133}\And
A.K.~Pandey\Irefn{org47}\And
D.~Pant\Irefn{org47}\And
V.~Papikyan\Irefn{org1}\And
G.S.~Pappalardo\Irefn{org106}\And
P.~Pareek\Irefn{org48}\And
W.J.~Park\Irefn{org96}\And
S.~Parmar\Irefn{org86}\And
A.~Passfeld\Irefn{org53}\And
V.~Paticchio\Irefn{org103}\And
B.~Paul\Irefn{org100}\And
T.~Peitzmann\Irefn{org56}\And
H.~Pereira Da Costa\Irefn{org15}\And
E.~Pereira De Oliveira Filho\Irefn{org118}\And
D.~Peresunko\Irefn{org75}\textsuperscript{,}\Irefn{org99}\And
C.E.~P\'erez Lara\Irefn{org80}\And
V.~Peskov\Irefn{org52}\And
Y.~Pestov\Irefn{org5}\And
V.~Petr\'{a}\v{c}ek\Irefn{org39}\And
V.~Petrov\Irefn{org111}\And
M.~Petrovici\Irefn{org77}\And
C.~Petta\Irefn{org29}\And
S.~Piano\Irefn{org109}\And
M.~Pikna\Irefn{org38}\And
P.~Pillot\Irefn{org112}\And
O.~Pinazza\Irefn{org104}\textsuperscript{,}\Irefn{org36}\And
L.~Pinsky\Irefn{org120}\And
D.B.~Piyarathna\Irefn{org120}\And
M.~P\l osko\'{n}\Irefn{org73}\And
M.~Planinic\Irefn{org127}\And
J.~Pluta\Irefn{org132}\And
S.~Pochybova\Irefn{org134}\And
P.L.M.~Podesta-Lerma\Irefn{org117}\And
M.G.~Poghosyan\Irefn{org85}\And
B.~Polichtchouk\Irefn{org111}\And
N.~Poljak\Irefn{org127}\And
W.~Poonsawat\Irefn{org113}\And
A.~Pop\Irefn{org77}\And
S.~Porteboeuf-Houssais\Irefn{org69}\And
J.~Porter\Irefn{org73}\And
J.~Pospisil\Irefn{org82}\And
S.K.~Prasad\Irefn{org4}\And
R.~Preghenella\Irefn{org36}\textsuperscript{,}\Irefn{org104}\And
F.~Prino\Irefn{org110}\And
C.A.~Pruneau\Irefn{org133}\And
I.~Pshenichnov\Irefn{org55}\And
M.~Puccio\Irefn{org110}\And
G.~Puddu\Irefn{org25}\And
P.~Pujahari\Irefn{org133}\And
V.~Punin\Irefn{org98}\And
J.~Putschke\Irefn{org133}\And
H.~Qvigstad\Irefn{org22}\And
A.~Rachevski\Irefn{org109}\And
S.~Raha\Irefn{org4}\And
S.~Rajput\Irefn{org89}\And
J.~Rak\Irefn{org121}\And
A.~Rakotozafindrabe\Irefn{org15}\And
L.~Ramello\Irefn{org32}\And
R.~Raniwala\Irefn{org90}\And
S.~Raniwala\Irefn{org90}\And
S.S.~R\"{a}s\"{a}nen\Irefn{org45}\And
B.T.~Rascanu\Irefn{org52}\And
D.~Rathee\Irefn{org86}\And
K.F.~Read\Irefn{org123}\And
J.S.~Real\Irefn{org70}\And
K.~Redlich\Irefn{org76}\And
R.J.~Reed\Irefn{org133}\And
A.~Rehman\Irefn{org18}\And
P.~Reichelt\Irefn{org52}\And
M.~Reicher\Irefn{org56}\And
F.~Reidt\Irefn{org92}\textsuperscript{,}\Irefn{org36}\And
X.~Ren\Irefn{org7}\And
R.~Renfordt\Irefn{org52}\And
A.R.~Reolon\Irefn{org71}\And
A.~Reshetin\Irefn{org55}\And
F.~Rettig\Irefn{org42}\And
J.-P.~Revol\Irefn{org12}\And
K.~Reygers\Irefn{org92}\And
V.~Riabov\Irefn{org84}\And
R.A.~Ricci\Irefn{org72}\And
T.~Richert\Irefn{org34}\And
M.~Richter\Irefn{org22}\And
P.~Riedler\Irefn{org36}\And
W.~Riegler\Irefn{org36}\And
F.~Riggi\Irefn{org29}\And
C.~Ristea\Irefn{org61}\And
A.~Rivetti\Irefn{org110}\And
E.~Rocco\Irefn{org56}\And
M.~Rodr\'{i}guez Cahuantzi\Irefn{org11}\textsuperscript{,}\Irefn{org2}\And
A.~Rodriguez Manso\Irefn{org80}\And
K.~R{\o}ed\Irefn{org22}\And
E.~Rogochaya\Irefn{org65}\And
D.~Rohr\Irefn{org42}\And
D.~R\"ohrich\Irefn{org18}\And
R.~Romita\Irefn{org122}\And
F.~Ronchetti\Irefn{org71}\And
L.~Ronflette\Irefn{org112}\And
P.~Rosnet\Irefn{org69}\And
A.~Rossi\Irefn{org36}\And
F.~Roukoutakis\Irefn{org87}\And
A.~Roy\Irefn{org48}\And
C.~Roy\Irefn{org54}\And
P.~Roy\Irefn{org100}\And
A.J.~Rubio Montero\Irefn{org10}\And
R.~Rui\Irefn{org26}\And
R.~Russo\Irefn{org27}\And
E.~Ryabinkin\Irefn{org99}\And
Y.~Ryabov\Irefn{org84}\And
A.~Rybicki\Irefn{org115}\And
S.~Sadovsky\Irefn{org111}\And
K.~\v{S}afa\v{r}\'{\i}k\Irefn{org36}\And
B.~Sahlmuller\Irefn{org52}\And
P.~Sahoo\Irefn{org48}\And
R.~Sahoo\Irefn{org48}\And
S.~Sahoo\Irefn{org60}\And
P.K.~Sahu\Irefn{org60}\And
J.~Saini\Irefn{org130}\And
S.~Sakai\Irefn{org71}\And
M.A.~Saleh\Irefn{org133}\And
C.A.~Salgado\Irefn{org17}\And
J.~Salzwedel\Irefn{org20}\And
S.~Sambyal\Irefn{org89}\And
V.~Samsonov\Irefn{org84}\And
X.~Sanchez Castro\Irefn{org54}\And
L.~\v{S}\'{a}ndor\Irefn{org58}\And
A.~Sandoval\Irefn{org63}\And
M.~Sano\Irefn{org126}\And
G.~Santagati\Irefn{org29}\And
D.~Sarkar\Irefn{org130}\And
E.~Scapparone\Irefn{org104}\And
F.~Scarlassara\Irefn{org30}\And
R.P.~Scharenberg\Irefn{org94}\And
C.~Schiaua\Irefn{org77}\And
R.~Schicker\Irefn{org92}\And
C.~Schmidt\Irefn{org96}\And
H.R.~Schmidt\Irefn{org35}\And
S.~Schuchmann\Irefn{org52}\And
J.~Schukraft\Irefn{org36}\And
M.~Schulc\Irefn{org39}\And
T.~Schuster\Irefn{org135}\And
Y.~Schutz\Irefn{org112}\textsuperscript{,}\Irefn{org36}\And
K.~Schwarz\Irefn{org96}\And
K.~Schweda\Irefn{org96}\And
G.~Scioli\Irefn{org28}\And
E.~Scomparin\Irefn{org110}\And
R.~Scott\Irefn{org123}\And
K.S.~Seeder\Irefn{org118}\And
J.E.~Seger\Irefn{org85}\And
Y.~Sekiguchi\Irefn{org125}\And
I.~Selyuzhenkov\Irefn{org96}\And
K.~Senosi\Irefn{org64}\And
J.~Seo\Irefn{org66}\textsuperscript{,}\Irefn{org95}\And
E.~Serradilla\Irefn{org10}\textsuperscript{,}\Irefn{org63}\And
A.~Sevcenco\Irefn{org61}\And
A.~Shabanov\Irefn{org55}\And
A.~Shabetai\Irefn{org112}\And
O.~Shadura\Irefn{org3}\And
R.~Shahoyan\Irefn{org36}\And
A.~Shangaraev\Irefn{org111}\And
A.~Sharma\Irefn{org89}\And
N.~Sharma\Irefn{org60}\textsuperscript{,}\Irefn{org123}\And
K.~Shigaki\Irefn{org46}\And
K.~Shtejer\Irefn{org9}\textsuperscript{,}\Irefn{org27}\And
Y.~Sibiriak\Irefn{org99}\And
S.~Siddhanta\Irefn{org105}\And
K.M.~Sielewicz\Irefn{org36}\And
T.~Siemiarczuk\Irefn{org76}\And
D.~Silvermyr\Irefn{org83}\textsuperscript{,}\Irefn{org34}\And
C.~Silvestre\Irefn{org70}\And
G.~Simatovic\Irefn{org127}\And
G.~Simonetti\Irefn{org36}\And
R.~Singaraju\Irefn{org130}\And
R.~Singh\Irefn{org78}\And
S.~Singha\Irefn{org78}\textsuperscript{,}\Irefn{org130}\And
V.~Singhal\Irefn{org130}\And
B.C.~Sinha\Irefn{org130}\And
T.~Sinha\Irefn{org100}\And
B.~Sitar\Irefn{org38}\And
M.~Sitta\Irefn{org32}\And
T.B.~Skaali\Irefn{org22}\And
M.~Slupecki\Irefn{org121}\And
N.~Smirnov\Irefn{org135}\And
R.J.M.~Snellings\Irefn{org56}\And
T.W.~Snellman\Irefn{org121}\And
C.~S{\o}gaard\Irefn{org34}\And
R.~Soltz\Irefn{org74}\And
J.~Song\Irefn{org95}\And
M.~Song\Irefn{org136}\And
Z.~Song\Irefn{org7}\And
F.~Soramel\Irefn{org30}\And
S.~Sorensen\Irefn{org123}\And
M.~Spacek\Irefn{org39}\And
E.~Spiriti\Irefn{org71}\And
I.~Sputowska\Irefn{org115}\And
M.~Spyropoulou-Stassinaki\Irefn{org87}\And
B.K.~Srivastava\Irefn{org94}\And
J.~Stachel\Irefn{org92}\And
I.~Stan\Irefn{org61}\And
G.~Stefanek\Irefn{org76}\And
M.~Steinpreis\Irefn{org20}\And
E.~Stenlund\Irefn{org34}\And
G.~Steyn\Irefn{org64}\And
J.H.~Stiller\Irefn{org92}\And
D.~Stocco\Irefn{org112}\And
P.~Strmen\Irefn{org38}\And
A.A.P.~Suaide\Irefn{org118}\And
T.~Sugitate\Irefn{org46}\And
C.~Suire\Irefn{org50}\And
M.~Suleymanov\Irefn{org16}\And
R.~Sultanov\Irefn{org57}\And
M.~\v{S}umbera\Irefn{org82}\And
T.J.M.~Symons\Irefn{org73}\And
A.~Szabo\Irefn{org38}\And
A.~Szanto de Toledo\Irefn{org118}\And
I.~Szarka\Irefn{org38}\And
A.~Szczepankiewicz\Irefn{org36}\And
M.~Szymanski\Irefn{org132}\And
J.~Takahashi\Irefn{org119}\And
N.~Tanaka\Irefn{org126}\And
M.A.~Tangaro\Irefn{org33}\And
J.D.~Tapia Takaki\Aref{idp5842272}\textsuperscript{,}\Irefn{org50}\And
A.~Tarantola Peloni\Irefn{org52}\And
M.~Tariq\Irefn{org19}\And
M.G.~Tarzila\Irefn{org77}\And
A.~Tauro\Irefn{org36}\And
G.~Tejeda Mu\~{n}oz\Irefn{org2}\And
A.~Telesca\Irefn{org36}\And
K.~Terasaki\Irefn{org125}\And
C.~Terrevoli\Irefn{org30}\textsuperscript{,}\Irefn{org25}\And
B.~Teyssier\Irefn{org128}\And
J.~Th\"{a}der\Irefn{org96}\textsuperscript{,}\Irefn{org73}\And
D.~Thomas\Irefn{org116}\And
R.~Tieulent\Irefn{org128}\And
A.R.~Timmins\Irefn{org120}\And
A.~Toia\Irefn{org52}\And
S.~Trogolo\Irefn{org110}\And
V.~Trubnikov\Irefn{org3}\And
W.H.~Trzaska\Irefn{org121}\And
T.~Tsuji\Irefn{org125}\And
A.~Tumkin\Irefn{org98}\And
R.~Turrisi\Irefn{org107}\And
T.S.~Tveter\Irefn{org22}\And
K.~Ullaland\Irefn{org18}\And
A.~Uras\Irefn{org128}\And
G.L.~Usai\Irefn{org25}\And
A.~Utrobicic\Irefn{org127}\And
M.~Vajzer\Irefn{org82}\And
M.~Vala\Irefn{org58}\And
L.~Valencia Palomo\Irefn{org69}\And
S.~Vallero\Irefn{org27}\And
J.~Van Der Maarel\Irefn{org56}\And
J.W.~Van Hoorne\Irefn{org36}\And
M.~van Leeuwen\Irefn{org56}\And
T.~Vanat\Irefn{org82}\And
P.~Vande Vyvre\Irefn{org36}\And
D.~Varga\Irefn{org134}\And
A.~Vargas\Irefn{org2}\And
M.~Vargyas\Irefn{org121}\And
R.~Varma\Irefn{org47}\And
M.~Vasileiou\Irefn{org87}\And
A.~Vasiliev\Irefn{org99}\And
A.~Vauthier\Irefn{org70}\And
V.~Vechernin\Irefn{org129}\And
A.M.~Veen\Irefn{org56}\And
M.~Veldhoen\Irefn{org56}\And
A.~Velure\Irefn{org18}\And
M.~Venaruzzo\Irefn{org72}\And
E.~Vercellin\Irefn{org27}\And
S.~Vergara Lim\'on\Irefn{org2}\And
R.~Vernet\Irefn{org8}\And
M.~Verweij\Irefn{org133}\And
L.~Vickovic\Irefn{org114}\And
G.~Viesti\Irefn{org30}\Aref{0}\And
J.~Viinikainen\Irefn{org121}\And
Z.~Vilakazi\Irefn{org124}\And
O.~Villalobos Baillie\Irefn{org101}\And
A.~Vinogradov\Irefn{org99}\And
L.~Vinogradov\Irefn{org129}\And
Y.~Vinogradov\Irefn{org98}\And
T.~Virgili\Irefn{org31}\And
V.~Vislavicius\Irefn{org34}\And
Y.P.~Viyogi\Irefn{org130}\And
A.~Vodopyanov\Irefn{org65}\And
M.A.~V\"{o}lkl\Irefn{org92}\And
K.~Voloshin\Irefn{org57}\And
S.A.~Voloshin\Irefn{org133}\And
G.~Volpe\Irefn{org36}\textsuperscript{,}\Irefn{org134}\And
B.~von Haller\Irefn{org36}\And
I.~Vorobyev\Irefn{org91}\And
D.~Vranic\Irefn{org96}\textsuperscript{,}\Irefn{org36}\And
J.~Vrl\'{a}kov\'{a}\Irefn{org40}\And
B.~Vulpescu\Irefn{org69}\And
A.~Vyushin\Irefn{org98}\And
B.~Wagner\Irefn{org18}\And
J.~Wagner\Irefn{org96}\And
H.~Wang\Irefn{org56}\And
M.~Wang\Irefn{org7}\textsuperscript{,}\Irefn{org112}\And
Y.~Wang\Irefn{org92}\And
D.~Watanabe\Irefn{org126}\And
M.~Weber\Irefn{org36}\And
S.G.~Weber\Irefn{org96}\And
J.P.~Wessels\Irefn{org53}\And
U.~Westerhoff\Irefn{org53}\And
J.~Wiechula\Irefn{org35}\And
J.~Wikne\Irefn{org22}\And
M.~Wilde\Irefn{org53}\And
G.~Wilk\Irefn{org76}\And
J.~Wilkinson\Irefn{org92}\And
M.C.S.~Williams\Irefn{org104}\And
B.~Windelband\Irefn{org92}\And
M.~Winn\Irefn{org92}\And
C.G.~Yaldo\Irefn{org133}\And
Y.~Yamaguchi\Irefn{org125}\And
H.~Yang\Irefn{org56}\And
P.~Yang\Irefn{org7}\And
S.~Yano\Irefn{org46}\And
Z.~Yin\Irefn{org7}\And
H.~Yokoyama\Irefn{org126}\And
I.-K.~Yoo\Irefn{org95}\And
V.~Yurchenko\Irefn{org3}\And
I.~Yushmanov\Irefn{org99}\And
A.~Zaborowska\Irefn{org132}\And
V.~Zaccolo\Irefn{org79}\And
A.~Zaman\Irefn{org16}\And
C.~Zampolli\Irefn{org104}\And
H.J.C.~Zanoli\Irefn{org118}\And
S.~Zaporozhets\Irefn{org65}\And
A.~Zarochentsev\Irefn{org129}\And
P.~Z\'{a}vada\Irefn{org59}\And
N.~Zaviyalov\Irefn{org98}\And
H.~Zbroszczyk\Irefn{org132}\And
I.S.~Zgura\Irefn{org61}\And
M.~Zhalov\Irefn{org84}\And
H.~Zhang\Irefn{org7}\And
X.~Zhang\Irefn{org73}\And
Y.~Zhang\Irefn{org7}\And
C.~Zhao\Irefn{org22}\And
N.~Zhigareva\Irefn{org57}\And
D.~Zhou\Irefn{org7}\And
Y.~Zhou\Irefn{org56}\And
Z.~Zhou\Irefn{org18}\And
H.~Zhu\Irefn{org7}\And
J.~Zhu\Irefn{org7}\textsuperscript{,}\Irefn{org112}\And
X.~Zhu\Irefn{org7}\And
A.~Zichichi\Irefn{org12}\textsuperscript{,}\Irefn{org28}\And
A.~Zimmermann\Irefn{org92}\And
M.B.~Zimmermann\Irefn{org53}\textsuperscript{,}\Irefn{org36}\And
G.~Zinovjev\Irefn{org3}\And
M.~Zyzak\Irefn{org42}
\renewcommand\labelenumi{\textsuperscript{\theenumi}~}

\section*{Affiliation notes}
\renewcommand\theenumi{\roman{enumi}}
\begin{Authlist}
\item \Adef{0}Deceased
\item \Adef{idp5842272}{Also at: University of Kansas, Lawrence, Kansas, United States}
\end{Authlist}

\section*{Collaboration Institutes}
\renewcommand\theenumi{\arabic{enumi}~}
\begin{Authlist}

\item \Idef{org1}A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute) Foundation, Yerevan, Armenia
\item \Idef{org2}Benem\'{e}rita Universidad Aut\'{o}noma de Puebla, Puebla, Mexico
\item \Idef{org3}Bogolyubov Institute for Theoretical Physics, Kiev, Ukraine
\item \Idef{org4}Bose Institute, Department of Physics and Centre for Astroparticle Physics and Space Science (CAPSS), Kolkata, India
\item \Idef{org5}Budker Institute for Nuclear Physics, Novosibirsk, Russia
\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, United States
\item \Idef{org7}Central China Normal University, Wuhan, China
\item \Idef{org8}Centre de Calcul de l'IN2P3, Villeurbanne, France
\item \Idef{org9}Centro de Aplicaciones Tecnol\'{o}gicas y Desarrollo Nuclear (CEADEN), Havana, Cuba
\item \Idef{org10}Centro de Investigaciones Energ\'{e}ticas Medioambientales y Tecnol\'{o}gicas (CIEMAT), Madrid, Spain
\item \Idef{org11}Centro de Investigaci\'{o}n y de Estudios Avanzados (CINVESTAV), Mexico City and M\'{e}rida, Mexico
\item \Idef{org12}Centro Fermi - Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Rome, Italy
\item \Idef{org13}Chicago State University, Chicago, Illinois, USA
\item \Idef{org14}China Institute of Atomic Energy, Beijing, China
\item \Idef{org15}Commissariat \`{a} l'Energie Atomique, IRFU, Saclay, France
\item \Idef{org16}COMSATS Institute of Information Technology (CIIT), Islamabad, Pakistan
\item \Idef{org17}Departamento de F\'{\i}sica de Part\'{\i}culas and IGFAE, Universidad de Santiago de Compostela, Santiago de Compostela, Spain
\item \Idef{org18}Department of Physics and Technology, University of Bergen, Bergen, Norway
\item \Idef{org19}Department of Physics, Aligarh Muslim University, Aligarh, India
\item \Idef{org20}Department of Physics, Ohio State University, Columbus, Ohio, United States
\item \Idef{org21}Department of Physics, Sejong University, Seoul, South Korea
\item \Idef{org22}Department of Physics, University of Oslo, Oslo, Norway
\item \Idef{org23}Dipartimento di Elettrotecnica ed Elettronica del Politecnico, Bari, Italy
\item \Idef{org24}Dipartimento di Fisica dell'Universit\`{a} 'La Sapienza' and Sezione INFN Rome, Italy
\item \Idef{org25}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Cagliari, Italy
\item \Idef{org26}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Trieste, Italy
\item \Idef{org27}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Turin, Italy
\item \Idef{org28}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Bologna, Italy
\item \Idef{org29}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Catania, Italy
\item \Idef{org30}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Padova, Italy
\item \Idef{org31}Dipartimento di Fisica `E.R.~Caianiello' dell'Universit\`{a} and Gruppo Collegato INFN, Salerno, Italy
\item \Idef{org32}Dipartimento di Scienze e Innovazione Tecnologica dell'Universit\`{a} del  Piemonte Orientale and Gruppo Collegato INFN, Alessandria, Italy
\item \Idef{org33}Dipartimento Interateneo di Fisica `M.~Merlin' and Sezione INFN, Bari, Italy
\item \Idef{org34}Division of Experimental High Energy Physics, University of Lund, Lund, Sweden
\item \Idef{org35}Eberhard Karls Universit\"{a}t T\"{u}bingen, T\"{u}bingen, Germany
\item \Idef{org36}European Organization for Nuclear Research (CERN), Geneva, Switzerland
\item \Idef{org37}Faculty of Engineering, Bergen University College, Bergen, Norway
\item \Idef{org38}Faculty of Mathematics, Physics and Informatics, Comenius University, Bratislava, Slovakia
\item \Idef{org39}Faculty of Nuclear Sciences and Physical Engineering, Czech Technical University in Prague, Prague, Czech Republic
\item \Idef{org40}Faculty of Science, P.J.~\v{S}af\'{a}rik University, Ko\v{s}ice, Slovakia
\item \Idef{org41}Faculty of Technology, Buskerud and Vestfold University College, Vestfold, Norway
\item \Idef{org42}Frankfurt Institute for Advanced Studies, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org43}Gangneung-Wonju National University, Gangneung, South Korea
\item \Idef{org44}Gauhati University, Department of Physics, Guwahati, India
\item \Idef{org45}Helsinki Institute of Physics (HIP), Helsinki, Finland
\item \Idef{org46}Hiroshima University, Hiroshima, Japan
\item \Idef{org47}Indian Institute of Technology Bombay (IIT), Mumbai, India
\item \Idef{org48}Indian Institute of Technology Indore, Indore (IITI), India
\item \Idef{org49}Inha University, Incheon, South Korea
\item \Idef{org50}Institut de Physique Nucl\'eaire d'Orsay (IPNO), Universit\'e Paris-Sud, CNRS-IN2P3, Orsay, France
\item \Idef{org51}Institut f\"{u}r Informatik, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org52}Institut f\"{u}r Kernphysik, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org53}Institut f\"{u}r Kernphysik, Westf\"{a}lische Wilhelms-Universit\"{a}t M\"{u}nster, M\"{u}nster, Germany
\item \Idef{org54}Institut Pluridisciplinaire Hubert Curien (IPHC), Universit\'{e} de Strasbourg, CNRS-IN2P3, Strasbourg, France
\item \Idef{org55}Institute for Nuclear Research, Academy of Sciences, Moscow, Russia
\item \Idef{org56}Institute for Subatomic Physics of Utrecht University, Utrecht, Netherlands
\item \Idef{org57}Institute for Theoretical and Experimental Physics, Moscow, Russia
\item \Idef{org58}Institute of Experimental Physics, Slovak Academy of Sciences, Ko\v{s}ice, Slovakia
\item \Idef{org59}Institute of Physics, Academy of Sciences of the Czech Republic, Prague, Czech Republic
\item \Idef{org60}Institute of Physics, Bhubaneswar, India
\item \Idef{org61}Institute of Space Science (ISS), Bucharest, Romania
\item \Idef{org62}Instituto de Ciencias Nucleares, Universidad Nacional Aut\'{o}noma de M\'{e}xico, Mexico City, Mexico
\item \Idef{org63}Instituto de F\'{\i}sica, Universidad Nacional Aut\'{o}noma de M\'{e}xico, Mexico City, Mexico
\item \Idef{org64}iThemba LABS, National Research Foundation, Somerset West, South Africa
\item \Idef{org65}Joint Institute for Nuclear Research (JINR), Dubna, Russia
\item \Idef{org66}Konkuk University, Seoul, South Korea
\item \Idef{org67}Korea Institute of Science and Technology Information, Daejeon, South Korea
\item \Idef{org68}KTO Karatay University, Konya, Turkey
\item \Idef{org69}Laboratoire de Physique Corpusculaire (LPC), Clermont Universit\'{e}, Universit\'{e} Blaise Pascal, CNRS--IN2P3, Clermont-Ferrand, France
\item \Idef{org70}Laboratoire de Physique Subatomique et de Cosmologie, Universit\'{e} Grenoble-Alpes, CNRS-IN2P3, Grenoble, France
\item \Idef{org71}Laboratori Nazionali di Frascati, INFN, Frascati, Italy
\item \Idef{org72}Laboratori Nazionali di Legnaro, INFN, Legnaro, Italy
\item \Idef{org73}Lawrence Berkeley National Laboratory, Berkeley, California, United States
\item \Idef{org74}Lawrence Livermore National Laboratory, Livermore, California, United States
\item \Idef{org75}Moscow Engineering Physics Institute, Moscow, Russia
\item \Idef{org76}National Centre for Nuclear Studies, Warsaw, Poland
\item \Idef{org77}National Institute for Physics and Nuclear Engineering, Bucharest, Romania
\item \Idef{org78}National Institute of Science Education and Research, Bhubaneswar, India
\item \Idef{org79}Niels Bohr Institute, University of Copenhagen, Copenhagen, Denmark
\item \Idef{org80}Nikhef, National Institute for Subatomic Physics, Amsterdam, Netherlands
\item \Idef{org81}Nuclear Physics Group, STFC Daresbury Laboratory, Daresbury, United Kingdom
\item \Idef{org82}Nuclear Physics Institute, Academy of Sciences of the Czech Republic, \v{R}e\v{z} u Prahy, Czech Republic
\item \Idef{org83}Oak Ridge National Laboratory, Oak Ridge, Tennessee, United States
\item \Idef{org84}Petersburg Nuclear Physics Institute, Gatchina, Russia
\item \Idef{org85}Physics Department, Creighton University, Omaha, Nebraska, United States
\item \Idef{org86}Physics Department, Panjab University, Chandigarh, India
\item \Idef{org87}Physics Department, University of Athens, Athens, Greece
\item \Idef{org88}Physics Department, University of Cape Town, Cape Town, South Africa
\item \Idef{org89}Physics Department, University of Jammu, Jammu, India
\item \Idef{org90}Physics Department, University of Rajasthan, Jaipur, India
\item \Idef{org91}Physik Department, Technische Universit\"{a}t M\"{u}nchen, Munich, Germany
\item \Idef{org92}Physikalisches Institut, Ruprecht-Karls-Universit\"{a}t Heidelberg, Heidelberg, Germany
\item \Idef{org93}Politecnico di Torino, Turin, Italy
\item \Idef{org94}Purdue University, West Lafayette, Indiana, United States
\item \Idef{org95}Pusan National University, Pusan, South Korea
\item \Idef{org96}Research Division and ExtreMe Matter Institute EMMI, GSI Helmholtzzentrum f\"ur Schwerionenforschung, Darmstadt, Germany
\item \Idef{org97}Rudjer Bo\v{s}kovi\'{c} Institute, Zagreb, Croatia
\item \Idef{org98}Russian Federal Nuclear Center (VNIIEF), Sarov, Russia
\item \Idef{org99}Russian Research Centre Kurchatov Institute, Moscow, Russia
\item \Idef{org100}Saha Institute of Nuclear Physics, Kolkata, India
\item \Idef{org101}School of Physics and Astronomy, University of Birmingham, Birmingham, United Kingdom
\item \Idef{org102}Secci\'{o}n F\'{\i}sica, Departamento de Ciencias, Pontificia Universidad Cat\'{o}lica del Per\'{u}, Lima, Peru
\item \Idef{org103}Sezione INFN, Bari, Italy
\item \Idef{org104}Sezione INFN, Bologna, Italy
\item \Idef{org105}Sezione INFN, Cagliari, Italy
\item \Idef{org106}Sezione INFN, Catania, Italy
\item \Idef{org107}Sezione INFN, Padova, Italy
\item \Idef{org108}Sezione INFN, Rome, Italy
\item \Idef{org109}Sezione INFN, Trieste, Italy
\item \Idef{org110}Sezione INFN, Turin, Italy
\item \Idef{org111}SSC IHEP of NRC Kurchatov institute, Protvino, Russia
\item \Idef{org112}SUBATECH, Ecole des Mines de Nantes, Universit\'{e} de Nantes, CNRS-IN2P3, Nantes, France
\item \Idef{org113}Suranaree University of Technology, Nakhon Ratchasima, Thailand
\item \Idef{org114}Technical University of Split FESB, Split, Croatia
\item \Idef{org115}The Henryk Niewodniczanski Institute of Nuclear Physics, Polish Academy of Sciences, Cracow, Poland
\item \Idef{org116}The University of Texas at Austin, Physics Department, Austin, Texas, USA
\item \Idef{org117}Universidad Aut\'{o}noma de Sinaloa, Culiac\'{a}n, Mexico
\item \Idef{org118}Universidade de S\~{a}o Paulo (USP), S\~{a}o Paulo, Brazil
\item \Idef{org119}Universidade Estadual de Campinas (UNICAMP), Campinas, Brazil
\item \Idef{org120}University of Houston, Houston, Texas, United States
\item \Idef{org121}University of Jyv\"{a}skyl\"{a}, Jyv\"{a}skyl\"{a}, Finland
\item \Idef{org122}University of Liverpool, Liverpool, United Kingdom
\item \Idef{org123}University of Tennessee, Knoxville, Tennessee, United States
\item \Idef{org124}University of the Witwatersrand, Johannesburg, South Africa
\item \Idef{org125}University of Tokyo, Tokyo, Japan
\item \Idef{org126}University of Tsukuba, Tsukuba, Japan
\item \Idef{org127}University of Zagreb, Zagreb, Croatia
\item \Idef{org128}Universit\'{e} de Lyon, Universit\'{e} Lyon 1, CNRS/IN2P3, IPN-Lyon, Villeurbanne, France
\item \Idef{org129}V.~Fock Institute for Physics, St. Petersburg State University, St. Petersburg, Russia
\item \Idef{org130}Variable Energy Cyclotron Centre, Kolkata, India
\item \Idef{org131}Vin\v{c}a Institute of Nuclear Sciences, Belgrade, Serbia
\item \Idef{org132}Warsaw University of Technology, Warsaw, Poland
\item \Idef{org133}Wayne State University, Detroit, Michigan, United States
\item \Idef{org134}Wigner Research Centre for Physics, Hungarian Academy of Sciences, Budapest, Hungary
\item \Idef{org135}Yale University, New Haven, Connecticut, United States
\item \Idef{org136}Yonsei University, Seoul, South Korea
\item \Idef{org137}Zentrum f\"{u}r Technologietransfer und Telekommunikation (ZTT), Fachhochschule Worms, Worms, Germany
\end{Authlist}
\endgroup

### 2016-10-27 acknowledgements_jan2015.tex
first commit v1

The ALICE Collaboration would like to thank all its engineers and technicians for their invaluable contributions to the construction of the experiment and the CERN accelerator teams for the outstanding performance of the LHC complex.
%
The ALICE Collaboration gratefully acknowledges the resources and support provided by all Grid centres and the Worldwide LHC Computing Grid (WLCG) collaboration.
%
The ALICE Collaboration acknowledges the following funding agencies for their support in building and
running the ALICE detector:
%
State Committee of Science,  World Federation of Scientists (WFS)
and Swiss Fonds Kidagan, Armenia,
%
Conselho Nacional de Desenvolvimento Cient\'{\i}fico e Tecnol\'{o}gico (CNPq), Financiadora de Estudos e Projetos (FINEP),
Funda\c{c}\~{a}o de Amparo \`{a} Pesquisa do Estado de S\~{a}o Paulo (FAPESP);
%
National Natural Science Foundation of China (NSFC), the Chinese Ministry of Education (CMOE)
and the Ministry of Science and Technology of China (MSTC);
%
Ministry of Education and Youth of the Czech Republic;
%
Danish Natural Science Research Council, the Carlsberg Foundation and the Danish National Research Foundation;
%
The European Research Council under the European Community's Seventh Framework Programme;
%
Helsinki Institute of Physics and the Academy of Finland;
%
French CNRS-IN2P3, the `Region Pays de Loire', `Region Alsace', `Region Auvergne' and CEA, France;
%
German Bundesministerium fur Bildung, Wissenschaft, Forschung und Technologie (BMBF) and the Helmholtz Association;
%
General Secretariat for Research and Technology, Ministry of
Development, Greece;
%
Hungarian Orszagos Tudomanyos Kutatasi Alappgrammok (OTKA) and National Office for Research and Technology (NKTH);
%
Department of Atomic Energy and Department of Science and Technology of the Government of India;
%
Istituto Nazionale di Fisica Nucleare (INFN) and Centro Fermi -
Museo Storico della Fisica e Centro Studi e Ricerche "Enrico
Fermi", Italy;
%
MEXT Grant-in-Aid for Specially Promoted Research, Ja\-pan;
%
Joint Institute for Nuclear Research, Dubna;
%
National Research Foundation of Korea (NRF);
%
Consejo Nacional de Cienca y Tecnologia (CONACYT), Direccion General de Asuntos del Personal Academico(DGAPA), M\'{e}xico, :Amerique Latine Formation academique – European Commission(ALFA-EC) and the EPLANET Program
(European Particle Physics Latin American Network)
%
Stichting voor Fundamenteel Onderzoek der Materie (FOM) and the Nederlandse Organisatie voor Wetenschappelijk Onderzoek (NWO), Netherlands;
%
Research Council of Norway (NFR);
%
National Science Centre, Poland;
%
Ministry of National Education/Institute for Atomic Physics and Consiliul Naţional al Cercetării Ştiinţifice - Executive Agency for Higher Education Research Development and Innovation Funding (CNCS-UEFISCDI) - Romania;
%
Ministry of Education and Science of Russian Federation, Russian
Academy of Sciences, Russian Federal Agency of Atomic Energy,
Russian Federal Agency for Science and Innovations and The Russian
Foundation for Basic Research;
%
Ministry of Education of Slovakia;
%
Department of Science and Technology, South Africa;
%
Centro de Investigaciones Energeticas, Medioambientales y Tecnologicas (CIEMAT), E-Infrastructure shared between Europe and Latin America (EELA), Ministerio de Econom\'{i}a y Competitividad (MINECO) of Spain, Xunta de Galicia (Conseller\'{\i}a de Educaci\'{o}n),
Centro de Aplicaciones Tecnológicas y Desarrollo Nuclear (CEA\-DEN), Cubaenerg\'{\i}a, Cuba, and IAEA (International Atomic Energy Agency);
%
Swedish Research Council (VR) and Knut $\&$ Alice Wallenberg
Foundation (KAW);
%
Ukraine Ministry of Education and Science;
%
United Kingdom Science and Technology Facilities Council (STFC);
%
The United States Department of Energy, the United States National
Science Foundation, the State of Texas, and the State of Ohio;
%
Ministry of Science, Education and Sports of Croatia and  Unity through Knowledge Fund, Croatia.
%
Council of Scientific and Industrial Research (CSIR), New Delhi, India

### 2016-10-27 paper.tex
first commit v1

\documentclass[ALICE,manyauthors]{cernphprep}
\usepackage[modulo]{lineno}
\usepackage{hyperref}
\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{amsmath,amssymb}% for advanced math typesetting 
\usepackage{url,color}
%\usepackage{pslatex}
\usepackage{mathrsfs} % produce the curly R with \mathscr not \mathcal

% \usepackage{palatino}%    Choose default roman font.  Others are times, pslatex, newcent, bookman, chancery                                                    
% can use mathpazo if no one uses \mathrm{\gamma}, etc., since it doesn't suppl\y Greek in rm. Google "mathpazo mathrm greek"                                   
% \usepackage{mathpazo}%  Matching math fonts (see http://www.math.uiuc.edu/~hartke/computer/latex/survey/survey.html)                                           
% \usepackage{helvet}%

\linenumbers

\input{helpers.tex}
\begin{document}
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%

\newcommand{\PbPb}{\textnormal{Pb--Pb}}
\newcommand{\AuAu}{\textnormal{Au--Au}}
\newcommand{\pp}{\ensuremath{\mbox{p}\mbox{p}}}
\newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
\newcommand{\pt}{\ensuremath{p_\tn{T}}}\newcommand{\pT}{\pt}
 % off by redefinding CKBNOTEje
\newcommand{\CKBNOTE}[1]{{\bf CKB:  #1}} 
\renewcommand{\CKBNOTE}[1]{}  % switch off

 % off by redefinding RHNOTE
\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
\renewcommand{\RHNOTE}[1]{}  % switch off

\begin{titlepage}
%
\PHyear{2016}
\PHnumber{040}                 % required, obtained from PH
\PHdate{24 Novermer}              % required, will be obtained from PH
%
%
%%% Put your own title + short title here:
\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
\ShortTitle{Correlations between event-by-event fluctuations of flow harmonics}   % appears on right page headers

%
%%% Do not change the nexts!
\Collaboration{ALICE Collaboration%
         \thanks{See Appendix~\ref{app:collab} for the list of collaboration
                      members}}
\ShortAuthor{ALICE Collaboration}      % appears on left page headers, do not change
%
\begin{abstract}

The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
in $\PbPb$ collisions at $\snn=2.76$~TeV were measured with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the multi-particle cumulant method.
The method is robust against systematic biases originating from non-flow effects. 
The centrality dependence of correlation between the higher Fourier harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$ -$v_2$ correlations are presented. 
Comparisons are made to predictions from viscous hydrodynamics and  A Multi-Phase Transport model  ({AMPT}) models.
The comparisons to viscous hydrodynamic models demonstrate that
the different order Fourier harmonic correlations respond differently to the initial conditions or $\eta/s$ and the small $\eta/s$ regardless of initial conditions is flavored and the small $\eta/s$ with the AMPT initial condition is closest to the results. 
%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.
\end{abstract}
\end{titlepage}
\setcounter{page}{2}

% \input{main.tex}               %%%%%%%%%%% put the body of the article here

% !TEX root = paper.tex

\section{Introduction}

%\textbf{{[A general history on HI]}}

The main emphasis of the ultra-relativistic heavy ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting matter, the Quark-Gluon Plasma (QGP). 
This matter exhibits strong collective and anisotropic flow in the transverse plane driven by the pressure gradients, with more particles emitted in the direction of the largest gradients.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also in LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}. This has been predicted by calculations utilising viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of strongly interacting matter is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy ion collisions at RHIC and LHC energies.

%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey. One such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53} that $\eta/s>1/15$ would be an order of magnitude for the lowest possible shear viscosity to entropy ratio in nature. Later it was found that one can calculate an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ using the AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations supports as well the view that the QGP matter indeed is close to that limit~\cite{Gale:2012rq}. This in turn may have an important implications to other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the QCD critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

Anisotropic flow is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

\noindent where $E$, $N$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the energy, particle yield, total momentum, transverse momentum, azimuthal angle and pseudorapidity of particles, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be derived as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow is understood as hydrodynamic response to spatial deformation of the initial density profile.
This profile fluctuates event to event due to quantum fluctuations of the positions of the constituents inside the colliding nuclei, which implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuation has led to triangular flow and higher harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Aad:2014fla}.
 As the result from ATLAS experiments, it shows that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
And the $v_{n}$ distributions carry detailed information about the initial density profile~\cite{Renk:2014jja,Yan:2014nsa}.

However, difficulties on extracting the shear viscosity in heavy ion has been realized since it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
The viscous effects reduce the magnitude of the elliptic flow. Furthermore, the magnitude of $\eta/s$ used in these calculations should be considered as an average over the temperature history of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature. 
In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
knowledge of both the temperature dependence and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.

The higher harmonics ($n>3$) are understood as superpositions of linear and nonlinear responses, through which they are correlated with lower-order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora}. When the harmonic order is large, the nonlinear response contribution in viscous hydrodynamics is dominant~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitude of the viscous corrections as a function of $\pt{}$ for $v_4$ and $v_5$ are sensitive to ansatz used for the viscous distribution function, $\delta f$, a small correction for the equilibrium distribution at hadronic freeze-out when QGP phase has become cool and dilute~\cite{Luzum:2010ad}.
Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $\pt{}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

Recently we measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics. The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators~\cite{ALICE:2016kpq}. 
It was demonstrated that they are sensitive to the $\eta/s$ of the expending medium and simultaneous descriptions of different order harmonic correlations would constrain 
both the initial conditions and the medium properties.
In this article, we have extended the analysis to higher order Fourier harmonic (up to 5th order) correlations as well as $\pt{}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include a systematic comparison to hydrodynamic and AMPT models.
In Sec.~\ref{sec:method} we present the details of the analysis methods. The experimental setting and measurements is described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}.
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.

%\input{sec_method}
\input{sec_method_0a}
\input{sec_eventtrack}
\input{sec_syst}

\section{Theoretical models}
\label{sec:models}
We have used various models in this article. The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $\pt{}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency. Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.

We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
%\textbf{Need a short descriotion of event-by-event viscous hydrody-namic calculations from VISH2+1}.

The VISH2+1~\cite{Zhu:2016puf} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics. With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $\pt{}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model. 
Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte-Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position space. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final-state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the measurements. It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement. The detail configurations on AMPT settings used for this article and the comparisons of $\pt{}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering. Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting. Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.

%

\section{Results}
\label{sec:results}

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC$(m,n)$(left figure) and NSC$(m,n)$(right figure) with flow harmonic order up to 5th in $\PbPb$ $\snn=2.76$~TeV. Note that the lower order harmonic correlations (SC(4,2),SC(3,2)) are scaled down by factor of 10 and only statistical errors are shown in the figure.}
        \label{fig:Figure_1}
              \end{center}
\end{figure}

The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}. Positive values of SC(4,2) are observed for all measured centralities. This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$. It also indicates that finding $v_2$ larger than average($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average($\langle v_4 \rangle$) in that event. On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average($v_3 < \langle v_3 \rangle$).

% \begin{figure}[htbp]
%            \begin{center}
%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly.eps}}
%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_T<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left). The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
%              \label{fig:Figure_1}
%              \end{center}
% \end{figure}

%\begin{figure}[h]
%	\begin{center}
%       	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC32_HIJING_ptdep.eps}}
%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC42_HIJING_ptdep.eps}}
%        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations. Defaults($0.2 < p_T < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend. A small shifts along the x axis were applied for better visibility.}
%        \label{fig:results_HIJING}
%        \end{center}   
%\end{figure}

The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)). The correlation between $v_3$ and $v_4$ is negative as similarly as $v_3$ and $v_2$ while the others are all positive. 
The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonics (SC(3,2) and SC(4,2)). Especially SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).

However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)). NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for most of centrality ranges within the errors.
These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also the individual flow strength. 
SC(5,2) is stronger than SC(5,3), but as for NSC, the correlation between $v_5$ and $v_3$ is stronger than the correlation between $v_5$ and $v_2$.

To obtain the $p_T$ dependence of SC$(m,n)$ results, we apply minimum $p_T$ cuts, instead of $p_T$ bin-by-bin interval in order to avoid large statistical fluctuations in the results. The various minimum $p_T$ cuts from 0.2 to 1.5 are applied.
The results of $p_T$ dependence with SC(3,2) and SC(4,2) for minimum $p_T$ cuts, $0.2<p_T<0.7$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_T$ increases. This indicates that the relationship between event-by-event fluctuation of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_T$ particles. 
This $p_T$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $\pt{}$ increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
The strong $p_T$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $\pt{}$ cuts. 
This suggests that the $p_T$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the different values of $p_T$  dependent individual $v_n$ values. 
The minimum $p_T$ cuts are extended from 0.8  to 1.5 $GeV/c$ and the results are shown on the bottom in Fig~.\ref{fig:Figure_2}.
As for SC$(m,n)$, the similar trends are observed as similarly as $\pt{}<0.8$ , however NSC$(m,n)$ tends to decrease as the minimum $p_T$ or the centrality increase.
The $\pt{}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_T$ dependence within the current statistical and systematic errors except for 40-50\% centrality
and NSC(4,2) shows a moderate decreasing trend for increasing $\pt{}$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_T$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_T$ cuts(Left) and results of normalized SC(3,2) and SC(4,2)(Right). The upper panels show the results for minimum $p_T$ range, $0.2<p_T<0.7$ $GeV/c$ and the bottom panels are for minimum $p_T$ range, $0.8<p_T<1.5$ $GeV/c$.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure}

\newpage
\section{Model comparisons}
\label{sec:theory}
\subsection{Low order harmonic correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_3}. Roughly the hydrodynamic calculations capture qualitatively the centrality dependence, but not quantitively. Both SC(3,2) with data and hydrodynamics have negative values for all centralities, while SC(4,2) results have positive values over all measured centralities. However, there is no single centrality for which a given $\eta/s(T)$ parameterization describes both SC(3,2) and SC(4,2) simultaneously. On the other hand, the same hydrodynamic calculations capture the centrality dependence of the individual $v_n$ quantitively~\cite{Eskola:2015uda}.

NSC(3,2) and NSC(4,2) are also compared to the same model on the right in Fig.~\ref{fig:Figure_3}. 
While NSC(3,2) doesn't show sensitivity to  different $\eta/s(T)$ parameterizations,  NSC(4,2) exhibit much better sensitivity
than NSC(3,2) observable and the individual flow harmonics~\cite{Niemi:2015qia}.
These findings indicate that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the prediction from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation will help to understand the fluctuations in initial conditions better.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations, i.e.\ medium property but the model cannot describe the centrality dependence nor the absolute values. These observed distinct discrepancies between data and models might indicate that the current understanding of initial conditions used in the model need to be revisited
to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
              \end{center}
        \caption{Results from SC(m,n) in $\PbPb$ $\snn=2.76$~TeV are compared to hydrodynamic calculations. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_3}
\end{figure}

The results with the comparison to VISH2+1 calculation are shown in Fig.~\ref{fig:Figure_4}.  All the models with the large share viscosity regardless of the initial conditions ($\eta/s$=0.2 for MC-KLN and MC-Glauber initial conditions and $\eta/s = 0.16$ for AMPT initial condition) failed to capture the centrality dependence of SC(3,2) and SC(4,2). 
And among the models with small shear viscosities ($\eta/s$=0.08), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but they cannot describe the data quantitively for most of the centrality ranges.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to the data in 0-10\% central collisions. NSC(3,2) doesn't show sensitivity to initial conditions or $\eta/s$ parametrizations and cannot be described by these models quantitively.
However, for NSC(4,2), it is sensitive both to initial conditions and $\eta/s$ parametrizations.
Even though NSC(4,2) is favoured both by AMPT initial condition with $\eta/s$=0.08 and MC-Glauber initial condition with $\eta/s$=0.20,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Therefore the Glauber initial condition with $\eta/s$=0.20 model can be ruled out and we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favoured by the data.

\begin{figure}[!p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations with different settings. Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s$=0.08) are shown as solid lines, and large shear viscosities ($\eta/s$=0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
         \label{fig:Figure_4}
        \end{center}   
 \end{figure}

Finally, the extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_5}.
As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest. The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
Interestingly the string melting AMPT model can't capture the data well where the strength of the correlation is weaker than the default model.
The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates the data. By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the data. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering make NSC(4,2) slightly smaller.
It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT.

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_5}
        \end{center}   
 \end{figure}

 \newpage
\subsection{Higher order harmonic correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculation, shown in Fig.~\ref{fig:Figure_6}. 
All the models with the large share viscosity regardless of the initial conditions ($\eta/s$=0.2 for MC-KLN and MC-Glauber initial conditions, and $\eta/s = 0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
And among the models with small shear viscosity ($\eta/s$=0.08), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
A quite clear separation between different initial conditions is observed for these higher order harmonics correlations compared to the lower order harmonic correlations.
NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(4,3) in these models is opposite to the data in 0-10\% central collisions. NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
SC(4,3) data is clearly favoured by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s$=0.08) are shown as solid lines, and large shear viscosities ($\eta/s$=0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure}

The extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_7}.
The string melting AMPT model describes SC(5,2) and SC(5,3) well. The same setting describes only NSC(5,3) but it overestimates NSC(5,2). 
However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as similarly as NSC(3,2) and NSC(4,2).
% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
in the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
In summary, the default AMPT model describes the normalized SC (NSC$(m,n)$) from lower to higher order harmonic correlation while the string melting AMPT model overestimates NSC(5,2) and 
underestimates (or very weak correlations) NSC(4,3).

%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_7}
        \end{center}   
 \end{figure}

 \newpage
\subsection{Transverse momentum dependence of Low order harmonic correlations}
\label{sec:ptdepsc}
NSC(3,2) and NSC(4,2) as a function of different minimum $\pt{}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
As discussed in Sec.~\ref{sec:results} in higher minimum $p_T$ cuts, the $p_T$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations.
The other AMPT configurations except for the default AMPT model give very strong $\pt{}$ dependence above 1 $GeV/c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
In the case of NSC(3,2), the default AMPT model describes the magnitude and $\pt{}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $\pt{}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $\pt{}$ dependence are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $\pt{}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
This might imply that the hadronic interaction is the source of this observed $\pt{}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
This observed moderate $\pt{}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad} when QGP phase has become cool and dilute.
%The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

\begin{figure}[htbp]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2)(Top) and SC(4,2)(Bottom) as a function of minimum $p_T$ cuts. The AMPT results are drawn as color bands for comparison. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
             \label{fig:Figure_8}
\end{figure}

\newpage
\section{Summary}
\label{sec:summary}
In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics. The observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities and fluctuations of $v_2$ and $v_4$ ( $v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities. 
This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies.
Furthermore, the sign of $v_3$-$v_2$ correlation in the model in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with the large share viscosity regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations and based on the tested model parameters that the $\eta/s$ should be small and AMPT initial condition is flavored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
Finally we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $\pt{}$ dependence in mid central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties in ultra-relativistic heavy-ion collisions.

%%%%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
%\input{acknowledgements_jan2015.tex}    %%%%%%% get the lates version before submitting
\end{acknowledgement}
%
%
%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
%\bibliographystyle{apsrev4-1}   % Put here the style file name for the paper, i.e.apsrev4-1
%\bibliography{biblio}
%\input {bibliography.tex}  
%

% \bibliographystyle{mybibstyle}
%\bibliographystyle{utphys}
%\bibliography{paper}
\bibliographystyle{utphys}
\bibliography{paper}

\newpage
%
%\input{}               %%%%%%%%%%% put your appendices here
%
%%%%%%%%% appendix with author list
\appendix
\section{The ALICE Collaboration}
\label{app:collab}
%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
%\input{}              %%%%%%%%%%%% put the references here
%
\end{document}

### 2016-10-27 sec_eventtrack.tex
first commit v1

\subsection{Event and Track Selection}
\label{sec:experiment}
The data sample recorded by ALICE during the 2010 heavy-ion run at the
LHC is used for this analysis. Detailed descriptions of the ALICE
detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudo-rapidity range $|\eta|<0.8$. Two scintillator
arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering, and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias Pb-Pb events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point in the beam direction are used for this
analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<\pt<5$ GeV/$c$ were selected. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks. The
charged particle track reconstruction efficiency and contamination
were estimated from {\sc HIJING} Monte Carlo
simulations~\cite{Wang:1991hta} combined with a {\sc
GEANT3}~\cite{Brun:1994aa} detector model, and found to be independent of
the collision centrality. The reconstruction efficiency increases from
70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
constant at $80 \pm 5$\% for $\pt>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $\pt=0.2$~GeV/$c$ and falls
below 1\% for $\pt>1$~GeV/$c$.
With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
at lower $\pt{}$, while the high $\pt{}$ cut-off was introduced to reduce the contribution to the anisotropies from jets. 
Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm
, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced 
in the detector material, particles from weak decays, etc.). 
Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.

### 2016-10-27 sec_method.tex
first commit v1

% !TEX root = paper.tex
%\textbf{{[Analysis technique.]}}
\subsection{Experimental observables}
\label{sec:method}
%\subsubsection{cumulant analysis}
In this Letter we study the relationship between event-by-event fluctuations of magnitudes of two different flow harmonics of order $n$ and $m$ by using a recently proposed 4-particle observable~\cite{Bilandzic:2013kga}
%
\begin{eqnarray}
\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$. We refer to these new observables as {\it Symmetric 2-harmonic 4-particle Cumulant}, and use notation SC$(m,n)$, or just SC. The double angular brackets indicate that the averaging procedure has been performed in two steps --- first over all distinct particle quadruplets in an event, and then in the second step the single-event averages were weighted with `number of combinations'. The latter for single-event average 4-particle correlations is mathematically equivalent to a unit weight for each individual quadruplet when the multiplicity differs event-by-event~\cite{Bilandzic:2012wva}. In both 2-particle correlators above all distinct particle pairs are considered in each case. The four-particle cumulant in Eq.~(\ref{eq:4p_cumulant}) is less sensitive to non-flow correlations than any 2- or 4-particle correlator on the right-hand side taken individually~\cite{Borghini:2001vi}. It is zero in the absence of flow fluctuations, or if the magnitudes of harmonics $v_m$ and $v_n$ are uncorrelated~\cite{Bilandzic:2013kga}. It is also unaffected by relationship between symmetry plane angles $\psi_m$ and $\psi_n$. The four-particle cumulant in Eq.~(\ref{eq:4p_cumulant}) is proportional to the linear correlation coefficient $c(a,b)$ introduced in~\cite{Niemi:2012aj} and discussed above, with $a=v_m^2$ and $b=v_n^2$. Experimentally it is more reliable to measure the higher order moments of flow harmonics $v_n^k\ (k \ge 2)$ with 2- and multiparticle correlation techniques~\cite{Borghini:2001vi,Bilandzic:2010jr,PhysRevC.44.1091}, than to measure the first moments $v_n$ with the event plane method, due to systematic uncertainties involved in the event-by-event estimation of symmetry planes~\cite{Poskanzer:1998yz,Luzum:2012da}. Therefore, we have used the new multiparticle observable in Eq.~(\ref{eq:4p_cumulant}) as meant to be the least biased measure of the correlation between event-by-event fluctuations of magnitudes of two different harmonics $v_m$ and $v_n$~\cite{Bilandzic:2013kga}.

The 2- and 4-particle correlations in Eq.~(\ref{eq:4p_cumulant}) were evaluated in terms of $Q$-vectors~\cite{Bilandzic:2010jr}. The $Q$-vector (or flow vector) in harmonic $n$ for a set of $M$ particles, where throughout this paper $M$ is multiplicity of an event, is defined as $Q_n\equiv\sum_{k=1}^Me^{in\varphi_k}$~\cite{Voloshin:1994mz,Barrette:1994xr}. We have used for a single-event average 2-particle correlation, $\left<\cos(n(\varphi_1\!-\!\varphi_2))\right>$, the following definition and analytic result in terms of $Q$-vectors:
%
\begin{equation}
\frac{1}{\binom{M}{2}2!}\,\sum_{\begin{subarray}{c}i,j=1\\ (i\neq j)\end{subarray}}^{M} e^{in(\varphi_i-\varphi_j)}
=\frac{1}{\binom{M}{2}2!}
\big[\left|Q_{n}\right|^2\!-\!M\big]\,.
\label{eq:two_n_n}
\end{equation}
%
For 4-particle correlation, $\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>$, we used:
%
\begin{eqnarray}
&&\!\!\!\!\!\! \frac{1}{\binom{M}{4}4!}\,\sum_{\begin{subarray}{c}i,j,k,l=1\\ (i\neq j\neq k\neq l)\end{subarray}}^{M} e^{i(m\varphi_i+n\varphi_j-m\varphi_k-n\varphi_l)} = \nonumber\\
&&\!\!\!\!\!\!\frac{1}{\binom{M}{4}4!}\big[\left|Q_{m}\right|^2\left|Q_{n}\right|^2\!-\!
2\mathfrak{Re}\left[Q_{m+n}Q_{m}^*Q_{n}^*\right]\!-\!
2\mathfrak{Re}\left[Q_{m}Q_{m-n}^*Q_{n}^*\right]\nonumber\\
&&{}\!\!\!\!\!\!\!+\!\left|Q_{m+n}\right|^2\!+\!\left|Q_{m-n}\right|^2\!-\!(M\!-\!4)(\left|Q_{m}\right|^2\!+\!\left|Q_{n}\right|^2)
+\!M(M\!-\!6)\big]\,.
\label{eq:four_m_n_m_m}
\end{eqnarray}
%
\noindent In order to obtain the all-event average correlations, denoted by $\left<\left<\cdots\right>\right>$ in Eq.~(\ref{eq:4p_cumulant}), we have weighted single-event expressions in Eqs.~(\ref{eq:two_n_n}) and (\ref{eq:four_m_n_m_m}) with weights $M(M\!-\!1)$ and $M(M\!-\!1)(M\!-\!2)(M\!-\!3)$, respectively~\cite{Bilandzic:2012wva}.

$SC(m,n)$ can be normalized with the products  $\left<v_{m}^2\right>\left<v_{n}^2\right>$:
\begin{equation}
NSC(m,n) = SC(m,n) / \left<v_{m}^2\right>\left<v_{n}^2\right>.
\label{eq:nsc}
\end{equation}
This normalized $SC(m,n)$ ($NSC(m,n)$) reflects  the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while $SC(m,n)$ contains both the degree of the correlation and individual $v_{n}$.
These products are obtained with two-particle correlations and using a psedorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle non flow correlations.

### 2016-10-27 sec_method_0a.tex
first commit v1

% Experimental observables
%% Flow correlations in general
   % Niemi, ATLAS paper
%% Symmetric Cumulants (SC)
%% Normalized Symmetric Cumulants (NSC)
%% Summary of results of 1st ALICE paper on SC
%% Review of papers which cited ALICE 
% !TEX root = paper.tex

\section{Data Analysis}
\label{sec:method}
\subsection{Experimental observables}
%\subsubsection{cumulant analysis}

While from existing measurements an estimate can be placed on the average value of QGP's $\eta/s$, both at RHIC and LHC energies, what remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$). This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging consensus of late is that it is unlikely that the study of individual flow harmonics $v_n$ will reveal the details of $\eta/s(T)$ dependence. In fact, in was demonstrated already in the initial study~\cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced by the theorists, which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their mesurement in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently. Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.

 For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}. Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most realiable way (i.e. nearly insensitive to nonflow) the correlation of amplitudes of two different flow harmonics. The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.

SC($m$,$n$) can be normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$ to obtain \textit{normalized} symmetric cumulants~\cite{ALICE:2016kpq,Giacalone:2016afq}, which we denote by NSC($m$,$n$), i.e.
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a psedorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations. On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demontrated in Ref.~\cite{ALICE:2016kpq}.

The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}. However, the details of the centrality dependence differ in the fluctutation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution. These results were also used to discriminate between different parameterizations of initial conditions and it was demonstrated that in the fluctuation-dominated regime (in central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.

\vspace{0.44cm}

\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}. This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms. In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants. As a concrete example it was discussed that the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.

Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge. The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events. This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow. To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases. However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected. Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow. Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

### 2016-10-27 sec_syst.tex
first commit v1

% !TEX root = paper.tex

\subsection{Systematic uncertainties}
\label{sec:uncertainties}
%\textbf{\tmp{[Track selection criteria.]}}

%p10================================================================================

%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}

The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
Each results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
The contributions from different sources were then added in quadrature to obtain the final value of the systematic uncertainty.

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination. The systematic uncertainty from centrality determination was evaluated by using Time Projection Chamber (TPC) and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors. The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), 8\% for  SC(5,3).

Because of limited acceptance of ALICE detector, primary vertex position along the longitudinal direction is important to ensure for the uniform pseudo-rapidity distribution over all events. As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis (z-vertex) is required to be located within 10 cm of interaction point (IP).  We measured the results with 8cm cut and the differences in the final results were less than 3\%.

The analyzed events were recorded with two settings of the magnetic filed polarities and they have almost the same number of events. Both magnetic polarization events were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings. 
Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions. The effects from $p_T$ dependence reconstruction efficiency were taken into systematic uncertainty. Magnetic polarizations, reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.

The systematic uncertainty due to the track reconstruction was estimated using two additional tracking, one relying on the so-called standalone TPC tracking with the 
same parameters described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the ITS detectors with tighter selection criteria.
Since some parts of the SPD were switched off during some run periods, inefficient regions for common track reconstruction are apparent. To recover non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combine with TPC were used.  Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow correlation effects on SC$(m,n)$. The difference between all charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were  7\% for SC(4,3) and 20\% for SC(5,3).

One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency. In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles. Then we force to have detector inefficiencies by imposing non-uniform azimuthal distribution from the data. For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainty from the non-uniform distribution of azimuthal angles were 9\%, 17\% and 11\%, respectively.
Generally, systematics uncertainties are large for the SC(5,3) and SC(5,2) than the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are sensitive to azimuthal modulation and $v_n$ decreases with $n$. Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.

### 2016-11-02 paper.tex
a mistake in the model comparison SC(3,2)
adopting comments from sami

@@
 The method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher Fourier harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$ -$v_2$ correlations are presented.
-Comparisons are made to predictions from viscous hydrodynamics and  A Multi-Phase Transport model  ({AMPT}) models.
+The centrality dependence of correlation between the higher Fourier harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
+The results are compared to predictions from viscous hydrodynamics and  A Multi-Phase Transport model  ({AMPT}) models.
 The comparisons to viscous hydrodynamic models demonstrate that
@@
 One such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53} that $\eta/s>1/15$ would be an order of magnitude for the lowest possible shear viscosity to entropy ratio in nature.
+It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be an order of magnitude for the lowest possible shear viscosity to entropy ratio in nature.
 Later it was found that one can calculate an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
@@
 The anisotropic flow is understood as hydrodynamic response to spatial deformation of the initial density profile.
-This profile fluctuates event to event due to quantum fluctuations of the positions of the constituents inside the colliding nuclei, which implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
+This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
 The recognition of the importance of flow fluctuation has led to triangular flow and higher harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Aad:2014fla}.
- As the result from ATLAS experiments, it shows that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
+%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
+The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}.
 And the $v_{n}$ distributions carry detailed information about the initial density profile~\cite{Renk:2014jja,Yan:2014nsa}.
@@
 When the harmonic order is large, the nonlinear response contribution in viscous hydrodynamics is dominant~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $\pt{}$ for $v_4$ and $v_5$ are sensitive to ansatz used for the viscous distribution function, $\delta f$, a small correction for the equilibrium distribution at hadronic freeze-out when QGP phase has become cool and dilute~\cite{Luzum:2010ad}.
-Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $\pt{}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
+The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, $\delta f$, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
+Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
 
@@
 both the initial conditions and the medium properties.
-In this article, we have extended the analysis to higher order Fourier harmonic (up to 5th order) correlations as well as $\pt{}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).
+In this article, we have extended the analysis to higher order Fourier harmonic (up to 5th order) correlations as well as $p_{\rm T}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).
 We also include a systematic comparison to hydrodynamic and AMPT models.
 In Sec.~\ref{sec:method} we present the details of the analysis methods.
-The experimental setting and measurements is described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
 The results of the measurements are presented in Sec.~\ref{sec:results}.
@@
 We have used various models in this article.
-The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $\pt{}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency.
+The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency.
 Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry).
@@
 The VISH2+1~\cite{Zhu:2016puf} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
-With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $\pt{}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model. 
@@
 It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement.
-The detail configurations on AMPT settings used for this article and the comparisons of $\pt{}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+The detail configurations on AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
 
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC$(m,n)$(left figure) and NSC$(m,n)$(right figure) with flow harmonic order up to 5th in $\PbPb$ $\snn=2.76$~TeV.
-Note that the lower order harmonic correlations (SC(4,2),SC(3,2)) are scaled down by factor of 10 and only statistical errors are shown in the figure.}
+        \caption{The result of SC$(m,n)$ (left figure) and NSC$(m,n)$ (right figure) with flow harmonic order up to 5th in $\PbPb$ $\snn=2.76$~TeV.
+Note that the lower order harmonic correlations (SC(4,2),SC(3,2)) are scaled down by factor of 10 and only statistical errors are shown in the left hand side figure.}
         \label{fig:Figure_1}
@@
 This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$.
-It also indicates that finding $v_2$ larger than average($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average($\langle v_4 \rangle$) in that event.
-On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average($v_3 < \langle v_3 \rangle$).
+It also indicates that finding $v_2$ larger than average ($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average ($\langle v_4 \rangle$) in that event.
+On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average ($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average ($v_3 < \langle v_3 \rangle$).
 
@@
 %                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
-%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_T<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left).
+%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_{\rm T}<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left).
 The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
@@
 %        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations.
-Defaults($0.2 < p_T < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend.
+Defaults($0.2 < p_{\rm T} < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend.
 A small shifts along the x axis were applied for better visibility.}
@@
 
-To obtain the $p_T$ dependence of SC$(m,n)$ results, we apply minimum $p_T$ cuts, instead of $p_T$ bin-by-bin interval in order to avoid large statistical fluctuations in the results.
-The various minimum $p_T$ cuts from 0.2 to 1.5 are applied.
-The results of $p_T$ dependence with SC(3,2) and SC(4,2) for minimum $p_T$ cuts, $0.2<p_T<0.7$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
-The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_T$ increases.
-This indicates that the relationship between event-by-event fluctuation of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_T$ particles.
-This $p_T$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $\pt{}$ increase. 
+To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we apply minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval in order to avoid large statistical fluctuations in the results.
+The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5 are applied.
+The results of $p_{\rm T}$ dependence with SC(3,2) and SC(4,2) for minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
+The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases.
+This indicates that the relationship between event-by-event fluctuation of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles.
+This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
-The strong $p_T$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $\pt{}$ cuts. 
-This suggests that the $p_T$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the different values of $p_T$  dependent individual $v_n$ values.
-The minimum $p_T$ cuts are extended from 0.8  to 1.5 $GeV/c$ and the results are shown on the bottom in Fig~.\ref{fig:Figure_2}.
-As for SC$(m,n)$, the similar trends are observed as similarly as $\pt{}<0.8$ , however NSC$(m,n)$ tends to decrease as the minimum $p_T$ or the centrality increase.
-The $\pt{}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_T$ dependence within the current statistical and systematic errors except for 40-50\% centrality
-and NSC(4,2) shows a moderate decreasing trend for increasing $\pt{}$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
+The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
+This suggests that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the different values of $p_{\rm T}$  dependent individual $v_n$ values.
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5 GeV$/c$ and the results are shown on the bottom in Fig.~\ref{fig:Figure_2}.
+As for SC$(m,n)$, the similar trends are observed as similarly as $p_{\rm T}<0.8$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
+The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors except for 40-50\% centrality
+and NSC(4,2) shows a moderate decreasing trend for increasing $p_{\rm T}$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
-%However within the current statistical and systematic errors, it is consistent with no $p_T$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
+%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
 
@@
         	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_T$ cuts(Left) and results of normalized SC(3,2) and SC(4,2)(Right).
-The upper panels show the results for minimum $p_T$ range, $0.2<p_T<0.7$ $GeV/c$ and the bottom panels are for minimum $p_T$ range, $0.8<p_T<1.5$ $GeV/c$.}
+        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
+The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$ GeV$/c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$ GeV$/c$.
+Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
         \label{fig:Figure_2}
@@
 First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_3}.
-Roughly the hydrodynamic calculations capture qualitatively the centrality dependence, but not quantitively.
+The hydrodynamic calculations roughly capture qualitatively the centrality dependence, but not quantitively.
 Both SC(3,2) with data and hydrodynamics have negative values for all centralities, while SC(4,2) results have positive values over all measured centralities.
@@
 NSC(3,2) and NSC(4,2) are also compared to the same model on the right in Fig.~\ref{fig:Figure_3}. 
-While NSC(3,2) doesn't show sensitivity to  different $\eta/s(T)$ parameterizations,  NSC(4,2) exhibit much better sensitivity
+While NSC(3,2) does not show sensitivity to  different $\eta/s(T)$ parameterizations,  NSC(4,2) exhibit much better sensitivity
 than NSC(3,2) observable and the individual flow harmonics~\cite{Niemi:2015qia}.
@@
 The results with the comparison to VISH2+1 calculation are shown in Fig.~\ref{fig:Figure_4}.
-All the models with the large share viscosity regardless of the initial conditions ($\eta/s$=0.2 for MC-KLN and MC-Glauber initial conditions and $\eta/s = 0.16$ for AMPT initial condition) failed to capture the centrality dependence of SC(3,2) and SC(4,2).
-And among the models with small shear viscosities ($\eta/s$=0.08), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but they cannot describe the data quantitively for most of the centrality ranges.
+All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fails to capture the centrality dependence of SC(3,2) and SC(4,2).
+And among the models with small shear viscosities ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but they cannot describe the data quantitively for most of the centrality ranges.
 As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to the data in 0-10\% central collisions.
-NSC(3,2) doesn't show sensitivity to initial conditions or $\eta/s$ parametrizations and cannot be described by these models quantitively.
+NSC(3,2) does not show sensitivity to initial conditions or $\eta/s$ parametrizations and cannot be described by these models quantitively.
 However, for NSC(4,2), it is sensitive both to initial conditions and $\eta/s$ parametrizations.
-Even though NSC(4,2) is favoured both by AMPT initial condition with $\eta/s$=0.08 and MC-Glauber initial condition with $\eta/s$=0.20,
+Even though NSC(4,2) is favoured both by AMPT initial condition with $\eta/s$=0.08 and MC-Glauber initial condition with $\eta/s=0.20$,
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Therefore the Glauber initial condition with $\eta/s$=0.20 model can be ruled out and we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favoured by the data.
+Therefore the Glauber initial condition with $\eta/s=0.20$ model can be ruled out and we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favoured by the data.
 
@@
 Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s$=0.08) are shown as solid lines, and large shear viscosities ($\eta/s$=0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
 Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
@@
 The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
-Interestingly the string melting AMPT model can't capture the data well where the strength of the correlation is weaker than the default model.
+Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
 The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
 This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
-Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates the data.
+Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
 By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the data.
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculation, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with the large share viscosity regardless of the initial conditions ($\eta/s$=0.2 for MC-KLN and MC-Glauber initial conditions, and $\eta/s = 0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
-And among the models with small shear viscosity ($\eta/s$=0.08), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
+All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
+And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
 A quite clear separation between different initial conditions is observed for these higher order harmonics correlations compared to the lower order harmonic correlations.
@@
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s$=0.08) are shown as solid lines, and large shear viscosities ($\eta/s$=0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
 Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
@@
 \label{sec:ptdepsc}
-NSC(3,2) and NSC(4,2) as a function of different minimum $\pt{}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-As discussed in Sec.~\ref{sec:results} in higher minimum $p_T$ cuts, the $p_T$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations.
-The other AMPT configurations except for the default AMPT model give very strong $\pt{}$ dependence above 1 $GeV/c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $\pt{}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $\pt{}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $\pt{}$ dependence are observed.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $\pt{}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
-This might imply that the hadronic interaction is the source of this observed $\pt{}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
-This observed moderate $\pt{}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad} when QGP phase has become cool and dilute.
+NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
+As discussed in Sec.~\ref{sec:results}, the $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1 GeV$/c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
+In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
+As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
+When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
+This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
+This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad} when QGP phase has become cool and dilute.
 %The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
@@
               \end{center}
-             \caption{NSC(3,2)(Top) and SC(4,2)(Bottom) as a function of minimum $p_T$ cuts.
+             \caption{NSC(3,2) (Top) and SC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts.
 The AMPT results are drawn as color bands for comparison.
@@
 A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-Finally we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $\pt{}$ dependence in mid central collisions.
+Finally we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.

### 2016-11-02 sec_eventtrack.tex
adopting comments from sami

@@
 Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm
-, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced 
+Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced
 in the detector material, particles from weak decays, etc.). 

### 2016-11-02 sec_method_0a.tex
adopting comments from sami

@@
 Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a psedorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demontrated in Ref.~\cite{ALICE:2016kpq}.
+In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
+On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
 
@@
 
-\vspace{0.44cm}
-
-\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
+%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
 The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.

### 2016-11-02 paper.tex
forgotten minor changes

@@
 Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the data.
+By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model.
 The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
@@
 This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
-This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad} when QGP phase has become cool and dilute.
+This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
 %The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.

### 2016-11-04 paper.tex
adopting Ante and You, ante before model

@@
 The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
-in $\PbPb$ collisions at $\snn=2.76$~TeV were measured with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the multi-particle cumulant method.
-The method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher Fourier harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
-The results are compared to predictions from viscous hydrodynamics and  A Multi-Phase Transport model  ({AMPT}) models.
+in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
+The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
+This method is robust against systematic biases originating from non-flow effects. 
+The centrality dependence of correlation between the higher harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
+The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
 The comparisons to viscous hydrodynamic models demonstrate that
-the different order Fourier harmonic correlations respond differently to the initial conditions or $\eta/s$ and the small $\eta/s$ regardless of initial conditions is flavored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
+the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
+The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
+We have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid central collisions.
+This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
 %However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
+%pt dependence ??
 Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
@@
 
-The main emphasis of the ultra-relativistic heavy ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong collective and anisotropic flow in the transverse plane driven by the pressure gradients, with more particles emitted in the direction of the largest gradients.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also in LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
+The main emphasis of the ultra-relativistic heavy-ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
+This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by the anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
 This has been predicted by calculations utilising viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
 %and microscopic transport models ~\cite{Xu:2007jv}.  
-These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of strongly interacting matter is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy ion collisions at RHIC and LHC energies.
+These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of QGP is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy-ion collisions at RHIC and LHC energies.
 
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
-One such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be an order of magnitude for the lowest possible shear viscosity to entropy ratio in nature.
-Later it was found that one can calculate an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations supports as well the view that the QGP matter indeed is close to that limit~\cite{Gale:2012rq}.
-This in turn may have an important implications to other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the QCD critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
-
-Anisotropic flow is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 \noindent where $E$, $N$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the energy, particle yield, total momentum, transverse momentum, azimuthal angle and pseudorapidity of particles, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be derived as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
+The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
 %Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
@@
 %One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow is understood as hydrodynamic response to spatial deformation of the initial density profile.
+The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile.
 This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuation has led to triangular flow and higher harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Aad:2014fla}.
+The recognition of the importance of flow fluctuations has led to triangular flow and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
 %The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
-The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}.
+The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while correlations have the potential to discriminate the two respective contributions to anisotropic flow development~\cite{Niemi:2012aj}.
 And the $v_{n}$ distributions carry detailed information about the initial density profile~\cite{Renk:2014jja,Yan:2014nsa}.
 
-However, difficulties on extracting the shear viscosity in heavy ion has been realized since it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
+The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
+For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
+It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
+This in turn may have an important implications for other fundamental physics goals.
+It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
+%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
+
+However, difficulties on extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
 The viscous effects reduce the magnitude of the elliptic flow.
@@
 
-The higher harmonics ($n>3$) are understood as superpositions of linear and nonlinear responses, through which they are correlated with lower-order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora}.
-When the harmonic order is large, the nonlinear response contribution in viscous hydrodynamics is dominant~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, $\delta f$, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
+While elliptic and triangular flow can be described well solely in terms of linear response, the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora}.
+When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant~\cite{Teaney:2012ke,Bravina:2013ora}.
+The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
 Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
 
-Recently we measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics.
-The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators~\cite{ALICE:2016kpq}.
-It was demonstrated that they are sensitive to the $\eta/s$ of the expending medium and simultaneous descriptions of different order harmonic correlations would constrain 
+Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
+The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators.
+It was demonstrated that they are sensitive to the $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain 
 both the initial conditions and the medium properties.
-In this article, we have extended the analysis to higher order Fourier harmonic (up to 5th order) correlations as well as $p_{\rm T}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include a systematic comparison to hydrodynamic and AMPT models.
+In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).
+We also include extensive comparisons to hydrodynamic and AMPT model calculations.
 In Sec.~\ref{sec:method} we present the details of the analysis methods.
 The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+Various theoretical models used in the articles are described in Sec.~\ref{sec:models}.
 The results of the measurements are presented in Sec.~\ref{sec:results}.
@@
 The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency.
-Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry).
+%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.
@@
 Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy.
+Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy.
 To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
@@
 to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.
+Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy-ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.
 

### 2016-11-04 sec_eventtrack.tex
adopting Ante and You, ante before model

@@
 tracks and measure their momenta with full azimuthal coverage in the
-pseudo-rapidity range $|\eta|<0.8$. Two scintillator
+pseudorapidity range $|\eta|<0.8$. Two scintillator
 arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
-and $2.8<\eta<5.1$ were used for triggering, and the determination of
+and $2.8<\eta<5.1$ were used for triggering and the determination of
 centrality~\cite{Aamodt:2010cz}. The trigger
@@
 described in~\cite{Aamodt:2010pa} were applied to minimize
-contamination from secondary charged particles and fake tracks. The
-charged particle track reconstruction efficiency and contamination
+contamination from secondary charged particles and fake tracks.
+The reconstruction efficiency and contamination of charged particles
 were estimated from {\sc HIJING} Monte Carlo
 simulations~\cite{Wang:1991hta} combined with a {\sc
-GEANT3}~\cite{Brun:1994aa} detector model, and found to be independent of
+GEANT3}~\cite{Brun:1994aa} detector model and were found to be independent of
 the collision centrality. The reconstruction efficiency increases from
 70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
-constant at $80 \pm 5$\% for $\pt>1$~GeV/$c$. The estimated
+constant at $(80 \pm 5)$\% for $\pt>1$~GeV/$c$. The estimated
 contamination by secondary charged particles from weak decays and
@@
 With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
-at lower $\pt{}$, while the high $\pt{}$ cut-off was introduced to reduce the contribution to the anisotropies from jets. 
+at lower $\pt{}$, while the high $\pt{}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
 Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 

### 2016-11-04 sec_method_0a.tex
adopting Ante and You, ante before model

@@
 \label{sec:method}
-\subsection{Experimental observables}
+\subsection{Experimental Observables}
 %\subsubsection{cumulant analysis}
@@
 For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
-Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most realiable way (i.e.
-nearly insensitive to nonflow) the correlation of amplitudes of two different flow harmonics.
 The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
+
+The SC observables are defined as:
+ %
+\begin{eqnarray}
+\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
+&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
+&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
+%&=&0\,.
+\label{eq:4p_cumulant}
+\end{eqnarray}
+%
+with the condition $m\neq n$ for two positive integers $m$ and $n$. The complete discussion can be found in Section IV C of Ref.~\cite{Bilandzic:2013kga}.
 
@@
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
+On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
 

### 2016-11-04 sec_syst.tex
adopting comments from sami
adopting Ante and You, ante before model

@@
 
-\subsection{Systematic uncertainties}
+\subsection{Systematic Uncertainties}
 \label{sec:uncertainties}
@@
 The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
-Each results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
+All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
 The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
@@
 The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination.
-The systematic uncertainty from centrality determination was evaluated by using Time Projection Chamber (TPC) and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
-The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), 8\% for  SC(5,3).
+The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
+The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
 
-Because of limited acceptance of ALICE detector, primary vertex position along the longitudinal direction is important to ensure for the uniform pseudo-rapidity distribution over all events.
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis (z-vertex) is required to be located within 10 cm of interaction point (IP).
-We measured the results with 8cm cut and the differences in the final results were less than 3\%.
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
+an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
+The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was less than 3\%.
 
-The analyzed events were recorded with two settings of the magnetic filed polarities and they have almost the same number of events.
-Both magnetic polarization events were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
+The analyzed events were recorded with two settings of the magnetic field polarities and the resulting data sets have almost the same number of events.
+Events with both magnetic polarizations were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
 Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions.
-The effects from $p_T$ dependence reconstruction efficiency were taken into systematic uncertainty.
-Magnetic polarizations, reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
+The effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty.
+Magnetic polarizations and reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
 
-The systematic uncertainty due to the track reconstruction was estimated using two additional tracking, one relying on the so-called standalone TPC tracking with the 
-same parameters described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the ITS detectors with tighter selection criteria.
+The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
+same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the (Inner Tracking System) ITS detectors with tighter selection criteria.
 Since some parts of the SPD were switched off during some run periods, inefficient regions for common track reconstruction are apparent.
-To recover non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combine with TPC were used.
+To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
 Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
-The systematic difference up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow correlation effects on SC$(m,n)$.
-The difference between all charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were  7\% for SC(4,3) and 20\% for SC(5,3).
+The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
+In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$.
+The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
 
@@
 In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
-Then we force to have detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
-For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainty from the non-uniform distribution of azimuthal angles were 9\%, 17\% and 11\%, respectively.
-Generally, systematics uncertainties are large for the SC(5,3) and SC(5,2) than the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are sensitive to azimuthal modulation and $v_n$ decreases with $n$.
-Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
+Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
+For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
+Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing.
+%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.

### 2016-11-05 paper.tex
longSC_v3.0

@@
 This method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher harmonics ($v_3$, $v_4$, $v_5$) and the lower harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
+The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
@@
 %One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile.
+The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
 This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
@@
 Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
-This in turn may have an important implications for other fundamental physics goals.
+This in turn may have important implications for other fundamental physics goals.
 It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
@@
 
-While elliptic and triangular flow can be described well solely in terms of linear response, the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora}.
-When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant~\cite{Teaney:2012ke,Bravina:2013ora}.
+An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the known probability distribution of nucleons in the incoming nuclei.
+This initial density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
+\begin{equation}
+ \varepsilon_{n} e^{in\Psi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
+  \label{eq:eccentricities}
+\end{equation}
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\} = \int dxdy\, e(x,y,\tau_0) (\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Psi_{n}$ is the participant plane angle (see Sec.3 in Ref.~\cite{Niemi:2015qia}).
+There is experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+$v_n \propto \varepsilon_n$ for n=2 or 3).
+$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva}(linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora}(nonlinear response).
+While elliptic and triangular flow can be described well solely in terms of linear response, the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
 The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
@@
 both the initial conditions and the medium properties.
-In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonic ($v_3$-$v_2$ and $v_4$-$v_2$).
+In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
 We also include extensive comparisons to hydrodynamic and AMPT model calculations.
@@
 
-The VISH2+1~\cite{Zhu:2016puf} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
+The VISH2+1~\cite{Shen:2010uy} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
 With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model. 
+Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model~\cite{Zhu:2016puf}. 
 Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
@@
 
-The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
+%The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
 Positive values of SC(4,2) are observed for all measured centralities.
@@
 
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)).
-The correlation between $v_3$ and $v_4$ is negative as similarly as $v_3$ and $v_2$ while the others are all positive.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)) which are the same as the published results~\cite{ALICE:2016kpq}.
+The correlation between $v_3$ and $v_4$ is negative as similarly as $v_3$ and $v_2$ while the others are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
 The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonics (SC(3,2) and SC(4,2)).
@@
 \newpage
-\section{Model comparisons}
+\section{Model Comparisons}
 \label{sec:theory}
-\subsection{Low order harmonic correlations}
+\subsection{Low Order Harmonic Correlations}
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_3}.
-The hydrodynamic calculations roughly capture qualitatively the centrality dependence, but not quantitively.
-Both SC(3,2) with data and hydrodynamics have negative values for all centralities, while SC(4,2) results have positive values over all measured centralities.
-However, there is no single centrality for which a given $\eta/s(T)$ parameterization describes both SC(3,2) and SC(4,2) simultaneously.
-On the other hand, the same hydrodynamic calculations capture the centrality dependence of the individual $v_n$ quantitively~\cite{Eskola:2015uda}.
-
-NSC(3,2) and NSC(4,2) are also compared to the same model on the right in Fig.~\ref{fig:Figure_3}. 
-While NSC(3,2) does not show sensitivity to  different $\eta/s(T)$ parameterizations,  NSC(4,2) exhibit much better sensitivity
-than NSC(3,2) observable and the individual flow harmonics~\cite{Niemi:2015qia}.
-These findings indicate that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the prediction from~\cite{Niemi:2012aj}.
+First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the in Fig2 in Ref.~\cite{ALICE:2016kpq}.
+It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the prediction from~\cite{Niemi:2012aj}.
 However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
@@
 NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations, i.e.\ medium property but the model cannot describe the centrality dependence nor the absolute values.
-These observed distinct discrepancies between data and models might indicate that the current understanding of initial conditions used in the model need to be revisited
-to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
+These observed distinct discrepancies between data and models might indicate that the current understanding of initial conditions used in the model need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
 Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy-ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.
-
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
-              \end{center}
-        \caption{Results from SC(m,n) in $\PbPb$ $\snn=2.76$~TeV are compared to hydrodynamic calculations.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_3}
-\end{figure}
 
@@
         	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations with different settings.
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
 Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
@@
  \newpage
-\subsection{Higher order harmonic correlations}
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculation, shown in Fig.~\ref{fig:Figure_6}. 
+\subsection{Higher Order Harmonic Correlations}
+The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
+First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_x}.
+\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al, figure will be replaced later, just a place holder]}}
+
+\begin{figure}[htbp]
+            \begin{center}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
+              \end{center}
+        \caption{Results from SC(m,n) in $\PbPb$ $\snn=2.76$~TeV are compared to hydrodynamic calculations.
+The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
+This will be replaced with new figures once we have the calculations for Harri}
+        \label{fig:Figure_4}
+\end{figure}
+
+The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
 All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
 And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
-A quite clear separation between different initial conditions is observed for these higher order harmonics correlations compared to the lower order harmonic correlations.
+A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations.
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
@@
 % intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
-in the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
+In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
 The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
@@
  \newpage
-\subsection{Transverse momentum dependence of Low order harmonic correlations}
+\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
 \label{sec:ptdepsc}

### 2016-11-05 sec_syst.tex
longSC_v3.0

@@
 an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
-The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was less than 3\%.
+The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
 
@@
 The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the (Inner Tracking System) ITS detectors with tighter selection criteria.
-Since some parts of the SPD were switched off during some run periods, inefficient regions for common track reconstruction are apparent.
+same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
 To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.

### 2016-11-06 paper.tex
minor fix
comment for 1st proof

@@
 \title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-\ShortTitle{Correlations between event-by-event fluctuations of flow harmonics}   % appears on right page headers
+%\title{Higher order event-by-event flow harmonic correlations in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
+\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
 
@@
 The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
-We have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
+$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid central collisions.
+This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out which is the least understood part of hydrodynamic calculations.
 %However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
@@
 
+The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
+For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
+It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
+This in turn may have important implications for other fundamental physics goals.
+It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
+%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
+
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
@@
 The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while correlations have the potential to discriminate the two respective contributions to anisotropic flow development~\cite{Niemi:2012aj}.
-And the $v_{n}$ distributions carry detailed information about the initial density profile~\cite{Renk:2014jja,Yan:2014nsa}.
-
-The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
-For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
-This in turn may have important implications for other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
+And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
 
@@
 
-An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the known probability distribution of nucleons in the incoming nuclei.
-This initial density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
+An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
+This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
 \begin{equation}
- \varepsilon_{n} e^{in\Psi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
+ \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
   \label{eq:eccentricities}
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\} = \int dxdy\, e(x,y,\tau_0) (\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Psi_{n}$ is the participant plane angle (see Sec.3 in Ref.~\cite{Niemi:2015qia}).
-There is experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\} = \int dxdy\, e(x,y,\tau_0) (\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
+There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
 $v_n \propto \varepsilon_n$ for n=2 or 3).
-$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva}(linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora}(nonlinear response).
-While elliptic and triangular flow can be described well solely in terms of linear response, the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
+Therefore the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
 When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
@@
 The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
-Various theoretical models used in the articles are described in Sec.~\ref{sec:models}.
+Various theoretical models used in the article are described in Sec.~\ref{sec:models}.
 The results of the measurements are presented in Sec.~\ref{sec:results}.
@@
 
-The VISH2+1~\cite{Shen:2010uy} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
+The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
 With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.

### 2016-11-06 paper.tex
merge section into one file

@@
 
-%\input{sec_method}
-\input{sec_method_0a}
-\input{sec_eventtrack}
-\input{sec_syst}
+% Experimental observables
+%% Flow correlations in general
+   % Niemi, ATLAS paper
+%% Symmetric Cumulants (SC)
+%% Normalized Symmetric Cumulants (NSC)
+%% Summary of results of 1st ALICE paper on SC
+%% Review of papers which cited ALICE 
+\section{Data Analysis}
+\label{sec:method}
+\subsection{Experimental Observables}
+%\subsubsection{cumulant analysis}
 
+While from existing measurements an estimate can be placed on the average value of QGP's $\eta/s$, both at RHIC and LHC energies, what remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
+This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
+The emerging consensus of late is that it is unlikely that the study of individual flow harmonics $v_n$ will reveal the details of $\eta/s(T)$ dependence.
+In fact, in was demonstrated already in the initial study~\cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
+In Ref.~\cite{Niemi:2012aj} new flow observables were introduced by the theorists, which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
+The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
+Therefore their mesurement in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
+Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.
+
+For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
+The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
+
+The SC observables are defined as:
+ %
+\begin{eqnarray}
+\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
+&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
+&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
+%&=&0\,.
+\label{eq:4p_cumulant}
+\end{eqnarray}
+%
+with the condition $m\neq n$ for two positive integers $m$ and $n$. The complete discussion can be found in Section IV C of Ref.~\cite{Bilandzic:2013kga}.
+
+SC($m$,$n$) can be normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$ to obtain \textit{normalized} symmetric cumulants~\cite{ALICE:2016kpq,Giacalone:2016afq}, which we denote by NSC($m$,$n$), i.e.
+%
+\begin{equation}
+\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
+\label{eq:nsc}
+\end{equation}
+%
+Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics.
+In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
+On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
+
+The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
+However, the details of the centrality dependence differ in the fluctutation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
+Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution.
+These results were also used to discriminate between different parameterizations of initial conditions and it was demonstrated that in the fluctuation-dominated regime (in central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+
+%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
+The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
+This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms.
+In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants.
+As a concrete example it was discussed that the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
+
+Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
+The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
+This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
+To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
+However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
+Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
+Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
+
+\subsection{Event and Track Selection}
+\label{sec:experiment}
+The data sample recorded by ALICE during the 2010 heavy-ion run at the
+LHC is used for this analysis. Detailed descriptions of the ALICE
+detector can be found
+in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
+Projection Chamber (TPC) was used to reconstruct charged particle
+tracks and measure their momenta with full azimuthal coverage in the
+pseudorapidity range $|\eta|<0.8$. Two scintillator
+arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
+and $2.8<\eta<5.1$ were used for triggering and the determination of
+centrality~\cite{Aamodt:2010cz}. The trigger
+conditions and the event selection criteria are identical to those
+described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
+Approximately $10^7$ minimum-bias Pb-Pb events with
+a reconstructed primary vertex within $\pm 10$ cm from the nominal
+interaction point in the beam direction are used for this
+analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
+and $0.2<\pt<5$ GeV/$c$ were selected. The charged track quality cuts
+described in~\cite{Aamodt:2010pa} were applied to minimize
+contamination from secondary charged particles and fake tracks.
+The reconstruction efficiency and contamination of charged particles
+were estimated from {\sc HIJING} Monte Carlo
+simulations~\cite{Wang:1991hta} combined with a {\sc
+GEANT3}~\cite{Brun:1994aa} detector model and were found to be independent of
+the collision centrality. The reconstruction efficiency increases from
+70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
+constant at $(80 \pm 5)$\% for $\pt>1$~GeV/$c$. The estimated
+contamination by secondary charged particles from weak decays and
+photon conversions is less than 6\% at $\pt=0.2$~GeV/$c$ and falls
+below 1\% for $\pt>1$~GeV/$c$.
+With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
+at lower $\pt{}$, while the high $\pt{}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
+Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
+Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced
+in the detector material, particles from weak decays, etc.). 
+Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.
+
+\subsection{Systematic Uncertainties}
+\label{sec:uncertainties}
+%\textbf{\tmp{[Track selection criteria.]}}
+
+%p10================================================================================
+
+%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}
+
+The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
+All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
+The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
+The contributions from different sources were then added in quadrature to obtain the final value of the systematic uncertainty.
+
+The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination.
+The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
+The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
+
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
+an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
+The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
+
+The analyzed events were recorded with two settings of the magnetic field polarities and the resulting data sets have almost the same number of events.
+Events with both magnetic polarizations were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
+Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions.
+The effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty.
+Magnetic polarizations and reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
+
+The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
+same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
+To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
+Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
+The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
+In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$.
+The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
+
+One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
+In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
+Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
+For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
+Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing.
+%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
 \section{Theoretical models}

### 2016-11-06 paper.tex
adopt song's comment

@@
 $v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out which is the least understood part of hydrodynamic calculations.
+This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
+% which is the least understood part of hydrodynamic calculations.
 %However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
@@
 The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
-It was demonstrated that they are sensitive to the $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain 
-both the initial conditions and the medium properties.
+It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
 In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
@@
 
-\newpage
+\pagebreak
+
 \section{Model Comparisons}
@@
 
- \newpage
+\pagebreak
+
 \subsection{Higher Order Harmonic Correlations}
@@
 
- \newpage
+\pagebreak
 \subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
@@
 
-\newpage
+\pagebreak
+
 \section{Summary}

### 2016-11-06 paper.tex
song's comment

@@
 To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we apply minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval in order to avoid large statistical fluctuations in the results.
-The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5 are applied.
+The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5 GeV$/c$ are applied.
 The results of $p_{\rm T}$ dependence with SC(3,2) and SC(4,2) for minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
@@
 The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
-This suggests that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the different values of $p_{\rm T}$  dependent individual $v_n$ values.
+This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
 The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5 GeV$/c$ and the results are shown on the bottom in Fig.~\ref{fig:Figure_2}.
@@
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
-As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(4,3) in these models is opposite to the data in 0-10\% central collisions.
+As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to the data in 0-10\% central collisions.
 NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.

### 2016-11-07 paper.tex
Ante comments on model description and also latest figures

@@
 We also include extensive comparisons to hydrodynamic and AMPT model calculations.
-In Sec.~\ref{sec:method} we present the details of the analysis methods.
+In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
 The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
@@
 %Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
+
 \section{Theoretical models}
@@
 We have used various models in this article.
-The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency.
+The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
 %Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
@@
 
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics.
-With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte-Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position space.
+The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical model for relativistic heavy-ion collisions based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
+With well tuned transport coefficients, decoupling temperature  and some initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
+Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
+In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei.
+For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
 Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
@@
 In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
-These partons are then combined into the final-state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
+These partons are then combined into the final state hadrons via a quark coalescence model.
+In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
 The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
 The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the measurements.
-It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement.
-The detail configurations on AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
+It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
+The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
 
@@
 However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for most of centrality ranges within the errors.
+NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors.
 These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also the individual flow strength.
@@
 NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
-SC(4,3) data is clearly favoured by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
+SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
 
@@
 %Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?
+
+As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
+Except for 0-10\% centrality range, we found that the hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) also holds for Hydrodynamic calculations and AMPT models.
+The observed difference between SC(5,2) and SC(5,3) (SC(5,2)$>$SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$$>$$v_3$). 
+The opposite trend are observed for the normalized SC (NSC(5,3)$>$NSC(5,2)).
+This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
+It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
+NSC($m$,$n$) correlators increase with the larger $\eta/s$ in Hydrodynamic calculations in 0-30\% centrality range in the same way as the event-plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
+In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
 

### 2016-11-07 makediff.sh

@@ -1,0 +1,4 @@
+#!/bin/bash 
+#1. version to PC 7f420a7
+#2. merge sec to one file 2cfb30f
+../git-latexdiff/git-latexdiff 7f420a7 $1

### 2016-11-07 paper.tex
ante's comment, need to improve centrality dependence tomorrow

@@
 When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
+The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
+%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
 Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
@@
 analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<\pt<5$ GeV/$c$ were selected. The charged track quality cuts
+and $0.2<\pt<5$~GeV/$c$ were selected. The charged track quality cuts
 described in~\cite{Aamodt:2010pa} were applied to minimize
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC$(m,n)$ (left figure) and NSC$(m,n)$ (right figure) with flow harmonic order up to 5th in $\PbPb$ $\snn=2.76$~TeV.
-Note that the lower order harmonic correlations (SC(4,2),SC(3,2)) are scaled down by factor of 10 and only statistical errors are shown in the left hand side figure.}
+        \caption{The result of SC$(m,n)$ (left figure) and NSC$(m,n)$ (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Note that the lower order harmonic correlations are taken from the recent publication~\cite{ALICE:2016kpq} and only statistical errors are shown for both figures.
+SC(4,2) and SC(3,2) are scaled down by factor of 10 on the left.}
         \label{fig:Figure_1}
@@
 
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)) which are the same as the published results~\cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative as similarly as $v_3$ and $v_2$ while the others are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonics (SC(3,2) and SC(4,2)).
-Especially SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
+\sloppy
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
+The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
+The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
+In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
 
 However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors.
-These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also the individual flow strength.
-SC(5,2) is stronger than SC(5,3), but as for NSC, the correlation between $v_5$ and $v_3$ is stronger than the correlation between $v_5$ and $v_2$.
+NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
+These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
+SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalize correlation between $v_5$ and $v_2$.
 
-To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we apply minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval in order to avoid large statistical fluctuations in the results.
-The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5 GeV$/c$ are applied.
-The results of $p_{\rm T}$ dependence with SC(3,2) and SC(4,2) for minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
+It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
+In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed.
+In case of NSC($m$,$n$), NSC(5,3) shows the strongest centrality dependence and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
+Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with similar magnitude.
+
+To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results.
+The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
+The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
 The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases. 
-This indicates that the relationship between event-by-event fluctuation of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles.
+%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
 This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
@@
 This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5 GeV$/c$ and the results are shown on the bottom in Fig.~\ref{fig:Figure_2}.
-As for SC$(m,n)$, the similar trends are observed as similarly as $p_{\rm T}<0.8$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
+As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
 The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors except for 40-50\% centrality
 and NSC(4,2) shows a moderate decreasing trend for increasing $p_{\rm T}$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
+%which is strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, which is nearly flat (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
@@
         \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
-The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$ GeV$/c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$ GeV$/c$.
+The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
 Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
@@
 As discussed in Sec.~\ref{sec:results}, the $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1 GeV$/c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
+The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
 In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.

### 2016-11-08 paper.tex
pt dep update and centrality dependence

@@
 
-\input{helpers.tex}
 \begin{document}
@@
 \newcommand{\pp}{\ensuremath{\mbox{p}\mbox{p}}}
+\newcommand{\tn}[1]{\textnormal{#1}}
 \newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
@@
 \PHyear{2016}
-\PHnumber{040}                 % required, obtained from PH
-\PHdate{24 Novermer}              % required, will be obtained from PH
+\PHnumber{xxx}                 % required, obtained from PH
+\PHdate{9 November}              % required, will be obtained from PH
 %
@@
 
-\sloppy
 The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
@@
 It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
-In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed.
-In case of NSC($m$,$n$), NSC(5,3) shows the strongest centrality dependence and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
-Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with similar magnitude.
+In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
+NSC(5,3) shows the strongest centrality dependence among all harmonic correlations and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
+Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
 
@@
 As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
-The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors except for 40-50\% centrality
-and NSC(4,2) shows a moderate decreasing trend for increasing $p_{\rm T}$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
-%which is strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, which is nearly flat (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
+The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase.
+These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
+3 in Ref.~\cite{Abelev:2012di}).
+%(see further discussions in Sec.~\ref{sec:ptdepsc})
+%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
 %However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
@@
 \label{sec:ptdepsc}
+
+The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors except for 40-50\% centrality
+and NSC(4,2) shows a moderate decreasing trend for increasing $p_{\rm T}$, which is strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, which is nearly flat (see Fig.
+3 in Ref.~\cite{Abelev:2012di}).
+
 NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
@@
 Hence this observation might help to understand the details of the fluctuations in initial conditions.
-The comparisons to VISH2+1 calculation show that all the models with the large share viscosity regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations and based on the tested model parameters that the $\eta/s$ should be small and AMPT initial condition is flavored by the data.
+The comparisons to VISH2+1 calculation show that all the models with the large share viscosity regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations and based on the tested model parameters that the $\eta/s$ should be small and AMPT initial condition is favored by the data.
 A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.

### 2016-11-08 paper.tex
fix the margin by adding spaces in some eq and add the latest cernphprep

@@
 \documentclass[ALICE,manyauthors]{cernphprep}
-\usepackage[modulo]{lineno}
+
+\usepackage[comma,square,numbers,sort&compress]{natbib}
 \usepackage{hyperref}
-\usepackage[comma,square,numbers,sort&compress]{natbib}
-\usepackage{amsmath,amssymb}% for advanced math typesetting 
+\usepackage{lineno}
 \usepackage{url,color}
-%\usepackage{pslatex}
-\usepackage{mathrsfs} % produce the curly R with \mathscr not \mathcal
+\linenumbers
 
-% \usepackage{palatino}%    Choose default roman font.  Others are times, pslatex, newcent, bookman, chancery                                                    
-% can use mathpazo if no one uses \mathrm{\gamma}, etc., since it doesn't suppl\y Greek in rm. Google "mathpazo mathrm greek"                                   
-% \usepackage{mathpazo}%  Matching math fonts (see http://www.math.uiuc.edu/~hartke/computer/latex/survey/survey.html)                                           
-% \usepackage{helvet}%
+\begin{document}%
 
@@
 %
-
 \newcommand{\PbPb}{\textnormal{Pb--Pb}}
@@
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\} = \int dxdy\, e(x,y,\tau_0) (\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
 There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
@@
 described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
-Approximately $10^7$ minimum-bias Pb-Pb events with
+Approximately $10^7$ minimum-bias $\PbPb$ events with
 a reconstructed primary vertex within $\pm 10$ cm from the nominal
@@
 
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2),SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
@@
 However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
+NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
 These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
@@
 
-The results with the comparison to VISH2+1 calculation are shown in Fig.~\ref{fig:Figure_4}.
+The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
 All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fails to capture the centrality dependence of SC(3,2) and SC(4,2).
@@
 Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-         \label{fig:Figure_4}
+         \label{fig:Figure_3}
         \end{center}   
@@
 
-Finally, the extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_5}.
+Finally, the extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_4}.
 As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
@@
 It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT.
+Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.
 
@@
 The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_5}
+        \label{fig:Figure_4}
         \end{center}   
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_x}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al, figure will be replaced later, just a place holder]}}
+First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
 
@@
 This will be replaced with new figures once we have the calculations for Harri}
-        \label{fig:Figure_4}
+        \label{fig:Figure_5}
 \end{figure}
@@
 
-As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0-10\% centrality range, we found that the hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) also holds for Hydrodynamic calculations and AMPT models.
-The observed difference between SC(5,2) and SC(5,3) (SC(5,2)$>$SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$$>$$v_3$). 
-The opposite trend are observed for the normalized SC (NSC(5,3)$>$NSC(5,2)).
+As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
+Except for 0-10\% centrality range, we found that the same hierarchy also holds for the hydrodynamic calculations and the AMPT models in this article.
+The observed difference between SC(5,2) and SC(5,3) (SC(5,2) $>$ SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$ $>$ $v_3$). 
+The opposite trend are observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
 This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
 It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
-NSC($m$,$n$) correlators increase with the larger $\eta/s$ in Hydrodynamic calculations in 0-30\% centrality range in the same way as the event-plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
+NSC($m$,$n$) correlators increase with the larger $\eta/s$ in hydrodynamic calculations in 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
 In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
@@
 
-The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors except for 40-50\% centrality
-and NSC(4,2) shows a moderate decreasing trend for increasing $p_{\rm T}$, which is strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, which is nearly flat (see Fig.
-3 in Ref.~\cite{Abelev:2012di}).
-
+It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
+In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
 NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-As discussed in Sec.~\ref{sec:results}, the $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
 The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
@@
 This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
-%The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
+The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
+\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
 
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and SC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts.
-The AMPT results are drawn as color bands for comparison.
+             \caption{NSC(3,2) (Top) and SC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
 The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}

### 2016-11-08 paper.tex
final ante's comment in place

@@
 \usepackage{url,color}
-\linenumbers
-
-\begin{document}%
-
 \linenumbers
@@
 The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
-$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid central collisions.
+$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC$(m,n)$ (left figure) and NSC$(m,n)$ (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
-Note that the lower order harmonic correlations are taken from the recent publication~\cite{ALICE:2016kpq} and only statistical errors are shown for both figures.
-SC(4,2) and SC(3,2) are scaled down by factor of 10 on the left.}
+        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
+Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
         \label{fig:Figure_1}
@@
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the in Fig2 in Ref.~\cite{ALICE:2016kpq}.
-It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the prediction from~\cite{Niemi:2012aj}.
+First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the in Fig.~2 in Ref.~\cite{ALICE:2016kpq}.
+It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
 However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
@@
 Hence this observation will help to understand the fluctuations in initial conditions better.
-NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations, i.e.\ medium property but the model cannot describe the centrality dependence nor the absolute values.
-These observed distinct discrepancies between data and models might indicate that the current understanding of initial conditions used in the model need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy-ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.
+NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values.
+These observed distinct discrepancy between data and theoretical predictions indicate that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
+Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial state conditions and the fluctuations of the medium created in heavy-ion collisions.
+The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.
 
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
-All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fails to capture the centrality dependence of SC(3,2) and SC(4,2).
-And among the models with small shear viscosities ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but they cannot describe the data quantitively for most of the centrality ranges.
-As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to the data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to initial conditions or $\eta/s$ parametrizations and cannot be described by these models quantitively.
-However, for NSC(4,2), it is sensitive both to initial conditions and $\eta/s$ parametrizations.
-Even though NSC(4,2) is favoured both by AMPT initial condition with $\eta/s$=0.08 and MC-Glauber initial condition with $\eta/s=0.20$,
+All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
+On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
+Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
+NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
+However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
+Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Therefore the Glauber initial condition with $\eta/s=0.20$ model can be ruled out and we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favoured by the data.
+Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
 
@@
 
-Finally, the extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_4}.
+Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
 As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
@@
 NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
-The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering make NSC(4,2) slightly smaller.
+The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
 It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
@@
               \end{center}
-        \caption{Results from SC(m,n) in $\PbPb$ $\snn=2.76$~TeV are compared to hydrodynamic calculations.
+        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
 The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
-And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
+All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
+Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
 A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
-As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to the data in 0-10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
+Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
+NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
+% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
 SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
@@
 
-The extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_7}.
-The string melting AMPT model describes SC(5,2) and SC(5,3) well. The same setting describes only NSC(5,3) but it overestimates NSC(5,2). 
-However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as similarly as NSC(3,2) and NSC(4,2).
+The extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_7}.
+The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
+However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{ig:Figure_4}.
 % intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
@@
 The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
-In summary, the default AMPT model describes the normalized SC (NSC$(m,n)$) from lower to higher order harmonic correlation while the string melting AMPT model overestimates NSC(5,2) and 
-underestimates (or very weak correlations) NSC(4,3).
+In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and underestimates (or predicts very weak correlation) NSC(4,3).
 
@@
 NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
+These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
 In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
@@
 This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
-This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
+This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
 The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and SC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
 The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
@@
 \label{sec:summary}
-In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics.
-The observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators.
-We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities and fluctuations of $v_2$ and $v_4$ ( $v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.
+In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC) to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.
 This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
 We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies.
-Furthermore, the sign of $v_3$-$v_2$ correlation in the model in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
+Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies.
+Furthermore, the sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
 In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
 Hence this observation might help to understand the details of the fluctuations in initial conditions.
-The comparisons to VISH2+1 calculation show that all the models with the large share viscosity regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations and based on the tested model parameters that the $\eta/s$ should be small and AMPT initial condition is favored by the data.
+The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations.
+Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data.
 A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-Finally we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid central collisions.
+Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
-The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties in ultra-relativistic heavy-ion collisions.
+The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
 

### 2016-11-08 paper.tex
closing PC comment

@@
 The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their mesurement in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
+Therefore their measurements in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
 Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.
@@
 \label{sec:summary}
-In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC) to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+In this article, we repot the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
+The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.
+It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and be free from symmetry plane correlations.
 We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.

### 2016-11-08 paper.tex
add missing part

@@
 For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
+Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most realiable way (i.e.
+nearly insensitivy to nonflow) the correlation of amplitudes of two different flow harmonics.
 The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.

### 2016-11-08 paper.tex
typo
fix few minor and real v3.0

@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most realiable way (i.e.
-nearly insensitivy to nonflow) the correlation of amplitudes of two different flow harmonics.
+nearly insensitive to nonflow) the correlation of amplitudes of two different flow harmonics.
 The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
@@
 \label{sec:summary}
-In this article, we repot the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
+In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
 The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.

### 2016-11-08 abstract.tex
split to content and main

--- 2016-11-08 paper.tex
@@
-\documentclass[ALICE,manyauthors]{cernphprep}
-
-\usepackage[comma,square,numbers,sort&compress]{natbib}
-\usepackage{hyperref}
-\usepackage{lineno}
-\usepackage{url,color}
-\linenumbers
-
-\begin{document}
-%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
-%
-%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
-%
-\newcommand{\PbPb}{\textnormal{Pb--Pb}}
-\newcommand{\AuAu}{\textnormal{Au--Au}}
-\newcommand{\pp}{\ensuremath{\mbox{p}\mbox{p}}}
-\newcommand{\tn}[1]{\textnormal{#1}}
-\newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
-\newcommand{\pt}{\ensuremath{p_\tn{T}}}\newcommand{\pT}{\pt}
- % off by redefinding CKBNOTEje
-\newcommand{\CKBNOTE}[1]{{\bf CKB:  #1}} 
-\renewcommand{\CKBNOTE}[1]{}  % switch off
-
- % off by redefinding RHNOTE
-\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
-\renewcommand{\RHNOTE}[1]{}  % switch off
-
-\begin{titlepage}
-%
-\PHyear{2016}
-\PHnumber{xxx}                 % required, obtained from PH
-\PHdate{9 November}              % required, will be obtained from PH
-%
-%
-%%% Put your own title + short title here:
-\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-%\title{Higher order event-by-event flow harmonic correlations in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
-
-%
-%%% Do not change the nexts!
-\Collaboration{ALICE Collaboration%
-         \thanks{See Appendix~\ref{app:collab} for the list of collaboration
-                      members}}
-\ShortAuthor{ALICE Collaboration}      % appears on left page headers, do not change
-%
-\begin{abstract}
-
 The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
@@
 on initial conditions and the transport properties of the system produced in heavy-ion collisions.
-\end{abstract}
-\end{titlepage}
-\setcounter{page}{2}
-
-% \input{main.tex}               %%%%%%%%%%% put the body of the article here
-
-% !TEX root = paper.tex
-
-\section{Introduction}
-
-%\textbf{{[A general history on HI]}}
-
-The main emphasis of the ultra-relativistic heavy-ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by the anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-This has been predicted by calculations utilising viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
-%and microscopic transport models ~\cite{Xu:2007jv}.  
-These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of QGP is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy-ion collisions at RHIC and LHC energies.
-
-The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
-For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
-This in turn may have important implications for other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
-
-%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
-
-\begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
-\label{Eq:Fourier}
-\end{equation}
-
-\noindent where $E$, $N$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the energy, particle yield, total momentum, transverse momentum, azimuthal angle and pseudorapidity of particles, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
-%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
-%\begin{equation}
-%\label{defVn}
-%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
-%\end{equation}
-%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
-%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations has led to triangular flow and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
-%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
-The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while correlations have the potential to discriminate the two respective contributions to anisotropic flow development~\cite{Niemi:2012aj}.
-And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
-
-However, difficulties on extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
-The viscous effects reduce the magnitude of the elliptic flow.
-Furthermore, the magnitude of $\eta/s$ used in these calculations should be considered as an average over the temperature history of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature.
-In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
-knowledge of both the temperature dependence and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.
-
-An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
-This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
-\begin{equation}
- \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
-  \label{eq:eccentricities}
-\end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for n=2 or 3).
-$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-Therefore the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
-When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
-%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
-
-Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
-It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
-In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include extensive comparisons to hydrodynamic and AMPT model calculations.
-In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
-The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
-Various theoretical models used in the article are described in Sec.~\ref{sec:models}.
-The results of the measurements are presented in Sec.~\ref{sec:results}.
- In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.
-
-% Experimental observables
-%% Flow correlations in general
-   % Niemi, ATLAS paper
-%% Symmetric Cumulants (SC)
-%% Normalized Symmetric Cumulants (NSC)
-%% Summary of results of 1st ALICE paper on SC
-%% Review of papers which cited ALICE 
-\section{Data Analysis}
-\label{sec:method}
-\subsection{Experimental Observables}
-%\subsubsection{cumulant analysis}
-
-While from existing measurements an estimate can be placed on the average value of QGP's $\eta/s$, both at RHIC and LHC energies, what remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
-This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
-The emerging consensus of late is that it is unlikely that the study of individual flow harmonics $v_n$ will reveal the details of $\eta/s(T)$ dependence.
-In fact, in was demonstrated already in the initial study~\cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
-In Ref.~\cite{Niemi:2012aj} new flow observables were introduced by the theorists, which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
-The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurements in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
-Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.
-
-For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
-The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
-
-The SC observables are defined as:
- %
-\begin{eqnarray}
-\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
-&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
-&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
-%&=&0\,.
-\label{eq:4p_cumulant}
-\end{eqnarray}
-%
-with the condition $m\neq n$ for two positive integers $m$ and $n$. The complete discussion can be found in Section IV C of Ref.~\cite{Bilandzic:2013kga}.
-
-SC($m$,$n$) can be normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$ to obtain \textit{normalized} symmetric cumulants~\cite{ALICE:2016kpq,Giacalone:2016afq}, which we denote by NSC($m$,$n$), i.e.
-%
-\begin{equation}
-\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
-\label{eq:nsc}
-\end{equation}
-%
-Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
-
-The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
-However, the details of the centrality dependence differ in the fluctutation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution.
-These results were also used to discriminate between different parameterizations of initial conditions and it was demonstrated that in the fluctuation-dominated regime (in central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-
-%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
-The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
-This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms.
-In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants.
-As a concrete example it was discussed that the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
-
-Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
-The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
-This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
-To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
-However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
-Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
-Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
-
-\subsection{Event and Track Selection}
-\label{sec:experiment}
-The data sample recorded by ALICE during the 2010 heavy-ion run at the
-LHC is used for this analysis. Detailed descriptions of the ALICE
-detector can be found
-in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
-Projection Chamber (TPC) was used to reconstruct charged particle
-tracks and measure their momenta with full azimuthal coverage in the
-pseudorapidity range $|\eta|<0.8$. Two scintillator
-arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
-and $2.8<\eta<5.1$ were used for triggering and the determination of
-centrality~\cite{Aamodt:2010cz}. The trigger
-conditions and the event selection criteria are identical to those
-described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
-Approximately $10^7$ minimum-bias $\PbPb$ events with
-a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point in the beam direction are used for this
-analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<\pt<5$~GeV/$c$ were selected. The charged track quality cuts
-described in~\cite{Aamodt:2010pa} were applied to minimize
-contamination from secondary charged particles and fake tracks.
-The reconstruction efficiency and contamination of charged particles
-were estimated from {\sc HIJING} Monte Carlo
-simulations~\cite{Wang:1991hta} combined with a {\sc
-GEANT3}~\cite{Brun:1994aa} detector model and were found to be independent of
-the collision centrality. The reconstruction efficiency increases from
-70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
-constant at $(80 \pm 5)$\% for $\pt>1$~GeV/$c$. The estimated
-contamination by secondary charged particles from weak decays and
-photon conversions is less than 6\% at $\pt=0.2$~GeV/$c$ and falls
-below 1\% for $\pt>1$~GeV/$c$.
-With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
-at lower $\pt{}$, while the high $\pt{}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
-Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced
-in the detector material, particles from weak decays, etc.). 
-Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.
-
-\subsection{Systematic Uncertainties}
-\label{sec:uncertainties}
-%\textbf{\tmp{[Track selection criteria.]}}
-
-%p10================================================================================
-
-%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}
-
-The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
-All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
-The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
-The contributions from different sources were then added in quadrature to obtain the final value of the systematic uncertainty.
-
-The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination.
-The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
-The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
-an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
-The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
-
-The analyzed events were recorded with two settings of the magnetic field polarities and the resulting data sets have almost the same number of events.
-Events with both magnetic polarizations were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
-Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions.
-The effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty.
-Magnetic polarizations and reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
-
-The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
-To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
-Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
-The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$.
-The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
-
-One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
-In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
-Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
-For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
-Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing.
-%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
-
-\section{Theoretical models}
-\label{sec:models}
-We have used various models in this article.
-The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
-%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.
-
-We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
-%\textbf{Need a short descriotion of event-by-event viscous hydrody-namic calculations from VISH2+1}.
-
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical model for relativistic heavy-ion collisions based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well tuned transport coefficients, decoupling temperature  and some initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
-The model then introduces the string melting procedure to produce initial partons.
-These partons are then evolved for the short duration using the ZPC parton cascade model.
-Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
-Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-
-Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy.
-To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
-For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model.
-In the default version, partons are recombined with their parent strings when they stop interacting.
-The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
-In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
-These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
-The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
-It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
-
-%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
-Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
-Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
-%
-
-\section{Results}
-\label{sec:results}
-
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
-        \label{fig:Figure_1}
-              \end{center}
-\end{figure}
-
-%The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
-Positive values of SC(4,2) are observed for all measured centralities.
-This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$.
-It also indicates that finding $v_2$ larger than average ($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average ($\langle v_4 \rangle$) in that event.
-On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average ($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average ($v_3 < \langle v_3 \rangle$).
-
-% \begin{figure}[htbp]
-%            \begin{center}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly.eps}}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
-%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_{\rm T}<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left).
-The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
-%              \label{fig:Figure_1}
-%              \end{center}
-% \end{figure}
-
-%\begin{figure}[h]
-%	\begin{center}
-%       	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC32_HIJING_ptdep.eps}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC42_HIJING_ptdep.eps}}
-%        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations.
-Defaults($0.2 < p_{\rm T} < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend.
-A small shifts along the x axis were applied for better visibility.}
-%        \label{fig:results_HIJING}
-%        \end{center}   
-%\end{figure}
-
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
-In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
-
-However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
-These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
-SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalize correlation between $v_5$ and $v_2$.
-
-It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
-In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
-NSC(5,3) shows the strongest centrality dependence among all harmonic correlations and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
-Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
-
-To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results.
-The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
-The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases. 
-%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
-NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
-This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
-As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
-The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase.
-These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
-3 in Ref.~\cite{Abelev:2012di}).
-%(see further discussions in Sec.~\ref{sec:ptdepsc})
-%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
-%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
-The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
-Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
-        \label{fig:Figure_2}
-        \end{center}   
-\end{figure}
-
-\pagebreak
-
-\section{Model Comparisons}
-\label{sec:theory}
-\subsection{Low Order Harmonic Correlations}
-SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the in Fig.~2 in Ref.~\cite{ALICE:2016kpq}.
-It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation will help to understand the fluctuations in initial conditions better.
-NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values.
-These observed distinct discrepancy between data and theoretical predictions indicate that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial state conditions and the fluctuations of the medium created in heavy-ion collisions.
-The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.
-
-The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
-However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
-Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
-SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
-
-\begin{figure}[!p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-         \label{fig:Figure_3}
-        \end{center}   
- \end{figure}
-
-Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
-The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
-Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
-The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
-This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
-Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
-
-In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
-NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
-The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure}
-
-\pagebreak
-
-\subsection{Higher Order Harmonic Correlations}
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
-
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
-              \end{center}
-        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
-This will be replaced with new figures once we have the calculations for Harri}
-        \label{fig:Figure_5}
-\end{figure}
-
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
-Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
-A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
-SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-        \label{fig:Figure_6}
-        \end{center}   
- \end{figure}
-
-The extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_7}.
-The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
-However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{ig:Figure_4}.
-% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
-In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
-The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and underestimates (or predicts very weak correlation) NSC(4,3).
-
-%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
-%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
-%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?
-
-As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0-10\% centrality range, we found that the same hierarchy also holds for the hydrodynamic calculations and the AMPT models in this article.
-The observed difference between SC(5,2) and SC(5,3) (SC(5,2) $>$ SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$ $>$ $v_3$). 
-The opposite trend are observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
-This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
-NSC($m$,$n$) correlators increase with the larger $\eta/s$ in hydrodynamic calculations in 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
-In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_7}
-        \end{center}   
- \end{figure}
-
-\pagebreak
-\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
-\label{sec:ptdepsc}
-
-It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
-In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
-NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
-This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
-The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
-
-\begin{figure}[htbp]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
-              \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-             \label{fig:Figure_8}
-\end{figure}
-
-\pagebreak
-
-\section{Summary}
-\label{sec:summary}
-In this article, we repot the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
-The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.
-It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and be free from symmetry plane correlations.
-We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.
-This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
-We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies.
-Furthermore, the sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation might help to understand the details of the fluctuations in initial conditions.
-The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations.
-Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data.
-A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
-The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
-
-%%%%%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-%\input{acknowledgements_jan2015.tex}    %%%%%%% get the lates version before submitting
-\end{acknowledgement}
-%
-%
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{apsrev4-1}   % Put here the style file name for the paper, i.e.apsrev4-1
-%\bibliography{biblio}
-%\input {bibliography.tex}  
-%
-
-% \bibliographystyle{mybibstyle}
-%\bibliographystyle{utphys}
-%\bibliography{paper}
-\bibliographystyle{utphys}
-\bibliography{paper}
-
-\newpage
-%
-%\input{}               %%%%%%%%%%% put your appendices here
-%
-%%%%%%%%% appendix with author list
-\appendix
-\section{The ALICE Collaboration}
-\label{app:collab}
-%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
-%\input{}              %%%%%%%%%%%% put the references here
-%
-\end{document}

### 2016-11-08 longSC.tex
split to content and main

--- 2016-11-08 paper.tex
@@
-\documentclass[ALICE,manyauthors]{cernphprep}
-
-\usepackage[comma,square,numbers,sort&compress]{natbib}
-\usepackage{hyperref}
-\usepackage{lineno}
-\usepackage{url,color}
-\linenumbers
-
-\begin{document}
-%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
-%
-%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
-%
-\newcommand{\PbPb}{\textnormal{Pb--Pb}}
-\newcommand{\AuAu}{\textnormal{Au--Au}}
-\newcommand{\pp}{\ensuremath{\mbox{p}\mbox{p}}}
-\newcommand{\tn}[1]{\textnormal{#1}}
-\newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
-\newcommand{\pt}{\ensuremath{p_\tn{T}}}\newcommand{\pT}{\pt}
- % off by redefinding CKBNOTEje
-\newcommand{\CKBNOTE}[1]{{\bf CKB:  #1}} 
-\renewcommand{\CKBNOTE}[1]{}  % switch off
-
- % off by redefinding RHNOTE
-\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
-\renewcommand{\RHNOTE}[1]{}  % switch off
-
-\begin{titlepage}
-%
-\PHyear{2016}
-\PHnumber{xxx}                 % required, obtained from PH
-\PHdate{9 November}              % required, will be obtained from PH
-%
-%
-%%% Put your own title + short title here:
-\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-%\title{Higher order event-by-event flow harmonic correlations in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
-
-%
-%%% Do not change the nexts!
-\Collaboration{ALICE Collaboration%
-         \thanks{See Appendix~\ref{app:collab} for the list of collaboration
-                      members}}
-\ShortAuthor{ALICE Collaboration}      % appears on left page headers, do not change
-%
-\begin{abstract}
-
-The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
-in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
-This method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
-The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
-The comparisons to viscous hydrodynamic models demonstrate that
-the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
-The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
-$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
-% which is the least understood part of hydrodynamic calculations.
-%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
-%pt dependence ??
-Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
-on initial conditions and the transport properties of the system produced in heavy-ion collisions.
-\end{abstract}
-\end{titlepage}
-\setcounter{page}{2}
-
-% \input{main.tex}               %%%%%%%%%%% put the body of the article here
-
 % !TEX root = paper.tex
@@
 analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<\pt<5$~GeV/$c$ were selected. The charged track quality cuts
+and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
 described in~\cite{Aamodt:2010pa} were applied to minimize
@@
 the collision centrality. The reconstruction efficiency increases from
-70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
-constant at $(80 \pm 5)$\% for $\pt>1$~GeV/$c$. The estimated
+70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
+constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
 contamination by secondary charged particles from weak decays and
-photon conversions is less than 6\% at $\pt=0.2$~GeV/$c$ and falls
-below 1\% for $\pt>1$~GeV/$c$.
-With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
-at lower $\pt{}$, while the high $\pt{}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
+photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
+below 1\% for $p_{\rm T}>1$~GeV/$c$.
+With this choice of low $p_{\rm T}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
+at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
 Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
@@
 The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
 It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
@@
 The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
-However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{ig:Figure_4}.
+However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{fig:Figure_4}.
 % intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
@@
 The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
-
-%%%%%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
-\begin{acknowledgement}
-\section*{Acknowledgements}
-%\input{acknowledgements_jan2015.tex}    %%%%%%% get the lates version before submitting
-\end{acknowledgement}
-%
-%
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{apsrev4-1}   % Put here the style file name for the paper, i.e.apsrev4-1
-%\bibliography{biblio}
-%\input {bibliography.tex}  
-%
-
-% \bibliographystyle{mybibstyle}
-%\bibliographystyle{utphys}
-%\bibliography{paper}
-\bibliographystyle{utphys}
-\bibliography{paper}
-
-\newpage
-%
-%\input{}               %%%%%%%%%%% put your appendices here
-%
-%%%%%%%%% appendix with author list
-\appendix
-\section{The ALICE Collaboration}
-\label{app:collab}
-%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
-%\input{}              %%%%%%%%%%%% put the references here
-%
-\end{document}

### 2016-11-08 paper.tex
split to content and main

--- 2016-11-08 paper.tex
@@
 \newcommand{\AuAu}{\textnormal{Au--Au}}
-\newcommand{\pp}{\ensuremath{\mbox{p}\mbox{p}}}
 \newcommand{\tn}[1]{\textnormal{#1}}
 \newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
-\newcommand{\pt}{\ensuremath{p_\tn{T}}}\newcommand{\pT}{\pt}
  % off by redefinding CKBNOTEje
@@
 %%% Put your own title + short title here:
-\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
-%\title{Higher order event-by-event flow harmonic correlations in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV}
+\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV}
 \ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
@@
 \begin{abstract}
-
-The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
-in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
-This method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
-The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
-The comparisons to viscous hydrodynamic models demonstrate that
-the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
-The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
-$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
-% which is the least understood part of hydrodynamic calculations.
-%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
-%pt dependence ??
-Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
-on initial conditions and the transport properties of the system produced in heavy-ion collisions.
+\input{abstract.tex}
 \end{abstract}
@@
 
-% \input{main.tex}               %%%%%%%%%%% put the body of the article here
-
-% !TEX root = paper.tex
-
-\section{Introduction}
-
-%\textbf{{[A general history on HI]}}
-
-The main emphasis of the ultra-relativistic heavy-ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by the anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-This has been predicted by calculations utilising viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
-%and microscopic transport models ~\cite{Xu:2007jv}.  
-These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of QGP is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy-ion collisions at RHIC and LHC energies.
-
-The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
-For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
-This in turn may have important implications for other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
-
-%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
-
-\begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
-\label{Eq:Fourier}
-\end{equation}
-
-\noindent where $E$, $N$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the energy, particle yield, total momentum, transverse momentum, azimuthal angle and pseudorapidity of particles, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
-%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
-%\begin{equation}
-%\label{defVn}
-%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
-%\end{equation}
-%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
-%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations has led to triangular flow and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
-%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
-The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while correlations have the potential to discriminate the two respective contributions to anisotropic flow development~\cite{Niemi:2012aj}.
-And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
-
-However, difficulties on extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
-The viscous effects reduce the magnitude of the elliptic flow.
-Furthermore, the magnitude of $\eta/s$ used in these calculations should be considered as an average over the temperature history of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature.
-In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
-knowledge of both the temperature dependence and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.
-
-An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
-This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
-\begin{equation}
- \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
-  \label{eq:eccentricities}
-\end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for n=2 or 3).
-$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-Therefore the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
-When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
-%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
-
-Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
-It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
-In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include extensive comparisons to hydrodynamic and AMPT model calculations.
-In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
-The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
-Various theoretical models used in the article are described in Sec.~\ref{sec:models}.
-The results of the measurements are presented in Sec.~\ref{sec:results}.
- In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.
-
-% Experimental observables
-%% Flow correlations in general
-   % Niemi, ATLAS paper
-%% Symmetric Cumulants (SC)
-%% Normalized Symmetric Cumulants (NSC)
-%% Summary of results of 1st ALICE paper on SC
-%% Review of papers which cited ALICE 
-\section{Data Analysis}
-\label{sec:method}
-\subsection{Experimental Observables}
-%\subsubsection{cumulant analysis}
-
-While from existing measurements an estimate can be placed on the average value of QGP's $\eta/s$, both at RHIC and LHC energies, what remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
-This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
-The emerging consensus of late is that it is unlikely that the study of individual flow harmonics $v_n$ will reveal the details of $\eta/s(T)$ dependence.
-In fact, in was demonstrated already in the initial study~\cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
-In Ref.~\cite{Niemi:2012aj} new flow observables were introduced by the theorists, which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
-The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurements in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
-Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.
-
-For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
-The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
-
-The SC observables are defined as:
- %
-\begin{eqnarray}
-\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
-&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
-&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
-%&=&0\,.
-\label{eq:4p_cumulant}
-\end{eqnarray}
-%
-with the condition $m\neq n$ for two positive integers $m$ and $n$. The complete discussion can be found in Section IV C of Ref.~\cite{Bilandzic:2013kga}.
-
-SC($m$,$n$) can be normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$ to obtain \textit{normalized} symmetric cumulants~\cite{ALICE:2016kpq,Giacalone:2016afq}, which we denote by NSC($m$,$n$), i.e.
-%
-\begin{equation}
-\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
-\label{eq:nsc}
-\end{equation}
-%
-Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
-
-The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
-However, the details of the centrality dependence differ in the fluctutation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution.
-These results were also used to discriminate between different parameterizations of initial conditions and it was demonstrated that in the fluctuation-dominated regime (in central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-
-%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
-The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
-This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms.
-In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants.
-As a concrete example it was discussed that the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
-
-Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
-The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
-This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
-To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
-However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
-Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
-Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
-
-\subsection{Event and Track Selection}
-\label{sec:experiment}
-The data sample recorded by ALICE during the 2010 heavy-ion run at the
-LHC is used for this analysis. Detailed descriptions of the ALICE
-detector can be found
-in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
-Projection Chamber (TPC) was used to reconstruct charged particle
-tracks and measure their momenta with full azimuthal coverage in the
-pseudorapidity range $|\eta|<0.8$. Two scintillator
-arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
-and $2.8<\eta<5.1$ were used for triggering and the determination of
-centrality~\cite{Aamodt:2010cz}. The trigger
-conditions and the event selection criteria are identical to those
-described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
-Approximately $10^7$ minimum-bias $\PbPb$ events with
-a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point in the beam direction are used for this
-analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<\pt<5$~GeV/$c$ were selected. The charged track quality cuts
-described in~\cite{Aamodt:2010pa} were applied to minimize
-contamination from secondary charged particles and fake tracks.
-The reconstruction efficiency and contamination of charged particles
-were estimated from {\sc HIJING} Monte Carlo
-simulations~\cite{Wang:1991hta} combined with a {\sc
-GEANT3}~\cite{Brun:1994aa} detector model and were found to be independent of
-the collision centrality. The reconstruction efficiency increases from
-70\% to 80\% for particles with $0.2<\pt<1$~GeV/$c$ and remains
-constant at $(80 \pm 5)$\% for $\pt>1$~GeV/$c$. The estimated
-contamination by secondary charged particles from weak decays and
-photon conversions is less than 6\% at $\pt=0.2$~GeV/$c$ and falls
-below 1\% for $\pt>1$~GeV/$c$.
-With this choice of low $\pt{}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
-at lower $\pt{}$, while the high $\pt{}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
-Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced
-in the detector material, particles from weak decays, etc.). 
-Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.
-
-\subsection{Systematic Uncertainties}
-\label{sec:uncertainties}
-%\textbf{\tmp{[Track selection criteria.]}}
-
-%p10================================================================================
-
-%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}
-
-The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
-All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
-The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
-The contributions from different sources were then added in quadrature to obtain the final value of the systematic uncertainty.
-
-The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination.
-The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
-The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
-an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
-The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
-
-The analyzed events were recorded with two settings of the magnetic field polarities and the resulting data sets have almost the same number of events.
-Events with both magnetic polarizations were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
-Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions.
-The effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty.
-Magnetic polarizations and reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
-
-The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
-To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
-Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
-The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$.
-The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
-
-One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
-In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
-Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
-For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
-Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing.
-%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
-
-\section{Theoretical models}
-\label{sec:models}
-We have used various models in this article.
-The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
-%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.
-
-We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
-%\textbf{Need a short descriotion of event-by-event viscous hydrody-namic calculations from VISH2+1}.
-
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical model for relativistic heavy-ion collisions based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well tuned transport coefficients, decoupling temperature  and some initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
-The model then introduces the string melting procedure to produce initial partons.
-These partons are then evolved for the short duration using the ZPC parton cascade model.
-Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
-Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-
-Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy.
-To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
-For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model.
-In the default version, partons are recombined with their parent strings when they stop interacting.
-The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
-In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
-These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
-The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
-It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
-
-%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
-Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
-Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
-%
-
-\section{Results}
-\label{sec:results}
-
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
-        \label{fig:Figure_1}
-              \end{center}
-\end{figure}
-
-%The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
-Positive values of SC(4,2) are observed for all measured centralities.
-This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$.
-It also indicates that finding $v_2$ larger than average ($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average ($\langle v_4 \rangle$) in that event.
-On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average ($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average ($v_3 < \langle v_3 \rangle$).
-
-% \begin{figure}[htbp]
-%            \begin{center}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly.eps}}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
-%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_{\rm T}<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left).
-The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
-%              \label{fig:Figure_1}
-%              \end{center}
-% \end{figure}
-
-%\begin{figure}[h]
-%	\begin{center}
-%       	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC32_HIJING_ptdep.eps}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC42_HIJING_ptdep.eps}}
-%        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations.
-Defaults($0.2 < p_{\rm T} < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend.
-A small shifts along the x axis were applied for better visibility.}
-%        \label{fig:results_HIJING}
-%        \end{center}   
-%\end{figure}
-
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
-In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
-
-However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
-These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
-SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalize correlation between $v_5$ and $v_2$.
-
-It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
-In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
-NSC(5,3) shows the strongest centrality dependence among all harmonic correlations and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
-Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
-
-To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results.
-The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
-The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases. 
-%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
-NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
-This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
-As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
-The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase.
-These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
-3 in Ref.~\cite{Abelev:2012di}).
-%(see further discussions in Sec.~\ref{sec:ptdepsc})
-%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
-%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
-The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
-Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
-        \label{fig:Figure_2}
-        \end{center}   
-\end{figure}
-
-\pagebreak
-
-\section{Model Comparisons}
-\label{sec:theory}
-\subsection{Low Order Harmonic Correlations}
-SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the in Fig.~2 in Ref.~\cite{ALICE:2016kpq}.
-It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation will help to understand the fluctuations in initial conditions better.
-NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values.
-These observed distinct discrepancy between data and theoretical predictions indicate that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial state conditions and the fluctuations of the medium created in heavy-ion collisions.
-The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.
-
-The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
-However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
-Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
-SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
-
-\begin{figure}[!p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-         \label{fig:Figure_3}
-        \end{center}   
- \end{figure}
-
-Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
-The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
-Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
-The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
-This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
-Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
-
-In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
-NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
-The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure}
-
-\pagebreak
-
-\subsection{Higher Order Harmonic Correlations}
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
-
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
-              \end{center}
-        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
-This will be replaced with new figures once we have the calculations for Harri}
-        \label{fig:Figure_5}
-\end{figure}
-
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
-Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
-A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
-SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-        \label{fig:Figure_6}
-        \end{center}   
- \end{figure}
-
-The extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_7}.
-The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
-However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{ig:Figure_4}.
-% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
-In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
-The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and underestimates (or predicts very weak correlation) NSC(4,3).
-
-%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
-%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
-%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?
-
-As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0-10\% centrality range, we found that the same hierarchy also holds for the hydrodynamic calculations and the AMPT models in this article.
-The observed difference between SC(5,2) and SC(5,3) (SC(5,2) $>$ SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$ $>$ $v_3$). 
-The opposite trend are observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
-This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
-NSC($m$,$n$) correlators increase with the larger $\eta/s$ in hydrodynamic calculations in 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
-In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_7}
-        \end{center}   
- \end{figure}
-
-\pagebreak
-\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
-\label{sec:ptdepsc}
-
-It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
-In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
-NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
-This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
-The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
-
-\begin{figure}[htbp]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
-              \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-             \label{fig:Figure_8}
-\end{figure}
-
-\pagebreak
-
-\section{Summary}
-\label{sec:summary}
-In this article, we repot the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
-The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.
-It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and be free from symmetry plane correlations.
-We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.
-This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
-We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies.
-Furthermore, the sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation might help to understand the details of the fluctuations in initial conditions.
-The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations.
-Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data.
-A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
-The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+\input{longSC.tex}               %%%%%%%%%%% put the body of the article here
 

### 2016-11-08 makediff.sh
remove paper_prc

@@ -1,4 +1,4 @@
 #!/bin/bash 
 #1. version to PC 7f420a7
 #2. merge sec to one file 2cfb30f
-../git-latexdiff/git-latexdiff 7f420a7 $1
+../git-latexdiff/git-latexdiff --main paper.tex 7f420a7 $1

### 2016-11-09 longSC.tex
small correction

@@
 The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.
-It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and be free from symmetry plane correlations.
-We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities.
+It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
+We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities.
 This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.

### 2016-11-09 longSC.tex
changed the place of figures

@@
 
-\begin{figure}[htbp]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
-        \label{fig:Figure_1}
-              \end{center}
-\end{figure}
-
 %The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
@@
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
+
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
+        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
+Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
+        \label{fig:Figure_1}
+              \end{center}
+\end{figure*}
+
 The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
@@
 
-\begin{figure}[p]
+\begin{figure*}
 	\begin{center}
@@
         \end{center}   
-\end{figure}
-
-\pagebreak
+\end{figure*}
 
@@
 
+\begin{figure*}[h]
+	\begin{center}
+        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
+Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+         \label{fig:Figure_3}
+        \end{center}   
+ \end{figure*}
+
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
@@
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
+Hence the Glauber initial condition with $\eta/s=0.20$ can be ruled out.
+We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
 
-\begin{figure}[!p]
+\begin{figure*}[!]
 	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-         \label{fig:Figure_3}
+        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations.
+Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+        \label{fig:Figure_4}
         \end{center}   
- \end{figure}
+ \end{figure*}
 
@@
 The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
+It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as it was demonstrated for SC(3,2).
 Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.
-
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure}
-
-\pagebreak
 
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[h]
             \begin{center}
@@
 The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
-This will be replaced with new figures once we have the calculations for Harri}
+This will be replaced with new figures once we have the calculations from Harri Niemi et.
+al~\cite{Niemi:2015qia}.}
         \label{fig:Figure_5}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[p]
+\begin{figure*}[!]
 	\begin{center}
@@
         \end{center}   
- \end{figure}
+ \end{figure*}
+
+ \begin{figure*}[h]
+	\begin{center}
+        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
+        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
+        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations.
+Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+        \label{fig:Figure_7}
+        \end{center}   
+ \end{figure*}
 
@@
 
-\begin{figure}[p]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_7}
-        \end{center}   
- \end{figure}
+\pagebreak
 
-\pagebreak
 \subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
@@
 In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
+
+\begin{figure}[p]
+             \begin{center}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
+              \end{center}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+             \label{fig:Figure_8}
+\end{figure}
+
 NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
@@
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
-
-\begin{figure}[htbp]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
-              \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-             \label{fig:Figure_8}
-\end{figure}
 

### 2016-11-09 makediff.sh

@@ -1,4 +1,4 @@
 #!/bin/bash 
 #1. version to PC 7f420a7
 #2. merge sec to one file 2cfb30f
-../git-latexdiff/git-latexdiff --main paper.tex 7f420a7 $1
+../git-latexdiff/git-latexdiff --main paper.tex d0c5866 a53b9e1

### 2016-11-09 longSC.tex
change the figures and small update on text

@@
         	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations.
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
 Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations.
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models.
 Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.

### 2016-11-10 abstract.tex
fix some spelling errors

@@
 $v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
+This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.
 % which is the least understood part of hydrodynamic calculations.

### 2016-11-10 longSC.tex
fix some spelling errors

@@
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-This has been predicted by calculations utilising viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
+This has been predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
 %and microscopic transport models ~\cite{Xu:2007jv}.  
@@
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be caculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
 Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
@@
 Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
+The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analyzed symmetry plane correlators. 
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
@@
 For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
-Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most realiable way (i.e.
+Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most reliable way (i.e.
 nearly insensitive to nonflow) the correlation of amplitudes of two different flow harmonics.
@@
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the psedorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
+On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the pseudorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
 
 The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
-However, the details of the centrality dependence differ in the fluctutation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
+However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
 Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution.
@@
 The reconstruction efficiency and contamination of charged particles
-were estimated from {\sc HIJING} Monte Carlo
-simulations~\cite{Wang:1991hta} combined with a {\sc
-GEANT3}~\cite{Brun:1994aa} detector model and were found to be independent of
+were estimated from HIJING Monte Carlo
+simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
 the collision centrality. The reconstruction efficiency increases from
@@
 
-The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
+The systematic uncertainty due to the track reconstruction was estimated using two additional tracking criteria, first relying on the so-called standalone TPC tracking with the 
 same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
@@
 We have used various models in this article.
-The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
+The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
 %Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
@@
 We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
-%\textbf{Need a short descriotion of event-by-event viscous hydrody-namic calculations from VISH2+1}.
+The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
+%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
 
@@
 However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitute is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
+NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
 These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
-SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalize correlation between $v_5$ and $v_2$.
+SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
 
@@
 On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
-However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
+Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
+NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
+However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
 Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
@@
         \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
+The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.
 This will be replaced with new figures once we have the calculations from Harri Niemi et.
@@
 A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
+NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
 Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
+NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
+% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
 SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
@@
 However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{fig:Figure_4}.
-% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
+% interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
 In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
@@
 We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities.
-This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
+This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
 We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.

### 2016-11-10 longSC_prc.tex
putting pic version for test
add working pic version

--- 2016-11-09 longSC.tex
@@
-% !TEX root = paper.tex
+% !TEX root = prc.tex
 
@@
  %
+\begin{widetext}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\end{widetext}
 %
@@
 
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
+\begin{figure}[htp]
+\subfloat[SC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig2_QConly_higherSC.eps}}\\
+\subfloat[NSC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig2_QConly_higherNSC.eps}}
+%                       \resizebox{0.40\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
+%                       \resizebox{0.40\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
         \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
         \label{fig:Figure_1}
-              \end{center}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
+\begin{figure*}[htp]
+\subfloat[SC($m$,$n$) for $p_{\rm T}<0.7$~GeV/$c$ ]{\includegraphics[clip,width=\columnwidth]{figs/fig4_QConly_SC_ptdep}}
+\subfloat[NSC($m$,$n$) for $p_{\rm T}<0.7$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4_QConly_nSC_ptdep}}\\
+\subfloat[SC($m$,$n$) for $0.8<p_{\rm T}$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4b_QConly_SC_ptdep}}
+\subfloat[NSC($m$,$n$) $0.8<p_{\rm T}$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4b_QConly_SC_ptdep}}
+%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
+%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
+%	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
+%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
         \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
@@
         \label{fig:Figure_2}
-        \end{center}   
 \end{figure*}
@@
 \subsection{Low Order Harmonic Correlations}
+
+\begin{widetext}
+\begin{figure*}[htp]
+\subfloat[SC(3,2) and NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+\subfloat[SC(4,2) and NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
+Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+ \label{fig:Figure_3}
+ \end{figure*}
+ \end{widetext}
+
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
@@
 
-\begin{figure*}[h]
-	\begin{center}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-         \label{fig:Figure_3}
-        \end{center}   
+ \begin{figure*}[hpt]
+\subfloat[SC(3,2) and NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+\subfloat[SC(4,2) and NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}	
+%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
+Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+        \label{fig:Figure_4}
  \end{figure*}
@@
 We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
-
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
 
@@
 \subsection{Higher Order Harmonic Correlations}
+
+\begin{widetext}
+\begin{figure*}[hpt]
+\subfloat[SC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig1_QConly_hydro.eps}}
+\subfloat[NSC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig1_QConly_hydro_norm.eps}}
+%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
+%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
+          \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
+The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.
+This will be replaced with new figures once we have the calculations from Harri Niemi et.
+al~\cite{Niemi:2015qia}.}
+        \label{fig:Figure_5}
+\end{figure*}
+\end{widetext}
+
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
@@
 
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
-              \end{center}
-        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}.
-This will be replaced with new figures once we have the calculations from Harri Niemi et.
-al~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_5}
+\begin{figure*}[hpt]
+\subfloat[SC(5,2) and NSC(5,2)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
+\subfloat[SC(5,3) and NSC(5,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
+\subfloat[SC(4,3) and NSC(4,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+        \label{fig:Figure_6}
 \end{figure*}
@@
 A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
+NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
 Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
+NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
+% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
 SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
 
+\begin{widetext}
 \begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-        \label{fig:Figure_6}
-        \end{center}   
- \end{figure*}
-
- \begin{figure*}[h]
-	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+\subfloat[SC(5,2) and NSC(5,2)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
+\subfloat[SC(5,3) and NSC(5,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
+\subfloat[SC(4,3) and NSC(4,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
         \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models.
@@
         \label{fig:Figure_7}
-        \end{center}   
  \end{figure*}
+ \end{widetext}
 
@@
 
-\pagebreak
-
 \subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
 \label{sec:ptdepsc}
+
+\begin{figure}[htp]
+\subfloat[NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig5_QConly_xminpt_nSC32.eps}}\\
+\subfloat[NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig5_QConly_xminpt_nSC42.eps}}
+%              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
+%              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+             \label{fig:Figure_8}
+\end{figure}
 
@@
 In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
-
-\begin{figure}[p]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
-              \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-             \label{fig:Figure_8}
-\end{figure}
 
@@
 
-\pagebreak
-
 \section{Summary}

### 2016-11-10 abstract.tex
add You's comment just before the result part

@@
 The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics 
-in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
+have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
+The results were obtained with the multi-particle cumulant method dubbed symmetric cumulants.
 This method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
+The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
 The comparisons to viscous hydrodynamic models demonstrate that
-the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
-The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results.
+the different order harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
+The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements.
 $v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.

### 2016-11-10 longSC.tex
add You's comment just before the result part

@@
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass from nucleon position, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
 There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
@@
 The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analyzed symmetry plane correlators. 
-It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
+It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
 In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
@@
 %
-Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlation and individual $v_{n}$ harmonics.
+Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlations between two different flow harmonics and individual $v_{n}$ harmonics.
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.

### 2016-11-10 longSC.tex
add alice paper

@@
 where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass from nucleon position, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
 $v_n \propto \varepsilon_n$ for n=2 or 3).

### 2016-11-11 longSC.tex
adopt the final comment from You, version for IRC R1

@@
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
+Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
         \label{fig:Figure_1}
@@
 To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results.
-The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
+Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
 The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
-The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases. 
+The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
 %This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
+This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
@@
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Hence the Glauber initial condition with $\eta/s=0.20$ can be ruled out.
+Hence the MC-Glauber initial condition with $\eta/s=0.20$ can be ruled out.
 We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
@@
 Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
+As for SC(3,2), none of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
 The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.

### 2016-11-11 makediff.sh
first IRC round

@@ -1,4 +1,4 @@
 #!/bin/bash 
 #1. version to PC 7f420a7
 #2. merge sec to one file 2cfb30f
-../git-latexdiff/git-latexdiff --main paper.tex d0c5866 a53b9e1
+../git-latexdiff/git-latexdiff --main paper.tex 102db06 b4ddae2

### 2016-11-13 longSC_prc.tex
pre version

@@
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass from nucleon position, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
+There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
 $v_n \propto \varepsilon_n$ for n=2 or 3).
@@
  %
-\begin{widetext}
+\begin{widetext} %PRC
 \begin{eqnarray}
@@
 \end{eqnarray}
-\end{widetext}
+\end{widetext} %PRC
 %
@@
 
-\begin{figure}[htp]
-\subfloat[SC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig2_QConly_higherSC.eps}}\\
-\subfloat[NSC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig2_QConly_higherNSC.eps}}
-%                       \resizebox{0.40\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-%                       \resizebox{0.40\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
+\begin{figure}[hpt]
+            \begin{center}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
         \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
+Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
         \label{fig:Figure_1}
+              \end{center}
 \end{figure}
@@
 
-\begin{figure*}[htp]
-\subfloat[SC($m$,$n$) for $p_{\rm T}<0.7$~GeV/$c$ ]{\includegraphics[clip,width=\columnwidth]{figs/fig4_QConly_SC_ptdep}}
-\subfloat[NSC($m$,$n$) for $p_{\rm T}<0.7$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4_QConly_nSC_ptdep}}\\
-\subfloat[SC($m$,$n$) for $0.8<p_{\rm T}$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4b_QConly_SC_ptdep}}
-\subfloat[NSC($m$,$n$) $0.8<p_{\rm T}$~GeV/$c$]{\includegraphics[clip,width=\columnwidth]{figs/fig4b_QConly_SC_ptdep}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-%	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
+\begin{widetext} %PRC
+\begin{figure*}[hpt]
+	\begin{center}
+        	\resizebox{0.9\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
+        	\resizebox{0.9\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
+	\resizebox{0.9\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
+        	\resizebox{0.9\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
         \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
@@
         \label{fig:Figure_2}
+        \end{center}   
 \end{figure*}
+\end{widetext} %PRC
 
@@
 \subsection{Low Order Harmonic Correlations}
-
-\begin{widetext}
-\begin{figure*}[htp]
-\subfloat[SC(3,2) and NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-\subfloat[SC(4,2) and NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
- \label{fig:Figure_3}
- \end{figure*}
- \end{widetext}
-
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
@@
 
- \begin{figure*}[hpt]
-\subfloat[SC(3,2) and NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-\subfloat[SC(4,2) and NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}	
-%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-%        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
+\begin{widetext} %PRC
+\begin{figure*}
+	\begin{center}
+        	\resizebox{0.85\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+        	\resizebox{0.85\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
+Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+         \label{fig:Figure_3}
+        \end{center}   
  \end{figure*}
+\end{widetext} %PRC
 
@@
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Hence the Glauber initial condition with $\eta/s=0.20$ can be ruled out.
+Hence the MC-Glauber initial condition with $\eta/s=0.20$ can be ruled out.
 We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
 
+\begin{widetext} %PRC
+\begin{figure*}[!]
+	\begin{center}
+        	\resizebox{0.85\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+        	\resizebox{0.85\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
+Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+        \label{fig:Figure_4}
+        \end{center}   
+ \end{figure*}
+ \end{widetext} %PRC
+
 Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
+As for SC(3,2), none of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
 The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
@@
 \subsection{Higher Order Harmonic Correlations}
+The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
+First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
 
-\begin{widetext}
-\begin{figure*}[hpt]
-\subfloat[SC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig1_QConly_hydro.eps}}
-\subfloat[NSC($m$,$n$)]{\includegraphics[clip,width=\columnwidth]{figs/fig1_QConly_hydro_norm.eps}}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
+\begin{widetext} %PRC
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
+                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
+              \end{center}
         \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
@@
 \end{figure*}
-\end{widetext}
-
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
-
-\begin{figure*}[hpt]
-\subfloat[SC(5,2) and NSC(5,2)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-\subfloat[SC(5,3) and NSC(5,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-\subfloat[SC(4,3) and NSC(4,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
-        \label{fig:Figure_6}
-\end{figure*}
+\end{widetext} %PRC
 
@@
 
-\begin{widetext}
+\begin{widetext} %PRC     
 \begin{figure*}[!]
-\subfloat[SC(5,2) and NSC(5,2)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-\subfloat[SC(5,3) and NSC(5,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-\subfloat[SC(4,3) and NSC(4,3)]{\includegraphics[clip,width=0.7\columnwidth]{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+	\begin{center}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+        \label{fig:Figure_6}
+        \end{center}   
+ \end{figure*}
+\end{widetext} %PRC
+
+ \begin{widetext} %PRC 
+ \begin{figure*}[h]
+	\begin{center}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
+        	\resizebox{0.62\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
         \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models.
@@
         \label{fig:Figure_7}
+        \end{center}   
  \end{figure*}
- \end{widetext}
+ \end{widetext} %PRC
 
@@
 
+\pagebreak
+
 \subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
 \label{sec:ptdepsc}
-
-\begin{figure}[htp]
-\subfloat[NSC(3,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig5_QConly_xminpt_nSC32.eps}}\\
-\subfloat[NSC(4,2)]{\includegraphics[clip,width=\columnwidth]{figs/fig5_QConly_xminpt_nSC42.eps}}
-%              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-%              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-             \label{fig:Figure_8}
-\end{figure}
 
@@
 In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
+
+\begin{widetext} %PRC
+\begin{figure*}
+             \begin{center}
+              \resizebox{0.45\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
+              \resizebox{0.45\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
+              \end{center}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
+The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+             \label{fig:Figure_8}
+\end{figure*}
+\end{widetext} %PRC
 
@@
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
+
+\pagebreak
 

### 2016-11-17 longSC.tex
add videotext
figure change with a b c

@@
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass from nucleon position, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
+where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
 There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
@@
  %
+%\begin{widetext}
 \begin{eqnarray}
@@
 \end{eqnarray}
+%\end{widetext}
 %
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{The result of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
+Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the panel (a) are scaled down by factor of 10.}
         \label{fig:Figure_1}
@@
         	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right).
-The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
+        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)).
+The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
 Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}

### 2016-11-17 makediff.sh

@@ -1,4 +1,5 @@
 #!/bin/bash 
 #1. version to PC 7f420a7
 #2. merge sec to one file 2cfb30f
-../git-latexdiff/git-latexdiff --main paper.tex 102db06 b4ddae2
+#3. IRC first round : 7f129af
+../git-latexdiff/git-latexdiff --main paper.tex 7f129af $1

### 2016-12-01 abstract.tex
first IRC round
change figures, on the way llya's comment

@@
 have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the multi-particle cumulant method dubbed symmetric cumulants.
-This method is robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented.
-The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
-The comparisons to viscous hydrodynamic models demonstrate that
+The results were obtained with the multi-particle correlation observables dubbed symmetric cumulants.
+These observables are robust against systematic biases originating from non-flow effects. 
+The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$ and $v_4$ and $v_2$ correlations are presented.
+The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
+The comparison to viscous hydrodynamic model demonstrates that
 the different order harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
 The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements.
-$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions.
+Correlations between $v_2$ , $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.
-% which is the least understood part of hydrodynamic calculations.
-%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
-%pt dependence ??
 Together with the existing measurements of individual flow harmonics the presented results provide further constraints 

### 2016-12-01 longSC.tex
change figures, on the way llya's comment

@@
 Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations support as well the view that the QGP matter is close to that limit~\cite{Gale:2012rq}.
-This in turn may have important implications for other fundamental physics goals.
+Hydrodynamical simulations support as well the view that $\eta/s$ of the QGP matter is close to that limit~\cite{Gale:2012rq}.
+This may have important implications for other fundamental physics goals.
 It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in the Fourier series decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in the Fourier decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 
-\noindent where $E$, $N$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the energy, particle yield, total momentum, transverse momentum, azimuthal angle and pseudorapidity of particles, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-The $n^{\mathrm{th}}$-order flow coefficients are denoted as $v_n$ and can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
+\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
+$v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
 %Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
@@
 The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuations of the positions of the constituents inside the colliding nuclei, which in turn implies that the flow also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations has led to triangular flow and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as the correlations between different Fourier harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
+This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
+The recognition of the importance of flow fluctuations led to triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
 %The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
-The higher order harmonics are expected to be particularly sensitive to fluctuations in the initial conditions and to the $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while correlations have the potential to discriminate the two respective contributions to anisotropic flow development~\cite{Niemi:2012aj}.
-And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
+The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
+%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
 
-However, difficulties on extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
+However, difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
 The viscous effects reduce the magnitude of the elliptic flow.
-Furthermore, the magnitude of $\eta/s$ used in these calculations should be considered as an average over the temperature history of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature.
+Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature.
 In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
-knowledge of both the temperature dependence and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.
+knowledge of both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.
 
-An important input to the hydrodynamic simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
+An important input to the hydrodynamic model simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
 This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
 \begin{equation}
- \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\} 
+ \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
   \label{eq:eccentricities}
@@
 $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-Therefore the higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
 When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
@@
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is probably the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
+Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
 
@@
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include extensive comparisons to hydrodynamic and AMPT model calculations.
+In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+We also include extensive comparison to hydrodynamic and AMPT model calculations.
 In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
@@
 %% Review of papers which cited ALICE 
-\section{Data Analysis}
+%\section{Data Analysis}
+
+\section{Experimental Observables}
 \label{sec:method}
-\subsection{Experimental Observables}
 %\subsubsection{cumulant analysis}
 
-While from existing measurements an estimate can be placed on the average value of QGP's $\eta/s$, both at RHIC and LHC energies, what remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
+The existing measurements provide an estimate only of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
+What remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
 This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
-The emerging consensus of late is that it is unlikely that the study of individual flow harmonics $v_n$ will reveal the details of $\eta/s(T)$ dependence.
-In fact, in was demonstrated already in the initial study~\cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
-In Ref.~\cite{Niemi:2012aj} new flow observables were introduced by the theorists, which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
-The initial success of these new observables was attributed to their potential to discriminate for the first time the two respective contributions to anisotropic flow development---from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurements in turn would enable the experimental verification of theoretical predictions for individual stages of heavy-ion evolution independently.
-Besides this advantage, it turned out that correlations of different flow harmonics are sensitive to the details of $\eta/s(T)$ dependence~\cite{ALICE:2016kpq}, to which individual flow harmonics are nearly insensitive~\cite{Niemi:2015qia}.
+The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
+It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
+In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
+These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
+Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently.
+In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
 
-For technical reasons, discussed in detail in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced by the theorists in Ref.~\cite{Niemi:2012aj}.
-Instead, in~\cite{Bilandzic:2013kga} the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced to quantify in the most reliable way (i.e.
-nearly insensitive to nonflow) the correlation of amplitudes of two different flow harmonics.
-The technical details are elaborated in Ref.~\cite{Bilandzic:2013kga}, while the first measurements of SC observables were recently released by ALICE Collaboration in Ref.~\cite{ALICE:2016kpq}.
+For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}.
+Based on \cite{Bilandzic:2013kga}, the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced.
+SC observables are nearly insensitive to nonflow and quantify the correlation of amplitudes of two different flow harmonics.
+The first measurements of SC observables were recently published by ALICE Collaboration in \cite{ALICE:2016kpq}.
 
-The SC observables are defined as:
+The SC observables are defined as (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}):
  %
@@
 %
-with the condition $m\neq n$ for two positive integers $m$ and $n$. The complete discussion can be found in Section IV C of Ref.~\cite{Bilandzic:2013kga}.
-
-SC($m$,$n$) can be normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$ to obtain \textit{normalized} symmetric cumulants~\cite{ALICE:2016kpq,Giacalone:2016afq}, which we denote by NSC($m$,$n$), i.e.
+with the condition $m\neq n$ for two positive integers $m$ and $n$.
+In this article SC($m$,$n$) normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq}, is denoted by NSC($m$,$n$):
 %
@@
 Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlations between two different flow harmonics and individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations and using a pseudorapidity gap of $|\Delta\eta|>1.0$ to suppress biases from few-particle nonflow correlations.
-On the other hand, in the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the pseudorapidity gap is not needed, since nonflow is suppressed by construction in SC observable, as the study based on HIJING model has clearly demonstrated in Ref.~\cite{ALICE:2016kpq}.
+In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
+For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
+This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.
 
-The first measurements of SC observables have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
+The ALICE measurements with \cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
 However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-Most importantly, the centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature plays an important role in describing QGP's $\eta/s$ dependence in various stages of heavy-ion evolution.
-These results were also used to discriminate between different parameterizations of initial conditions and it was demonstrated that in the fluctuation-dominated regime (in central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+The observed centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature dependence plays an important role.
+These results were also used to discriminate between different parameterizations of initial conditions.
+It was demonstrated that in the fluctuation-dominated regime (central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
 
 %\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
-The SC observables provide orthogonal information to recently measured symmetry plane correlators in Refs.~\cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
+The SC observables provide independent information to that obtained from recently measured symmetry plane correlators in \cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
 This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms.
 In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants.
-As a concrete example it was discussed that the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
+As an  example, the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
 

### 2016-12-01 longSC.tex
finish lly's comment

@@
 
-\subsection{Event and Track Selection}
+\section{Data Analysis}
 \label{sec:experiment}
-The data sample recorded by ALICE during the 2010 heavy-ion run at the
+A sample of $\PbPb$ collisions at $\snn=2.76$~TeV recorded by ALICE during the 2010 heavy-ion run at the
 LHC is used for this analysis. Detailed descriptions of the ALICE
@@
 a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point in the beam direction are used for this
-analysis. Charged particles reconstructed in the TPC in $|\eta|<0.8$
+interaction point in the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
 and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
@@
 below 1\% for $p_{\rm T}>1$~GeV/$c$.
-With this choice of low $p_{\rm T}$ cut-off we are reducing event-by-event biases from smaller reconstruction efficiency 
-at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ was introduced to reduce the contribution to the anisotropies from jets. 
-Reconstructed tracks were required to have at least 70 TPC space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted to reduce the contamination from secondary tracks (for instance the charged particles produced
-in the detector material, particles from weak decays, etc.). 
+The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
+at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the contribution to the anisotropies from jets. 
+Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
+Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted.
+This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
 Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.
 
-\subsection{Systematic Uncertainties}
+\section{Systematic Uncertainties}
 \label{sec:uncertainties}
@@
 The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
-The contributions from different sources were then added in quadrature to obtain the final value of the systematic uncertainty.
+The contributions from different sources were added in quadrature to obtain the total systematic uncertainty.
 
-The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution of centrality determination.
-The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the default, V0 detectors.
-The systematic uncertainties from the centrality determinations were about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
+The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution.
+The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of V0 detectors.
+The systematic uncertainty from the centrality determinations is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
 
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
-an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
+a uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
 The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
 
-The analyzed events were recorded with two settings of the magnetic field polarities and the resulting data sets have almost the same number of events.
-Events with both magnetic polarizations were used for the default analysis and the systematic uncertainties were evaluated from the results from each of two polarized magnetic field settings.
-Moreover, because of incompleteness of track reconstruction, correction steps are necessary to trace back from reconstructed tracks to the originally generated particles from the collisions.
-The effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty.
-Magnetic polarizations and reconstruction efficiency effects are relatively small and difference from the default settings were less than 2\%.
+The analyzed events were recorded with two settings of the L3 magnet polarity and the resulting data sets have almost the same number of events.
+Events with both magnet polarity were used for the default analysis and the systematic uncertainties were evaluated from variation between each of two magnetic field settings.
+Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. Magnetic polarity variation and reconstruction efficiency effects are less than 2\%.
 
-The systematic uncertainty due to the track reconstruction was estimated using two additional tracking criteria, first relying on the so-called standalone TPC tracking with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
+The systematic uncertainty due to the track reconstruction was estimated from comparison between results for the so-called standalone TPC tracks with the 
+same parameters as described in Sec.~\ref{sec:experiment}, and combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
 To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
 Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
-The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$.
-The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
+The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
+In addition, we applied the like-sign technique to estimate non-flow contribution in SC$(m,n)$.
+The difference between two charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
 
-One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
-In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
-Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data.
-For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
-Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing.
+Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
+In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
+Detector inefficiencies was introduced to mimic non-uniform azimuthal distribution in the data.
+For the observables SC(5,2), SC(5,3) and SC(4,3) variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
+Overall, the systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
+This is because $v_{n}$ are decreasing with n increasing and become more sensitive to azimuthal modulation due to detector imperfections. 
 %Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
@@
 \label{sec:models}
-We have used various models in this article.
+%We have used various models in this article.
 The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
@@
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-
 We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
@@
 
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical model for relativistic heavy-ion collisions based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well tuned transport coefficients, decoupling temperature  and some initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
+With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei.
+Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
+In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
@@
 
-Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy.
+The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
+Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
 To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
@@
 In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
+The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
 The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
@@
 
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from \cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The result of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the panel (a) are scaled down by factor of 10.}
+        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
+Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the panel (a) are scaled by factor of 0.1.}
         \label{fig:Figure_1}
@@
 
-However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
+However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
 NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
@@
 In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
-NSC(5,3) shows the strongest centrality dependence among all harmonic correlations and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
+NSC(5,3) shows the strongest correlation among all harmonics and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
 Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
 
-To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we change the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ interval, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
+The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
 The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
@@
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
-This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
+The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
+This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of $\left<v_n\right>$ values. 
 The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
-As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
+While SC$(m,n)$ show the similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$ or the centrality.
 The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
@@
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the in Fig.~2 in Ref.~\cite{ALICE:2016kpq}.
+The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
@@
 In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation will help to understand the fluctuations in initial conditions better.
+This observation helps to understand better the fluctuations in initial energy density.
 NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values.
-These observed distinct discrepancy between data and theoretical predictions indicate that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial state conditions and the fluctuations of the medium created in heavy-ion collisions.
+This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
+The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions.
 The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.
@@
         	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
+        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines.
+}
          \label{fig:Figure_3}
@@
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
+Similarly to hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
 NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
@@
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Hence the MC-Glauber initial condition with $\eta/s=0.20$ can be ruled out.
-We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.
+Hence the calculations with large $\eta/s=0.20$ is ruled out.
+We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.
 
@@
         	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT models.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
+        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models.
+Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).
 The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
@@
 
-Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), none of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest.
-The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
-Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
-The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
-This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
+The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
+As for SC(3,2), none of the calculations can describe the data and calculation with the default AMPT setting follows the trend of the data closest.
+The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
+Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
+The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
+The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
 Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
@@
 NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
-The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
+The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
 It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as it was demonstrated for SC(3,2).
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
@@
 
-\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
+\subsection{Transverse Momentum Dependence of Correlations between $v_2$, $v_3$ and $v_4$}
 \label{sec:ptdepsc}
@@
 In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
-The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC) method.
-It was demonstrated in the recent ALICE paper that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
+The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC).
+It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
 We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities.
-This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
-We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies.
-Furthermore, the sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-Hence this observation might help to understand the details of the fluctuations in initial conditions.
+This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
+It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
+Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
+The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
+In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role.
+This observation might help to understand the details of the fluctuations in initial conditions.
 The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations.

### 2016-12-01 longSC.tex
one missing, also alice's comment

@@
 Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analyzed symmetry plane correlators. 
+The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.

### 2016-12-02 longSC.tex
version to sami

@@
 
-The existing measurements provide an estimate only of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
-What remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$).
+The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
+What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2015qia}.
 This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
@@
 It was demonstrated that in the fluctuation-dominated regime (central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-
-%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
-The SC observables provide independent information to that obtained from recently measured symmetry plane correlators in \cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}.
-This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms.
-In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants.
-As an  example, the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.
-
-Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
-The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
-This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
-To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
-However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
-Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
-Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
 
@@
 
-Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency.
+Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency in azimuthal angle.
 In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
@@
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
+Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
 %The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
@@
 
-%The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}.
-Positive values of SC(4,2) are observed for all measured centralities.
-This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$.
-It also indicates that finding $v_2$ larger than average ($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average ($\langle v_4 \rangle$) in that event.
-On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average ($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average ($v_3 < \langle v_3 \rangle$).
-
-% \begin{figure}[htbp]
-%            \begin{center}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly.eps}}
-%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
-%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_{\rm T}<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left).
-The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
-%              \label{fig:Figure_1}
-%              \end{center}
-% \end{figure}
-
-%\begin{figure}[h]
-%	\begin{center}
-%       	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC32_HIJING_ptdep.eps}}
-%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC42_HIJING_ptdep.eps}}
-%        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations.
-Defaults($0.2 < p_{\rm T} < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend.
-A small shifts along the x axis were applied for better visibility.}
-%        \label{fig:results_HIJING}
-%        \end{center}   
-%\end{figure}
-
 The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from \cite{ALICE:2016kpq}.
@@
 However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
+NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the panel (b) in Fig.~\ref{fig:Figure_1}.
 These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
@@
 
-It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
+It can be seen on the panel (a) in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
 In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
@@
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
+The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the panel (a) in Fig.~\ref{fig:Figure_2}.
 The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
@@
 This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
-NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
+NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the panel (b) and (d) in Fig.~\ref{fig:Figure_2}.
 The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of $\left<v_n\right>$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the panel (c) and (d) in Fig.~\ref{fig:Figure_2}.
 While SC$(m,n)$ show the similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$ or the centrality.
@@
 	\begin{center}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
+        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
+        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
+	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
+        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
         \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)).
@@
 The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+
+\section{Discussion}
+Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
+The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
+This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
+To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
+However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
+Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
+Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
+Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
+%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

### 2016-12-02 longSC.tex
add reference and moving model to the comparison part

@@
 This may have important implications for other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
+It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc,Csernai:2006zz}.
 %which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
@@
 The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
-What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2015qia}.
+What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2011ix,Niemi:2015qia}.
 This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
@@
 
-\section{Theoretical models}
-\label{sec:models}
-%We have used various models in this article.
-The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
-%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
-%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
-
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
-The model then introduces the string melting procedure to produce initial partons.
-These partons are then evolved for the short duration using the ZPC parton cascade model.
-Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
-Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-
-The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
-To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
-For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model.
-In the default version, partons are recombined with their parent strings when they stop interacting.
-The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
-In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
-These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
-The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
-It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
-
-%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
-Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
-Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
-%
-
 \section{Results}
@@
 \label{sec:theory}
+\subsection{Theoretical models}
+\label{sec:models}
+%We have used various models in this article.
+The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
+%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
+%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
+We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions.
+%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
+
+The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
+With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
+Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
+In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei.
+For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
+Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
+%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
+The model then introduces the string melting procedure to produce initial partons.
+These partons are then evolved for the short duration using the ZPC parton cascade model.
+Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
+Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
+
+The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
+Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
+To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
+For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
+The AMPT model can be run in two main configurations, the default and the string melting model.
+In the default version, partons are recombined with their parent strings when they stop interacting.
+The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
+In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
+These partons are then combined into the final state hadrons via a quark coalescence model.
+In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
+The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
+The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
+The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+
+%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
+Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
+Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
+
+%
+
 \subsection{Low Order Harmonic Correlations}
@@
 The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), none of the calculations can describe the data and calculation with the default AMPT setting follows the trend of the data closest.
+As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest.
 The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
@@
 
+We list here a few important findings from the model comparison:
+\begin{itemize}
+	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
+This hierarchy is well reproduced by hydrodynamic model calculations and AMPT model calculations.
+	\item All the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
+	\item Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
+	\item The sign of $v_3$ and $v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item The default AMPT model can describe NSC quantitively.
+	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
+\end{itemize}
+
 \pagebreak

### 2016-12-02 longSC.tex
accepting ante's comment

@@
 
-However, difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
+Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
 The viscous effects reduce the magnitude of the elliptic flow.
@@
 $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics ~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
 When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
@@
 The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+The results of the measurements are presented in Sec.~\ref{sec:results}.
+ In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations.
 Various theoretical models used in the article are described in Sec.~\ref{sec:models}.
-The results of the measurements are presented in Sec.~\ref{sec:results}.
- In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.
+Sec.~\ref{sec:summary} summarizes our findings.
 
@@
 In addition, we applied the like-sign technique to estimate non-flow contribution in SC$(m,n)$.
-The difference between two charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
+The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and it is about 7\% for SC(4,3) and 20\% for SC(5,3).
 
@@
 A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
+The default configuration of AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most of centralities and for most combinations of harmonics which were considered.
+Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminating between theoretical models.
+Finally, we have found that $v_3$ and $v_2$, $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.

### 2016-12-03 longSC.tex
model name

@@
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+We have compared the centrality dependence of our observables with the EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
 The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
@@
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
@@
 It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
-We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities.
+We have found that fluctuations of $v_3$-$v_2$ and $v_4$-$v_3$ are anti-correlated in all centralities while fluctuations of $v_4$-$v_2$, $v_5$-$v_2$ and $v_5$-$v_3$ are correlated for all centralities.
 This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.

### 2016-12-03 longSC.tex
add the list

@@
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-We have compared the centrality dependence of our observables with the EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+We have compared the centrality dependence of our observables with the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
 The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
@@
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
-The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
@@
 
-We list here a few important findings from the model comparison:
-\begin{itemize}
+We list here important findings from the model comparison:
+\begin{enumerate}[(i)]
+	\item All the VISH2+1 model calculations with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better in general but it cannot describe the data quantitively for most of the centrality ranges.
+	\item The correlation strength of $v_3$ and $v_2$,  $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is underestimated in hydrodynamic model calculations.
+	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of centralities.
+	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
 	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-This hierarchy is well reproduced by hydrodynamic model calculations and AMPT model calculations.
-	\item All the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
-	\item Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-	\item The sign of $v_3$ and $v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe NSC quantitively.
-	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
-\end{itemize}
+This hierarchy is well reproduced both by hydrodynamic and AMPT model calculations.
 
-\pagebreak
+\end{enumerate}
 

### 2016-12-03 longSC.tex
add sami's comment

@@
 The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
-What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2011ix,Niemi:2015qia}.
-This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
+What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$).
+The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}.
+The effects to hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.
+A more systematic study with the event-by-event EKRT+viscous hydrodynamic calculations has been just initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
 The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
@@
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
-For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~\ref{eq:4p_cumulant} the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
+For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
 This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.
 
-The ALICE measurements with \cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
+The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
 However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
@@
 
-However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
+However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
 NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the panel (b) in Fig.~\ref{fig:Figure_1}.
@@
 The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
+This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Fig.~11-13 in \cite{Niemi:2015qia}).
 Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
@@
 The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
+Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
 To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.

### 2016-12-03 longSC.tex
ampt footnote

@@
 
+\begin{figure*}
+	\begin{center}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
+	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
+        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)).
+The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
+Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
+        \label{fig:Figure_2}
+        \end{center}   
+\end{figure*}
+
 To study the $p_{\rm T}$ dependence of SC$(m,n)$, we change the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ interval, in order to avoid large statistical fluctuations in the results.
@@
 %However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
-
-\begin{figure*}
-	\begin{center}
-        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)).
-The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
-Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
-        \label{fig:Figure_2}
-        \end{center}   
-\end{figure*}
 
@@
 For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model.
+The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
 In the default version, partons are recombined with their parent strings when they stop interacting.
@@
 The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
-The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
 Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
@@
 Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
-%
 
@@
 	\begin{center}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
         \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
@@
  \end{figure*}
-
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
@@
 	\begin{center}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
         \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models.
@@
  \end{figure*}
-
 The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.

### 2016-12-03 longSC.tex
need to add eta/s(T)

@@
  \end{figure*}
+
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
@@
 \begin{enumerate}[(i)]
+	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
 	\item All the VISH2+1 model calculations with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.

### 2016-12-04 longSC.tex
finalizing the text and comment

@@
  In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations.
-Various theoretical models used in the article are described in Sec.~\ref{sec:models}.
+Various theoretical models used in the article are described in Sec.~\ref{sec:theory}.
 Sec.~\ref{sec:summary} summarizes our findings.
@@
 \label{sec:theory}
-\subsection{Theoretical models}
-\label{sec:models}
+%\subsection{Theoretical models}
+%\label{sec:models}
 %We have used various models in this article.
@@
 This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Fig.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~14 in \cite{Niemi:2015qia}). 
 %\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
@@
 
+\begin{figure*}[!]
+	\begin{center}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).}
+        \label{fig:Figure_4}
+        \end{center}   
+ \end{figure*}
+
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
@@
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly to hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
-However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
+Similarly to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
+NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described by these models quantitively.
+However NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
 Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
@@
 
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models.
-Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
 The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.}
         \label{fig:Figure_7}
@@
 	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of centralities.
+	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of centralities while the string melting AMPT model fails to describe them.
 	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
-	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-This hierarchy is well reproduced both by hydrodynamic and AMPT model calculations.
+	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is well reproduced both by hydrodynamic and AMPT model calculations.
 
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.
-The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.}
              \label{fig:Figure_8}

### 2016-12-04 longSC.tex
final for IRC2

@@
 
-\section{Discussion}
-Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
+%\section{Discussion}
+%Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
 The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
@@
 Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
-Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
+%Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
 %%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

### 2016-12-04 longSC.tex
final version to IRC R2

@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
-The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}.
+The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
 \noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
@@
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of centralities while the string melting AMPT model fails to describe them.
-	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
+	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
 	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is well reproduced both by hydrodynamic and AMPT model calculations.
@@
 The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
+%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
 

### 2016-12-04 makediff.sh

@@ -2,4 +2,5 @@
 #1. version to PC 7f420a7
 #2. merge sec to one file 2cfb30f
 #3. IRC first round : 7f129af
-../git-latexdiff/git-latexdiff --main paper.tex 7f129af $1
+#../git-latexdiff/git-latexdiff --main paper.tex 7f129af $1
+../git-latexdiff/git-latexdiff --main paper.tex master IRCR1

### 2016-12-05 longSC.tex
final version for IRC R2

@@
         	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)).
+        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
@@
 
-\begin{figure*}[h]
-	\begin{center}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
-        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines.
-}
-         \label{fig:Figure_3}
-        \end{center}   
- \end{figure*}
-
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
-
 The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
@@
 We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.
+
+\begin{figure*}[!]
+	\begin{center}
+        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
+Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
+        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines.
+}
+         \label{fig:Figure_3}
+        \end{center}   
+ \end{figure*}
+
+\begin{figure*}[!]
+	\begin{center}
+        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).}
+        \label{fig:Figure_4}
+        \end{center}   
+ \end{figure*}
 
@@
 
-\begin{figure*}[h]
+\begin{figure*}[!]
             \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_32.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
               \end{center}
-        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
 The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.
-This will be replaced with new figures once we have the calculations from Harri Niemi et.
+These SC(3,2) and SC(4,2) will be replaced with new figures for higher order correlations once we have the calculations from Harri Niemi et.
 al~\cite{Niemi:2015qia}.}
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
@@
 
- \begin{figure*}[h]
+ \begin{figure*}[!]
 	\begin{center}
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT models. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
+Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.}
         \label{fig:Figure_7}
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models.}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
              \label{fig:Figure_8}

### 2016-12-05 longSC.tex
figure style change

@@
               \end{center}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to hydrodynamic calculations.
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.

### 2016-12-05 abstract.tex

@@
 These observables are robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$ and $v_4$ and $v_2$ correlations are presented.
+The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$, $v_4$ and $v_2$ correlations are presented.
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
 The comparison to viscous hydrodynamic model demonstrates that
-the different order harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
+the different order harmonic correlations respond differently to the initial conditions or the temperature dependence of the shear viscosity to the entropy density ratio ($\eta/s$).
 The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements.
-Correlations between $v_2$ , $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
+Correlations between $v_2$, $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.

### 2016-12-05 longSC.tex
small english correction

@@
 SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Hence the calculations with large $\eta/s=0.20$ is ruled out.
+Hence these calculations with large $\eta/s=0.20$ are ruled out.
 We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.
@@
 As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest.
-The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
+The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe either of them in the most central collisions.
 Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
@@
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
+All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber, and $\eta/s=0.16$ for AMPT initial conditions) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
 Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
@@
 As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
+When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength gets weaker by the hadronic rescattering.
 This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.

### 2016-12-06 abstract.tex
alice's comment English first part

--- 2016-12-01 abstract.tex
@@
-The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics 
+The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
 have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
 The results were obtained with the multi-particle correlation observables dubbed symmetric cumulants.
-These observables are robust against systematic biases originating from non-flow effects. 
-The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$ and $v_4$ and $v_2$ correlations are presented.
+These observables are robust against biases originating from non-flow effects. 
+The centrality dependence of correlations between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$), as well as the transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ are presented.
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
-The comparison to viscous hydrodynamic model demonstrates that
-the different order harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$).
-The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements.
-Correlations between $v_2$ , $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.
-Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
+The comparisons to viscous hydrodynamic models demonstrate that
+the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
+A small $\eta/s$ is favored regardless of initial conditions and the AMPT initial condition yield results closest to the measurements. 
+Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
+This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.
+Together with existing measurements of individual flow harmonics, the results presented here provide further constraints 
 on initial conditions and the transport properties of the system produced in heavy-ion collisions.

### 2016-12-06 longSC.tex
alice's comment English first part

@@
 
-The main emphasis of the ultra-relativistic heavy-ion collisions at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study deconfined phase of the strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by the anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} continues to increase also at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
+The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
+This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
 This has been predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
 %and microscopic transport models ~\cite{Xu:2007jv}.  
-These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of QGP is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de} in heavy-ion collisions at RHIC and LHC energies.
+These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.
 
-The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey.
+The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
 For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations support as well the view that $\eta/s$ of the QGP matter is close to that limit~\cite{Gale:2012rq}.
+It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
 This may have important implications for other fundamental physics goals.
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc,Csernai:2006zz}.
+It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
 %which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in the Fourier decomposition of particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 %One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow in heavy-ion collisions is understood as hydrodynamic response of produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
+The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
 This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations led to triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
+The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
 %The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
@@
 
-Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
-The viscous effects reduce the magnitude of the elliptic flow.
-Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ of other fluids depends on temperature.
+Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions in the models used for comparison~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
+Viscous effects also reduce the magnitude of the elliptic flow.
+Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ depends on temperature.
 In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
-knowledge of both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify $\eta/s$ of the partonic fluid.
+both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify the $\eta/s$ of the QGP.
 
-An important input to the hydrodynamic model simulations is the distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
+An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
 This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
@@
 where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There are experimental and theoretical evidences~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for n=2 or 3).
+There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+$v_n \propto \varepsilon_n$ for $n$=2 or 3).
 $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-The higher harmonics ($n>3$) could be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
-When the order of harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and become larger for more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
+The higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
+The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence the studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood part of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
+Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
 
-Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
+Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
 The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
-It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include extensive comparison to hydrodynamic and AMPT model calculations.
+It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
+In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as measured the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+We also include extensive comparisons to hydrodynamic and AMPT model calculations.
 In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
-The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
 The results of the measurements are presented in Sec.~\ref{sec:results}.
  In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations.
-Various theoretical models used in the article are described in Sec.~\ref{sec:theory}.
+Various theoretical models used in this article are described in Sec.~\ref{sec:theory}.
 Sec.~\ref{sec:summary} summarizes our findings.
@@
 
-The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies.
-What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$).
+Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies.
+What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
 The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}.
-The effects to hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.
-A more systematic study with the event-by-event EKRT+viscous hydrodynamic calculations has been just initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein).
-The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
-It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
+The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.
+A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
+The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
+It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
 In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
-These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently.
+These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
+Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently.
 In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
@@
 For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}.
-Based on \cite{Bilandzic:2013kga}, the new flow observables obtained from multiparticle correlations, so-called \textit{Symmetric Cumulants~(SC)}, were introduced.
-SC observables are nearly insensitive to nonflow and quantify the correlation of amplitudes of two different flow harmonics.
-The first measurements of SC observables were recently published by ALICE Collaboration in \cite{ALICE:2016kpq}.
+Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants~(SC)}, were introduced.
+SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
+The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
 
-The SC observables are defined as (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}):
+The SC observables are defined as:
  %
@@
 %
-with the condition $m\neq n$ for two positive integers $m$ and $n$.
-In this article SC($m$,$n$) normalized with the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq}, is denoted by NSC($m$,$n$):
+with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
+In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
 %
@@
 %
-Normalized symmetric cumulants reflect only the degree of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ contains both the degree of the correlations between two different flow harmonics and individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained with two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
+Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
+In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
 For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
@@
 However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-The observed centrality dependence of SC(4,2) cannot be captured with the constant $\eta/s$ dependence, indicating clearly that the temperature dependence plays an important role.
+The observed centrality dependence of SC(4,2) cannot be captured by the models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role.
 These results were also used to discriminate between different parameterizations of initial conditions.
-It was demonstrated that in the fluctuation-dominated regime (central collisions) MC-Glauber initial conditions with binary collisions weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
 
@@
 \label{sec:experiment}
-A sample of $\PbPb$ collisions at $\snn=2.76$~TeV recorded by ALICE during the 2010 heavy-ion run at the
+Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
 LHC is used for this analysis. Detailed descriptions of the ALICE
@@
 a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point in the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
+interaction point along the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
 and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
@@
 contamination from secondary charged particles and fake tracks.
-The reconstruction efficiency and contamination of charged particles
+The track reconstruction efficiency and contamination
 were estimated from HIJING Monte Carlo
@@
 The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
-at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the contribution to the anisotropies from jets. 
+at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effect of jets on the measured correlations. 
 Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in longitudinal and transverse direction, are accepted.
+Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
 This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
-Tracks with kinks (the tracks that appear to change direction due to multiple scattering, $K^{\pm}$ decays) were rejected.
+Tracks with kinks (i.e, tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
 
@@
 The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
-All results of SC$(m,n)$ with a selected criterion are compared to ones from the default event and track selection described in the previous section.
-The differences between the default results and the ones obtained from the variation of the selection criteria are taken as systematic uncertainty of each individual source.
+The SC$(m,n)$ values resulting from each variation are compared to ones from the default event and track selection described in the previous section,
+and differences are taken as the systematic uncertainty due to each individual source.
 The contributions from different sources were added in quadrature to obtain the total systematic uncertainty.
@@
 The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution.
-The systematic uncertainty from centrality determination was evaluated by using TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of V0 detectors.
-The systematic uncertainty from the centrality determinations is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
+The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
+The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
 
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
-a uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices.
-The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
+The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8cm and was found to be less than 3\%.
 
-The analyzed events were recorded with two settings of the L3 magnet polarity and the resulting data sets have almost the same number of events.
-Events with both magnet polarity were used for the default analysis and the systematic uncertainties were evaluated from variation between each of two magnetic field settings.
-Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. Magnetic polarity variation and reconstruction efficiency effects are less than 2\%.
+The analyzed events were recorded with two settings of the magnet polarity and the resulting data sets have almost equal numbers of events.
+Events with both magnet polarities were used in the default analysis, and the systematic uncertainties were evaluated from the variation between each of the two magnetic field settings.
+The uncertainty on the $p_{\rm T}$ dependent track reconstruction efficiency was also taken into account.
+%Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. 
+Magnetic polarity variation and reconstruction efficiency effects contribute less than 2\% to the systematic uncertainty.
 
-The systematic uncertainty due to the track reconstruction was estimated from comparison between results for the so-called standalone TPC tracks with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
-To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
-Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
+The systematic uncertainty due to the track reconstruction was estimated from comparisons between results for the so-called standalone TPC tracks with the 
+same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
+To correct for non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
+Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level.
 The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow contribution in SC$(m,n)$.
+In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$.
 The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and it is about 7\% for SC(4,3) and 20\% for SC(5,3).
 
-Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency in azimuthal angle.
-In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
-Detector inefficiencies was introduced to mimic non-uniform azimuthal distribution in the data.
-For the observables SC(5,2), SC(5,3) and SC(4,3) variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
-Overall, the systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
-This is because $v_{n}$ are decreasing with n increasing and become more sensitive to azimuthal modulation due to detector imperfections. 
+Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the efficiency.
+In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which has a uniform distribution in azimuthal angle.
+Detector inefficiencies were introduced to mimic the non-uniform azimuthal distribution in the data.
+For the observables SC(5,2), SC(5,3) and SC(4,3) the variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
+Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
+This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
 %Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
@@
 
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from \cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
+The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
 
@@
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the panel (a) are scaled by factor of 0.1.}
+Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.}
         \label{fig:Figure_1}
@@
 
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
+The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
 In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
@@
 However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the panel (b) in Fig.~\ref{fig:Figure_1}.
-These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics.
-SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
+The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors as shown in Fig.~\ref{fig:Figure_1}b.
+These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
+SC(5,2) is stronger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
 
-It can be seen on the panel (a) in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
+It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
 In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.

### 2016-12-06 longSC.tex
small leftover things

@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-The observed centrality dependence of SC(4,2) cannot be captured by the models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role.
+The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role.
 These results were also used to discriminate between different parameterizations of initial conditions.

### 2016-12-06 longSC.tex
new figures with EKRT

@@
             \begin{center}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_32.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
               \end{center}
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
               \end{center}

### 2016-12-06 longSC.tex
first try for EKRT higher order

@@
 \subsection{Low Order Harmonic Correlations}
+\label{sec:theory_loworder}
 SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
@@
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$, only the calculations with two parameters which describe the lower order harmonic correlations better are compared to the higher order harmonic correlations.
+It is seen that the temperature at the minimum of $\eta/s$ for "parm1" is larger than the other parameters.
+The correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are described better than the lower order harmonic correlations. 
+The discrepancy between data and model is observed for the correlation between $v_3$ and $v_2$ is seen also for the correlation between $v_4$ and $v_3$.
 
@@
 \begin{enumerate}[(i)]
-	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
+	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
 	\item All the VISH2+1 model calculations with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models and event-by-event EKRT+viscous hydrodynamic calculations~\ref{Niemi:2015qia}.}
              \label{fig:Figure_8}
@@
 This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
+
+The event-by-event EKRT+viscous hydrodynamic calculations are compared to data in Fig.~\ref{fig:Figure_8}.
+Only two calculations which describe the data better are shown.
+
 This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.

### 2016-12-07 longSC.tex
add reference and improve EKRT comparison

--- 2016-12-06 longSC.tex
@@
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Teaney:2012ke,Niemi:2015qia}.
+Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 
@@
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
-\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the higher order harmonic correlations.
+The other calculations show a quite clear deviation from the data.
+As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "param1" (at $T$ = 150~MeV) is smaller than the other parameters used.
+The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
+As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described.
+The model calculations give better description than the correlations between $v_4$ and $v_2$.
+In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.
 
@@
 \begin{enumerate}[(i)]
-	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
 	\item All the VISH2+1 model calculations with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
 	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better in general but it cannot describe the data quantitively for most of the centrality ranges.
-	\item The correlation strength of $v_3$ and $v_2$,  $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is underestimated in hydrodynamic model calculations.
+	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
+	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
 	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
@@
               \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
+             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_8}
@@
 This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
+
+The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
+As it has been discussed in Sec~\ref{sec:theory_loworder}, NSC(3,2) is underestimated by the hydrodynamic calculations. 
+The hydrodynamic calculations show very weak $p_{\rm T}$ dependence for NSC(3,2) and a moderate $p_{\rm T}$ dependence for NSC(4,2).
+The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
+In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges reported.
+
 This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
@@
 
-%\section{Discussion}
+%\section{Outlooks}
+%\label{sec:outlook}
 %Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
@@
 Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
-%Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
-%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
+%%Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
+%%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

### 2016-12-07 longSC.tex
finishing alice's comment

@@
 
-It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
-In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
-NSC(5,3) shows the strongest correlation among all harmonics and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
+It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations (SC(3,2) and SC(4,2)) as well as SC(5,2) increase non-linearly towards peripheral collisions.
+In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
+NSC(5,3) shows the strongest correlation among all harmonics while NSC(5,2) shows a weak centrality dependence.
 Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
@@
         	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$.
+        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T}<1.5$~GeV/$c$.
 Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we change the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ interval, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the panel (a) in Fig.~\ref{fig:Figure_2}.
+The $p_{\rm T}$-dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
 The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
 %This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
-NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the panel (b) and (d) in Fig.~\ref{fig:Figure_2}.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
-This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of $\left<v_n\right>$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the panel (c) and (d) in Fig.~\ref{fig:Figure_2}.
-While SC$(m,n)$ show the similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$ or the centrality.
-The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase.
-These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
+These $p_{\rm T}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
+NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
+The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within errors for all minimum $p_{\rm T}$ cuts. 
+This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Fig.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
+While SC$(m,n)$ shows similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$.
+The $p_{\rm T}$-dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ increases.
+These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
 3 in Ref.~\cite{Abelev:2012di}).
@@
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-We have compared the centrality dependence of our observables with the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
 The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Fig.~11-13 in \cite{Niemi:2015qia}).
+This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
 Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~14 in \cite{Niemi:2015qia}). 
@@
 The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+With well-tuned transport coefficients and decoupling temperature, and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei.
+Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
+In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
@@
 
-The centrality dependence of SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short time scale.
+The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
+Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime.
 To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
@@
 In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version used in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
-It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
+The details of the configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
 
@@
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
-It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
-In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime.
-This observation helps to understand better the fluctuations in initial energy density.
-NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values.
-This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions.
-The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.
+In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
+However, the sign of NSC(3,2) is negative in the data in 0-10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
+This observation helps us to better understand the fluctuations in initial energy density.
+NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
+This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
+The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
+The better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
 
-The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
-Similarly to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
-NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described by these models quantitively.
-However NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
-Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
-SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions.
-Hence these calculations with large $\eta/s=0.20$ are ruled out.
-We conclude that $\eta/s$ should be small and AMPT initial condition is favored by the data.
+The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_3}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
+Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
+NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
+However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
+Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
+SC(4,2) can only be described by models with smaller $\eta/s$.
+Hence the calculation with large $\eta/s=0.20$ is ruled out.
+We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
 
@@
 Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
-        Calculations with three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT are drawn as dashed lines.
+        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
+The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s (0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
 }
@@
         	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper panels (lower) are the results of SC$(m,n)$ (NSC$(m,n)$).}
+        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_4}
@@
 
-The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
-As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest.
-The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe either of them in the most central collisions.
-Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
+SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_4}.
+For SC(3,2), the calculation with the default AMPT settings is closet to the data, but none of the AMPT configurations can describe the data fully. 
+The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
+Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
 The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
 The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
-Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
+Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
+By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possibe to recover the difference in SC(3,2) between the data and the model.
+The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all the centrality ranges.
 
-In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
-NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
-The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as it was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.
+In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
+NSC(4,2) is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
+The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
+It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
+Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
 
 \subsection{Higher Order Harmonic Correlations}
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
+The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
@@
               \end{center}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.
-These SC(3,2) and SC(4,2) will be replaced with new figures for higher order correlations once we have the calculations from Harri Niemi et.
-al~\cite{Niemi:2015qia}.}
+        \caption{Measurements of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
         \label{fig:Figure_5}
@@
 
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
-All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber, and $\eta/s=0.16$ for AMPT initial conditions) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
-Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
+The higher order harmonic correlations are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
+All the models with large $\eta/s$ ($\eta/s=0.2$ for MC-KLN and MC-Glauber, and $\eta/s=0.16$ for AMPT initial conditions) regardless of the initial conditions fail to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), with larger disagreements than observed for the lower order harmonic correlations.
+Among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data much better than the ones with other initial conditions. 
 A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
-Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions.
+Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0-10\% central collisions.
 NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
 % while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
-SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.
+The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
 
@@
 
-The extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_7}.
-The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
-However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{fig:Figure_4}.
+The results from AMPT simulations are compared to the data in Fig.~\ref{fig:Figure_7}.
+The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
+The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of the lower harmonics seen in Fig.~\ref{fig:Figure_4}.
 % interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
-In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
+In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
 The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and underestimates (or predicts very weak correlation) NSC(4,3).
+In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and predicts a very weak correlation in NSC(4,3).
 
@@
 As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0-10\% centrality range, we found that the same hierarchy also holds for the hydrodynamic calculations and the AMPT models in this article.
-The observed difference between SC(5,2) and SC(5,3) (SC(5,2) $>$ SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$ $>$ $v_3$). 
-The opposite trend are observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
-This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
-NSC($m$,$n$) correlators increase with the larger $\eta/s$ in hydrodynamic calculations in 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
+Except for 0-10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
+The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
+The opposite trend is observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
+This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
+This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
+NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
 In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
 
-We list here important findings from the model comparison:
+We list here the important findings from the model comparisons:
 \begin{enumerate}[(i)]
-	\item All the VISH2+1 model calculations with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better in general but it cannot describe the data quantitively for most of the centrality ranges.
-	\item NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
+	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most centrality ranges.
+	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
 	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
-	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of centralities while the string melting AMPT model fails to describe them.
+	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
 	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
-	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is well reproduced both by hydrodynamic and AMPT model calculations.
+	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
 
@@
 
-It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
+It can be seen in Fig.~\ref{fig:Figure_2} that for the NSC(3,2) observable no $p_{\rm T}$ dependence is seen in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T}$ is seen for the $>$30\% centrality range.
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
-In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
+In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
 
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
+              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
               \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
               \end{center}
-             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_8}
@@
 
-NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
-These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength gets weaker by the hadronic rescattering.
-This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
+\begin{figure}[p]
+             \begin{center}
+              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
+              \end{center}
+             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \label{fig:Figure_9}
+\end{figure}
+
+NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cuts are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
+The observed $p_{\rm T}$-dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data for both NSC(3,2) and NSC(4,2) simultaneously.
+In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
+As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10-20\%$ and $40-50\%$ centralities where some deviations from the data are observed.
+When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
+This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
 
@@
 
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
-The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
+This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Luzum:2010ad}.
+The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 %\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
@@
 \label{sec:summary}
-In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
-The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC).
+In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
+The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).
 It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
-We have found that fluctuations of $v_3$-$v_2$ and $v_4$-$v_3$ are anti-correlated in all centralities while fluctuations of $v_4$-$v_2$, $v_5$-$v_2$ and $v_5$-$v_3$ are correlated for all centralities.
-This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
+We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
+These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
 It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
-The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role.
-This observation might help to understand the details of the fluctuations in initial conditions.
-The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations.
-Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data.
-A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-The default configuration of AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most of centralities and for most combinations of harmonics which were considered.
-Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminating between theoretical models.
-Finally, we have found that $v_3$ and $v_2$, $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
+Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
+The sign of SC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
+In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.
+This observation might help to understand the details of the fluctuations in the initial stage.
+The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to capture the centrality dependence of higher order correlations. 
+Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions.
+A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
+The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered.
+Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
+Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
+This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
 The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.

### 2016-12-07 longSC.tex
EKRT

@@
 \subsection{Higher Order Harmonic Correlations}
+\label{sec:theory_highorder}
 The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the higher order harmonic correlations.
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the results of higher order harmonic correlations.
 The other calculations show a quite clear deviation from the data.
-As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "param1" (at $T$ = 150~MeV) is smaller than the other parameters used.
+As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "\textit{param1}" (at $T$ = 150~MeV) is smaller than the other parameters used.
 The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
-As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described.
-The model calculations give better description than the correlations between $v_4$ and $v_2$.
+As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within the errors.
+The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$.
 In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.
+
+%\begin{figure*}[!]
+%            \begin{center}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
+%                \end{center}
+%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
+%        \label{fig:Figure_5_0}
+%\end{figure*}
 

### 2016-12-07 longSC.tex
leftover alice's comment and small fix for new text

@@
 The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well-tuned transport coefficients and decoupling temperature, and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+With well-tuned transport coefficients and decoupling temperature, and given initial condition discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
@@
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of the configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
 
@@
 NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
-This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
+This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
+%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
 The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
@@
         Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s (0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$ (0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
 }
@@
 The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
-As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within the errors.
+As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within errors.
 The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$.

### 2016-12-07 longSC.tex
adopting ante's

@@
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the results of higher order harmonic correlations.
-The other calculations show a quite clear deviation from the data.
-As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "\textit{param1}" (at $T$ = 150~MeV) is smaller than the other parameters used.
-The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
-As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within errors.
-The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$.
-In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results of higher order harmonic correlations.
+As it can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ''param1'' parameterization the phase transition from hadronic to QGP phase occurs at lowest temperature, already around 150~MeV.
+This parameterization is also characterized with moderate slope of $\eta/s(T)$ of decreasing (increasing) in hadronic (QGP) phase.
+The model calculations with the parameters for which the temperature of phase transition is larger than for ``param1`` can be ruled out already with the previous measurement~\cite{ALICE:2016kpq}.
+As shown in Fig.~\ref{fig:Figure_5}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
+On the other hand, for correlations between $v_5$ and $v_3$ the description fails in the transition towards more peripheral collisions, providing further independent constraints for the models.
+%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
+In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly.
+Most notably, this measurement is so far the most dramatic example of a failure of constant $\eta/s$ to describe the data.
 
-%\begin{figure*}[!]
-%            \begin{center}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
-%                \end{center}
-%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+\begin{figure*}[!]
+            \begin{center}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
+                \end{center}
+        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
-%        \label{fig:Figure_5_0}
-%\end{figure*}
+        \label{fig:Figure_5_0}
+\end{figure*}
 
@@
         \caption{Measurements of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_5}
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}}        \label{fig:Figure_5}
 \end{figure*}
@@
 The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
-In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges reported.
+In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges.
 

### 2016-12-07 longSC.tex
final to PC

@@
             \begin{center}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
+                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
                 \end{center}
@@
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most centrality ranges.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
@@
 	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
+	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of the centrality ranges while the string melting AMPT model fails to describe them.
 	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
@@
              \begin{center}
-              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
               \end{center}
@@
              \begin{center}
-              %\resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
               \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
@@
 The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
-As it has been discussed in Sec~\ref{sec:theory_loworder}, NSC(3,2) is underestimated by the hydrodynamic calculations. 
-The hydrodynamic calculations show very weak $p_{\rm T}$ dependence for NSC(3,2) and a moderate $p_{\rm T}$ dependence for NSC(4,2).
-The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
-In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges.
+In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
+The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models.
+The difference of the model calculation between two parametrizations is very small.
+As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%.
+However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities.
+While the difference of the model calculations between two parametrizations in most of the centrality ranges is rather small, the clear separation between two parametrizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
 

### 2016-12-07 longSC.tex
remove old low order

@@
 
-\begin{figure*}[!]
-            \begin{center}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
-                \end{center}
-        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+%\begin{figure*}[!]
+%            \begin{center}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
+%                \end{center}
+%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_5_0}
-\end{figure*}
+%        \label{fig:Figure_5_0}
+%\end{figure*}
+%
 

### 2016-12-07 longSC.tex
small fixes

@@
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.}
+Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
+Systematical errors are represented with boxes.}
         \label{fig:Figure_1}
@@
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within errors for all minimum $p_{\rm T}$ cuts. 
+The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all minimum $p_{\rm T}$ cuts. 
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
@@
 While SC$(m,n)$ shows similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$.
-The $p_{\rm T}$-dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$30\% centrality range.
+The $p_{\rm T}$-dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the statistical and systematic errors for the centrality range $<$30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$30\% centrality range.
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ increases.
@@
               \end{center}
-        \caption{Measurements of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}}        \label{fig:Figure_5}
@@
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
-In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
+In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}.
 

### 2016-12-08 longSC.tex
few minor changes

@@
         \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}}        \label{fig:Figure_5}
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
+Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+        \label{fig:Figure_5}
 \end{figure*}
@@
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
+Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_6}
@@
         	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
-Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.}
+        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_7}
@@
 	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of the centrality ranges while the string melting AMPT model fails to describe them.
+	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
 	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.

### 2016-12-08 longSC.tex
same for parameterization instead of parametrization

@@
 The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}.
-The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.
+The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
 A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
@@
 Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possibe to recover the difference in SC(3,2) between the data and the model.
+By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
 The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all the centrality ranges.
@@
 The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models.
-The difference of the model calculation between two parametrizations is very small.
+The difference between the model calculations with the two parameterizations is very small.
 As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%.
 However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities.
-While the difference of the model calculations between two parametrizations in most of the centrality ranges is rather small, the clear separation between two parametrizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
+While the difference of the model calculations between two parameterizations in most of the centrality ranges is rather small, the clear separation between two parameterizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
 

### 2016-12-08 longSC.tex
correct for the references of freeze-out

@@
 In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
-The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% centrality range where the data shows stronger $p_{\rm T}$ dependence than the models.
+The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
 The difference between the model calculations with the two parameterizations is very small.
-As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centrality range and underestimate in the centrality range $>$20\%.
+As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centralities and underestimate in the centrality range $>$20\%.
 However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities.
-While the difference of the model calculations between two parameterizations in most of the centrality ranges is rather small, the clear separation between two parameterizations are observed in 10-20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
+While the difference of the model calculations between two parameterizations in most centralities is rather small, the clear separation between two parameterizations are observed in 10-20\% where both the magnitude and $p_{\rm T}$ dependence are different.
 
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Luzum:2010ad}.
-The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
+This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Niemi:2012aj}.
+The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 %\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

### 2016-12-08 longSC.tex
small update on figure and abstract

@@
 The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
-For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
+For instance, one such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
@@
 \noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-$v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
+Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
 %Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
@@
 The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuating position of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlation between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
+This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
+The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
 %The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
@@
 An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
-This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricity~\cite{Alver:2010gr},
+This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
 \begin{equation}
@@
 \end{equation}
-where the curly brackets denote the average over the transverse plane, i.e., $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Ref.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for $n$=2 or 3).
-$v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower-order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-The higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+where the curly brackets denote the average over the transverse plane, i.e.
+$\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
+There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+$v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
+Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
+Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
 When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
+The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
@@
 Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators. 
+The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as measured the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
 We also include extensive comparisons to hydrodynamic and AMPT model calculations.
@@
 Various theoretical models used in this article are described in Sec.~\ref{sec:theory}.
-Sec.~\ref{sec:summary} summarizes our findings.
+Finally, Sec.~\ref{sec:summary} summarizes our findings.
 
@@
 It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+%The first theoretical studies of SC observables can be found in Refs.~cite{}
 
@@
 a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point along the beam direction are selected. Charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<p_{\rm T}<5$~GeV/$c$ were selected. The charged track quality cuts
+interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
+and $0.2<p_{\rm T}<5$~GeV/$c$ were taken for the analysis. The charged track quality cuts
 described in~\cite{Aamodt:2010pa} were applied to minimize
@@
 The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
-at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effect of jets on the measured correlations. 
+at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
 Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
@@
 This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
-Tracks with kinks (i.e, tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
+Tracks with kinks (i.e.
+tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
 
@@
 
-The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution.
+The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed.
 The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
@@
 As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
-The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8cm and was found to be less than 3\%.
+The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.
 
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonic up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
@@
 The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
-In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).
+In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).
 
@@
 
-It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations (SC(3,2) and SC(4,2)) as well as SC(5,2) increase non-linearly towards peripheral collisions.
+It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
 In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
-NSC(5,3) shows the strongest correlation among all harmonics while NSC(5,2) shows a weak centrality dependence.
+NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
 Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.

### 2016-12-08 longSC.tex
add references for SC theory
final for IRC round3

@@
 It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-%The first theoretical studies of SC observables can be found in Refs.~cite{}
+The first theoretical studies of SC observables can be found in Refs.~\cite{Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
 
@@
 However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors as shown in Fig.~\ref{fig:Figure_1}b.
+The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}b.
 These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
@@
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$-dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
+The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
 The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Fig.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
 While SC$(m,n)$ shows similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$.
-The $p_{\rm T}$-dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the statistical and systematic errors for the centrality range $<$30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$30\% centrality range.
+The $p_{\rm T}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$~30\% centrality range.
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ increases.
-These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
+These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
 3 in Ref.~\cite{Abelev:2012di}).
@@
 This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~14 in \cite{Niemi:2015qia}). 
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}). 
 %\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
@@
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}.
+Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
 In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
@@
 The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
@@
 In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is negative in the data in 0-10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
+However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
 This observation helps us to better understand the fluctuations in initial energy density.
@@
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig~\ref{fig:Figure_3} is opposite to that in data in 0-10\% central collisions.
+Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_3} is opposite to that in data in 0--10\% central collisions.
 NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
@@
         Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$ (0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
 }
@@
 SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_4}.
-For SC(3,2), the calculation with the default AMPT settings is closet to the data, but none of the AMPT configurations can describe the data fully. 
+For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
 The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
@@
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
-Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0-10\% central collisions.
+Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions.
 NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
@@
 As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0-10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
+Except for 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
 The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
@@
 	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
-	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
 NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cuts are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
-The observed $p_{\rm T}$-dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
 With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data for both NSC(3,2) and NSC(4,2) simultaneously.
@@
 Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
-The sign of SC(3,2) in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
+The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
 In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.

### 2016-12-08 abstract.tex
small leftover things

@@
 have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the multi-particle correlation observables dubbed symmetric cumulants.
+The results were obtained with the multiparticle correlation observables dubbed Symmetric Cumulants.
 These observables are robust against biases originating from non-flow effects. 
-The centrality dependence of correlations between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$), as well as the transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ are presented.
+The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow), as well as the transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ are presented.
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
@@
 the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
-A small $\eta/s$ is favored regardless of initial conditions and the AMPT initial condition yield results closest to the measurements. 
-Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions.
+A small average value of $\eta/s$ is favored regardless of initial conditions and the AMPT initial condition yields results closest to the measurements. 
+Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.

### 2016-12-08 longSC.tex

@@
 In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
-The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40-50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
-The difference between the model calculations with the two parameterizations is very small.
-As for NSC(4,2), the model calculations overestimate the magnitude in the 5-20\% centralities and underestimate in the centrality range $>$20\%.
+The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
+The difference between the model calculations with two different parameterizations is very small.
+As for NSC(4,2), the model calculations overestimate the magnitude in the 5--20\% centralities and underestimate in the centrality range $>$~20\%.
 However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities.
-While the difference of the model calculations between two parameterizations in most centralities is rather small, the clear separation between two parameterizations are observed in 10-20\% where both the magnitude and $p_{\rm T}$ dependence are different.
+While the difference of the model calculations between two parameterizations in most centralities is rather small, a clear separation between two parameterizations are observed in 10--20\% where both the magnitude and $p_{\rm T}$ dependence are different.
 
@@
 \label{sec:summary}
-In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
+In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
 The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).

### 2016-12-16 longSC.tex
adopt comments from Alice

@@
 When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitude of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ is sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
+The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
@@
 A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
-The emerging picture is that the study of individual flow harmonics $v_n$ alone are unlikely to reveal the details of the temperature dependence of $\eta/s$.
+The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
 It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
@@
 These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of heavy-ion system evolution independently.
+Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of the heavy-ion system evolution independently.
 In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
@@
 pseudorapidity range $|\eta|<0.8$. Two scintillator
-arrays (V0) which cover the pseudo-rapidity ranges $-3.7<\eta<-1.7$
+arrays (V0) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
 and $2.8<\eta<5.1$ were used for triggering and the determination of
@@
 interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<p_{\rm T}<5$~GeV/$c$ were taken for the analysis. The charged track quality cuts
+and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
 described in~\cite{Aamodt:2010pa} were applied to minimize
@@
 same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
-To correct for non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.
+To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
 Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
-The systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
+A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
 In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$.
-The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and it is about 7\% for SC(4,3) and 20\% for SC(5,3).
+The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).
 
@@
 Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
-Systematical errors are represented with boxes.}
+Systematic errors are represented with boxes.}
         \label{fig:Figure_1}
@@
 It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
-In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations and a monotonic increase is observed.
+In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
 NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
-Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.
+Both NSC(3,2) and NSC(4,3) are getting more anticorrelated toward peripheral collisions with the similar magnitude.
 
@@
         \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
-Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T}<1.5$~GeV/$c$.
-Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
+Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$.
+Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
         \label{fig:Figure_2}
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
-The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
+The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
+The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
 %This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-These $p_{\rm T}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
+These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or $p_{\rm T, min}$ increase. 
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
-The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all minimum $p_{\rm T}$ cuts. 
+The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
 The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
-While SC$(m,n)$ shows similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$.
-The $p_{\rm T}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T}$ for the $>$~30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ increases.
+While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.
+The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
 These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
@@
 The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well-tuned transport coefficients and decoupling temperature, and given initial condition discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
@@
 This observation helps us to better understand the fluctuations in initial energy density.
-NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
-This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
+NSC(4,2) shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
+This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
 %, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
-The better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
+The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
+Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
 
@@
 All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
 Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_3} is opposite to that in data in 0--10\% central collisions.
@@
 While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results of higher order harmonic correlations.
-As it can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ''param1'' parameterization the phase transition from hadronic to QGP phase occurs at lowest temperature, already around 150~MeV.
-This parameterization is also characterized with moderate slope of $\eta/s(T)$ of decreasing (increasing) in hadronic (QGP) phase.
-The model calculations with the parameters for which the temperature of phase transition is larger than for ``param1`` can be ruled out already with the previous measurement~\cite{ALICE:2016kpq}.
+As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
+This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
+The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
 As shown in Fig.~\ref{fig:Figure_5}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
-On the other hand, for correlations between $v_5$ and $v_3$ the description fails in the transition towards more peripheral collisions, providing further independent constraints for the models.
+On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
 %The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
-In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly.
-Most notably, this measurement is so far the most dramatic example of a failure of constant $\eta/s$ to describe the data.
+In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly.
+Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
 
@@
 Among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data much better than the ones with other initial conditions. 
-A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
+A clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
@@
 As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
-Except for 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
+Except for the 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
 The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
@@
 This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model.
+This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model.
 NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
@@
 
-It can be seen in Fig.~\ref{fig:Figure_2} that for the NSC(3,2) observable no $p_{\rm T}$ dependence is seen in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T}$ is seen for the $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
-In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}.
+It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T}$ is observed in the $>$30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or centrality increases. 
+In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.
 
@@
               \end{center}
-             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_8}
@@
               \end{center}
-             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_9}
@@
 The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data for both NSC(3,2) and NSC(4,2) simultaneously.
+With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
 In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10-20\%$ and $40-50\%$ centralities where some deviations from the data are observed.
+As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10-20\%$ and $40-50\%$ centralities where some deviations are observed.
 When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
@@
 The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
-In case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
+In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
 The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
-The difference between the model calculations with two different parameterizations is very small.
-As for NSC(4,2), the model calculations overestimate the magnitude in the 5--20\% centralities and underestimate in the centrality range $>$~20\%.
-However the $p_{\rm T}$ dependence is well described by the model calculations in all centralities.
-While the difference of the model calculations between two parameterizations in most centralities is rather small, a clear separation between two parameterizations are observed in 10--20\% where both the magnitude and $p_{\rm T}$ dependence are different.
+The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
+As for NSC(4,2), the model calculations overestimate the result in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
+However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality range.
+While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
 
@@
 \label{sec:summary}
-In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
+In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
 The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).
-It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
+It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to non-flow effects and independent of symmetry plane correlations.
 We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
@@
 The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered.
-Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
+%Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
 Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
-The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+Together with the measurements of individual harmonics these results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
 

### 2016-12-16 longSC.tex
one more fix

@@
 %This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or $p_{\rm T, min}$ increase. 
+These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
@@
 
-It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T}$ is observed in the $>$30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or centrality increases. 
+It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$30\% centrality range.
+NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases. 
 In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.

### 2016-12-16 longSC.tex
alice's comments

@@
 
-NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cuts are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
+NSC(3,2) and NSC(4,2) as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
 The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.

### 2016-12-17 longSC.tex
Sudhir's comment

@@
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-This has been predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
+This was predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
 %and microscopic transport models ~\cite{Xu:2007jv}.  
@@
 Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
-This may have important implications for other fundamental physics goals.
+Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to the lower bound~\cite{Gale:2012rq}.
+%This may have important implications for other fundamental physics goals. 
 It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
@@
 The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
-A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations has just been initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
+A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in ~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
 The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
@@
 By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all the centrality ranges.
+The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.
 

### 2016-12-18 longSC.tex
fix in all centrality ranges
R2 reply

@@
 Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to the lower bound~\cite{Gale:2012rq}.
+Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
 %This may have important implications for other fundamental physics goals. 
@@
 As for NSC(4,2), the model calculations overestimate the result in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
-However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality range.
+However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges.
 While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

### 2016-12-19 abstract.tex
first half llya's comment

@@
 These observables are robust against biases originating from non-flow effects. 
-The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow), as well as the transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ are presented.
+The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow)
+is presented. The transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ is also reported. 
 The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
@@
 the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
-A small average value of $\eta/s$ is favored regardless of initial conditions and the AMPT initial condition yields results closest to the measurements. 
+A small average value of $\eta/s$ is favored independent of specific choice of initial conditions in the models.
+The calculations with the AMPT initial conditions yield results closest to the measurements.
 Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.
-Together with existing measurements of individual flow harmonics, the results presented here provide further constraints 
+Together with existing measurements of individual flow harmonics, the presented results provide further constraints 
 on initial conditions and the transport properties of the system produced in heavy-ion collisions.

### 2016-12-19 longSC.tex
first half llya's comment

@@
 The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong collective and anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-This was predicted by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
+The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
 %and microscopic transport models ~\cite{Xu:2007jv}.  
@@
 The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
-For instance, one such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
+One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is traditionally quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is nowadays quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
 
@@
 Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions in the models used for comparison~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
-Viscous effects also reduce the magnitude of the elliptic flow.
+Viscous effects reduce the magnitude of the anisotropic flow.
 Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ depends on temperature.
@@
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence, studies of the higher order ($n>3$) to lower order ($v_2$ or $v_3$) harmonic correlations and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
+Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 
-Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
+%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
+The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called Symmetric 2-harmonic 4-particle Cumulants (SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
 The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended the analysis of SC observables to higher order Fourier harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also include extensive comparisons to hydrodynamic and AMPT model calculations.
+In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+We also present a systematic comparison comparison to hydrodynamic and AMPT model calculations.
 In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
@@
 The results of the measurements are presented in Sec.~\ref{sec:results}.
- In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations.
-Various theoretical models used in this article are described in Sec.~\ref{sec:theory}.
+ In Sec.~\ref{sec:theory} we present comparisons to model calculations.
+Various models used in this article are described in Sec.~\ref{sec:theory}.
 Finally, Sec.~\ref{sec:summary} summarizes our findings.
@@
 The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
-However, the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating clearly that the temperature dependence of $\eta/s$ plays an important role.
+It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
+The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role.
 These results were also used to discriminate between different parameterizations of initial conditions.
@@
 Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
-Systematic errors are represented with boxes.}
+Systematic uncertainties are represented with boxes.}
         \label{fig:Figure_1}
@@
 
-However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}b.
+Unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
+This demonstrates the advantage of using the normalized SC observables in which the correlation strength between flow harmonics is not hindered by the differences in magnitudes of different flow harmonics.
+The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
 These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
@@
 
-It can be seen in Fig.~\ref{fig:Figure_1}a that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
+It can be seen in Fig.~\ref{fig:Figure_1}(a) that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
 In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we gradually change the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
+The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}(a).
 The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
@@
 The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
-This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
+This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
+The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}(c) and \ref{fig:Figure_2}(d).
 While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.

### 2016-12-19 longSC.tex
adopt one more llya

@@
 The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+The matter produced in a heavy-ion collision exhibits strong collective radial expansion.
+Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.

### 2016-12-21 longSC.tex
final for IRC R3

@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is nowadays quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is nowadays quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
 

### 2017-05-03 longSC.tex
final for IRC3
first try with new figures

@@
 In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also present a systematic comparison comparison to hydrodynamic and AMPT model calculations.
+We also present a systematic comparison to hydrodynamic and AMPT model calculations.
 In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
@@
 	\begin{center}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
-Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$.
-Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
+        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.}
         \label{fig:Figure_2}
@@
 
+%\begin{figure*}
+%	\begin{center}
+%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
+%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
+%	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
+%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
+%        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$.
+Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
+%        \label{fig:Figure_2}
+%        \end{center}   
+%\end{figure*}
+
 To study the $p_{\rm T}$ dependence of SC$(m,n)$, we gradually change the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}(a).
+The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
 The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
@@
 NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
-The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
+The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
@@
 
-\subsection{Low Order Harmonic Correlations}
-\label{sec:theory_loworder}
-SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
+\subsection{Centrality Dependence}
+\label{sec:theory_allorder}
+
+%\begin{figure*}[!]
+%	\begin{center}
+%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
+%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
+%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
+Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
+%        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
+The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+}
+%         \label{fig:Figure_3}
+%        \end{center}   
+% \end{figure*}
+% 
+%\begin{figure*}[!]
+%	\begin{center}
+%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
+%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
+%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+%        \label{fig:Figure_4}
+%        \end{center}   
+% \end{figure*}
+
+%\subsection{Higher Order Harmonic Correlations}
+%\label{sec:theory_highorder}
+SC($m$,$n$) and NSC($m$,$n$) are compared to several theoretical calculations. 
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
@@
 
-The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_3}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_3} is opposite to that in data in 0--10\% central collisions.
-NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
-However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
-Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
-SC(4,2) can only be described by models with smaller $\eta/s$.
-Hence the calculation with large $\eta/s=0.20$ is ruled out.
-We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
-        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-}
-         \label{fig:Figure_3}
-        \end{center}   
- \end{figure*}
-
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
-
-SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_4}.
-For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
-The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
-Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
-The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
-The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
-Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.
-
-In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
-NSC(4,2) is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
-The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
-
-\subsection{Higher Order Harmonic Correlations}
-\label{sec:theory_highorder}
-The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
-The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}.
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results of higher order harmonic correlations.
+The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_3}.
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results.
 As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
@@
 The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-As shown in Fig.~\ref{fig:Figure_5}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
+As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
 On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
@@
             \begin{center}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
-                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
+                       \resizebox{0.80\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
               \end{center}
@@
 Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_5}
+        \label{fig:Figure_3}
 \end{figure*}
 
-The higher order harmonic correlations are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
+%\begin{figure*}[!]
+%            \begin{center}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
+%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
+%              \end{center}
+%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
+Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+%        \label{fig:Figure_5}
+%\end{figure*}
+The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_3}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
+Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_3} is opposite to that in data in 0--10\% central collisions.
+NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
+However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
+Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
+SC(4,2) can only be described by models with smaller $\eta/s$.
+Hence the calculation with large $\eta/s=0.20$ is ruled out.
+We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
+
+The higher order harmonic correlations are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_4}. 
 All the models with large $\eta/s$ ($\eta/s=0.2$ for MC-KLN and MC-Glauber, and $\eta/s=0.16$ for AMPT initial conditions) regardless of the initial conditions fail to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), with larger disagreements than observed for the lower order harmonic correlations.
@@
 	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
+        	\resizebox{0.80\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
         \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
@@
 Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_6}
+        \label{fig:Figure_4}
         \end{center}   
@@
 
+%\begin{figure*}[!]
+%	\begin{center}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
+%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+%        \label{fig:Figure_6}
+%        \end{center}   
+% \end{figure*}
+
  \begin{figure*}[!]
 	\begin{center}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+        	\resizebox{0.80\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
         \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_7}
+        \label{fig:Figure_5}
         \end{center}   
@@
 
+%  \begin{figure*}[!]
+%	\begin{center}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
+%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
+%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+%        \label{fig:Figure_7}
+%        \end{center}   
+% \end{figure*}
+
+SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
+For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
+The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
+Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
+The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
+The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
+Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
+By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
+The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.
+
+In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
+NSC(4,2) is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
+The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
+It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
+Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
 The results from AMPT simulations are compared to the data in Fig.~\ref{fig:Figure_7}.
@@
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.
-In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.
 
@@
              \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_8}
+             \label{fig:Figure_6}
 \end{figure}
@@
              \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_9}
+             \label{fig:Figure_7}
 \end{figure}
 
-NSC(3,2) and NSC(4,2) as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
+NSC(3,2) and NSC(4,2) as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
 The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
@@
 
-The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
+The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
 In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.

### 2017-05-04 longSC.tex
v6.0 to PC

@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
-        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.}
+        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
+The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels.
+The systematic uncertainties of SC(3,2) and SC(4,2) are not shown for visibility.}
         \label{fig:Figure_2}
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}(c) and \ref{fig:Figure_2}(d).
-While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.
 The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
@@
 
-\subsection{Centrality Dependence}
+\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
 \label{sec:theory_allorder}
@@
 
-The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_3}.
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results.
+%SC($m$,$n$) and NSC($m$,$n$) for $m$+$n$$<$7
+While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}.
 As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
@@
             \begin{center}
-                       \resizebox{0.80\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
+                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
               \end{center}
-        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_3}
@@
 %\end{figure*}
-The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_3}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of SC(3,2) and SC(4,2).
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better both for SC(3,2) and SC(4,2) but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_3} is opposite to that in data in 0--10\% central collisions.
+The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
+Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
 NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
@@
 We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-
-The higher order harmonic correlations are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_4}. 
-All the models with large $\eta/s$ ($\eta/s=0.2$ for MC-KLN and MC-Glauber, and $\eta/s=0.16$ for AMPT initial conditions) regardless of the initial conditions fail to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), with larger disagreements than observed for the lower order harmonic correlations.
-Among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data much better than the ones with other initial conditions. 
-A clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
 NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
@@
 	\begin{center}
-        	\resizebox{0.80\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
+        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_4}
@@
 	\begin{center}
-        	\resizebox{0.80\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
-        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
+        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_5}
@@
 
-SC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
+SC($m$,$n$) and NSC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
 For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
@@
 Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
-The results from AMPT simulations are compared to the data in Fig.~\ref{fig:Figure_7}.
 The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
-The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of the lower harmonics seen in Fig.~\ref{fig:Figure_4}.
+The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
 % interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
@@
 
-We list here the important findings from the model comparisons:
+We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
 \begin{enumerate}[(i)]
@@
 The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
-In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_loworder} and show very weak $p_{\rm T}$ dependence for all centralities.
+In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
 The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.

### 2017-05-04 longSC.tex
vn in appendix

@@
 The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels.
+Systematic uncertainties are represented with boxes.
 The systematic uncertainties of SC(3,2) and SC(4,2) are not shown for visibility.}
@@
 %%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
+
+\newpage
+
+\appendix
+\section{Model comparison of the Individual $v_n$}
+
+While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do a quantitative comparison of individual flow harmonics $v_n$ to the various models.
+
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
+        \label{fig:Figure_8}
+              \end{center}
+\end{figure*}
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
+        \label{fig:Figure_9}
+              \end{center}
+\end{figure*}
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
+        \label{fig:Figure_10}
+              \end{center}
+\end{figure*}

### 2017-05-04 makediff.sh

@@ -3,4 +3,4 @@
 #2. merge sec to one file 2cfb30f
 #3. IRC first round : 7f129af
 #../git-latexdiff/git-latexdiff --main paper.tex 7f129af $1
-../git-latexdiff/git-latexdiff --main paper.tex master IRC-Round3
+../git-latexdiff/git-latexdiff --main paper.tex master IRC-Round5

### 2017-05-06 longSC.tex
final figures and few ante's comment

@@
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}.
 Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is nowadays quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
 

### 2017-05-06 longSC.tex
ante 2nd part The NSC(3,2) and NSC(4,2) observables

@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
 Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
-Systematic uncertainties are represented with boxes.}
+Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
         \label{fig:Figure_1}
@@
 These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
-SC(5,2) is stronger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
+The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
 
@@
 In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
-NSC(5,3) shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
-Both NSC(3,2) and NSC(4,3) are getting more anticorrelated toward peripheral collisions with the similar magnitude.
+The NSC(5,3) observable shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
+Both NSC(3,2) and NSC(4,3) are getting more anti-correlated toward peripheral collisions and have the similar magnitude.
 
@@
 These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
-NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
+The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
 The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
@@
 The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
+The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
 These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
@@
 %\label{sec:theory_highorder}
-SC($m$,$n$) and NSC($m$,$n$) are compared to several theoretical calculations.
+The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations.
 The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
@@
 This observation helps us to better understand the fluctuations in initial energy density.
-NSC(4,2) shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
+The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
 This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
@@
 The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
-Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
+%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
 
@@
 Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
-NSC(3,2) does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
+The NSC(3,2) observable does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
 However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
@@
 We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
+The NSC(5,2) and SC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
 Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions.
-NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
+The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
 % while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
@@
 
-SC($m$,$n$) and NSC($m$,$n$) calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
+The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
 For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
@@
 In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
-NSC(4,2) is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
+The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
 The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
@@
 
-NSC(3,2) and NSC(4,2) as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
+The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
 The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.

### 2017-05-06 longSC.tex
more...

@@
 %Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called Symmetric 2-harmonic 4-particle Cumulants (SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
+The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
 The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
@@
 What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
-The temperature dependence of $\eta/s$ in the QGP was discussed in ~\cite{Csernai:2006zz}.
-The effects on hadron spectra and elliptic flow were studied in ~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
-A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in ~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
+The temperature dependence of $\eta/s$ in the QGP was discussed in~\cite{Csernai:2006zz}.
+The effects on hadron spectra and elliptic flow were studied in~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
+A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
 The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
 It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
-In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$.
+In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between amplitudes of two different harmonics $v_m$ and $v_n$.
 These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
@@
 For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}.
-Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants~(SC)}, were introduced.
-SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
+Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced.
+The SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
 The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
@@
                        \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
@@
 Systematic uncertainties are represented with boxes.
-The systematic uncertainties of SC(3,2) and SC(4,2) are not shown for visibility.}
+The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.}
         \label{fig:Figure_2}
@@
               \end{center}
-        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in~\cite{Niemi:2015qia}.
 Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
@@
         	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
-        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
@@
         	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
-        \caption{Measurements of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
+Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
         \label{fig:Figure_5}

### 2017-05-06 longSC.tex
finish ante comment 1st

@@
 Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
-The NSC(3,2) observable does not show sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
+The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
 However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
@@
 We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-The NSC(5,2) and SC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
+The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
 Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions.
@@
 The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
-Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
+%Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
 The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
@@
 In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
-The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and predicts a very weak correlation in NSC(4,3).
+The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
+In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(4,2) and NSC(5,2) and predicts a very weak correlation both for NSC(4,2) and NSC(4,3).
 
@@
 
-As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
+As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors.
 Except for the 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
+While NSC(5,2) is smaller than NSC(5,3), SC(5,2) is larger than SC(5,3).
 The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
-The opposite trend is observed for the normalized SC (NSC(5,3) $>$ NSC(5,2)).
 This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
@@
 NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
-In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
+In semi-peripheral collisions ($>$~40\%), the opposite trend is observed.
 
@@
 	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
-	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
+	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
 
@@
 
-It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$30\% centrality range.
+It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
 NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.
@@
 With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10-20\%$ and $40-50\%$ centralities where some deviations are observed.
+In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40--50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
+As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10--20\%$ and $40--50\%$ centralities.
 When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.

### 2017-05-06 longSC.tex
few more from ante

@@
 The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
+The new observables are particularly robust against few-particle nonflow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
@@
 Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced. 
-The SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
-The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
+%The SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
+%The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
 
@@
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
-For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
+For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable.
 This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.
@@
 Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
+Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
 This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
@@
 
-The analyzed events were recorded with two settings of the magnet polarity and the resulting data sets have almost equal numbers of events.
-Events with both magnet polarities were used in the default analysis, and the systematic uncertainties were evaluated from the variation between each of the two magnetic field settings.
+The analyzed events were recorded with two settings of the magnet field polarity and the resulting data sets have almost equal numbers of events.
+Events with both magnet field polarities were used in the default analysis, and the systematic uncertainties were evaluated from the variation between each of the two magnetic field settings.
 The uncertainty on the $p_{\rm T}$ dependent track reconstruction efficiency was also taken into account.
 %Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. 
-Magnetic polarity variation and reconstruction efficiency effects contribute less than 2\% to the systematic uncertainty.
+Magnetic field polarity variation and reconstruction efficiency effects contribute less than 2\% to the systematic uncertainty.
 
@@
 A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$.
+In addition, we applied the like-sign technique to estimate nonflow contributions to SC$(m,n)$.
 The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).
 
-Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the efficiency.
+Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the reconstruction efficiency.
 In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which has a uniform distribution in azimuthal angle.
@@
 Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
-This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
+%This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
 %Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
@@
 The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
+%Secondly, the HIJING model was used to estimate the strength of nonflow correlations (typically few-particle correlations insensitive to the collision geometry). 
 %We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
@@
 The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).
-It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to non-flow effects and independent of symmetry plane correlations.
+It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to nonflow effects and independent of symmetry plane correlations.
 We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 

### 2017-05-06 longSC.tex
magnetite

@@
 \begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
+E\frac{\mathrm{d}^3N}{\mathrm{d}\bold{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
 \label{Eq:Fourier}
@@
 
-\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
+\noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
 Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
@@
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
@@
 The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
-In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
-The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
+In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
+The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
 The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
-As for NSC(4,2), the model calculations overestimate the result in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
+As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
 However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges.
@@
 
-While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do a quantitative comparison of individual flow harmonics $v_n$ to the various models.
+While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do quantitative comparison of individual flow harmonics $v_n$ to the various models.
 

### 2017-05-06 appendix.tex
final from Ante's comments

--- 2017-05-06 longSC.tex
@@
 % !TEX root = paper.tex
-
-\section{Introduction}
-
-%\textbf{{[A general history on HI]}}
-
-The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
-%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
-The matter produced in a heavy-ion collision exhibits strong collective radial expansion.
-Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
-The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
-%and microscopic transport models ~\cite{Xu:2007jv}.  
-These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.
-
-The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
-One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
-It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
-%This may have important implications for other fundamental physics goals. 
-It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
-
-%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
-
-\begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
-\label{Eq:Fourier}
-\end{equation}
-
-\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
-%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
-%\begin{equation}
-%\label{defVn}
-%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
-%\end{equation}
-%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
-%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
-The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
-The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
-%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
-The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
-%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
-
-Difficulties in extracting $\eta/s$ in heavy-ion collisions can be attributed mostly to the fact that it strongly depends on the specific choice of the initial conditions in the models used for comparison~\cite{Romatschke:2007mq,Luzum:2012wu,Shen:2011zc}.
-Viscous effects reduce the magnitude of the anisotropic flow.
-Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ depends on temperature.
-In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
-both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify the $\eta/s$ of the QGP.
-
-An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
-This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
-\begin{equation}
- \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
-  \label{eq:eccentricities}
-\end{equation}
-where the curly brackets denote the average over the transverse plane, i.e.
-$\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
-Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
-When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
-%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
-Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
-
-%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle non-flow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
-It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
-We also present a systematic comparison to hydrodynamic and AMPT model calculations.
-In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
-The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
-The results of the measurements are presented in Sec.~\ref{sec:results}.
- In Sec.~\ref{sec:theory} we present comparisons to model calculations.
-Various models used in this article are described in Sec.~\ref{sec:theory}.
-Finally, Sec.~\ref{sec:summary} summarizes our findings.
-
-% Experimental observables
-%% Flow correlations in general
-   % Niemi, ATLAS paper
-%% Symmetric Cumulants (SC)
-%% Normalized Symmetric Cumulants (NSC)
-%% Summary of results of 1st ALICE paper on SC
-%% Review of papers which cited ALICE 
-%\section{Data Analysis}
-
-\section{Experimental Observables}
-\label{sec:method}
-%\subsubsection{cumulant analysis}
-
-Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies.
-What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
-The temperature dependence of $\eta/s$ in the QGP was discussed in~\cite{Csernai:2006zz}.
-The effects on hadron spectra and elliptic flow were studied in~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
-A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
-The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
-It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
-In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between amplitudes of two different harmonics $v_m$ and $v_n$.
-These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of the heavy-ion system evolution independently.
-In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
-
-For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}.
-Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced.
-The SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
-The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
-
-The SC observables are defined as:
- %
-%\begin{widetext}
-\begin{eqnarray}
-\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
-&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
-&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
-%&=&0\,.
-\label{eq:4p_cumulant}
-\end{eqnarray}
-%\end{widetext}
-%
-with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
-In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
-%
-\begin{equation}
-\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
-\label{eq:nsc}
-\end{equation}
-%
-Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
-For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this case.
-This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.
-
-The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
-It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
-The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role.
-These results were also used to discriminate between different parameterizations of initial conditions.
-It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-The first theoretical studies of SC observables can be found in Refs.~\cite{Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
-
-\section{Data Analysis}
-\label{sec:experiment}
-Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
-LHC is used for this analysis. Detailed descriptions of the ALICE
-detector can be found
-in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
-Projection Chamber (TPC) was used to reconstruct charged particle
-tracks and measure their momenta with full azimuthal coverage in the
-pseudorapidity range $|\eta|<0.8$. Two scintillator
-arrays (V0) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
-and $2.8<\eta<5.1$ were used for triggering and the determination of
-centrality~\cite{Aamodt:2010cz}. The trigger
-conditions and the event selection criteria are identical to those
-described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
-Approximately $10^7$ minimum-bias $\PbPb$ events with
-a reconstructed primary vertex within $\pm 10$ cm from the nominal
-interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
-and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
-described in~\cite{Aamodt:2010pa} were applied to minimize
-contamination from secondary charged particles and fake tracks.
-The track reconstruction efficiency and contamination
-were estimated from HIJING Monte Carlo
-simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
-the collision centrality. The reconstruction efficiency increases from
-70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
-constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
-contamination by secondary charged particles from weak decays and
-photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
-below 1\% for $p_{\rm T}>1$~GeV/$c$.
-The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
-at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
-Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
-Only tracks with a transverse distance of closest approach (DCA) to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
-This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
-Tracks with kinks (i.e.
-tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
-
-\section{Systematic Uncertainties}
-\label{sec:uncertainties}
-%\textbf{\tmp{[Track selection criteria.]}}
-
-%p10================================================================================
-
-%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}
-
-The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
-The SC$(m,n)$ values resulting from each variation are compared to ones from the default event and track selection described in the previous section,
-and differences are taken as the systematic uncertainty due to each individual source.
-The contributions from different sources were added in quadrature to obtain the total systematic uncertainty.
-
-The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed.
-The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
-The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
-The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.
-
-The analyzed events were recorded with two settings of the magnet polarity and the resulting data sets have almost equal numbers of events.
-Events with both magnet polarities were used in the default analysis, and the systematic uncertainties were evaluated from the variation between each of the two magnetic field settings.
-The uncertainty on the $p_{\rm T}$ dependent track reconstruction efficiency was also taken into account.
-%Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. 
-Magnetic polarity variation and reconstruction efficiency effects contribute less than 2\% to the systematic uncertainty.
-
-The systematic uncertainty due to the track reconstruction was estimated from comparisons between results for the so-called standalone TPC tracks with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
-To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
-Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
-A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
-In addition, we applied the like-sign technique to estimate non-flow contributions to SC$(m,n)$.
-The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).
-
-Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the efficiency.
-In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which has a uniform distribution in azimuthal angle.
-Detector inefficiencies were introduced to mimic the non-uniform azimuthal distribution in the data.
-For the observables SC(5,2), SC(5,3) and SC(4,3) the variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
-Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
-This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
-%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
-
-\section{Results}
-\label{sec:results}
-
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
-
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
-Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
-        \label{fig:Figure_1}
-              \end{center}
-\end{figure*}
-
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
-In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).
-
-Unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
-This demonstrates the advantage of using the normalized SC observables in which the correlation strength between flow harmonics is not hindered by the differences in magnitudes of different flow harmonics.
-The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
-These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
-The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
-
-It can be seen in Fig.~\ref{fig:Figure_1}(a) that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
-In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
-The NSC(5,3) observable shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
-Both NSC(3,2) and NSC(4,3) are getting more anti-correlated toward peripheral collisions and have the similar magnitude.
-
-\begin{figure*}
-	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
-        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
-The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels.
-Systematic uncertainties are represented with boxes.
-The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.}
-        \label{fig:Figure_2}
-        \end{center}   
-\end{figure*}
-
-%\begin{figure*}
-%	\begin{center}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-%	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-%        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
-Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$.
-Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
-%        \label{fig:Figure_2}
-%        \end{center}   
-%\end{figure*}
-
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we gradually change the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
-Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
-The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
-%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
-The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
-The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
-This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
-The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
-These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
-3 in Ref.~\cite{Abelev:2012di}).
-%(see further discussions in Sec.~\ref{sec:ptdepsc})
-%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
-%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
-
-\section{Model Comparisons}
-\label{sec:theory}
-%\subsection{Theoretical models}
-%\label{sec:models}
-%We have used various models in this article.
-The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
-%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
-We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}). 
-%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
-
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
-The model then introduces the string melting procedure to produce initial partons.
-These partons are then evolved for the short duration using the ZPC parton cascade model.
-Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
-Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-
-The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime.
-To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
-For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
-In the default version, partons are recombined with their parent strings when they stop interacting.
-The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
-In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
-These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
-It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
-The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
-
-%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
-Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
-Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
-\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
-\label{sec:theory_allorder}
-
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
-%        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-}
-%         \label{fig:Figure_3}
-%        \end{center}   
-% \end{figure*}
-% 
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_4}
-%        \end{center}   
-% \end{figure*}
-
-%\subsection{Higher Order Harmonic Correlations}
-%\label{sec:theory_highorder}
-The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations.
-The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
-In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
-This observation helps us to better understand the fluctuations in initial energy density.
-The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
-This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
-%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
-%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
-
-%SC($m$,$n$) and NSC($m$,$n$) for $m$+$n$$<$7
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}.
-As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
-This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
-The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
-On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
-%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
-In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly.
-Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
-
-%\begin{figure*}[!]
-%            \begin{center}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
-%                \end{center}
-%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
-%        \label{fig:Figure_5_0}
-%\end{figure*}
-%
-
-\begin{figure*}[!]
-            \begin{center}
-                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
-              \end{center}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in~\cite{Niemi:2015qia}.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_3}
-\end{figure*}
-
-%\begin{figure*}[!]
-%            \begin{center}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
-%              \end{center}
-%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_5}
-%\end{figure*}
-The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
-The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
-However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
-Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
-SC(4,2) can only be described by models with smaller $\eta/s$.
-Hence the calculation with large $\eta/s=0.20$ is ruled out.
-We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
-Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions.
-The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
-The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
-
-\begin{figure*}[!]
-	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
-
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_6}
-%        \end{center}   
-% \end{figure*}
-
- \begin{figure*}[!]
-	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_5}
-        \end{center}   
- \end{figure*}
-
-%  \begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_7}
-%        \end{center}   
-% \end{figure*}
-
-The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
-For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
-The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
-%Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
-The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
-The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
-Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
-By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.
-
-In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
-The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
-The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
-The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
-The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
-% interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
-In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
-The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(4,2) and NSC(5,2) and predicts a very weak correlation both for NSC(4,2) and NSC(4,3).
-
-%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
-%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
-%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?
-
-As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors.
-Except for the 0--10\% centrality range, we found that the same hierarchy also holds in the hydrodynamic calculations and the AMPT models explored in this article.
-While NSC(5,2) is smaller than NSC(5,3), SC(5,2) is larger than SC(5,3).
-The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
-This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model.
-NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
-In semi-peripheral collisions ($>$~40\%), the opposite trend is observed.
-
-We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
-\begin{enumerate}[(i)]
-	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
-	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
-	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
-	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
-	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
-	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
-
-\end{enumerate}
-
-\subsection{Transverse Momentum Dependence of Correlations between $v_2$, $v_3$ and $v_4$}
-\label{sec:ptdepsc}
-
-It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.
-
-\begin{figure}[p]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
-              \end{center}
-             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_6}
-\end{figure}
-
-\begin{figure}[p]
-             \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
-              \end{center}
-             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_7}
-\end{figure}
-
-The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
-The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40--50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10--20\%$ and $40--50\%$ centralities.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
-This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
-
-The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
-In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
-The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
-The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
-As for NSC(4,2), the model calculations overestimate the result in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
-However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges.
-While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
-
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Niemi:2012aj}.
-The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
-%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
-
-\section{Summary}
-\label{sec:summary}
-In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
-The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).
-It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to non-flow effects and independent of symmetry plane correlations.
-We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
-These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
-It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
-The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.
-This observation might help to understand the details of the fluctuations in the initial stage.
-The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to capture the centrality dependence of higher order correlations. 
-Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions.
-A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
-The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered.
-%Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
-Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
-This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
-Together with the measurements of individual harmonics these results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
-
-%\section{Outlooks}
-%\label{sec:outlook}
-%Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
-The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
-This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
-To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
-However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
-Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
-Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
-%%Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
-%%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
-
-\newpage
-
 \appendix
@@
 
-While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do a quantitative comparison of individual flow harmonics $v_n$ to the various models.
-
+As discussed in Sec~\ref{sec:sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
+Therefore quantitative comparison of individual flow harmonics $v_n$ to the various models is to guide how....
+%be imperative to ensure that the models being used are tuned to reproduce
 \begin{figure*}[h]
@@
 \end{figure*}
+The event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}). 
+EKRT The difference to the data is less than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+VISH The difference to the data is less than 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
+AMPT about 20\% for the default and the string melting version, in case of the string melting version without
+
 \begin{figure*}[h]
@@
 \end{figure*}
+
+%neither MC-Glauber nor MC-KLN initial con- ditions can simultaneously describe v2, v3, and v4, as once reported in [41].
+More specifically, for MC-Glauber initial conditions, VISH2+1 with η/s = 0.08 could nicely fit the integrated v2 from central to semi-peripheral col- lisions, but overestimates v3 and v4 for the same central- ity classes.
+For MC-KLN initial conditions, VISH2+1 with η/s = 0.20 reproduces the integrated flow v2 but under- estimates v3 and v4 for the presented centrality classes.
+Compared with these two results, hydrodynamic calcu- lations with AMPT initial conditions improves the descrip- tions of vn (n = 2, 3, 4).
+Panel (c) shows that VISH2+1 with AMPT initial condition and η/s = 0.08 roughly describe v2, v3 and v4 from central to semi-peripheral collisions.
+
 \begin{figure*}[h]

### 2017-05-06 longSC.tex
final from Ante's comments

@@
 \label{sec:results}
-
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
-
 \begin{figure*}[h]
@@
 \end{figure*}
+
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
+The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
 
@@
 
-%\begin{figure*}
-%	\begin{center}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
-%	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
-%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
-%        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV.
-Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$.
-Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
-%        \label{fig:Figure_2}
-%        \end{center}   
-%\end{figure*}
-
 To study the $p_{\rm T}$ dependence of SC$(m,n)$, we gradually change the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
@@
 \label{sec:theory}
-%\subsection{Theoretical models}
-%\label{sec:models}
-%We have used various models in this article.
-The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum.
-%Secondly, the HIJING model was used to estimate the strength of nonflow correlations (typically few-particle correlations insensitive to the collision geometry). 
-%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
 We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
@@
 Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}).
-%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.
 
@@
 
-%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering.
-Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting.
-Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.
-
 \subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
 \label{sec:theory_allorder}
-
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
-%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings.
-Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
-%        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers.
-The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-}
-%         \label{fig:Figure_3}
-%        \end{center}   
-% \end{figure*}
-% 
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
-%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
-%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_4}
-%        \end{center}   
-% \end{figure*}
-
-%\subsection{Higher Order Harmonic Correlations}
-%\label{sec:theory_highorder}
 The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations.
@@
 
-%SC($m$,$n$) and NSC($m$,$n$) for $m$+$n$$<$7
+\begin{figure*}[!]
+            \begin{center}
+                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
+              \end{center}
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in~\cite{Niemi:2015qia}.
+Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+        \label{fig:Figure_3}
+\end{figure*}
+
 While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}.
@@
 
-%\begin{figure*}[!]
-%            \begin{center}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
-%                \end{center}
-%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
-%        \label{fig:Figure_5_0}
-%\end{figure*}
-%
-
 \begin{figure*}[!]
 	\begin{center}
-                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
+Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+        \label{fig:Figure_4}
         \end{center}   
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in~\cite{Niemi:2015qia}.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_3}
  \end{figure*}
 
-%\begin{figure*}[!]
-%            \begin{center}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
-%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
-%              \end{center}
-%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_5}
-%\end{figure*}
 The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
-        \label{fig:Figure_4}
-        \end{center}   
- \end{figure*}
-
-%\begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
-%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_6}
-%        \end{center}   
-% \end{figure*}
-
- \begin{figure*}[!]
-	\begin{center}
         	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
@@
  \end{figure*}
-
-%  \begin{figure*}[!]
-%	\begin{center}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
-%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
-%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
-%        \label{fig:Figure_7}
-%        \end{center}   
-% \end{figure*}
 
@@
 In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(4,2) and NSC(5,2) and predicts a very weak correlation both for NSC(4,2) and NSC(4,3).
-
-%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
-%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
-%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
-%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?
 
@@
 
-\appendix
-\section{Model comparison of the Individual $v_n$}
-
-While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do quantitative comparison of individual flow harmonics $v_n$ to the various models.
-
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_8}
-              \end{center}
-\end{figure*}
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
-        \label{fig:Figure_9}
-              \end{center}
-\end{figure*}
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
-        \label{fig:Figure_10}
-              \end{center}
-\end{figure*}
+%\input{appendix.tex}

### 2017-05-06 longSC.tex
-- \% fix

@@
 This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model.
-NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0-30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
+NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0--30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
 In semi-peripheral collisions ($>$~40\%), the opposite trend is observed.
@@
 With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40--50\%$ where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the $10--20\%$ and $40--50\%$ centralities.
+In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for 40--50\% where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
+As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the 10--20\% and 40--50\% centralities.
 When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.

### 2017-05-08 appendix.tex
fix figure1 and improved appendix11

@@
 \appendix
-\section{Model comparison of the Individual $v_n$}
+\section{Model comparison of the Individual flow harmonics $v_n$}
+As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
+Therefore it is important to check how well the individual flow harmonics $v_n$ are tuned in the models.
 
-As discussed in Sec~\ref{sec:sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
-Therefore quantitative comparison of individual flow harmonics $v_n$ to the various models is to guide how....
-%be imperative to ensure that the models being used are tuned to reproduce
 \begin{figure*}[h]
@@
                        \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
@@
 \end{figure*}
-The event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}). 
-EKRT The difference to the data is less than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
-VISH The difference to the data is less than 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
-AMPT about 20\% for the default and the string melting version, in case of the string melting version without
+
+The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
+The calculations captures the centrality dependence of the individual $v_2$ , $v_3$ , and $v_4$ harmonics in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
                        \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
@@
 
-%neither MC-Glauber nor MC-KLN initial con- ditions can simultaneously describe v2, v3, and v4, as once reported in [41].
-More specifically, for MC-Glauber initial conditions, VISH2+1 with η/s = 0.08 could nicely fit the integrated v2 from central to semi-peripheral col- lisions, but overestimates v3 and v4 for the same central- ity classes.
-For MC-KLN initial conditions, VISH2+1 with η/s = 0.20 reproduces the integrated flow v2 but under- estimates v3 and v4 for the presented centrality classes.
-Compared with these two results, hydrodynamic calcu- lations with AMPT initial conditions improves the descrip- tions of vn (n = 2, 3, 4).
-Panel (c) shows that VISH2+1 with AMPT initial condition and η/s = 0.08 roughly describe v2, v3 and v4 from central to semi-peripheral collisions.
+The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the individual flow harmonics $v_n$ (n=2, 3 and 4) in Fig.~\ref{fig:Figure_9}.
+Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$ , $v_3$ and $v_4$.
+More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
+For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
+Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4).
+Overall difference to the data is less than 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
 
@@
                        \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
         \label{fig:Figure_10}
@@
 \end{figure*}
+
+The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
+The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ (n=2, 3 and 4) as shown in Fig.~\ref{fig:Figure_10} with a precision better than 5\%.
+The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that large fraction of the flow is developed during the hadronic rescattering stage in the string melting version of AMPT.
+However the default version of AMPT underestimates $v_n$ (n=2, 3 and 4) by almost 20\%.
+It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
+
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the best models for each theory model.}
+        \label{fig:Figure_11}
+              \end{center}
+\end{figure*}
+
+Finally, only the best calculations from three models are compared to the data in Fig.~\ref{fig:Figure_11}.
+The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence is different for there models in different order harmonic flows.
+The simultaneous description of all order flow harmonics is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-05-08 appendix.tex
6.2

@@
 \appendix
-\section{Model comparison of the Individual flow harmonics $v_n$}
+\section{Model comparisons of the Individual flow harmonics $v_n$}
 As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
-Therefore it is important to check how well the individual flow harmonics $v_n$ are tuned in the models.
+Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.
 
@@
 The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
-The calculations captures the centrality dependence of the individual $v_2$ , $v_3$ , and $v_4$ harmonics in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors.
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
@@
 
-The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the individual flow harmonics $v_n$ (n=2, 3 and 4) in Fig.~\ref{fig:Figure_9}.
-Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$ , $v_3$ and $v_4$.
+The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to $v_n$ data in Fig.~\ref{fig:Figure_9}.
+Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
 More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
@@
 Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4).
-Overall difference to the data is less than 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
+Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
+The calculations with AMPT initial conditions describe the data better with the precision 10-20\%
 
@@
 The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
-The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ (n=2, 3 and 4) as shown in Fig.~\ref{fig:Figure_10} with a precision better than 5\%.
-The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that large fraction of the flow is developed during the hadronic rescattering stage in the string melting version of AMPT.
-However the default version of AMPT underestimates $v_n$ (n=2, 3 and 4) by almost 20\%.
+The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
+However the default version of AMPT underestimates $v_n$ by $\approx$ 20\%.
 It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
 
-Finally, only the best calculations from three models are compared to the data in Fig.~\ref{fig:Figure_11}.
-The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence is different for there models in different order harmonic flows.
-The simultaneous description of all order flow harmonics is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.
+Finally, only the best calculations from three models are compared to the $v_n$ data in Fig.~\ref{fig:Figure_11}.
+The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence differs in three models as well as in different order harmonic flows.
+The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-05-08 appendix.tex
first version with vn appendix

@@
 \section{Model comparisons of the Individual flow harmonics $v_n$}
+\label{sec:vn}
 As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}
+                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}

### 2017-05-08 longSC.tex
to PC
first version with vn appendix

@@
 \section{Introduction}
-
-%\textbf{{[A general history on HI]}}
-
+\label{sec:intro}
 The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
@@
 %%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
-
-\newpage
-
-%\input{appendix.tex}

### 2017-05-08 longSC.tex
add ref to the appendix

@@
 This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}).
+Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia} and Appendix~\ref{sec:vn}).
 
@@
 Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions.
-The model then introduces the string melting procedure to produce initial partons.
-These partons are then evolved for the short duration using the ZPC parton cascade model.
-Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution.
-Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
+The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.
 
@@
 The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons).
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.

### 2017-05-08 appendix.tex
final to IRC with appendix ?

@@
 \label{sec:vn}
-As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
-Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.
+As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
+Therefore it is important to check how well the theoretical models used in Sec~\ref{sec:theory} describe the measured $v_n$ data~\cite{Adam:2016izf}.
 
@@
 
-The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
+The measured $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}.
+In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
 The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
@@
 
-The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to $v_n$ data in Fig.~\ref{fig:Figure_9}.
+The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_9}.
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
@@
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
-Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4).
-Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_2$ and $v_3$,  50\% for $v_4$.
-The calculations with AMPT initial conditions describe the data better with the precision 10-20\%
+Compared with these two calculations, the calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3 and 4).
+Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$.
+The calculations with AMPT initial conditions describe the data better with the precision 10-20\%.
 
@@
 
-The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
+The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_10}.
 The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
-The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
-However the default version of AMPT underestimates $v_n$ by $\approx$ 20\%.
+The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
+The default version of AMPT underestimates $v_n$ (n = 2, 3 and 4) by $\approx$ 20\%.
 It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
                        \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the best models for each theory model.}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
         \label{fig:Figure_11}
@@
 
-Finally, only the best calculations from three models are compared to the $v_n$ data in Fig.~\ref{fig:Figure_11}.
-The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence differs in three models as well as in different order harmonic flows.
+Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_11}.
+The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% and the centrality dependence differs in three models as well as in different order flow harmonics.
 The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-05-08 longSC.tex
final to IRC with appendix ?

@@
 %The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
-Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow coefficients $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
 
@@
 $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonic coefficients, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
 $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
-Harmonic $v_4$ and higher order flow coefficients can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
+Harmonic $v_4$ and higher order flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
 Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
@@
 %
-Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics.
-In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta|>1.0$ which suppresses biases from few-particle nonflow correlations.
+Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
+In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations.
 For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable.
@@
 The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons).
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons).
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.

### 2017-05-10 longSC.tex
figure location

@@
 \label{sec:results}
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
+The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
+
 \begin{figure*}[h]
             \begin{center}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
-                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}\hspace{-0.67cm}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 \end{figure*}
-
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
 

### 2017-05-10 appendix.tex
add a reply

@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
@@
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
-More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
+In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
-Compared with these two calculations, the calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3 and 4).
+The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ (n = 2, 3 and 4).
 Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$.
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
@@
             \begin{center}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}
-                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}\hspace{-0.37cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}

### 2017-05-11 appendix.tex
cleanup name of figures

@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
-        \label{fig:Figure_8}
+        \label{fig:Figure_A1}
               \end{center}
@@
 
-The measured $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}.
+The measured $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
 In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
@@
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
-        \label{fig:Figure_9}
+        \label{fig:Figure_A2}
               \end{center}
@@
 
-The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_9}.
+The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
-        \label{fig:Figure_10}
+        \label{fig:Figure_A3}
               \end{center}
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v2_modelcomparisonBest.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v3_modelcomparisonBest.eps}}\hspace{-0.37cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/v4_modelcomparisonBest.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v2_modelcomparisonBest.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v3_modelcomparisonBest.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
-        \label{fig:Figure_11}
+        \label{fig:Figure_A4}
               \end{center}

### 2017-05-11 longSC.tex
cleanup name of figures

@@
 Finally, Sec.~\ref{sec:summary} summarizes our findings.
-
-% Experimental observables
-%% Flow correlations in general
-   % Niemi, ATLAS paper
-%% Symmetric Cumulants (SC)
-%% Normalized Symmetric Cumulants (NSC)
-%% Summary of results of 1st ALICE paper on SC
-%% Review of papers which cited ALICE 
-%\section{Data Analysis}
 
@@
             \begin{center}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}\hspace{-0.67cm}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC.eps}}
         \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
@@
             \begin{center}
-                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/ModelComparison_All_EKRT.eps}}
+                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig3_ModelComparison_EKRT.eps}}
               \end{center}
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_VISH.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_VISH.eps}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/ModelComparison_All_AMPT.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_AMPT.eps}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig6_pt_NSC32_Models.eps}}
               \end{center}
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig7_pt_NSC42_Models.eps}}
               \end{center}

### 2017-05-30 longSC.tex
sudhir comment1

@@
 \label{sec:intro}
-The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
+The main emphasis of the ultra-relativistic heavy-ion collision program at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
 %This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
@@
 $\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, are to a good approximation linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
+There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
 $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
@@
 
-For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the same set of observables introduced in \cite{Niemi:2012aj}.
+For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the set of observables introduced in \cite{Niemi:2012aj}.
 Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced. 
@@
 Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
-%This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
+This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections. 
 %Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
@@
 The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
+The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$. 
 These results indicate that the lower order harmonic correlations are larger than higher order harmonic correlations, not only because of the correlation strength itself but also because of the strength of the individual flow harmonics.
-The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.
 

### 2017-05-31 appendix.tex
add new fig2A and sudir's comment

@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT.eps}}\hspace{-0.36cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT.eps}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT.eps}}\hspace{-0.27cm}
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT.eps}}
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH.eps}}\hspace{-0.36cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH.eps}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH.eps}}\hspace{-0.27cm}
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH.eps}}
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT.eps}}\hspace{-0.36cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT.eps}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT.eps}}\hspace{-0.27cm}
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT.eps}}
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v2_modelcomparisonBest.eps}}\hspace{-0.36cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v3_modelcomparisonBest.eps}}\hspace{-0.36cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v2_modelcomparisonBest.eps}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v3_modelcomparisonBest.eps}}\hspace{-0.27cm}
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest.eps}}

### 2017-05-31 longSC.tex
add new fig2A and sudir's comment

@@
 \label{sec:results}
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which were measured in \cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations (SC($m$,$n$) for $m$+$n$ $>$ 6) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC($m$,$n$) for $m$+$n$ $\leq$ 6) which were measured in \cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
@@
 %However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
+
+\begin{figure*}
+	\begin{center}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
+The $p_{\rm T}$  dependence of $v_n$ (n=2, 3 and 4) is shown on the right panels.
+}
+        \label{fig:Figure_2A}
+        \end{center}   
+\end{figure*}
 

### 2017-06-01 appendix.tex
final answers to Sudir

@@
 As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
-Therefore it is important to check how well the theoretical models used in Sec~\ref{sec:theory} describe the measured $v_n$ data~\cite{Adam:2016izf}.
-
+Therefore it is important to check how well the theoretical models used in Sec~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\cite{sec:results}.
+The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
+%to date
 \begin{figure*}[h]
@@
 In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
-The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
 Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$.
-The calculations with AMPT initial conditions describe the data better with the precision 10-20\%.
+The calculations with AMPT initial conditions reproduce the observed centrality dependence with the accuracy of 10-20\%.
 
@@
 The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_10}.
-The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} within 20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
@@
 
-Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_11}.
-The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% and the centrality dependence differs in three models as well as in different order flow harmonics.
+Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_A4}.
+The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with the accuracy of 5-20\% and the centrality dependence differs in three models as well as in different order flow harmonics.
 The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-06-01 longSC.tex
final answers to Sudir

@@
 When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
-The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, and to the correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
+The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
 %and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
@@
 
-The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations.
+The higher order flow harmonic correlations are much smaller compared to the lower order harmonic correlations.
 In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).
@@
 	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
-The $p_{\rm T}$  dependence of $v_n$ (n=2, 3 and 4) is shown on the right panels.
-}
+        	\resizebox{0.6\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
+        \caption{The individual flow harmonics $v_n$ (n=2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels ((A), (B) and (C)).
+The $p_{\rm T, min}$ dependence of $v_n$ (n=2, 3 and 4) is shown on the right panels ((a), (b) and (c)).
+Note that $v_5$ is shown in the panel (C) with $v_4$.}
         \label{fig:Figure_2A}
@@
 \end{figure*}
+
+As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
+These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
+%While these product are reconstructed and normalized directly for NSC calculations,
+The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
+The centrality dependence of $v_n$ (n=2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
+The results of $v_n$ (n $<$ 5) are equivalent to those in \cite{Adam:2016izf}.
+The fifth order flow harmonics $v_5$ is shown on the panel (C) as an new addition in this article.
+The $p_{\rm T, min}$ dependence of $v_n$ (n=2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
 
@@
 The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV (see Appendix~\ref{sec:vn} for the quantitative comparisons).
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
 The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+The quantitative comparisons of the measured $v_n$ to various AMPT configurations are provided in Appendix~\ref{sec:vn}.
 
@@
 \begin{enumerate}[(i)]
-	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
@@
 	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

### 2017-06-01 appendix.tex
minor fix

@@
 \label{sec:vn}
-As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
-Therefore it is important to check how well the theoretical models used in Sec~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\cite{sec:results}.
+As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
+Therefore it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}.
 The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

### 2017-06-01 longSC.tex
minor fix

@@
 	\begin{center}
-        	\resizebox{0.6\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
         \caption{The individual flow harmonics $v_n$ (n=2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels ((A), (B) and (C)).
@@
 The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
-In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
+In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
 The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.

### 2017-06-12 longSC.tex
sudhir's comment

@@
 %Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The first results for a new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
+The first results for the new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
 The new observables are particularly robust against few-particle nonflow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
@@
 The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
-The centrality dependence of $v_n$ (n=2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
+The centrality dependence of $v_n$ (n=2, 3, 4 and 5) is shown on the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
 The results of $v_n$ (n $<$ 5) are equivalent to those in \cite{Adam:2016izf}.
-The fifth order flow harmonics $v_5$ is shown on the panel (C) as an new addition in this article.
+The fifth order flow harmonics $v_5$ is shown on the panel (C).
 The $p_{\rm T, min}$ dependence of $v_n$ (n=2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

### 2017-06-13 longSC.tex
Alice's comments

@@
 \label{sec:intro}
-The main emphasis of the ultra-relativistic heavy-ion collision program at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
+The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
 %This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
@@
 $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
-Harmonic $v_4$ and higher order flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-Therefore, the higher harmonics ($n>3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
+Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
 When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
@@
 %Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
-The first results for the new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the so-called \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle nonflow correlations and they provide independent information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
+The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
+The new observables are particularly robust against few-particle nonflow correlations and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}.
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
@@
 What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
-The temperature dependence of $\eta/s$ in the QGP was discussed in~\cite{Csernai:2006zz}.
+The temperature dependence of $\eta/s$ of the QGP was discussed in~\cite{Csernai:2006zz}.
 The effects on hadron spectra and elliptic flow were studied in~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
@@
 %
-Normalized symmetric cumulants reflect only the strength of the correlation which is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
+Normalized symmetric cumulants reflect only the strength of the correlation between $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics.
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations.
@@
 
-The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated in all centralities~\cite{ALICE:2016kpq}.
+The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}.
 It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
@@
 pseudorapidity range $|\eta|<0.8$. Two scintillator
-arrays (V0) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
+arrays (V0A and V0C) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
 and $2.8<\eta<5.1$ were used for triggering and the determination of
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC.eps}}
-        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels.
-The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels.
-Systematic uncertainties are represented with boxes.
-The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.}
+        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels.
+The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown in the right panels.
+Systematic uncertainties are represented with boxes.} % The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.
         \label{fig:Figure_2}
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we gradually change the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
@@
 %This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
-These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
+The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
 The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels ((A), (B) and (C)).
-The $p_{\rm T, min}$ dependence of $v_n$ (n=2, 3 and 4) is shown on the right panels ((a), (b) and (c)).
-Note that $v_5$ is shown in the panel (C) with $v_4$.}
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
+The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)).
+Note that $v_5$ is also shown in panel (C).}
         \label{fig:Figure_2A}
@@
 The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
-The centrality dependence of $v_n$ (n=2, 3, 4 and 5) is shown on the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
-The results of $v_n$ (n $<$ 5) are equivalent to those in \cite{Adam:2016izf}.
-The fifth order flow harmonics $v_5$ is shown on the panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ (n=2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
+The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
+The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}.
+The fifth order flow harmonic $v_5$ is shown in panel (C).
+The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
 
@@
 Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
+In {MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
@@
 
-The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
+%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
 Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime.
@@
 \label{sec:theory_allorder}
-The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations.
-The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}.
+First, we have compared our observables with event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
@@
 While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}.
-As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
+As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
 This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
-The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
+The model calculations in which the temperature of the phase transition is larger than for ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
 As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
@@
 The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders shown in the left panels in Fig.~\ref{fig:Figure_4}.
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.

### 2017-06-13 longSC.tex
minor fix

@@
 Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In {MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
+In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.

### 2017-06-13 appendix.tex

@@
 The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
-%to date
+
 \begin{figure*}[h]
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
@@
 
-The measured $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
+The measured $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
 In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
-The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The calculations capture the centrality dependence of $v_n$ in the central and midcentral collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
         \label{fig:Figure_A2}
@@
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
-In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
+In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
-The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ (n = 2, 3 and 4).
-Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ (n = 2 and 3),  50\% for $v_4$.
-The calculations with AMPT initial conditions reproduce the observed centrality dependence with the accuracy of 10-20\%.
+The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3 and 4).
+The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$.
+The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10-20\%.
 
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
         \label{fig:Figure_A3}
@@
 
-The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_10}.
-The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} within 20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
-The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
-The default version of AMPT underestimates $v_n$ (n = 2, 3 and 4) by $\approx$ 20\%.
+The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A3}.
+The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_A3} within 20\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The version based on the string melting configuration without the hadronic rescattering phase underestimates the data compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
+The default version of AMPT underestimates $v_n$ ($n$ = 2, 3 and 4) by $\approx$ 20\%.
 It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest.eps}}
-        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
         \label{fig:Figure_A4}
@@
 Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_A4}.
-The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with the accuracy of 5-20\% and the centrality dependence differs in three models as well as in different order flow harmonics.
-The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.
+The calculations from event-by-event EKRT+viscous hydrodynamics, VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) with an accuracy of 5-20\%.
+The centrality dependence differs in the three models as well as in the different order flow harmonics.
+The simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

### 2017-07-17 longSC.tex
Babara's comment minor ones

@@
 Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}.
-Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
+Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
 %This may have important implications for other fundamental physics goals. 
@@
 The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
-The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-
+The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
 As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this avoids large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
@@
 The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
-These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
+These observations are strikingly different from the $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig.
 3 in Ref.~\cite{Abelev:2012di}).
@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$.
+We use the notation $v_n$ instead of $v_{2}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
 %While these product are reconstructed and normalized directly for NSC calculations,
@@
 Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
-First, we have compared our observables with event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+We compare to event-by-event EKRT+viscous hydrodynamics predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
@@
 The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders shown in the left panels in Fig.~\ref{fig:Figure_4}.
-Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
+Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
 Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
@@
 
-The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
+The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
 In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
@@
 
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Niemi:2012aj}.
+This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in ~\cite{Niemi:2012aj}.
 The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
@@
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
-Together with the measurements of individual harmonics these results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+Together with the measurements of individual harmonics these results can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
 

### 2017-07-17 makediff.sh

@@ -3,4 +3,4 @@
 #2. merge sec to one file 2cfb30f
 #3. IRC first round : 7f129af
 #../git-latexdiff/git-latexdiff --main paper.tex 7f129af $1
-../git-latexdiff/git-latexdiff --main paper.tex master IRC-Round7
+../git-latexdiff/git-latexdiff --main paper.tex master EB-R1

### 2017-07-17 longSC.tex
finishing barbara's comments

@@
 Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
+For instance, $v_4$ can develop both as a linear response to $\varepsilon_4$ and/or as a nonlinear response to $\varepsilon_2^2$.
 Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
+The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
 The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
@@
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
-On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
+As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
+%For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
+%providing further independent constraints for the models.
 %The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
-In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly.
+In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly in midcentral collisions and it fails similarly for the anticorrelation between $v_3$ and $v_2$.
 Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
@@
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions.
-The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
+Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions.
+NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
+
 However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
@@
 Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. 
-The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
-% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
 The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
@@
 When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
-This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
+%This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
+Consequently, the observed weak $p_{\rm T}$ dependence may be due to hadronic rescattering.
+To clarify, the relative contributions to the final state particle distributions from partonic and hadronic stages need further study.
 
@@
 As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
-However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges.
-While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
+However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parameterizations in most centralities is rather small.
+%While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
 
@@
 It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to nonflow effects and independent of symmetry plane correlations.
+
 We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
@@
 Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions.
+
 A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.

### 2017-07-17 abstract.tex
part of Ante's comment

@@
 The results were obtained with the multiparticle correlation observables dubbed Symmetric Cumulants.
-These observables are robust against biases originating from non-flow effects. 
+These observables are robust against biases originating from nonflow effects. 
 The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow)
@@
 the different order harmonic correlations respond differently to the initial conditions and the temperature dependence of the ratio of shear viscosity to entropy density ($\eta/s$). 
-A small average value of $\eta/s$ is favored independent of specific choice of initial conditions in the models.
+A small average value of $\eta/s$ is favored independent of the specific choice of initial conditions in the models.
 The calculations with the AMPT initial conditions yield results closest to the measurements.

### 2017-07-17 longSC.tex
part of Ante's comment

@@
 Various models used in this article are described in Sec.~\ref{sec:theory}.
-Finally, Sec.~\ref{sec:summary} summarizes our findings.
+Finally, Sec.~\ref{sec:summary} summarizes our new results.
 
@@
 \label{sec:results}
-The centrality dependence of the higher order harmonic correlations (SC($m$,$n$) for $m$+$n$ $>$ 6) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC($m$,$n$) for $m$+$n$ $\leq$ 6) which were measured in \cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)) which were measured in \cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
@@
 The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed later, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
+With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed next, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
 Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
@@
 In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate.
+For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and spatial coordinates.
 Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
@@
 Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
-It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for the quantitative disagreement~\cite{Adam:2016nfo}.
+It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}.
 The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

### 2017-07-18 longSC.tex
finishing ante's comment

@@
 The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}.
-The fifth order flow harmonic $v_5$ is shown in panel (C).
+The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C).
 The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
@@
 %The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
-In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly in midcentral collisions and it fails similarly for the anticorrelation between $v_3$ and $v_2$.
+In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and it fails similarly for the anti-correlation between $v_3$ and $v_2$.
 Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
@@
 The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(4,2) and NSC(5,2) and predicts a very weak correlation both for NSC(4,2) and NSC(4,3).
+In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(3,2) and NSC(5,2) and predicts a very weak correlation both for NSC(3,2) and NSC(4,3).
 
@@
 While NSC(5,2) is smaller than NSC(5,3), SC(5,2) is larger than SC(5,3).
-The observed reversal of the hierarchy SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
+The observed reversal of the hierarchy, SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
 This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
@@
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
-	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
+	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
 	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
@@
 The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
-The observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
+The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
 With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.

### 2017-07-18 longSC.tex
fix vn
You's comment

@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$.
-We use the notation $v_n$ instead of $v_{2}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
+We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
 %While these product are reconstructed and normalized directly for NSC calculations,
@@
 Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
-We compare to event-by-event EKRT+viscous hydrodynamics predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+We compare to event-by-event EKRT+viscous hydrodynamic predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
 In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.

### 2017-07-19 appendix.tex

@@
 \appendix
-\section{Model comparisons of the Individual flow harmonics $v_n$}
+\section{Model Comparisons of the Individual Flow Harmonics $v_n$}
 \label{sec:vn}
@@
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
-In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
+In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.

### 2017-07-19 longSC.tex

@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
-We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
+In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$.
+%We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
 %While these product are reconstructed and normalized directly for NSC calculations,
@@
 Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions.
-NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
+%NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
+The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, though the model does not describe them quantitatively.
 

### 2017-08-08 appendix.tex
adopt most of CR1

@@
 As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$.
-Therefore it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}.
+Therefore, it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}.
 The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
@@
 The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$.
-The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10-20\%.
+The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10--20\%.
 
@@
 Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_A4}.
-The calculations from event-by-event EKRT+viscous hydrodynamics, VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) with an accuracy of 5-20\%.
+The calculations from event-by-event EKRT+viscous hydrodynamics, VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) with an accuracy of 5--20\%.
 The centrality dependence differs in the three models as well as in the different order flow harmonics.
-The simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.
+Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.

### 2017-08-08 longSC.tex
adopt most of CR1

@@
 Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}.
+The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf,Aad:2014eoa}.
 The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
@@
 \noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
+Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angle brackets denote an average over all particles in all events.
 %Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
@@
 In Sec.~\ref{sec:theory} we present comparisons to model calculations.
-Various models used in this article are described in Sec.~\ref{sec:theory}.
+%Various models used in this article are described in Sec.~\ref{sec:theory}. 
 Finally, Sec.~\ref{sec:summary} summarizes our new results.
@@
 simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
-the collision centrality. The reconstruction efficiency increases from
+the collision centrality. The reconstruction efficiency increases with transverse momenta from
 70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
@@
 at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
-Reconstructed TPC tracks were required to have at least 70 space points (out of a maximum of 159). 
+Reconstructed TPC tracks are required to have at least 70 space points (out of a maximum of 159). 
 Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
@@
 
-The systematic uncertainty due to the track reconstruction was estimated from comparisons between results for the so-called standalone TPC tracks with the 
+The systematic uncertainty due to the track reconstruction procedure was estimated from comparisons between results for the so-called standalone TPC tracks with the 
 same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this avoids large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we obtain the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
@@
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in~\cite{Niemi:2015qia}.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations.
 Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
@@
 	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
-	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
+	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.

### 2017-08-09 longSC.tex
final to PC

@@
 %This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
+%The matter produced in a heavy-ion collision exhibits strong collective radial expansion.
+Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
 The matter produced in a heavy-ion collision exhibits strong collective radial expansion. 
-Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
+Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into short direction of the almond,
+that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf,Aad:2014eoa}.
@@
 \label{sec:experiment}
-Data recorded by ALICE in $\PbPb$ collisions at $\snn=2.76$~TeV during the 2010 heavy-ion run at the
-LHC is used for this analysis. Detailed descriptions of the ALICE
-detector can be found
+The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
+Detailed descriptions of the ALICE detector can be found
 in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
@@
 In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
-This observation helps us to better understand the fluctuations in initial energy density.
+%However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
+%This observation helps us to better understand the fluctuations in initial energy density.
 The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
@@
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
-Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions.
+%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions.
 %NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
@@
 The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
-Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. 
+%Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. 
 The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
@@
 For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
-The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
+%The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
 %Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
@@
 	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
-	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
+	%\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
@@
 Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
-The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.
+%The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
+%In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.
 This observation might help to understand the details of the fluctuations in the initial stage.

### 2017-08-11 longSC.tex
You and Ante's comments

@@
 The matter produced in a heavy-ion collision exhibits strong collective radial expansion. 
-Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into short direction of the almond,
+Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
 that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
-The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf,Aad:2014eoa}.
+The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} is also observed at LHC energies~\cite{Aamodt:2010pa,ALICE:2011ab,Abelev:2014pua,Adam:2016izf,ATLAS:2011ah,ATLAS:2012at,Aad:2013xma,Aad:2014eoa,Chatrchyan:2012wg,Chatrchyan:2012ta,Chatrchyan:2012xq}.
 The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
@@
 \noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
-Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angle brackets denote an average over all particles in all events.
+Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
 %Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
@@
 It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-The first theoretical studies of SC observables can be found in Refs.~\cite{Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
+The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
 
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we obtain the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we present the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
@@
 %NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
-The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, though the model does not describe them quantitatively.
+The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, but it is clear that this model does not describe them quantitatively.
 

### 2017-08-11 longSC.tex
tsukuba's comments

@@
 Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
-The matter produced in a heavy-ion collision exhibits strong collective radial expansion. 
+The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
 Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
@@
 where the curly brackets denote the average over the transverse plane, i.e.
-$\{\cdots\}$ = $\int dxdy$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
+$\{\cdots\}$ = $\int$ d$x$d$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
 There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.

### 2017-08-14 appendix.tex
tsukuba's comments
minor fix

@@
 Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+
+\section{Chi-Square test for SC observables}
+
+We perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
+
+\begin{equation}
+\chi^{2} = \sum_{i=0}^{nbins} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+\label{Eq:chisq}
+\end{equation}
+where $y_i$ is a measurement in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC obserables best is shown in Fig.~\ref{fig:Figure_A5}.
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
+        \caption{The resulting ${\chi}^2$ from the comparison of few selected calculations from three theoretical models are shown for each SC observable.
+Closed (open) markers show SC($m$,$n$) (NSC($m$,$n$).}
+        \label{fig:Figure_A5}
+              \end{center}
+\end{figure*}
+
+We found that the overall ${\chi}^2$ for SC($m$,$n$) is larger than one for NSC($m$,$n$) and ${\chi}^2$. 
+Even with the best model calculations from three theoretical models, ${\chi}^2$ varies a lot depending on the models, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.

### 2017-08-14 longSC.tex
minor fix

@@
 %, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
-The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
+The measurement of SC($m$,$n$) and NSC($m$,$n$) can provide new constraints for the detailed modeling of fluctuating initial conditions.
 %Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
@@
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+Left (right) panels show SC($m$,$n$) (NSC($m$,$n$)).}
         \label{fig:Figure_3}
@@
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
         \label{fig:Figure_4}
@@
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
-Left (right) panels show SC$(m,n)$ (NSC$(m,n)$).}
+Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
         \label{fig:Figure_5}
@@
 The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
-It should be noted that the agreement with SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
-Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints on the parameters in AMPT models.
+It should be noted that the agreement with SC($m$,$n$) should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
+Hence the simultaneous description of SC($m$,$n$) and NSC($m$,$n$) should give better constraints on the parameters in AMPT models.
 The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
@@
 The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(3,2) and NSC(5,2) and predicts a very weak correlation both for NSC(3,2) and NSC(4,3).
+In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(3,2) and NSC(5,2) and predicts a very weak correlation both for NSC(3,2) and NSC(4,3).
 

### 2017-08-14 appendix.tex
add chisq test

--- 2017-08-08 appendix.tex
@@
 In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
-The calculations capture the centrality dependence of $v_n$ in the central and midcentral collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The calculations capture the centrality dependence of $v_n$ in the central and mid-central collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
 Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
-In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
+In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to mid-central collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
@@
 Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+
+\newpage
+\section{Chi-Square test for SC observables}
+\label{sec:chisq}
+We perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
+
+\begin{equation}
+\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+\label{Eq:chisq}
+\end{equation}
+
+where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
+The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
+        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables.
+Closed (open) markers are for SC($m$,$n$) (NSC($m$,$n$)).}
+        \label{fig:Figure_A5}
+              \end{center}
+\end{figure*}
+
+We found that in case of VISH2+1 calculations, the ${\chi}^2$ values of SC($m$,$n$) is larger than those of NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ is not well described as shown in Fig.~\ref{fig:Figure_A4} compared to other models.
+Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
+values are bit large especially for the observables related with $v_3$. 
+Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.

### 2017-08-15 appendix.tex
add a reference and correct wording

@@
         \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables.
-Closed (open) markers are for SC($m$,$n$) (NSC($m$,$n$)).}
+The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
         \label{fig:Figure_A5}
@@
 
-We found that in case of VISH2+1 calculations, the ${\chi}^2$ values of SC($m$,$n$) is larger than those of NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ is not well described as shown in Fig.~\ref{fig:Figure_A4} compared to other models.
+We found that in case of the calculations from VISH2+1 and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to event-by-event EKRT+viscous hydrodynamics as shown in Fig.~\ref{fig:Figure_A4}.
 Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
-values are bit large especially for the observables related with $v_3$. 
-Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
+values are large especially for the observables related with $v_3$. 
+Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.

### 2017-08-15 longSC.tex
add chisq test
add a reference and correct wording

@@
 The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
-The new observables are particularly robust against few-particle nonflow correlations and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}.
+The new observables are particularly robust against few-particle nonflow correlations~\cite{Aamodt:2010pa} and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}.
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
@@
 A systematic difference of up to 12\% was observed in SC$(m,n)$ from the different track selections. 
-In addition, we applied the like-sign technique to estimate nonflow contributions to SC$(m,n)$.
+In addition, we applied the like-sign technique to estimate nonflow contributions~\cite{Aamodt:2010pa} to SC$(m,n)$.
 The difference between results obtained by selecting all charged particles and results obtained after either selecting only positively or only negatively charged particles was the largest contribution to the systematic uncertainty and is about 7\% for SC(4,3) and 20\% for SC(5,3).
@@
 	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
+\end{enumerate}
 
-\end{enumerate}
+Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
 

### 2017-08-15 longSC.tex
added a reference for nonlinear
final to CR2

@@
 Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
-For instance, $v_4$ can develop both as a linear response to $\varepsilon_4$ and/or as a nonlinear response to $\varepsilon_2^2$.
-Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva}.
+For instance, $v_4$ can develop both as a linear response to $\varepsilon_4$ and/or as a nonlinear response to $\varepsilon_2^2$~\cite{Gardim:2011xv}.
+Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva,Acharya:2017zfg}.
 When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.

### 2017-08-17 appendix.tex
llya's comments

--- 2017-08-14 appendix.tex
@@
 
-\newpage
-\section{Chi-Square test for SC observables}
-\label{sec:chisq}
-We perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
-
-\begin{equation}
-\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
-\label{Eq:chisq}
-\end{equation}
-
-where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
-The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
-The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
-\begin{figure*}[h]
-            \begin{center}
-                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
-        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables.
-Closed (open) markers are for SC($m$,$n$) (NSC($m$,$n$)).}
-        \label{fig:Figure_A5}
-              \end{center}
-\end{figure*}
-
-We found that in case of VISH2+1 calculations, the ${\chi}^2$ values of SC($m$,$n$) is larger than those of NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ is not well described as shown in Fig.~\ref{fig:Figure_A4} compared to other models.
-Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
-values are bit large especially for the observables related with $v_3$. 
-Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
+%\newpage
+%\section{Chi-Square test for SC observables}
+%\label{sec:chisq}
+%We perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
+%
+%\begin{equation}
+%\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+%\label{Eq:chisq}
+%\end{equation}
+%
+%where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+%The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
+%The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+%\begin{figure*}[h]
+%            \begin{center}
+%                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
+%        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables.
+The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
+%        \label{fig:Figure_A5}
+%              \end{center}
+%\end{figure*}
+%
+%We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to event-by-event EKRT+viscous hydrodynamics as shown in Fig.~\ref{fig:Figure_A4}.
+%Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
+%values are large especially for the observables related with $v_3$. 
+%Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.
+%
+%
+%

### 2017-08-17 longSC.tex
llya's comments

@@
 
-Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
+%Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
+Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
+
+\begin{equation}
+\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+\label{Eq:chisq}
+\end{equation}
+
+where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
+The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+
+\begin{figure*}[h]
+            \begin{center}
+                       \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_SC_bestfits.eps}}\hspace{-0.60cm}
+                        \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_vn_bestfits.eps}}
+        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for all SC observables (a) and individual harmonics $v_n$ (b).
+The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
+        \label{fig:Figure_A5}
+              \end{center}
+\end{figure*}
+
+The results for the SC observables are presented in Fig~\ref{fig:Figure_A5}(a) and the ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}(b).
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08), the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by the model compared to the event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_A5}(b), showing that the ${\chi}^2$ values for $v_n$ are much larger for the VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
+The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the models.
+As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.
+This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
+
+Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
+values are large especially for the observables related with $v_3$. 
+Even with the best model calculations from theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.
 

### 2017-08-17 longSC.tex
with hydro only

@@
 The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
+%The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
 The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
@@
             \begin{center}
-                       \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_SC_bestfits.eps}}\hspace{-0.60cm}
-                        \resizebox{0.49\textwidth}{!}{\includegraphics{figs/chisq_vn_bestfits.eps}}
-        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for all SC observables (a) and individual harmonics $v_n$ (b).
-The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
+                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad_wo_ampt.eps}}
+        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
+        %The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
         \label{fig:Figure_A5}
@@
 
-The results for the SC observables are presented in Fig~\ref{fig:Figure_A5}(a) and the ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}(b).
+%The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
+The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for the VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+%The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values are worst for $v_n$ among the models.
+%The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
+As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.
+This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
+The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
+The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
 We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08), the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
 This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by the model compared to the event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}(b), showing that the ${\chi}^2$ values for $v_n$ are much larger for the VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
-The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the models.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger for VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
+The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
 As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.

### 2017-08-17 longSC.tex
adding AMPT default

@@
 The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
-%The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
-The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+%The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
 
@@
             \begin{center}
-                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad_wo_ampt.eps}}
-        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from two viscous hydrodynamic models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
+                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
+        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
         %The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
@@
 
-%The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
+The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
 The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for the VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
-%The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values are worst for $v_n$ among the models.
-%The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
+This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2).
+However the ${\chi}^2$ values of this model are worst for $v_n$ among the models and noticeably larger for $v_2$.
+
+The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
 As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.
 This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
-The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
+%The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
 The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
@@
 This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger for VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
-The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
+%The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
 As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.

### 2017-08-18 longSC.tex
with Constantin

@@
 
-The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
-The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
+The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
+The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig.~\ref{fig:Figure_A5}c.
 We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to the event-by-event EKRT+viscous hydrodynamics.
+This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
 This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.

### 2017-08-18 longSC.tex

@@
                        \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
-        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
-        %The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
+        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
+The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
         \label{fig:Figure_A5}

### 2017-08-19 longSC.tex
adopting Ilya's comment halfway

@@
 \label{sec:intro}
-The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP).
+The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the Quark-Gluon Plasma (QGP).
 %This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
@@
 The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
-Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
-that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
+%Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
+%that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
+Difference in pressure gradients and the interactions among matter constituents produced in the spatially anisotropic overlap region of the two colliding nuclei result in anisotropic transverse flow in the momentum space.
 The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} is also observed at LHC energies~\cite{Aamodt:2010pa,ALICE:2011ab,Abelev:2014pua,Adam:2016izf,ATLAS:2011ah,ATLAS:2012at,Aad:2013xma,Aad:2014eoa,Chatrchyan:2012wg,Chatrchyan:2012ta,Chatrchyan:2012xq}.
@@
 
-The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
+%The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
 One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
+The temperature dependence of $\eta/s$ has some generic features typical to the most known fluids.
+This ratio reaches its minimum value close to the phase transition region~\cite{Kovtun:2004de,Lacey:2006bc}.
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
@@
 Furthermore, the magnitude of $\eta/s$ used in hydrodynamic calculations should be considered as an average over the temperature evolution of the expanding fireball as it is known that $\eta/s$ depends on temperature.
-In addition, part of the elliptic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
+In addition, part of the anisotropic flow can also originate from the hadronic phase~\cite{Bozek:2011ua,Rose:2014fba,Ryu:2015vwa}. Therefore,
 both the temperature dependence of $\eta/s$ and the relative contributions from the partonic and hadronic phases should be understood better to quantify the $\eta/s$ of the QGP.
@@
 In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
-The experimental setup and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+The experimental setup and measurements are described in Sec.~\ref{sec:experiment}.
+The sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
 The results of the measurements are presented in Sec.~\ref{sec:results}.
@@
 
-Existing measurements provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies.
+Existing measurements for anisotropic flow observables provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies.
 What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
@@
 These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurement would provide experimental constraints on theoretical predictions for the individual stages of the heavy-ion system evolution independently.
+Therefore their measurement would provide experimental constraints on theoretical parameters used to describe the individual stages of the heavy-ion system evolution.
 In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
@@
 \begin{eqnarray}
-\left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
+\mathrm{SC}(m,n) \equiv \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
 &&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
@@
 It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
+The first theoretical studies of SC observables can be found in \cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
 
@@
 \label{sec:experiment}
-The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
+%The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
+The data samples of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article were recorded by ALICE during the 2010 heavy-ion run of the LHC.
 Detailed descriptions of the ALICE detector can be found
@@
 at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
-Reconstructed TPC tracks are required to have at least 70 space points (out of a maximum of 159). 
+Reconstructed TPC tracks constrained to vertex are required to have at least 70 space points (out of a maximum of 159). 
 Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted.
@@
 The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
 The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.
@@
 Events with both magnet field polarities were used in the default analysis, and the systematic uncertainties were evaluated from the variation between each of the two magnetic field settings.
-The uncertainty on the $p_{\rm T}$ dependent track reconstruction efficiency was also taken into account.
+The uncertainty due to the $p_{\rm T}$ dependence of the track reconstruction efficiency was also taken into account.
 %Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. 
@@
 \label{sec:results}
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)) which were measured in \cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)) which were published in \cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
@@
             \begin{center}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV.
+%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
+%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
+			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
+        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3-5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
-Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1.
+The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations.
+The SC(4,2) and SC(3,2) are downscaled by 0.1.
 Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
@@
 
-Unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
+Unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost the same order of the correlation strength as the lower order flow harmonic correlations NSC(3,2) or NSC(4,2).
 This demonstrates the advantage of using the normalized SC observables in which the correlation strength between flow harmonics is not hindered by the differences in magnitudes of different flow harmonics.
-The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>$~20\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
+The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality range 20--50\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
 The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$. 
@@
         \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels.
-The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown in the right panels.
+The NSC(3,2) and NSC(4,2) ((b) and (d)) are shown in the right panels.
 Systematic uncertainties are represented with boxes.} % The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
+The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range 0--30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the 30--50\% centrality.
 The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3, 4 and 5) in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
-The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)).
-Note that $v_5$ is also shown in panel (C).}
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2-5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
+$v_4$ and $v_5$ are shown in the same panel (C).
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2-4 is shown in the right panels ((a), (b) and (c)).}
         \label{fig:Figure_2A}
@@
 %While these product are reconstructed and normalized directly for NSC calculations,
-The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
+The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
 The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
@@
 \label{sec:theory}
-We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
+We have performed a systematic comparison of the centrality and transverse momentum dependence of the SC($m$,$n$) and NSC($m$,$n$) to the event-by-event  EKRT+viscous hydrodynamics~\cite{Niemi:2015qia}, VISH2+1~\cite{Shen:2010uy,Shen:2014vra}, and the AMPT~\cite{Qian:2016pau,Lin:2004en,Lin:2014tya} models.
+Comparisons for $v_n$ coefficients with the model calculations are presented in Appendix~\ref{sec:vn}.
+
+In the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+The subsequent space-time evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
 This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
@@
 
-The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics.
-With well-tuned transport coefficients and decoupling temperature, and given initial conditions discussed next, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
-Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
-Traditionally, the Glauber model constructs the initial entropy density with contributions from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
-For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and spatial coordinates.
+The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes the QGP phase and the highly dissipative and off-equilibrium late hadronic stages with fluid dynamics.
+By tuning transport coefficients and decoupling temperature for a given scenario of initial conditions, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya} energies.
+Three different types of initial conditions~\cite{Zhu:2016puf} ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values have been used for our data to model comparisons.
+Traditionally, the Glauber model constructs the initial entropy density from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}.
+The {KLN} model assumes that the initial energy density is proportional to that of the initial gluons calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
+In Monte Carlo versions {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah} of these models an additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
+For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy distribution of individual partons, which fluctuate in both momentum and coordinate space.
 Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.
+%The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.
 
@@
 Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime.
-To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
+To address such non-equilibrium many-body dynamics, AMPT~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
 For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
@@
 This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
-%The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig~\ref{fig:Figure_A5}a and Fig~\ref{fig:Figure_A5}b, respectively.
-The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig~\ref{fig:Figure_A5}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08), the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by the model compared to the event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger for VISH2+1 calculations than event-by-event EKRT+viscous hydrodynamics.
-%The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
-As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.
-This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
+
+%As discussed in \cite{ALICE:2016kpq}, the other $\eta/s(T)$ parameterizations in event-by-event EKRT+viscous hydrodynamics give worse descriptions for SC(4,2) and NSC(4,2) compared to ``param1''. 
+Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$).
+Furthermore we observe a clear separation of two parameterizations for SC(5,3) which is even larger than SC(4,2).
+These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.
 

### 2017-08-20 appendix.tex
finishing Ilya's comment

@@
 Therefore, it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}.
-The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
+The $v_n$ is measured for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
+%The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
 
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT.eps}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
+Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} for two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
         \label{fig:Figure_A1}
@@
 
-The measured $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
+The measured $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
 In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH.eps}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
+Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+Three initial conditions from AMPT, MC-KLN and MC-Glauber are shown in different colors.
+The results for different $\eta/s$ values are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber and, 0.16 for AMPT) are drawn as dashed lines.}
         \label{fig:Figure_A2}
@@
 The version based on the string melting configuration without the hadronic rescattering phase underestimates the data compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
-The default version of AMPT underestimates $v_n$ ($n$ = 2, 3 and 4) by $\approx$ 20\%.
+The default version of AMPT underestimates $v_n$ for $n$ = 2--4 by $\approx$ 20\%.
 It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest.eps}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to few selected model calculations from three theoretical models which describe the $v_n$ data best.}
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
+The results are compared with selected calculations from three different types of models which are best in describing $v_n$ coefficients.}
         \label{fig:Figure_A4}

### 2017-08-20 longSC.tex
finishing Ilya's comment

@@
 \begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}\bold{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
+E\frac{\mathrm{d}^3N}{\mathrm{d}{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
 \label{Eq:Fourier}
@@
 
-\noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
+\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
 Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
-        \caption{The individual flow harmonics $v_n$ for $n$ = 2-5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
 $v_4$ and $v_5$ are shown in the same panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2-4 is shown in the right panels ((a), (b) and (c)).}
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)).}
         \label{fig:Figure_2A}
@@
 The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
-The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
+The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
 The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}.
 The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
 
@@
 %The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
-Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and short lifetime.
-To address such non-equilibrium many-body dynamics, AMPT~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
-For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-The AMPT model can be run in two main configurations, the default and the string melting model~\footnote{The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.}.
-In the default version, partons are recombined with their parent strings when they stop interacting.
+Even though thermalization could be achieved shortly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime.
+To address such non-equilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
+The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
+For the data comparisons three different configurations of the AMPT model has been used: the default one and string melting with and without hadronic rescattering.
+The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
+In the default configuration, partons are recombined with their parent strings when they stop interacting.
 The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
-In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
+In the string melting configuration, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
 These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
-The third version used in this article is based on the string melting configuration in which the hadronic rescattering phase is switched off to study its influence on the development of anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
+The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}.
 The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
-The quantitative comparisons of the measured $v_n$ to various AMPT configurations are provided in Appendix~\ref{sec:vn}.
 
@@
 \label{sec:theory_allorder}
-Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
-We compare to event-by-event EKRT+viscous hydrodynamic predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
-In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
+Comparison to event-by-event EKRT+viscous hydrodynamic predictions with various parameterizations of the temperature dependence of $\eta/s(T)$ was shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+It was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
 %However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
 %This observation helps us to better understand the fluctuations in initial energy density.
-The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values.
-This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
+The model calculations for NSC(4,2) observable show that it has better sensitivity for different $\eta/s(T)$ parameterizations but they cannot
+describe neither the centrality dependence nor the absolute values.
+The discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
 %, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
@@
               \end{center}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
 The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations.
@@
 
-While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}.
+The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_3}. 
 As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
 This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
-The model calculations in which the temperature of the phase transition is larger than for ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
+The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
 As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
@@
 In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and it fails similarly for the anti-correlation between $v_3$ and $v_2$.
-Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
+%Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
 
@@
         	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_VISH.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
 Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
-The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.
-Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
+The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber and 0.16 for AMPT) are drawn as dashed lines.
+Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$)).}
         \label{fig:Figure_4}
@@
 %NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
-The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, but it is clear that this model does not describe them quantitatively.
+%The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, but it is clear that this model does not describe them quantitatively.
 
@@
         	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_AMPT.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.
+        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Results are compared to various AMPT models.
 Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
@@
 
-In the case of SC(4,2), the string melting AMPT model can describe the data fairly well while the default model underestimates it.
+In the case of SC(4,2), the string melting configuration of the AMPT model can describe the data fairly well while the default configuration underestimates it.
 The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
@@
 While NSC(5,2) is smaller than NSC(5,3), SC(5,2) is larger than SC(5,3).
-The observed reversal of the hierarchy, SC(5,2) $>$ SC(5,3), can be explained by the magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
+The observed inverse hierarchy, SC(5,2) $>$ SC(5,3), can be explained by different magnitudes of the individual flow harmonics ($v_2$ $>$ $v_3$). 
 This can be attributed to the fact that flow fluctuations are stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}.
-This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on an AMPT model.
+This was claimed in Ref.~\cite{Zhu:2016puf} and also seen in Ref.~\cite{Bhalerao:2014xra} based on the AMPT model calculations.
 NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0--30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
@@
 %Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
-Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
+The agreement of various model calculations with the data is quantified using the log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} by calculating the ${\chi}^2$:
 
@@
 
-where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
-The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
-The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
-%The resulting ${\chi}^2$ for few selected calculations from two viscous hydrodynamic models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
+where $y_i$ ($f_i$) is a measurement (model) value in a centrality bin $i$.
+The systematical and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+The total number of data samples $N$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in ${\chi}^2$ calculations.
+The ${\chi}^2$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
 
@@
                        \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
-        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
-The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
+        \caption{The ${\chi}^2$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
+Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
         \label{fig:Figure_A5}
@@
 \end{figure*}
-
+% The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
@@
 We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, showing that the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
-The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2).
-However the ${\chi}^2$ values of this model are worst for $v_n$ among the models and noticeably larger for $v_2$.
+This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, where the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values of this model are largest for $v_n$ among the models especially for $v_2$.
 
 The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
-As for the calculations from event-by-event EKRT+viscous hydrodynamics, the ${\chi}^2$ values for SC(4,2) and NSC(4,2) are comparable to that for $v_2$ but they are larger than that for $v_4$.
-This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
+The ${\chi}^2$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
+This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
+%This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
 
@@
 Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
-values are large especially for the observables related with $v_3$. 
-Even with the best model calculations from theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.
+values are large especially for the observables which include $v_3$. 
+Even with the best model calculations from theoretical models, the ${\chi}^2$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
 
-\subsection{Transverse Momentum Dependence of Correlations between $v_2$, $v_3$ and $v_4$}
+\subsection{Transverse Momentum Dependence of NSC(3,2) and NSC(4,2)}
 \label{sec:ptdepsc}
-
-It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
-NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases.
-
+%It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
+%NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases. 
 \begin{figure}[p]
@@
 The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
-The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
-With the exception of the default configuration, the other AMPT settings predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
+The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
+The default configuration of the AMPT is well reproducing NSC(3,2), while the other AMPT configurations predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
 In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for 40--50\% where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
-As for  NSC(4,2), the same model which describes NSC(3,2) can also reproduce the data well except for the 10--20\% and 40--50\% centralities.
-When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
+As for  NSC(4,2), the default AMPT configuration which describes NSC(3,2) can also reproduce the data well except for the 10--20\% and 40--50\% centralities.
+Comparison of the string melting AMPT configuration with and without hadronic rescattering suggests that a very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
 %This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
@@
 The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
-As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%.
+As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range 30--50\%.
 However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parameterizations in most centralities is rather small.
@@
 
-This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in ~\cite{Niemi:2012aj}.
+The observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in ~\cite{Niemi:2012aj}.
 The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
@@
 In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
-The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC).
-It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to nonflow effects and independent of symmetry plane correlations.
+The results are presented in terms of the Symmetric Cumulants SC($m$,$n$).
+It was demonstrated earlier in \cite{ALICE:2016kpq} that SC($m$,$n$) is insensitive to nonflow effects and independent of symmetry plane correlations.
 
@@
 
-A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
+A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order.
 The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered.
@@
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
-Together with the measurements of individual harmonics these results can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+Together with the measurements of individual harmonics the new results for SC($m$,$n$) and NSC($m$,$n$) can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
 

### 2017-08-20 longSC.tex
new figures

@@
             \begin{center}
-%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
-%                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
-			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
-        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3-5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
+%			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
+        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.

### 2017-08-20 abstract.tex
adopting Ilya's comment halfway
adding shudir's comment

@@
 have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
-The results were obtained with the multiparticle correlation observables dubbed Symmetric Cumulants.
+The results are reported in terms of multiparticle correlation observables dubbed Symmetric Cumulants.
 These observables are robust against biases originating from nonflow effects. 
@@
 Together with existing measurements of individual flow harmonics, the presented results provide further constraints 
-on initial conditions and the transport properties of the system produced in heavy-ion collisions.
+on the initial conditions and the transport properties of the system produced in heavy-ion collisions.

### 2017-08-20 appendix.tex
adding shudir's comment

@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT.eps}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
         \label{fig:Figure_A3}
@@
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
-The results are compared with selected calculations from three different types of models which are best in describing $v_n$ coefficients.}
+Results are compared with selected calculations from three different types of models which are best in describing $v_n$ coefficients.}
         \label{fig:Figure_A4}

### 2017-08-20 longSC.tex
dd
commit
adding shudir's comment

@@
 We also present a systematic comparison to hydrodynamic and AMPT model calculations.
-In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods.
+In Sec.~\ref{sec:method} we present the analysis methods and summarize our findings from the previous work~\cite{ALICE:2016kpq}.
 The experimental setup and measurements are described in Sec.~\ref{sec:experiment}.
@@
 The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations.
-The SC(4,2) and SC(3,2) are downscaled by 0.1.
+The SC(4,2) and SC(3,2) are downscaled by a factor of 0.1.
 Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
@@
 The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-For the data comparisons three different configurations of the AMPT model has been used: the default one and string melting with and without hadronic rescattering.
+For the data comparisons three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering.
 The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
@@
 The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was seen clearly in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}.
@@
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
+%As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
+While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are well described for the more central collisions and deviate by a little more than one sigma for 40--50\% centrality, as shown in Fig.~\ref{fig:Figure_3}.
 %For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
@@
 The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to describe the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
@@
 	%\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
-	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
+	\item All the VISH2+1 model calculations with large $\eta/s$ fail to describe the centrality dependence of the correlations regardless of the initial conditions.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively, but not quantitively for most of the centrality ranges.
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
@@
 %Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
-The agreement of various model calculations with the data is quantified using the log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} by calculating the ${\chi}^2$:
+The agreement of various model calculations with the data is quantified using the least squares-${\chi}^2$ method~\cite{PDBook} by calculating the ${\chi}^2$:
 
@@
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
-The ${\chi}^2$ values for the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) are shown in Fig.~\ref{fig:Figure_A5}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
+The ${\chi}^2$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
 This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
 This is quantified in Fig.~\ref{fig:Figure_A5}c, where the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
-The default AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2). However the ${\chi}^2$ values of this model are largest for $v_n$ among the models especially for $v_2$.
+The default configuration of the AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2).
+However the ${\chi}^2$ values of this model are largest for $v_n$ among the models especially for $v_2$.
 
@@
 
-\subsection{Transverse Momentum Dependence of NSC(3,2) and NSC(4,2)}
+\subsection{Transverse Momentum Dependence of Correlations between $v_2$ and $v_3$ and between $v_2$ and $v_4$}
 \label{sec:ptdepsc}
@@
               \end{center}
-             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_6}
@@
               \end{center}
-             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV is compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
+             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV.
+Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
              \label{fig:Figure_7}
@@
 This observation might help to understand the details of the fluctuations in the initial stage.
-The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to capture the centrality dependence of higher order correlations. 
+The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to describe the centrality dependence of higher order correlations. 
 Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions.

### 2017-08-20 longSC.tex
Ilya and constantan's comments

@@
 \begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d}{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
+E\frac{\mathrm{d}^3N}{\mathrm{d^3}{p}} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
 \label{Eq:Fourier}
@@
 %The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
-The data samples of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article were recorded by ALICE during the 2010 heavy-ion run of the LHC.
+The data sample of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
 Detailed descriptions of the ALICE detector can be found
@@
 For the data comparisons three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering.
-The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
+The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb.
 In the default configuration, partons are recombined with their parent strings when they stop interacting.
 The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
+The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
 In the string melting configuration, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
@@
 %As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
-While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are well described for the more central collisions and deviate by a little more than one sigma for 40--50\% centrality, as shown in Fig.~\ref{fig:Figure_3}.
+While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
 %For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
@@
 The ${\chi}^2$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
-This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
-%This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.
+The ${\chi}^2$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
+This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.
 
-%As discussed in \cite{ALICE:2016kpq}, the other $\eta/s(T)$ parameterizations in event-by-event EKRT+viscous hydrodynamics give worse descriptions for SC(4,2) and NSC(4,2) compared to ``param1''. 
-Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$).
+%This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
+%Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$).
 Furthermore we observe a clear separation of two parameterizations for SC(5,3) which is even larger than SC(4,2).
-These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.
+%These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.
 

### 2017-08-21 longSC.tex
final EB for CR2

@@
 %The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
-In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and it fails similarly for the anti-correlation between $v_3$ and $v_2$.
+In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and fail similarly for the anti-correlation between $v_3$ and $v_2$.
 %Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
@@
 %Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. 
-The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
+The SC(4,3) results clearly favor smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
 
@@
 The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
-The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
-Further investigations proved why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2).
+The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) smaller in the string melting AMPT model but not enough to describe the data.
+Further investigations proved why the default AMPT model can describe NSC(3,2) but underestimates SC(3,2).
 By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
@@
 %Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
-The agreement of various model calculations with the data is quantified using the least squares-${\chi}^2$ method~\cite{PDBook} by calculating the ${\chi}^2$:
+The agreement of various model calculations with the data is quantified by calculating the $\chi^{2}_{ndf}$:
 
 \begin{equation}
-\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+\chi^{2}_{ndf} = \frac{1}{N} \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
 \label{Eq:chisq}
@@
 The systematical and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
-The total number of data samples $N$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in ${\chi}^2$ calculations.
-The ${\chi}^2$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
+The total number of data samples $N$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chi^{2}_{ndf}$ calculations.
+The $\chi^{2}_{ndf}$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
 
@@
             \begin{center}
-                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
-        \caption{The ${\chi}^2$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
+                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisqndf_bestfits_3pad.eps}}
+        \caption{The $\chi^{2}_{ndf}$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
 Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
@@
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
-The ${\chi}^2$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the ${\chi}^2$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
+The $\chi^{2}_{ndf}$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chi^{2}_{ndf}$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
 This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, where the ${\chi}^2$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
-The default configuration of the AMPT model gives best ${\chi}^2$ values for NSC($m$,$n$), especially for NSC(3,2).
-However the ${\chi}^2$ values of this model are largest for $v_n$ among the models especially for $v_2$.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, where the $\chi^{2}_{ndf}$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+The default configuration of the AMPT model gives best $\chi^{2}_{ndf}$ values for NSC($m$,$n$), especially for NSC(3,2).
+However the $\chi^{2}_{ndf}$ values of this model are largest for $v_n$ among the models especially for $v_2$.
 
-The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
-The ${\chi}^2$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
-The ${\chi}^2$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
+The $\chi^{2}_{ndf}$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
+The $\chi^{2}_{ndf}$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
+The $\chi^{2}_{ndf}$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
 This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.
@@
 
-Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
+Even though the calculations from event-by-event EKRT+viscous hydrodynamics give the best $\chi^{2}_{ndf}$ values for both SC($m$,$n$) and NSC($m$,$n$), the $\chi^{2}_{ndf}$
 values are large especially for the observables which include $v_3$. 
-Even with the best model calculations from theoretical models, the ${\chi}^2$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
+Even with the best model calculations, the $\chi^{2}_{ndf}$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
 
@@
 The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
-The default configuration of the AMPT is well reproducing NSC(3,2), while the other AMPT configurations predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
+The default configuration of the AMPT reproduces NSC(3,2), while the other AMPT configurations predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
 In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for 40--50\% where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
@@
 Consequently, the observed weak $p_{\rm T}$ dependence may be due to hadronic rescattering.
-To clarify, the relative contributions to the final state particle distributions from partonic and hadronic stages need further study.
+The relative contributions to the final state particle distributions from partonic and hadronic stages need further study.
 
@@
 The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to describe the centrality dependence of higher order correlations. 
-Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions.
+Based on the tested model parameters, the data favor small $\eta/s$ and the AMPT initial conditions.
 

### 2017-08-21 longSC.tex
final fix

@@
 where the curly brackets denote the average over the transverse plane, i.e.
-$\{\cdots\}$ = $\int$ d$x$d$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
+$\{\cdots\}$ = $\int$ d$x$d$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $\phi$ is azimuthal angle, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
 There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.

### 2017-08-21 longSC.tex
minor fix
final version to CR2

@@
 %Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
-The agreement of various model calculations with the data is quantified by calculating the $\chi^{2}_{ndf}$:
+The agreement of various model calculations with the data is quantified by calculating the $\chisqndf$:
 
 \begin{equation}
-\chi^{2}_{ndf} = \frac{1}{N} \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
+\chi^2/N_{\rm dof} = \frac{1}{N_{\rm dof}} \sum_{i=1}^{N_{\rm dof}} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
 \label{Eq:chisq}
@@
 The systematical and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
-The total number of data samples $N$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chi^{2}_{ndf}$ calculations.
-The $\chi^{2}_{ndf}$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
+The total number of data samples $N_{\rm dof}$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
+The $\chisqndf$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
 
@@
                        \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisqndf_bestfits_3pad.eps}}
-        \caption{The $\chi^{2}_{ndf}$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
+        \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
 Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
@@
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
-The $\chi^{2}_{ndf}$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chi^{2}_{ndf}$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
+The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
+We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
 This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, where the $\chi^{2}_{ndf}$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
-The default configuration of the AMPT model gives best $\chi^{2}_{ndf}$ values for NSC($m$,$n$), especially for NSC(3,2).
-However the $\chi^{2}_{ndf}$ values of this model are largest for $v_n$ among the models especially for $v_2$.
+This is quantified in Fig.~\ref{fig:Figure_A5}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+The default configuration of the AMPT model gives the best $\chisqndf$ values for NSC($m$,$n$), especially for NSC(3,2).
+However the $\chisqndf$ values of this model are largest for $v_n$ among the models especially for $v_2$.
 
-The $\chi^{2}_{ndf}$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
-The $\chi^{2}_{ndf}$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
-The $\chi^{2}_{ndf}$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
+The $\chisqndf$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations.
+The $\chisqndf$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
+The $\chisqndf$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
 This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.
@@
 
-Even though the calculations from event-by-event EKRT+viscous hydrodynamics give the best $\chi^{2}_{ndf}$ values for both SC($m$,$n$) and NSC($m$,$n$), the $\chi^{2}_{ndf}$
+Even though the calculations from event-by-event EKRT+viscous hydrodynamics give the best $\chisqndf$ values for both SC($m$,$n$) and NSC($m$,$n$), the $\chisqndf$
 values are large especially for the observables which include $v_3$. 
-Even with the best model calculations, the $\chi^{2}_{ndf}$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
+Even with the best model calculations, the $\chisqndf$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
 

### 2017-08-21 abstract.tex
no definition on title and abstract

@@
 The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
-have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
+have been measured in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV with the ALICE detector at the Large Hadron Collider. 
 The results are reported in terms of multiparticle correlation observables dubbed Symmetric Cumulants.

### 2017-08-21 appendix.tex

@@
 Therefore, it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}.
-The $v_n$ is measured for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
+$v_n$ results presented in this section are for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
 %The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

### 2017-08-21 paper.tex
putting pic version for test
add working pic version
add sami's comment
final for IRC2
remove unused papers from bib
final for IRC3
v6.0 to PC
final from Ante's comments
to PC
fix figure1 and improved appendix11
6.2
final to IRC with appendix ?
add a reply
before You's comment
add a reference and correct wording
final for CR2
final version to CR2

@@
 \documentclass[ALICE,manyauthors]{cernphprep}
-
 \usepackage[comma,square,numbers,sort&compress]{natbib}
@@
 \usepackage{url,color}
+\usepackage{enumerate}   
+%\usepackage{refcheck}
 \linenumbers
@@
 \newcommand{\snn}{\ensuremath{\sqrt{s_\tn{NN}}}}
+\newcommand{\chisqndf}{\chi^2/N_{\rm dof}}
  % off by redefinding CKBNOTEje
@@
 \renewcommand{\RHNOTE}[1]{}  % switch off
-
+\newcommand{\multfigsize}{0.95}
 \begin{titlepage}
 %
-\PHyear{2016}
+\PHyear{2017}
 \PHnumber{xxx}                 % required, obtained from PH
-\PHdate{9 November}              % required, will be obtained from PH
+\PHdate{21 August}              % required, will be obtained from PH
 %
@@
 %%% Put your own title + short title here:
-\title{Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV}
+\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV}
 \ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
@@
 
+%\nocite{*}
+
 % \bibliographystyle{mybibstyle}
@@
 \bibliographystyle{utphys}
-\bibliography{paper}
-
+\bibliography{paper.bib}
 \newpage
@@
 %\input{}               %%%%%%%%%%% put your appendices here
+\input{appendix.tex}
 %
 %%%%%%%%% appendix with author list
-\appendix
 \section{The ALICE Collaboration}

### 2017-08-21 makediff.sh
final version for CR2

@@ -6,4 +6,6 @@
 #../git-latexdiff/git-latexdiff --main paper.tex master EB-R1
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 CR-Round1
 #../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1 CR-Round1.EB
-../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1.EB CR-Round1.EB.final
+#../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1.EB CR-Round1.EB.final
+../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
+../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe

### 2017-08-22 Alice_Authorlist_2017-Aug-21.tex
adding ack

% Collaboration: CERN-LHC-ALICE
% Generation Date is 2017-Aug-21

% How to use:
%%%%%%%%% appendix with author list
%\appendix
%\section{The ALICE Collaboration}
%\label{app:collab}
%\input{Alice_Authorslist_XXXX-Axx-XX.tex}
\begingroup
\small
\begin{flushleft}
S.~Acharya\Irefn{org137}\And, 
J.~Adam\Irefn{org96}\And, 
D.~Adamov\'{a}\Irefn{org93}\And, 
J.~Adolfsson\Irefn{org32}\And, 
M.M.~Aggarwal\Irefn{org98}\And, 
G.~Aglieri Rinella\Irefn{org33}\And, 
M.~Agnello\Irefn{org29}\And, 
N.~Agrawal\Irefn{org46}\And, 
Z.~Ahammed\Irefn{org137}\And, 
N.~Ahmad\Irefn{org15}\And, 
S.U.~Ahn\Irefn{org78}\And, 
S.~Aiola\Irefn{org141}\And, 
A.~Akindinov\Irefn{org63}\And, 
M.~Al-Turany\Irefn{org106}\And, 
S.N.~Alam\Irefn{org137}\And, 
J.L.B.~Alba\Irefn{org111}\And, 
D.S.D.~Albuquerque\Irefn{org122}\And, 
D.~Aleksandrov\Irefn{org89}\And, 
B.~Alessandro\Irefn{org57}\And, 
R.~Alfaro Molina\Irefn{org73}\And, 
A.~Alici\Irefn{org11}\textsuperscript{,}\Irefn{org25}\textsuperscript{,}\Irefn{org52}\And, 
A.~Alkin\Irefn{org3}\And, 
J.~Alme\Irefn{org20}\And, 
T.~Alt\Irefn{org69}\And, 
L.~Altenkamper\Irefn{org20}\And, 
I.~Altsybeev\Irefn{org136}\And, 
C.~Alves Garcia Prado\Irefn{org121}\And, 
C.~Andrei\Irefn{org86}\And, 
D.~Andreou\Irefn{org33}\And, 
H.A.~Andrews\Irefn{org110}\And, 
A.~Andronic\Irefn{org106}\And, 
V.~Anguelov\Irefn{org103}\And, 
C.~Anson\Irefn{org96}\And, 
T.~Anti\v{c}i\'{c}\Irefn{org107}\And, 
F.~Antinori\Irefn{org55}\And, 
P.~Antonioli\Irefn{org52}\And, 
R.~Anwar\Irefn{org124}\And, 
L.~Aphecetche\Irefn{org114}\And, 
H.~Appelsh\"{a}user\Irefn{org69}\And, 
S.~Arcelli\Irefn{org25}\And, 
R.~Arnaldi\Irefn{org57}\And, 
O.W.~Arnold\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
I.C.~Arsene\Irefn{org19}\And, 
M.~Arslandok\Irefn{org103}\And, 
B.~Audurier\Irefn{org114}\And, 
A.~Augustinus\Irefn{org33}\And, 
R.~Averbeck\Irefn{org106}\And, 
M.D.~Azmi\Irefn{org15}\And, 
A.~Badal\`{a}\Irefn{org54}\And, 
Y.W.~Baek\Irefn{org59}\textsuperscript{,}\Irefn{org77}\And, 
S.~Bagnasco\Irefn{org57}\And, 
R.~Bailhache\Irefn{org69}\And, 
R.~Bala\Irefn{org100}\And, 
A.~Baldisseri\Irefn{org74}\And, 
M.~Ball\Irefn{org43}\And, 
R.C.~Baral\Irefn{org66}\textsuperscript{,}\Irefn{org87}\And, 
A.M.~Barbano\Irefn{org24}\And, 
R.~Barbera\Irefn{org26}\And, 
F.~Barile\Irefn{org51}\textsuperscript{,}\Irefn{org31}\And, 
L.~Barioglio\Irefn{org24}\And, 
G.G.~Barnaf\"{o}ldi\Irefn{org140}\And, 
L.S.~Barnby\Irefn{org92}\And, 
V.~Barret\Irefn{org131}\And, 
P.~Bartalini\Irefn{org7}\And, 
K.~Barth\Irefn{org33}\And, 
E.~Bartsch\Irefn{org69}\And, 
M.~Basile\Irefn{org25}\And, 
N.~Bastid\Irefn{org131}\And, 
S.~Basu\Irefn{org139}\And, 
G.~Batigne\Irefn{org114}\And, 
B.~Batyunya\Irefn{org76}\And, 
P.C.~Batzing\Irefn{org19}\And, 
I.G.~Bearden\Irefn{org90}\And, 
H.~Beck\Irefn{org103}\And, 
C.~Bedda\Irefn{org62}\And, 
N.K.~Behera\Irefn{org59}\And, 
I.~Belikov\Irefn{org133}\And, 
F.~Bellini\Irefn{org25}\textsuperscript{,}\Irefn{org33}\And, 
H.~Bello Martinez\Irefn{org2}\And, 
R.~Bellwied\Irefn{org124}\And, 
L.G.E.~Beltran\Irefn{org120}\And, 
V.~Belyaev\Irefn{org82}\And, 
G.~Bencedi\Irefn{org140}\And, 
S.~Beole\Irefn{org24}\And, 
A.~Bercuci\Irefn{org86}\And, 
Y.~Berdnikov\Irefn{org95}\And, 
D.~Berenyi\Irefn{org140}\And, 
R.A.~Bertens\Irefn{org127}\And, 
D.~Berzano\Irefn{org33}\And, 
L.~Betev\Irefn{org33}\And, 
A.~Bhasin\Irefn{org100}\And, 
I.R.~Bhat\Irefn{org100}\And, 
A.K.~Bhati\Irefn{org98}\And, 
B.~Bhattacharjee\Irefn{org42}\And, 
J.~Bhom\Irefn{org118}\And, 
A.~Bianchi\Irefn{org24}\And, 
L.~Bianchi\Irefn{org124}\And, 
N.~Bianchi\Irefn{org49}\And, 
C.~Bianchin\Irefn{org139}\And, 
J.~Biel\v{c}\'{\i}k\Irefn{org37}\And, 
J.~Biel\v{c}\'{\i}kov\'{a}\Irefn{org93}\And, 
A.~Bilandzic\Irefn{org34}\textsuperscript{,}\Irefn{org104}\And, 
G.~Biro\Irefn{org140}\And, 
R.~Biswas\Irefn{org4}\And, 
S.~Biswas\Irefn{org4}\And, 
J.T.~Blair\Irefn{org119}\And, 
D.~Blau\Irefn{org89}\And, 
C.~Blume\Irefn{org69}\And, 
G.~Boca\Irefn{org134}\And, 
F.~Bock\Irefn{org103}\textsuperscript{,}\Irefn{org81}\textsuperscript{,}\Irefn{org33}\And, 
A.~Bogdanov\Irefn{org82}\And, 
L.~Boldizs\'{a}r\Irefn{org140}\And, 
M.~Bombara\Irefn{org38}\And, 
G.~Bonomi\Irefn{org135}\And, 
M.~Bonora\Irefn{org33}\And, 
J.~Book\Irefn{org69}\And, 
H.~Borel\Irefn{org74}\And, 
A.~Borissov\Irefn{org17}\textsuperscript{,}\Irefn{org103}\And, 
M.~Borri\Irefn{org126}\And, 
E.~Botta\Irefn{org24}\And, 
C.~Bourjau\Irefn{org90}\And, 
L.~Bratrud\Irefn{org69}\And, 
P.~Braun-Munzinger\Irefn{org106}\And, 
M.~Bregant\Irefn{org121}\And, 
T.A.~Broker\Irefn{org69}\And, 
M.~Broz\Irefn{org37}\And, 
E.J.~Brucken\Irefn{org44}\And, 
E.~Bruna\Irefn{org57}\And, 
G.E.~Bruno\Irefn{org33}\textsuperscript{,}\Irefn{org31}\And, 
D.~Budnikov\Irefn{org108}\And, 
H.~Buesching\Irefn{org69}\And, 
S.~Bufalino\Irefn{org29}\And, 
P.~Buhler\Irefn{org113}\And, 
P.~Buncic\Irefn{org33}\And, 
O.~Busch\Irefn{org130}\And, 
Z.~Buthelezi\Irefn{org75}\And, 
J.B.~Butt\Irefn{org14}\And, 
J.T.~Buxton\Irefn{org16}\And, 
J.~Cabala\Irefn{org116}\And, 
D.~Caffarri\Irefn{org33}\textsuperscript{,}\Irefn{org91}\And, 
H.~Caines\Irefn{org141}\And, 
A.~Caliva\Irefn{org62}\textsuperscript{,}\Irefn{org106}\And, 
E.~Calvo Villar\Irefn{org111}\And, 
P.~Camerini\Irefn{org23}\And, 
A.A.~Capon\Irefn{org113}\And, 
F.~Carena\Irefn{org33}\And, 
W.~Carena\Irefn{org33}\And, 
F.~Carnesecchi\Irefn{org25}\textsuperscript{,}\Irefn{org11}\And, 
J.~Castillo Castellanos\Irefn{org74}\And, 
A.J.~Castro\Irefn{org127}\And, 
E.A.R.~Casula\Irefn{org53}\And, 
C.~Ceballos Sanchez\Irefn{org9}\And, 
P.~Cerello\Irefn{org57}\And, 
S.~Chandra\Irefn{org137}\And, 
B.~Chang\Irefn{org125}\And, 
S.~Chapeland\Irefn{org33}\And, 
M.~Chartier\Irefn{org126}\And, 
S.~Chattopadhyay\Irefn{org137}\And, 
S.~Chattopadhyay\Irefn{org109}\And, 
A.~Chauvin\Irefn{org34}\textsuperscript{,}\Irefn{org104}\And, 
C.~Cheshkov\Irefn{org132}\And, 
B.~Cheynis\Irefn{org132}\And, 
V.~Chibante Barroso\Irefn{org33}\And, 
D.D.~Chinellato\Irefn{org122}\And, 
S.~Cho\Irefn{org59}\And, 
P.~Chochula\Irefn{org33}\And, 
M.~Chojnacki\Irefn{org90}\And, 
S.~Choudhury\Irefn{org137}\And, 
T.~Chowdhury\Irefn{org131}\And, 
P.~Christakoglou\Irefn{org91}\And, 
C.H.~Christensen\Irefn{org90}\And, 
P.~Christiansen\Irefn{org32}\And, 
T.~Chujo\Irefn{org130}\And, 
S.U.~Chung\Irefn{org17}\And, 
C.~Cicalo\Irefn{org53}\And, 
L.~Cifarelli\Irefn{org11}\textsuperscript{,}\Irefn{org25}\And, 
F.~Cindolo\Irefn{org52}\And, 
J.~Cleymans\Irefn{org99}\And, 
F.~Colamaria\Irefn{org31}\And, 
D.~Colella\Irefn{org33}\textsuperscript{,}\Irefn{org64}\textsuperscript{,}\Irefn{org51}\And, 
A.~Collu\Irefn{org81}\And, 
M.~Colocci\Irefn{org25}\And, 
M.~Concas\Irefn{org57}\textsuperscript{,}\Aref{orgI}\And, 
G.~Conesa Balbastre\Irefn{org80}\And, 
Z.~Conesa del Valle\Irefn{org60}\And, 
M.E.~Connors\Irefn{org141}\textsuperscript{,}\Aref{orgII}\And, 
J.G.~Contreras\Irefn{org37}\And, 
T.M.~Cormier\Irefn{org94}\And, 
Y.~Corrales Morales\Irefn{org57}\And, 
I.~Cort\'{e}s Maldonado\Irefn{org2}\And, 
P.~Cortese\Irefn{org30}\And, 
M.R.~Cosentino\Irefn{org123}\And, 
F.~Costa\Irefn{org33}\And, 
S.~Costanza\Irefn{org134}\And, 
J.~Crkovsk\'{a}\Irefn{org60}\And, 
P.~Crochet\Irefn{org131}\And, 
E.~Cuautle\Irefn{org71}\And, 
L.~Cunqueiro\Irefn{org70}\And, 
T.~Dahms\Irefn{org34}\textsuperscript{,}\Irefn{org104}\And, 
A.~Dainese\Irefn{org55}\And, 
M.C.~Danisch\Irefn{org103}\And, 
A.~Danu\Irefn{org67}\And, 
D.~Das\Irefn{org109}\And, 
I.~Das\Irefn{org109}\And, 
S.~Das\Irefn{org4}\And, 
A.~Dash\Irefn{org87}\And, 
S.~Dash\Irefn{org46}\And, 
S.~De\Irefn{org47}\textsuperscript{,}\Irefn{org121}\And, 
A.~De Caro\Irefn{org28}\And, 
G.~de Cataldo\Irefn{org51}\And, 
C.~de Conti\Irefn{org121}\And, 
J.~de Cuveland\Irefn{org40}\And, 
A.~De Falco\Irefn{org22}\And, 
D.~De Gruttola\Irefn{org28}\textsuperscript{,}\Irefn{org11}\And, 
N.~De Marco\Irefn{org57}\And, 
S.~De Pasquale\Irefn{org28}\And, 
R.D.~De Souza\Irefn{org122}\And, 
H.F.~Degenhardt\Irefn{org121}\And, 
A.~Deisting\Irefn{org106}\textsuperscript{,}\Irefn{org103}\And, 
A.~Deloff\Irefn{org85}\And, 
C.~Deplano\Irefn{org91}\And, 
P.~Dhankher\Irefn{org46}\And, 
D.~Di Bari\Irefn{org31}\And, 
A.~Di Mauro\Irefn{org33}\And, 
P.~Di Nezza\Irefn{org49}\And, 
B.~Di Ruzza\Irefn{org55}\And, 
T.~Dietel\Irefn{org99}\And, 
P.~Dillenseger\Irefn{org69}\And, 
R.~Divi\`{a}\Irefn{org33}\And, 
{\O}.~Djuvsland\Irefn{org20}\And, 
A.~Dobrin\Irefn{org33}\And, 
D.~Domenicis Gimenez\Irefn{org121}\And, 
B.~D\"{o}nigus\Irefn{org69}\And, 
O.~Dordic\Irefn{org19}\And, 
L.V.R.~Doremalen\Irefn{org62}\And, 
A.K.~Dubey\Irefn{org137}\And, 
A.~Dubla\Irefn{org106}\And, 
L.~Ducroux\Irefn{org132}\And, 
A.K.~Duggal\Irefn{org98}\And, 
M.~Dukhishyam\Irefn{org87}\And, 
P.~Dupieux\Irefn{org131}\And, 
R.J.~Ehlers\Irefn{org141}\And, 
D.~Elia\Irefn{org51}\And, 
E.~Endress\Irefn{org111}\And, 
H.~Engel\Irefn{org68}\And, 
E.~Epple\Irefn{org141}\And, 
B.~Erazmus\Irefn{org114}\And, 
F.~Erhardt\Irefn{org97}\And, 
B.~Espagnon\Irefn{org60}\And, 
S.~Esumi\Irefn{org130}\And, 
G.~Eulisse\Irefn{org33}\And, 
J.~Eum\Irefn{org17}\And, 
D.~Evans\Irefn{org110}\And, 
S.~Evdokimov\Irefn{org112}\And, 
L.~Fabbietti\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
J.~Faivre\Irefn{org80}\And, 
A.~Fantoni\Irefn{org49}\And, 
M.~Fasel\Irefn{org94}\textsuperscript{,}\Irefn{org81}\And, 
L.~Feldkamp\Irefn{org70}\And, 
A.~Feliciello\Irefn{org57}\And, 
G.~Feofilov\Irefn{org136}\And, 
A.~Fern\'{a}ndez T\'{e}llez\Irefn{org2}\And, 
A.~Ferretti\Irefn{org24}\And, 
A.~Festanti\Irefn{org27}\textsuperscript{,}\Irefn{org33}\And, 
V.J.G.~Feuillard\Irefn{org74}\textsuperscript{,}\Irefn{org131}\And, 
J.~Figiel\Irefn{org118}\And, 
M.A.S.~Figueredo\Irefn{org121}\And, 
S.~Filchagin\Irefn{org108}\And, 
D.~Finogeev\Irefn{org61}\And, 
F.M.~Fionda\Irefn{org20}\textsuperscript{,}\Irefn{org22}\And, 
M.~Floris\Irefn{org33}\And, 
S.~Foertsch\Irefn{org75}\And, 
P.~Foka\Irefn{org106}\And, 
S.~Fokin\Irefn{org89}\And, 
E.~Fragiacomo\Irefn{org58}\And, 
A.~Francescon\Irefn{org33}\And, 
A.~Francisco\Irefn{org114}\And, 
U.~Frankenfeld\Irefn{org106}\And, 
G.G.~Fronze\Irefn{org24}\And, 
U.~Fuchs\Irefn{org33}\And, 
C.~Furget\Irefn{org80}\And, 
A.~Furs\Irefn{org61}\And, 
M.~Fusco Girard\Irefn{org28}\And, 
J.J.~Gaardh{\o}je\Irefn{org90}\And, 
M.~Gagliardi\Irefn{org24}\And, 
A.M.~Gago\Irefn{org111}\And, 
K.~Gajdosova\Irefn{org90}\And, 
M.~Gallio\Irefn{org24}\And, 
C.D.~Galvan\Irefn{org120}\And, 
P.~Ganoti\Irefn{org84}\And, 
C.~Garabatos\Irefn{org106}\And, 
E.~Garcia-Solis\Irefn{org12}\And, 
K.~Garg\Irefn{org26}\And, 
C.~Gargiulo\Irefn{org33}\And, 
P.~Gasik\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
E.F.~Gauger\Irefn{org119}\And, 
M.B.~Gay Ducati\Irefn{org72}\And, 
M.~Germain\Irefn{org114}\And, 
J.~Ghosh\Irefn{org109}\And, 
P.~Ghosh\Irefn{org137}\And, 
S.K.~Ghosh\Irefn{org4}\And, 
P.~Gianotti\Irefn{org49}\And, 
P.~Giubellino\Irefn{org33}\textsuperscript{,}\Irefn{org106}\textsuperscript{,}\Irefn{org57}\And, 
P.~Giubilato\Irefn{org27}\And, 
E.~Gladysz-Dziadus\Irefn{org118}\And, 
P.~Gl\"{a}ssel\Irefn{org103}\And, 
D.M.~Gom\'{e}z Coral\Irefn{org73}\And, 
A.~Gomez Ramirez\Irefn{org68}\And, 
A.S.~Gonzalez\Irefn{org33}\And, 
P.~Gonz\'{a}lez-Zamora\Irefn{org2}\And, 
S.~Gorbunov\Irefn{org40}\And, 
L.~G\"{o}rlich\Irefn{org118}\And, 
S.~Gotovac\Irefn{org117}\And, 
V.~Grabski\Irefn{org73}\And, 
L.K.~Graczykowski\Irefn{org138}\And, 
K.L.~Graham\Irefn{org110}\And, 
L.~Greiner\Irefn{org81}\And, 
A.~Grelli\Irefn{org62}\And, 
C.~Grigoras\Irefn{org33}\And, 
V.~Grigoriev\Irefn{org82}\And, 
A.~Grigoryan\Irefn{org1}\And, 
S.~Grigoryan\Irefn{org76}\And, 
J.M.~Gronefeld\Irefn{org106}\And, 
F.~Grosa\Irefn{org29}\And, 
J.F.~Grosse-Oetringhaus\Irefn{org33}\And, 
R.~Grosso\Irefn{org106}\And, 
L.~Gruber\Irefn{org113}\And, 
F.~Guber\Irefn{org61}\And, 
R.~Guernane\Irefn{org80}\And, 
B.~Guerzoni\Irefn{org25}\And, 
K.~Gulbrandsen\Irefn{org90}\And, 
T.~Gunji\Irefn{org129}\And, 
A.~Gupta\Irefn{org100}\And, 
R.~Gupta\Irefn{org100}\And, 
I.B.~Guzman\Irefn{org2}\And, 
R.~Haake\Irefn{org33}\And, 
C.~Hadjidakis\Irefn{org60}\And, 
H.~Hamagaki\Irefn{org83}\And, 
G.~Hamar\Irefn{org140}\And, 
J.C.~Hamon\Irefn{org133}\And, 
M.R.~Haque\Irefn{org62}\And, 
J.W.~Harris\Irefn{org141}\And, 
A.~Harton\Irefn{org12}\And, 
H.~Hassan\Irefn{org80}\And, 
D.~Hatzifotiadou\Irefn{org11}\textsuperscript{,}\Irefn{org52}\And, 
S.~Hayashi\Irefn{org129}\And, 
S.T.~Heckel\Irefn{org69}\And, 
E.~Hellb\"{a}r\Irefn{org69}\And, 
H.~Helstrup\Irefn{org35}\And, 
A.~Herghelegiu\Irefn{org86}\And, 
E.G.~Hernandez\Irefn{org2}\And, 
G.~Herrera Corral\Irefn{org10}\And, 
F.~Herrmann\Irefn{org70}\And, 
B.A.~Hess\Irefn{org102}\And, 
K.F.~Hetland\Irefn{org35}\And, 
H.~Hillemanns\Irefn{org33}\And, 
C.~Hills\Irefn{org126}\And, 
B.~Hippolyte\Irefn{org133}\And, 
J.~Hladky\Irefn{org65}\And, 
B.~Hohlweger\Irefn{org104}\And, 
D.~Horak\Irefn{org37}\And, 
S.~Hornung\Irefn{org106}\And, 
R.~Hosokawa\Irefn{org130}\textsuperscript{,}\Irefn{org80}\And, 
P.~Hristov\Irefn{org33}\And, 
C.~Hughes\Irefn{org127}\And, 
T.J.~Humanic\Irefn{org16}\And, 
N.~Hussain\Irefn{org42}\And, 
T.~Hussain\Irefn{org15}\And, 
D.~Hutter\Irefn{org40}\And, 
D.S.~Hwang\Irefn{org18}\And, 
S.A.~Iga~Buitron\Irefn{org71}\And, 
R.~Ilkaev\Irefn{org108}\And, 
M.~Inaba\Irefn{org130}\And, 
M.~Ippolitov\Irefn{org82}\textsuperscript{,}\Irefn{org89}\And, 
M.~Irfan\Irefn{org15}\And, 
M.S.~Islam\Irefn{org109}\And, 
M.~Ivanov\Irefn{org106}\And, 
V.~Ivanov\Irefn{org95}\And, 
V.~Izucheev\Irefn{org112}\And, 
B.~Jacak\Irefn{org81}\And, 
N.~Jacazio\Irefn{org25}\And, 
P.M.~Jacobs\Irefn{org81}\And, 
M.B.~Jadhav\Irefn{org46}\And, 
J.~Jadlovsky\Irefn{org116}\And, 
S.~Jaelani\Irefn{org62}\And, 
C.~Jahnke\Irefn{org34}\And, 
M.J.~Jakubowska\Irefn{org138}\And, 
M.A.~Janik\Irefn{org138}\And, 
P.H.S.Y.~Jayarathna\Irefn{org124}\And, 
C.~Jena\Irefn{org87}\And, 
S.~Jena\Irefn{org124}\And, 
M.~Jercic\Irefn{org97}\And, 
R.T.~Jimenez Bustamante\Irefn{org106}\And, 
P.G.~Jones\Irefn{org110}\And, 
A.~Jusko\Irefn{org110}\And, 
P.~Kalinak\Irefn{org64}\And, 
A.~Kalweit\Irefn{org33}\And, 
J.H.~Kang\Irefn{org142}\And, 
V.~Kaplin\Irefn{org82}\And, 
S.~Kar\Irefn{org137}\And, 
A.~Karasu Uysal\Irefn{org79}\And, 
O.~Karavichev\Irefn{org61}\And, 
T.~Karavicheva\Irefn{org61}\And, 
L.~Karayan\Irefn{org103}\textsuperscript{,}\Irefn{org106}\And, 
P.~Karczmarczyk\Irefn{org33}\And, 
E.~Karpechev\Irefn{org61}\And, 
U.~Kebschull\Irefn{org68}\And, 
R.~Keidel\Irefn{org143}\And, 
D.L.D.~Keijdener\Irefn{org62}\And, 
M.~Keil\Irefn{org33}\And, 
B.~Ketzer\Irefn{org43}\And, 
Z.~Khabanova\Irefn{org91}\And, 
P.~Khan\Irefn{org109}\And, 
S.A.~Khan\Irefn{org137}\And, 
A.~Khanzadeev\Irefn{org95}\And, 
Y.~Kharlov\Irefn{org112}\And, 
A.~Khatun\Irefn{org15}\And, 
A.~Khuntia\Irefn{org47}\And, 
M.M.~Kielbowicz\Irefn{org118}\And, 
B.~Kileng\Irefn{org35}\And, 
B.~Kim\Irefn{org130}\And, 
D.~Kim\Irefn{org142}\And, 
D.J.~Kim\Irefn{org125}\And, 
H.~Kim\Irefn{org142}\And, 
J.S.~Kim\Irefn{org41}\And, 
J.~Kim\Irefn{org103}\And, 
M.~Kim\Irefn{org59}\And, 
M.~Kim\Irefn{org142}\And, 
S.~Kim\Irefn{org18}\And, 
T.~Kim\Irefn{org142}\And, 
S.~Kirsch\Irefn{org40}\And, 
I.~Kisel\Irefn{org40}\And, 
S.~Kiselev\Irefn{org63}\And, 
A.~Kisiel\Irefn{org138}\And, 
G.~Kiss\Irefn{org140}\And, 
J.L.~Klay\Irefn{org6}\And, 
C.~Klein\Irefn{org69}\And, 
J.~Klein\Irefn{org33}\And, 
C.~Klein-B\"{o}sing\Irefn{org70}\And, 
S.~Klewin\Irefn{org103}\And, 
A.~Kluge\Irefn{org33}\And, 
M.L.~Knichel\Irefn{org33}\textsuperscript{,}\Irefn{org103}\And, 
A.G.~Knospe\Irefn{org124}\And, 
C.~Kobdaj\Irefn{org115}\And, 
M.~Kofarago\Irefn{org140}\And, 
M.K.~K\"{o}hler\Irefn{org103}\And, 
T.~Kollegger\Irefn{org106}\And, 
V.~Kondratiev\Irefn{org136}\And, 
N.~Kondratyeva\Irefn{org82}\And, 
E.~Kondratyuk\Irefn{org112}\And, 
A.~Konevskikh\Irefn{org61}\And, 
M.~Konyushikhin\Irefn{org139}\And, 
M.~Kopcik\Irefn{org116}\And, 
M.~Kour\Irefn{org100}\And, 
C.~Kouzinopoulos\Irefn{org33}\And, 
O.~Kovalenko\Irefn{org85}\And, 
V.~Kovalenko\Irefn{org136}\And, 
M.~Kowalski\Irefn{org118}\And, 
G.~Koyithatta Meethaleveedu\Irefn{org46}\And, 
I.~Kr\'{a}lik\Irefn{org64}\And, 
A.~Krav\v{c}\'{a}kov\'{a}\Irefn{org38}\And, 
L.~Kreis\Irefn{org106}\And, 
M.~Krivda\Irefn{org110}\textsuperscript{,}\Irefn{org64}\And, 
F.~Krizek\Irefn{org93}\And, 
E.~Kryshen\Irefn{org95}\And, 
M.~Krzewicki\Irefn{org40}\And, 
A.M.~Kubera\Irefn{org16}\And, 
V.~Ku\v{c}era\Irefn{org93}\And, 
C.~Kuhn\Irefn{org133}\And, 
P.G.~Kuijer\Irefn{org91}\And, 
A.~Kumar\Irefn{org100}\And, 
J.~Kumar\Irefn{org46}\And, 
L.~Kumar\Irefn{org98}\And, 
S.~Kumar\Irefn{org46}\And, 
S.~Kundu\Irefn{org87}\And, 
P.~Kurashvili\Irefn{org85}\And, 
A.~Kurepin\Irefn{org61}\And, 
A.B.~Kurepin\Irefn{org61}\And, 
A.~Kuryakin\Irefn{org108}\And, 
S.~Kushpil\Irefn{org93}\And, 
M.J.~Kweon\Irefn{org59}\And, 
Y.~Kwon\Irefn{org142}\And, 
S.L.~La Pointe\Irefn{org40}\And, 
P.~La Rocca\Irefn{org26}\And, 
C.~Lagana Fernandes\Irefn{org121}\And, 
Y.S.~Lai\Irefn{org81}\And, 
I.~Lakomov\Irefn{org33}\And, 
R.~Langoy\Irefn{org39}\And, 
K.~Lapidus\Irefn{org141}\And, 
C.~Lara\Irefn{org68}\And, 
A.~Lardeux\Irefn{org74}\textsuperscript{,}\Irefn{org19}\And, 
A.~Lattuca\Irefn{org24}\And, 
E.~Laudi\Irefn{org33}\And, 
R.~Lavicka\Irefn{org37}\And, 
R.~Lea\Irefn{org23}\And, 
L.~Leardini\Irefn{org103}\And, 
S.~Lee\Irefn{org142}\And, 
F.~Lehas\Irefn{org91}\And, 
S.~Lehner\Irefn{org113}\And, 
J.~Lehrbach\Irefn{org40}\And, 
R.C.~Lemmon\Irefn{org92}\And, 
V.~Lenti\Irefn{org51}\And, 
E.~Leogrande\Irefn{org62}\And, 
I.~Le\'{o}n Monz\'{o}n\Irefn{org120}\And, 
P.~L\'{e}vai\Irefn{org140}\And, 
X.~Li\Irefn{org13}\And, 
J.~Lien\Irefn{org39}\And, 
R.~Lietava\Irefn{org110}\And, 
B.~Lim\Irefn{org17}\And, 
S.~Lindal\Irefn{org19}\And, 
V.~Lindenstruth\Irefn{org40}\And, 
S.W.~Lindsay\Irefn{org126}\And, 
C.~Lippmann\Irefn{org106}\And, 
M.A.~Lisa\Irefn{org16}\And, 
V.~Litichevskyi\Irefn{org44}\And, 
W.J.~Llope\Irefn{org139}\And, 
D.F.~Lodato\Irefn{org62}\And, 
P.I.~Loenne\Irefn{org20}\And, 
V.~Loginov\Irefn{org82}\And, 
C.~Loizides\Irefn{org81}\And, 
P.~Loncar\Irefn{org117}\And, 
X.~Lopez\Irefn{org131}\And, 
E.~L\'{o}pez Torres\Irefn{org9}\And, 
A.~Lowe\Irefn{org140}\And, 
P.~Luettig\Irefn{org69}\And, 
J.R.~Luhder\Irefn{org70}\And, 
M.~Lunardon\Irefn{org27}\And, 
G.~Luparello\Irefn{org58}\textsuperscript{,}\Irefn{org23}\And, 
M.~Lupi\Irefn{org33}\And, 
T.H.~Lutz\Irefn{org141}\And, 
A.~Maevskaya\Irefn{org61}\And, 
M.~Mager\Irefn{org33}\And, 
S.~Mahajan\Irefn{org100}\And, 
S.M.~Mahmood\Irefn{org19}\And, 
A.~Maire\Irefn{org133}\And, 
R.D.~Majka\Irefn{org141}\And, 
M.~Malaev\Irefn{org95}\And, 
L.~Malinina\Irefn{org76}\textsuperscript{,}\Aref{orgIII}\And, 
D.~Mal'Kevich\Irefn{org63}\And, 
P.~Malzacher\Irefn{org106}\And, 
A.~Mamonov\Irefn{org108}\And, 
V.~Manko\Irefn{org89}\And, 
F.~Manso\Irefn{org131}\And, 
V.~Manzari\Irefn{org51}\And, 
Y.~Mao\Irefn{org7}\And, 
M.~Marchisone\Irefn{org75}\textsuperscript{,}\Irefn{org128}\And, 
J.~Mare\v{s}\Irefn{org65}\And, 
G.V.~Margagliotti\Irefn{org23}\And, 
A.~Margotti\Irefn{org52}\And, 
J.~Margutti\Irefn{org62}\And, 
A.~Mar\'{\i}n\Irefn{org106}\And, 
C.~Markert\Irefn{org119}\And, 
M.~Marquard\Irefn{org69}\And, 
N.A.~Martin\Irefn{org106}\And, 
P.~Martinengo\Irefn{org33}\And, 
J.A.L.~Martinez\Irefn{org68}\And, 
M.I.~Mart\'{\i}nez\Irefn{org2}\And, 
G.~Mart\'{\i}nez Garc\'{\i}a\Irefn{org114}\And, 
M.~Martinez Pedreira\Irefn{org33}\And, 
S.~Masciocchi\Irefn{org106}\And, 
M.~Masera\Irefn{org24}\And, 
A.~Masoni\Irefn{org53}\And, 
E.~Masson\Irefn{org114}\And, 
A.~Mastroserio\Irefn{org51}\And, 
A.M.~Mathis\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
P.F.T.~Matuoka\Irefn{org121}\And, 
A.~Matyja\Irefn{org127}\And, 
C.~Mayer\Irefn{org118}\And, 
J.~Mazer\Irefn{org127}\And, 
M.~Mazzilli\Irefn{org31}\And, 
M.A.~Mazzoni\Irefn{org56}\And, 
F.~Meddi\Irefn{org21}\And, 
Y.~Melikyan\Irefn{org82}\And, 
A.~Menchaca-Rocha\Irefn{org73}\And, 
E.~Meninno\Irefn{org28}\And, 
J.~Mercado P\'erez\Irefn{org103}\And, 
M.~Meres\Irefn{org36}\And, 
S.~Mhlanga\Irefn{org99}\And, 
Y.~Miake\Irefn{org130}\And, 
M.M.~Mieskolainen\Irefn{org44}\And, 
D.L.~Mihaylov\Irefn{org104}\And, 
K.~Mikhaylov\Irefn{org63}\textsuperscript{,}\Irefn{org76}\And, 
J.~Milosevic\Irefn{org19}\And, 
A.~Mischke\Irefn{org62}\And, 
A.N.~Mishra\Irefn{org47}\And, 
D.~Mi\'{s}kowiec\Irefn{org106}\And, 
J.~Mitra\Irefn{org137}\And, 
C.M.~Mitu\Irefn{org67}\And, 
N.~Mohammadi\Irefn{org62}\And, 
B.~Mohanty\Irefn{org87}\And, 
M.~Mohisin Khan\Irefn{org15}\textsuperscript{,}\Aref{orgIV}\And, 
D.A.~Moreira De Godoy\Irefn{org70}\And, 
L.A.P.~Moreno\Irefn{org2}\And, 
S.~Moretto\Irefn{org27}\And, 
A.~Morreale\Irefn{org114}\And, 
A.~Morsch\Irefn{org33}\And, 
V.~Muccifora\Irefn{org49}\And, 
E.~Mudnic\Irefn{org117}\And, 
D.~M{\"u}hlheim\Irefn{org70}\And, 
S.~Muhuri\Irefn{org137}\And, 
M.~Mukherjee\Irefn{org4}\And, 
J.D.~Mulligan\Irefn{org141}\And, 
M.G.~Munhoz\Irefn{org121}\And, 
K.~M\"{u}nning\Irefn{org43}\And, 
R.H.~Munzer\Irefn{org69}\And, 
H.~Murakami\Irefn{org129}\And, 
S.~Murray\Irefn{org75}\And, 
L.~Musa\Irefn{org33}\And, 
J.~Musinsky\Irefn{org64}\And, 
C.J.~Myers\Irefn{org124}\And, 
J.W.~Myrcha\Irefn{org138}\And, 
D.~Nag\Irefn{org4}\And, 
B.~Naik\Irefn{org46}\And, 
R.~Nair\Irefn{org85}\And, 
B.K.~Nandi\Irefn{org46}\And, 
R.~Nania\Irefn{org52}\textsuperscript{,}\Irefn{org11}\And, 
E.~Nappi\Irefn{org51}\And, 
A.~Narayan\Irefn{org46}\And, 
M.U.~Naru\Irefn{org14}\And, 
H.~Natal da Luz\Irefn{org121}\And, 
C.~Nattrass\Irefn{org127}\And, 
S.R.~Navarro\Irefn{org2}\And, 
K.~Nayak\Irefn{org87}\And, 
R.~Nayak\Irefn{org46}\And, 
T.K.~Nayak\Irefn{org137}\And, 
S.~Nazarenko\Irefn{org108}\And, 
A.~Nedosekin\Irefn{org63}\And, 
R.A.~Negrao De Oliveira\Irefn{org33}\And, 
L.~Nellen\Irefn{org71}\And, 
S.V.~Nesbo\Irefn{org35}\And, 
F.~Ng\Irefn{org124}\And, 
M.~Nicassio\Irefn{org106}\And, 
M.~Niculescu\Irefn{org67}\And, 
J.~Niedziela\Irefn{org138}\textsuperscript{,}\Irefn{org33}\And, 
B.S.~Nielsen\Irefn{org90}\And, 
S.~Nikolaev\Irefn{org89}\And, 
S.~Nikulin\Irefn{org89}\And, 
V.~Nikulin\Irefn{org95}\And, 
F.~Noferini\Irefn{org11}\textsuperscript{,}\Irefn{org52}\And, 
P.~Nomokonov\Irefn{org76}\And, 
G.~Nooren\Irefn{org62}\And, 
J.C.C.~Noris\Irefn{org2}\And, 
J.~Norman\Irefn{org126}\And, 
A.~Nyanin\Irefn{org89}\And, 
J.~Nystrand\Irefn{org20}\And, 
H.~Oeschler\Irefn{org17}\textsuperscript{,}\Irefn{org103}\textsuperscript{,}\Aref{org*}\And, 
S.~Oh\Irefn{org141}\And, 
A.~Ohlson\Irefn{org33}\textsuperscript{,}\Irefn{org103}\And, 
T.~Okubo\Irefn{org45}\And, 
L.~Olah\Irefn{org140}\And, 
J.~Oleniacz\Irefn{org138}\And, 
A.C.~Oliveira Da Silva\Irefn{org121}\And, 
M.H.~Oliver\Irefn{org141}\And, 
J.~Onderwaater\Irefn{org106}\And, 
C.~Oppedisano\Irefn{org57}\And, 
R.~Orava\Irefn{org44}\And, 
M.~Oravec\Irefn{org116}\And, 
A.~Ortiz Velasquez\Irefn{org71}\And, 
A.~Oskarsson\Irefn{org32}\And, 
J.~Otwinowski\Irefn{org118}\And, 
K.~Oyama\Irefn{org83}\And, 
Y.~Pachmayer\Irefn{org103}\And, 
V.~Pacik\Irefn{org90}\And, 
D.~Pagano\Irefn{org135}\And, 
P.~Pagano\Irefn{org28}\And, 
G.~Pai\'{c}\Irefn{org71}\And, 
P.~Palni\Irefn{org7}\And, 
J.~Pan\Irefn{org139}\And, 
A.K.~Pandey\Irefn{org46}\And, 
S.~Panebianco\Irefn{org74}\And, 
V.~Papikyan\Irefn{org1}\And, 
G.S.~Pappalardo\Irefn{org54}\And, 
P.~Pareek\Irefn{org47}\And, 
J.~Park\Irefn{org59}\And, 
S.~Parmar\Irefn{org98}\And, 
A.~Passfeld\Irefn{org70}\And, 
S.P.~Pathak\Irefn{org124}\And, 
R.N.~Patra\Irefn{org137}\And, 
B.~Paul\Irefn{org57}\And, 
H.~Pei\Irefn{org7}\And, 
T.~Peitzmann\Irefn{org62}\And, 
X.~Peng\Irefn{org7}\And, 
L.G.~Pereira\Irefn{org72}\And, 
H.~Pereira Da Costa\Irefn{org74}\And, 
D.~Peresunko\Irefn{org89}\textsuperscript{,}\Irefn{org82}\And, 
E.~Perez Lezama\Irefn{org69}\And, 
V.~Peskov\Irefn{org69}\And, 
Y.~Pestov\Irefn{org5}\And, 
V.~Petr\'{a}\v{c}ek\Irefn{org37}\And, 
V.~Petrov\Irefn{org112}\And, 
M.~Petrovici\Irefn{org86}\And, 
C.~Petta\Irefn{org26}\And, 
R.P.~Pezzi\Irefn{org72}\And, 
S.~Piano\Irefn{org58}\And, 
M.~Pikna\Irefn{org36}\And, 
P.~Pillot\Irefn{org114}\And, 
L.O.D.L.~Pimentel\Irefn{org90}\And, 
O.~Pinazza\Irefn{org52}\textsuperscript{,}\Irefn{org33}\And, 
L.~Pinsky\Irefn{org124}\And, 
D.B.~Piyarathna\Irefn{org124}\And, 
M.~P\l osko\'{n}\Irefn{org81}\And, 
M.~Planinic\Irefn{org97}\And, 
F.~Pliquett\Irefn{org69}\And, 
J.~Pluta\Irefn{org138}\And, 
S.~Pochybova\Irefn{org140}\And, 
P.L.M.~Podesta-Lerma\Irefn{org120}\And, 
M.G.~Poghosyan\Irefn{org94}\And, 
B.~Polichtchouk\Irefn{org112}\And, 
N.~Poljak\Irefn{org97}\And, 
W.~Poonsawat\Irefn{org115}\And, 
A.~Pop\Irefn{org86}\And, 
H.~Poppenborg\Irefn{org70}\And, 
S.~Porteboeuf-Houssais\Irefn{org131}\And, 
V.~Pozdniakov\Irefn{org76}\And, 
S.K.~Prasad\Irefn{org4}\And, 
R.~Preghenella\Irefn{org52}\And, 
F.~Prino\Irefn{org57}\And, 
C.A.~Pruneau\Irefn{org139}\And, 
I.~Pshenichnov\Irefn{org61}\And, 
M.~Puccio\Irefn{org24}\And, 
G.~Puddu\Irefn{org22}\And, 
P.~Pujahari\Irefn{org139}\And, 
V.~Punin\Irefn{org108}\And, 
J.~Putschke\Irefn{org139}\And, 
S.~Raha\Irefn{org4}\And, 
S.~Rajput\Irefn{org100}\And, 
J.~Rak\Irefn{org125}\And, 
A.~Rakotozafindrabe\Irefn{org74}\And, 
L.~Ramello\Irefn{org30}\And, 
F.~Rami\Irefn{org133}\And, 
D.B.~Rana\Irefn{org124}\And, 
R.~Raniwala\Irefn{org101}\And, 
S.~Raniwala\Irefn{org101}\And, 
S.S.~R\"{a}s\"{a}nen\Irefn{org44}\And, 
B.T.~Rascanu\Irefn{org69}\And, 
D.~Rathee\Irefn{org98}\And, 
V.~Ratza\Irefn{org43}\And, 
I.~Ravasenga\Irefn{org29}\And, 
K.F.~Read\Irefn{org127}\textsuperscript{,}\Irefn{org94}\And, 
K.~Redlich\Irefn{org85}\textsuperscript{,}\Aref{orgV}\And, 
A.~Rehman\Irefn{org20}\And, 
P.~Reichelt\Irefn{org69}\And, 
F.~Reidt\Irefn{org33}\And, 
X.~Ren\Irefn{org7}\And, 
R.~Renfordt\Irefn{org69}\And, 
A.R.~Reolon\Irefn{org49}\And, 
A.~Reshetin\Irefn{org61}\And, 
K.~Reygers\Irefn{org103}\And, 
V.~Riabov\Irefn{org95}\And, 
R.A.~Ricci\Irefn{org50}\And, 
T.~Richert\Irefn{org32}\And, 
M.~Richter\Irefn{org19}\And, 
P.~Riedler\Irefn{org33}\And, 
W.~Riegler\Irefn{org33}\And, 
F.~Riggi\Irefn{org26}\And, 
C.~Ristea\Irefn{org67}\And, 
M.~Rodr\'{i}guez Cahuantzi\Irefn{org2}\And, 
K.~R{\o}ed\Irefn{org19}\And, 
E.~Rogochaya\Irefn{org76}\And, 
D.~Rohr\Irefn{org33}\textsuperscript{,}\Irefn{org40}\And, 
D.~R\"ohrich\Irefn{org20}\And, 
P.S.~Rokita\Irefn{org138}\And, 
F.~Ronchetti\Irefn{org49}\And, 
E.D.~Rosas\Irefn{org71}\And, 
P.~Rosnet\Irefn{org131}\And, 
A.~Rossi\Irefn{org27}\textsuperscript{,}\Irefn{org55}\And, 
A.~Rotondi\Irefn{org134}\And, 
F.~Roukoutakis\Irefn{org84}\And, 
A.~Roy\Irefn{org47}\And, 
C.~Roy\Irefn{org133}\And, 
P.~Roy\Irefn{org109}\And, 
O.V.~Rueda\Irefn{org71}\And, 
R.~Rui\Irefn{org23}\And, 
B.~Rumyantsev\Irefn{org76}\And, 
A.~Rustamov\Irefn{org88}\And, 
E.~Ryabinkin\Irefn{org89}\And, 
Y.~Ryabov\Irefn{org95}\And, 
A.~Rybicki\Irefn{org118}\And, 
S.~Saarinen\Irefn{org44}\And, 
S.~Sadhu\Irefn{org137}\And, 
S.~Sadovsky\Irefn{org112}\And, 
K.~\v{S}afa\v{r}\'{\i}k\Irefn{org33}\And, 
S.K.~Saha\Irefn{org137}\And, 
B.~Sahlmuller\Irefn{org69}\And, 
B.~Sahoo\Irefn{org46}\And, 
P.~Sahoo\Irefn{org47}\And, 
R.~Sahoo\Irefn{org47}\And, 
S.~Sahoo\Irefn{org66}\And, 
P.K.~Sahu\Irefn{org66}\And, 
J.~Saini\Irefn{org137}\And, 
S.~Sakai\Irefn{org130}\And, 
M.A.~Saleh\Irefn{org139}\And, 
J.~Salzwedel\Irefn{org16}\And, 
S.~Sambyal\Irefn{org100}\And, 
V.~Samsonov\Irefn{org95}\textsuperscript{,}\Irefn{org82}\And, 
A.~Sandoval\Irefn{org73}\And, 
D.~Sarkar\Irefn{org137}\And, 
N.~Sarkar\Irefn{org137}\And, 
P.~Sarma\Irefn{org42}\And, 
M.H.P.~Sas\Irefn{org62}\And, 
E.~Scapparone\Irefn{org52}\And, 
F.~Scarlassara\Irefn{org27}\And, 
B.~Schaefer\Irefn{org94}\And, 
R.P.~Scharenberg\Irefn{org105}\And, 
H.S.~Scheid\Irefn{org69}\And, 
C.~Schiaua\Irefn{org86}\And, 
R.~Schicker\Irefn{org103}\And, 
C.~Schmidt\Irefn{org106}\And, 
H.R.~Schmidt\Irefn{org102}\And, 
M.O.~Schmidt\Irefn{org103}\And, 
M.~Schmidt\Irefn{org102}\And, 
N.V.~Schmidt\Irefn{org94}\textsuperscript{,}\Irefn{org69}\And, 
J.~Schukraft\Irefn{org33}\And, 
Y.~Schutz\Irefn{org33}\textsuperscript{,}\Irefn{org133}\And, 
K.~Schwarz\Irefn{org106}\And, 
K.~Schweda\Irefn{org106}\And, 
G.~Scioli\Irefn{org25}\And, 
E.~Scomparin\Irefn{org57}\And, 
M.~\v{S}ef\v{c}\'ik\Irefn{org38}\And, 
J.E.~Seger\Irefn{org96}\And, 
Y.~Sekiguchi\Irefn{org129}\And, 
D.~Sekihata\Irefn{org45}\And, 
I.~Selyuzhenkov\Irefn{org106}\textsuperscript{,}\Irefn{org82}\And, 
K.~Senosi\Irefn{org75}\And, 
S.~Senyukov\Irefn{org3}\textsuperscript{,}\Irefn{org133}\textsuperscript{,}\Irefn{org33}\And, 
E.~Serradilla\Irefn{org73}\And, 
P.~Sett\Irefn{org46}\And, 
A.~Sevcenco\Irefn{org67}\And, 
A.~Shabanov\Irefn{org61}\And, 
A.~Shabetai\Irefn{org114}\And, 
R.~Shahoyan\Irefn{org33}\And, 
W.~Shaikh\Irefn{org109}\And, 
A.~Shangaraev\Irefn{org112}\And, 
A.~Sharma\Irefn{org98}\And, 
A.~Sharma\Irefn{org100}\And, 
M.~Sharma\Irefn{org100}\And, 
M.~Sharma\Irefn{org100}\And, 
N.~Sharma\Irefn{org98}\textsuperscript{,}\Irefn{org127}\And, 
A.I.~Sheikh\Irefn{org137}\And, 
K.~Shigaki\Irefn{org45}\And, 
Q.~Shou\Irefn{org7}\And, 
K.~Shtejer\Irefn{org9}\textsuperscript{,}\Irefn{org24}\And, 
Y.~Sibiriak\Irefn{org89}\And, 
S.~Siddhanta\Irefn{org53}\And, 
K.M.~Sielewicz\Irefn{org33}\And, 
T.~Siemiarczuk\Irefn{org85}\And, 
S.~Silaeva\Irefn{org89}\And, 
D.~Silvermyr\Irefn{org32}\And, 
C.~Silvestre\Irefn{org80}\And, 
G.~Simatovic\Irefn{org97}\And, 
G.~Simonetti\Irefn{org33}\And, 
R.~Singaraju\Irefn{org137}\And, 
R.~Singh\Irefn{org87}\And, 
V.~Singhal\Irefn{org137}\And, 
T.~Sinha\Irefn{org109}\And, 
B.~Sitar\Irefn{org36}\And, 
M.~Sitta\Irefn{org30}\And, 
T.B.~Skaali\Irefn{org19}\And, 
M.~Slupecki\Irefn{org125}\And, 
N.~Smirnov\Irefn{org141}\And, 
R.J.M.~Snellings\Irefn{org62}\And, 
T.W.~Snellman\Irefn{org125}\And, 
J.~Song\Irefn{org17}\And, 
M.~Song\Irefn{org142}\And, 
F.~Soramel\Irefn{org27}\And, 
S.~Sorensen\Irefn{org127}\And, 
F.~Sozzi\Irefn{org106}\And, 
E.~Spiriti\Irefn{org49}\And, 
I.~Sputowska\Irefn{org118}\And, 
B.K.~Srivastava\Irefn{org105}\And, 
J.~Stachel\Irefn{org103}\And, 
I.~Stan\Irefn{org67}\And, 
P.~Stankus\Irefn{org94}\And, 
E.~Stenlund\Irefn{org32}\And, 
D.~Stocco\Irefn{org114}\And, 
M.M.~Storetvedt\Irefn{org35}\And, 
P.~Strmen\Irefn{org36}\And, 
A.A.P.~Suaide\Irefn{org121}\And, 
T.~Sugitate\Irefn{org45}\And, 
C.~Suire\Irefn{org60}\And, 
M.~Suleymanov\Irefn{org14}\And, 
M.~Suljic\Irefn{org23}\And, 
R.~Sultanov\Irefn{org63}\And, 
M.~\v{S}umbera\Irefn{org93}\And, 
S.~Sumowidagdo\Irefn{org48}\And, 
K.~Suzuki\Irefn{org113}\And, 
S.~Swain\Irefn{org66}\And, 
A.~Szabo\Irefn{org36}\And, 
I.~Szarka\Irefn{org36}\And, 
U.~Tabassam\Irefn{org14}\And, 
J.~Takahashi\Irefn{org122}\And, 
G.J.~Tambave\Irefn{org20}\And, 
N.~Tanaka\Irefn{org130}\And, 
M.~Tarhini\Irefn{org60}\And, 
M.~Tariq\Irefn{org15}\And, 
M.G.~Tarzila\Irefn{org86}\And, 
A.~Tauro\Irefn{org33}\And, 
G.~Tejeda Mu\~{n}oz\Irefn{org2}\And, 
A.~Telesca\Irefn{org33}\And, 
K.~Terasaki\Irefn{org129}\And, 
C.~Terrevoli\Irefn{org27}\And, 
B.~Teyssier\Irefn{org132}\And, 
D.~Thakur\Irefn{org47}\And, 
S.~Thakur\Irefn{org137}\And, 
D.~Thomas\Irefn{org119}\And, 
F.~Thoresen\Irefn{org90}\And, 
R.~Tieulent\Irefn{org132}\And, 
A.~Tikhonov\Irefn{org61}\And, 
A.R.~Timmins\Irefn{org124}\And, 
A.~Toia\Irefn{org69}\And, 
S.R.~Torres\Irefn{org120}\And, 
S.~Tripathy\Irefn{org47}\And, 
S.~Trogolo\Irefn{org24}\And, 
G.~Trombetta\Irefn{org31}\And, 
L.~Tropp\Irefn{org38}\And, 
V.~Trubnikov\Irefn{org3}\And, 
W.H.~Trzaska\Irefn{org125}\And, 
B.A.~Trzeciak\Irefn{org62}\And, 
T.~Tsuji\Irefn{org129}\And, 
A.~Tumkin\Irefn{org108}\And, 
R.~Turrisi\Irefn{org55}\And, 
T.S.~Tveter\Irefn{org19}\And, 
K.~Ullaland\Irefn{org20}\And, 
E.N.~Umaka\Irefn{org124}\And, 
A.~Uras\Irefn{org132}\And, 
G.L.~Usai\Irefn{org22}\And, 
A.~Utrobicic\Irefn{org97}\And, 
M.~Vala\Irefn{org116}\textsuperscript{,}\Irefn{org64}\And, 
J.~Van Der Maarel\Irefn{org62}\And, 
J.W.~Van Hoorne\Irefn{org33}\And, 
M.~van Leeuwen\Irefn{org62}\And, 
T.~Vanat\Irefn{org93}\And, 
P.~Vande Vyvre\Irefn{org33}\And, 
D.~Varga\Irefn{org140}\And, 
A.~Vargas\Irefn{org2}\And, 
M.~Vargyas\Irefn{org125}\And, 
R.~Varma\Irefn{org46}\And, 
M.~Vasileiou\Irefn{org84}\And, 
A.~Vasiliev\Irefn{org89}\And, 
A.~Vauthier\Irefn{org80}\And, 
O.~V\'azquez Doce\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
V.~Vechernin\Irefn{org136}\And, 
A.M.~Veen\Irefn{org62}\And, 
A.~Velure\Irefn{org20}\And, 
E.~Vercellin\Irefn{org24}\And, 
S.~Vergara Lim\'on\Irefn{org2}\And, 
R.~Vernet\Irefn{org8}\And, 
R.~V\'ertesi\Irefn{org140}\And, 
L.~Vickovic\Irefn{org117}\And, 
S.~Vigolo\Irefn{org62}\And, 
J.~Viinikainen\Irefn{org125}\And, 
Z.~Vilakazi\Irefn{org128}\And, 
O.~Villalobos Baillie\Irefn{org110}\And, 
A.~Villatoro Tello\Irefn{org2}\And, 
A.~Vinogradov\Irefn{org89}\And, 
L.~Vinogradov\Irefn{org136}\And, 
T.~Virgili\Irefn{org28}\And, 
V.~Vislavicius\Irefn{org32}\And, 
A.~Vodopyanov\Irefn{org76}\And, 
M.A.~V\"{o}lkl\Irefn{org103}\textsuperscript{,}\Irefn{org102}\And, 
K.~Voloshin\Irefn{org63}\And, 
S.A.~Voloshin\Irefn{org139}\And, 
G.~Volpe\Irefn{org31}\And, 
B.~von Haller\Irefn{org33}\And, 
I.~Vorobyev\Irefn{org104}\textsuperscript{,}\Irefn{org34}\And, 
D.~Voscek\Irefn{org116}\And, 
D.~Vranic\Irefn{org33}\textsuperscript{,}\Irefn{org106}\And, 
J.~Vrl\'{a}kov\'{a}\Irefn{org38}\And, 
B.~Wagner\Irefn{org20}\And, 
H.~Wang\Irefn{org62}\And, 
M.~Wang\Irefn{org7}\And, 
D.~Watanabe\Irefn{org130}\And, 
Y.~Watanabe\Irefn{org129}\textsuperscript{,}\Irefn{org130}\And, 
M.~Weber\Irefn{org113}\And, 
S.G.~Weber\Irefn{org106}\And, 
D.F.~Weiser\Irefn{org103}\And, 
S.C.~Wenzel\Irefn{org33}\And, 
J.P.~Wessels\Irefn{org70}\And, 
U.~Westerhoff\Irefn{org70}\And, 
A.M.~Whitehead\Irefn{org99}\And, 
J.~Wiechula\Irefn{org69}\And, 
J.~Wikne\Irefn{org19}\And, 
G.~Wilk\Irefn{org85}\And, 
J.~Wilkinson\Irefn{org103}\textsuperscript{,}\Irefn{org52}\And, 
G.A.~Willems\Irefn{org70}\And, 
M.C.S.~Williams\Irefn{org52}\And, 
E.~Willsher\Irefn{org110}\And, 
B.~Windelband\Irefn{org103}\And, 
W.E.~Witt\Irefn{org127}\And, 
S.~Yalcin\Irefn{org79}\And, 
K.~Yamakawa\Irefn{org45}\And, 
P.~Yang\Irefn{org7}\And, 
S.~Yano\Irefn{org45}\And, 
Z.~Yin\Irefn{org7}\And, 
H.~Yokoyama\Irefn{org130}\textsuperscript{,}\Irefn{org80}\And, 
I.-K.~Yoo\Irefn{org17}\And, 
J.H.~Yoon\Irefn{org59}\And, 
V.~Yurchenko\Irefn{org3}\And, 
V.~Zaccolo\Irefn{org57}\And, 
A.~Zaman\Irefn{org14}\And, 
C.~Zampolli\Irefn{org33}\And, 
H.J.C.~Zanoli\Irefn{org121}\And, 
N.~Zardoshti\Irefn{org110}\And, 
A.~Zarochentsev\Irefn{org136}\And, 
P.~Z\'{a}vada\Irefn{org65}\And, 
N.~Zaviyalov\Irefn{org108}\And, 
H.~Zbroszczyk\Irefn{org138}\And, 
M.~Zhalov\Irefn{org95}\And, 
H.~Zhang\Irefn{org20}\textsuperscript{,}\Irefn{org7}\And, 
X.~Zhang\Irefn{org7}\And, 
Y.~Zhang\Irefn{org7}\And, 
C.~Zhang\Irefn{org62}\And, 
Z.~Zhang\Irefn{org7}\textsuperscript{,}\Irefn{org131}\And, 
C.~Zhao\Irefn{org19}\And, 
N.~Zhigareva\Irefn{org63}\And, 
D.~Zhou\Irefn{org7}\And, 
Y.~Zhou\Irefn{org90}\And, 
Z.~Zhou\Irefn{org20}\And, 
H.~Zhu\Irefn{org20}\And, 
J.~Zhu\Irefn{org7}\And, 
A.~Zichichi\Irefn{org25}\textsuperscript{,}\Irefn{org11}\And, 
A.~Zimmermann\Irefn{org103}\And, 
M.B.~Zimmermann\Irefn{org33}\And, 
G.~Zinovjev\Irefn{org3}\And, 
J.~Zmeskal\Irefn{org113}\And, 
S.~Zou\Irefn{org7}\And
\renewcommand\labelenumi{\textsuperscript{\theenumi}~}

\section*{Affiliation notes}
\renewcommand\theenumi{\roman{enumi}}
\begin{Authlist}
\item \Adef{org*}Deceased
\item \Adef{orgI}Dipartimento DET del Politecnico di Torino, Turin, Italy
\item \Adef{orgII}Georgia State University, Atlanta, Georgia, United States
\item \Adef{orgIII}M.V. Lomonosov Moscow State University, D.V. Skobeltsyn Institute of Nuclear, Physics, Moscow, Russia
\item \Adef{orgIV}Department of Applied Physics, Aligarh Muslim University, Aligarh, India
\item \Adef{orgV}Institute of Theoretical Physics, University of Wroclaw, Poland
\end{Authlist}

\section*{Collaboration Institutes}
\renewcommand\theenumi{\arabic{enumi}~}
\begin{Authlist}
\item \Idef{org1}A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute) Foundation, Yerevan, Armenia
\item \Idef{org2}Benem\'{e}rita Universidad Aut\'{o}noma de Puebla, Puebla, Mexico
\item \Idef{org3}Bogolyubov Institute for Theoretical Physics, Kiev, Ukraine
\item \Idef{org4}Bose Institute, Department of Physics  and Centre for Astroparticle Physics and Space Science (CAPSS), Kolkata, India
\item \Idef{org5}Budker Institute for Nuclear Physics, Novosibirsk, Russia
\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, United States
\item \Idef{org7}Central China Normal University, Wuhan, China
\item \Idef{org8}Centre de Calcul de l'IN2P3, Villeurbanne, Lyon, France
\item \Idef{org9}Centro de Aplicaciones Tecnol\'{o}gicas y Desarrollo Nuclear (CEADEN), Havana, Cuba
\item \Idef{org10}Centro de Investigaci\'{o}n y de Estudios Avanzados (CINVESTAV), Mexico City and M\'{e}rida, Mexico
\item \Idef{org11}Centro Fermi - Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi', Rome, Italy
\item \Idef{org12}Chicago State University, Chicago, Illinois, United States
\item \Idef{org13}China Institute of Atomic Energy, Beijing, China
\item \Idef{org14}COMSATS Institute of Information Technology (CIIT), Islamabad, Pakistan
\item \Idef{org15}Department of Physics, Aligarh Muslim University, Aligarh, India
\item \Idef{org16}Department of Physics, Ohio State University, Columbus, Ohio, United States
\item \Idef{org17}Department of Physics, Pusan National University, Pusan, Republic of Korea
\item \Idef{org18}Department of Physics, Sejong University, Seoul, Republic of Korea
\item \Idef{org19}Department of Physics, University of Oslo, Oslo, Norway
\item \Idef{org20}Department of Physics and Technology, University of Bergen, Bergen, Norway
\item \Idef{org21}Dipartimento di Fisica dell'Universit\`{a} 'La Sapienza' and Sezione INFN, Rome, Italy
\item \Idef{org22}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Cagliari, Italy
\item \Idef{org23}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Trieste, Italy
\item \Idef{org24}Dipartimento di Fisica dell'Universit\`{a} and Sezione INFN, Turin, Italy
\item \Idef{org25}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Bologna, Italy
\item \Idef{org26}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Catania, Italy
\item \Idef{org27}Dipartimento di Fisica e Astronomia dell'Universit\`{a} and Sezione INFN, Padova, Italy
\item \Idef{org28}Dipartimento di Fisica `E.R.~Caianiello' dell'Universit\`{a} and Gruppo Collegato INFN, Salerno, Italy
\item \Idef{org29}Dipartimento DISAT del Politecnico and Sezione INFN, Turin, Italy
\item \Idef{org30}Dipartimento di Scienze e Innovazione Tecnologica dell'Universit\`{a} del Piemonte Orientale and INFN Sezione di Torino, Alessandria, Italy
\item \Idef{org31}Dipartimento Interateneo di Fisica `M.~Merlin' and Sezione INFN, Bari, Italy
\item \Idef{org32}Division of Experimental High Energy Physics, University of Lund, Lund, Sweden
\item \Idef{org33}European Organization for Nuclear Research (CERN), Geneva, Switzerland
\item \Idef{org34}Excellence Cluster Universe, Technische Universit\"{a}t M\"{u}nchen, Munich, Germany
\item \Idef{org35}Faculty of Engineering, Bergen University College, Bergen, Norway
\item \Idef{org36}Faculty of Mathematics, Physics and Informatics, Comenius University, Bratislava, Slovakia
\item \Idef{org37}Faculty of Nuclear Sciences and Physical Engineering, Czech Technical University in Prague, Prague, Czech Republic
\item \Idef{org38}Faculty of Science, P.J.~\v{S}af\'{a}rik University, Ko\v{s}ice, Slovakia
\item \Idef{org39}Faculty of Technology, Buskerud and Vestfold University College, Tonsberg, Norway
\item \Idef{org40}Frankfurt Institute for Advanced Studies, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org41}Gangneung-Wonju National University, Gangneung, Republic of Korea
\item \Idef{org42}Gauhati University, Department of Physics, Guwahati, India
\item \Idef{org43}Helmholtz-Institut f\"{u}r Strahlen- und Kernphysik, Rheinische Friedrich-Wilhelms-Universit\"{a}t Bonn, Bonn, Germany
\item \Idef{org44}Helsinki Institute of Physics (HIP), Helsinki, Finland
\item \Idef{org45}Hiroshima University, Hiroshima, Japan
\item \Idef{org46}Indian Institute of Technology Bombay (IIT), Mumbai, India
\item \Idef{org47}Indian Institute of Technology Indore, Indore, India
\item \Idef{org48}Indonesian Institute of Sciences, Jakarta, Indonesia
\item \Idef{org49}INFN, Laboratori Nazionali di Frascati, Frascati, Italy
\item \Idef{org50}INFN, Laboratori Nazionali di Legnaro, Legnaro, Italy
\item \Idef{org51}INFN, Sezione di Bari, Bari, Italy
\item \Idef{org52}INFN, Sezione di Bologna, Bologna, Italy
\item \Idef{org53}INFN, Sezione di Cagliari, Cagliari, Italy
\item \Idef{org54}INFN, Sezione di Catania, Catania, Italy
\item \Idef{org55}INFN, Sezione di Padova, Padova, Italy
\item \Idef{org56}INFN, Sezione di Roma, Rome, Italy
\item \Idef{org57}INFN, Sezione di Torino, Turin, Italy
\item \Idef{org58}INFN, Sezione di Trieste, Trieste, Italy
\item \Idef{org59}Inha University, Incheon, Republic of Korea
\item \Idef{org60}Institut de Physique Nucl\'eaire d'Orsay (IPNO), Universit\'e Paris-Sud, CNRS-IN2P3, Orsay, France
\item \Idef{org61}Institute for Nuclear Research, Academy of Sciences, Moscow, Russia
\item \Idef{org62}Institute for Subatomic Physics of Utrecht University, Utrecht, Netherlands
\item \Idef{org63}Institute for Theoretical and Experimental Physics, Moscow, Russia
\item \Idef{org64}Institute of Experimental Physics, Slovak Academy of Sciences, Ko\v{s}ice, Slovakia
\item \Idef{org65}Institute of Physics, Academy of Sciences of the Czech Republic, Prague, Czech Republic
\item \Idef{org66}Institute of Physics, Bhubaneswar, India
\item \Idef{org67}Institute of Space Science (ISS), Bucharest, Romania
\item \Idef{org68}Institut f\"{u}r Informatik, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org69}Institut f\"{u}r Kernphysik, Johann Wolfgang Goethe-Universit\"{a}t Frankfurt, Frankfurt, Germany
\item \Idef{org70}Institut f\"{u}r Kernphysik, Westf\"{a}lische Wilhelms-Universit\"{a}t M\"{u}nster, M\"{u}nster, Germany
\item \Idef{org71}Instituto de Ciencias Nucleares, Universidad Nacional Aut\'{o}noma de M\'{e}xico, Mexico City, Mexico
\item \Idef{org72}Instituto de F\'{i}sica, Universidade Federal do Rio Grande do Sul (UFRGS), Porto Alegre, Brazil
\item \Idef{org73}Instituto de F\'{\i}sica, Universidad Nacional Aut\'{o}noma de M\'{e}xico, Mexico City, Mexico
\item \Idef{org74}IRFU, CEA, Universit\'{e} Paris-Saclay, Saclay, France
\item \Idef{org75}iThemba LABS, National Research Foundation, Somerset West, South Africa
\item \Idef{org76}Joint Institute for Nuclear Research (JINR), Dubna, Russia
\item \Idef{org77}Konkuk University, Seoul, Republic of Korea
\item \Idef{org78}Korea Institute of Science and Technology Information, Daejeon, Republic of Korea
\item \Idef{org79}KTO Karatay University, Konya, Turkey
\item \Idef{org80}Laboratoire de Physique Subatomique et de Cosmologie, Universit\'{e} Grenoble-Alpes, CNRS-IN2P3, Grenoble, France
\item \Idef{org81}Lawrence Berkeley National Laboratory, Berkeley, California, United States
\item \Idef{org82}Moscow Engineering Physics Institute, Moscow, Russia
\item \Idef{org83}Nagasaki Institute of Applied Science, Nagasaki, Japan
\item \Idef{org84}National and Kapodistrian University of Athens, Physics Department, Athens, Greece
\item \Idef{org85}National Centre for Nuclear Studies, Warsaw, Poland
\item \Idef{org86}National Institute for Physics and Nuclear Engineering, Bucharest, Romania
\item \Idef{org87}National Institute of Science Education and Research, HBNI, Jatni, India
\item \Idef{org88}National Nuclear Research Center, Baku, Azerbaijan
\item \Idef{org89}National Research Centre Kurchatov Institute, Moscow, Russia
\item \Idef{org90}Niels Bohr Institute, University of Copenhagen, Copenhagen, Denmark
\item \Idef{org91}Nikhef, Nationaal instituut voor subatomaire fysica, Amsterdam, Netherlands
\item \Idef{org92}Nuclear Physics Group, STFC Daresbury Laboratory, Daresbury, United Kingdom
\item \Idef{org93}Nuclear Physics Institute, Academy of Sciences of the Czech Republic, \v{R}e\v{z} u Prahy, Czech Republic
\item \Idef{org94}Oak Ridge National Laboratory, Oak Ridge, Tennessee, United States
\item \Idef{org95}Petersburg Nuclear Physics Institute, Gatchina, Russia
\item \Idef{org96}Physics Department, Creighton University, Omaha, Nebraska, United States
\item \Idef{org97}Physics department, Faculty of science, University of Zagreb, Zagreb, Croatia
\item \Idef{org98}Physics Department, Panjab University, Chandigarh, India
\item \Idef{org99}Physics Department, University of Cape Town, Cape Town, South Africa
\item \Idef{org100}Physics Department, University of Jammu, Jammu, India
\item \Idef{org101}Physics Department, University of Rajasthan, Jaipur, India
\item \Idef{org102}Physikalisches Institut, Eberhard Karls Universit\"{a}t T\"{u}bingen, T\"{u}bingen, Germany
\item \Idef{org103}Physikalisches Institut, Ruprecht-Karls-Universit\"{a}t Heidelberg, Heidelberg, Germany
\item \Idef{org104}Physik Department, Technische Universit\"{a}t M\"{u}nchen, Munich, Germany
\item \Idef{org105}Purdue University, West Lafayette, Indiana, United States
\item \Idef{org106}Research Division and ExtreMe Matter Institute EMMI, GSI Helmholtzzentrum f\"ur Schwerionenforschung GmbH, Darmstadt, Germany
\item \Idef{org107}Rudjer Bo\v{s}kovi\'{c} Institute, Zagreb, Croatia
\item \Idef{org108}Russian Federal Nuclear Center (VNIIEF), Sarov, Russia
\item \Idef{org109}Saha Institute of Nuclear Physics, Kolkata, India
\item \Idef{org110}School of Physics and Astronomy, University of Birmingham, Birmingham, United Kingdom
\item \Idef{org111}Secci\'{o}n F\'{\i}sica, Departamento de Ciencias, Pontificia Universidad Cat\'{o}lica del Per\'{u}, Lima, Peru
\item \Idef{org112}SSC IHEP of NRC Kurchatov institute, Protvino, Russia
\item \Idef{org113}Stefan Meyer Institut f\"{u}r Subatomare Physik (SMI), Vienna, Austria
\item \Idef{org114}SUBATECH, IMT Atlantique, Universit\'{e} de Nantes, CNRS-IN2P3, Nantes, France
\item \Idef{org115}Suranaree University of Technology, Nakhon Ratchasima, Thailand
\item \Idef{org116}Technical University of Ko\v{s}ice, Ko\v{s}ice, Slovakia
\item \Idef{org117}Technical University of Split FESB, Split, Croatia
\item \Idef{org118}The Henryk Niewodniczanski Institute of Nuclear Physics, Polish Academy of Sciences, Cracow, Poland
\item \Idef{org119}The University of Texas at Austin, Physics Department, Austin, Texas, United States
\item \Idef{org120}Universidad Aut\'{o}noma de Sinaloa, Culiac\'{a}n, Mexico
\item \Idef{org121}Universidade de S\~{a}o Paulo (USP), S\~{a}o Paulo, Brazil
\item \Idef{org122}Universidade Estadual de Campinas (UNICAMP), Campinas, Brazil
\item \Idef{org123}Universidade Federal do ABC, Santo Andre, Brazil
\item \Idef{org124}University of Houston, Houston, Texas, United States
\item \Idef{org125}University of Jyv\"{a}skyl\"{a}, Jyv\"{a}skyl\"{a}, Finland
\item \Idef{org126}University of Liverpool, Liverpool, United Kingdom
\item \Idef{org127}University of Tennessee, Knoxville, Tennessee, United States
\item \Idef{org128}University of the Witwatersrand, Johannesburg, South Africa
\item \Idef{org129}University of Tokyo, Tokyo, Japan
\item \Idef{org130}University of Tsukuba, Tsukuba, Japan
\item \Idef{org131}Universit\'{e} Clermont Auvergne, CNRS/IN2P3, LPC, Clermont-Ferrand, France
\item \Idef{org132}Universit\'{e} de Lyon, Universit\'{e} Lyon 1, CNRS/IN2P3, IPN-Lyon, Villeurbanne, Lyon, France
\item \Idef{org133}Universit\'{e} de Strasbourg, CNRS, IPHC UMR 7178, F-67000 Strasbourg, France, Strasbourg, France
\item \Idef{org134}Universit\`{a} degli Studi di Pavia, Pavia, Italy
\item \Idef{org135}Universit\`{a} di Brescia, Brescia, Italy
\item \Idef{org136}V.~Fock Institute for Physics, St. Petersburg State University, St. Petersburg, Russia
\item \Idef{org137}Variable Energy Cyclotron Centre, Kolkata, India
\item \Idef{org138}Warsaw University of Technology, Warsaw, Poland
\item \Idef{org139}Wayne State University, Detroit, Michigan, United States
\item \Idef{org140}Wigner Research Centre for Physics, Hungarian Academy of Sciences, Budapest, Hungary
\item \Idef{org141}Yale University, New Haven, Connecticut, United States
\item \Idef{org142}Yonsei University, Seoul, Republic of Korea
\item \Idef{org143}Zentrum f\"{u}r Technologietransfer und Telekommunikation (ZTT), Fachhochschule Worms, Worms, Germany
\end{Authlist}
\endgroup

### 2017-08-22 longSC.tex
cleaning up figure numbering

@@
 	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2A_vn_xpt.eps}}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt.eps}}
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
@@
 The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)).}
-        \label{fig:Figure_2A}
+        \label{fig:Figure_3}
         \end{center}   
@@
 %While these product are reconstructed and normalized directly for NSC calculations,
-The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
-The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}.
+The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
+The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_3}.
 The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}.
 The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_3} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
 
@@
             \begin{center}
-                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig3_ModelComparison_EKRT.eps}}
+                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_EKRT.eps}}
               \end{center}
@@
 Left (right) panels show SC($m$,$n$) (NSC($m$,$n$)).}
-        \label{fig:Figure_3}
+        \label{fig:Figure_4}
 \end{figure*}
 
-The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_3}. 
+The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_4}. 
 As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
@@
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-%As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
+%As shown in Fig.~\ref{fig:Figure_4}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
 While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_VISH.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_VISH.eps}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$)).}
-        \label{fig:Figure_4}
+        \label{fig:Figure_5}
         \end{center}   
@@
 
-The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.
-All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to describe the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
+The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_5}.
+All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to describe the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_5}.
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
-%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions.
+%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_5} is opposite to that in data in 5--10\% central collisions.
 %NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_AMPT.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig6_ModelComparison_AMPT.eps}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
-        \label{fig:Figure_5}
+        \label{fig:Figure_6}
         \end{center}   
@@
 
-The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_5}.
+The SC($m$,$n$) and NSC($m$,$n$) observables calculated from AMPT simulations are compared with data in Fig.~\ref{fig:Figure_6}.
 For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
@@
 The total number of data samples $N_{\rm dof}$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
-The $\chisqndf$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_A5}.
+The $\chisqndf$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_7}.
 
@@
             \begin{center}
-                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisqndf_bestfits_3pad.eps}}
+                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad.eps}}
         \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
 Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
-        \label{fig:Figure_A5}
+        \label{fig:Figure_7}
               \end{center}
@@
 % The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.
-The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_A5}a and \ref{fig:Figure_A5}b, respectively.
-The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_A5}c.
+The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively.
+The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_7}c.
 We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
 This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_A5}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_7}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
 The default configuration of the AMPT model gives the best $\chisqndf$ values for NSC($m$,$n$), especially for NSC(3,2).
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig6_pt_NSC32_Models.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig8_pt_NSC32_Models.eps}}
               \end{center}
@@
 Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_6}
+             \label{fig:Figure_8}
 \end{figure}
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig7_pt_NSC42_Models.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig9_pt_NSC42_Models.eps}}
               \end{center}
@@
 Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
-             \label{fig:Figure_7}
+             \label{fig:Figure_9}
 \end{figure}
 
-The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}, respectively.
+The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
 The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
@@
 
-The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
+The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}.
 In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.

### 2017-08-24 longSC.tex
removed comment-out

@@
 The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the Quark-Gluon Plasma (QGP).
-%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
-%The matter produced in a heavy-ion collision exhibits strong collective radial expansion.
-Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
 The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
-%Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
-%that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
 Difference in pressure gradients and the interactions among matter constituents produced in the spatially anisotropic overlap region of the two colliding nuclei result in anisotropic transverse flow in the momentum space.
@@
 The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
-%and microscopic transport models ~\cite{Xu:2007jv}.  
 These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.
 
-%The temperature dependence of $\eta/s$ has some generic features that most known fluids obey.
-One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}.
 The temperature dependence of $\eta/s$ has some generic features typical to the most known fluids.
@@
 Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
-%This may have important implications for other fundamental physics goals. 
 It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
-%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.
 
-%The magnitude of the anisotropic flow has been to found to be sensitive to the transport properties, as well as the space-momentum profile in the initial state~\cite{}. 
 Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
@@
 Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
-%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
-%\begin{equation}
-%\label{defVn}
-%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
-%\end{equation}
-%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
-%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
 The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
@@
 The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
-%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
 The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
-%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.
 
@@
 The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
-%and the $p_{\rm T}$ dependence of linear and nonlinear response contributions to the higher order flow harmonics is discussed further in~\cite{Teaney:2012ke}. 
 Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 
-%Recently, the ALICE Collaboration measured for the first time the Symmetric 2-harmonic 4-particle %Cumulants (SC), new multiparticle observables which quantify the relationship between event-by-%event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}.
 The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
@@
 In Sec.~\ref{sec:theory} we present comparisons to model calculations.
-%Various models used in this article are described in Sec.~\ref{sec:theory}. 
 Finally, Sec.~\ref{sec:summary} summarizes our new results.
@@
 \label{sec:method}
-%\subsubsection{cumulant analysis}
 
@@
 Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced.
-%The SC observables are nearly insensitive to nonflow and quantify the correlation of the amplitudes of two different flow harmonics.
-%The first measurements of SC observables were recently published by the ALICE Collaboration in \cite{ALICE:2016kpq}.
 
@@
 \label{sec:experiment}
-%The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
 The data sample of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
@@
 \label{sec:uncertainties}
-%\textbf{\tmp{[Track selection criteria.]}}
-
-%p10================================================================================
-
-%\textbf{\tmp{[An independent analysis with different tracks (if any).]}}
-
 The systematic uncertainties are estimated by varying the event and track selection criteria. All systematic checks described here are performed independently. 
@@
 The uncertainty due to the $p_{\rm T}$ dependence of the track reconstruction efficiency was also taken into account.
-%Moreover, the effects from $p_{\rm T}$ dependence reconstruction efficiency were taken into systematic uncertainty. 
 Magnetic field polarity variation and reconstruction efficiency effects contribute less than 2\% to the systematic uncertainty.
@@
 This is because $v_{n}$ decreases with increasing $n$ and becomes more sensitive to azimuthal modulation due to detector imperfections.
-%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
 
@@
                        \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
-%			 \resizebox{0.98\textwidth}{!}{\includegraphics{figs/Fig1.eps}}
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 The NSC(3,2) and NSC(4,2) ((b) and (d)) are shown in the right panels.
-Systematic uncertainties are represented with boxes.} % The systematic uncertainties for SC(3,2) and SC(4,2) are not shown for visibility.
-        \label{fig:Figure_2}
+Systematic uncertainties are represented with boxes.}         \label{fig:Figure_2}
         \end{center}   
@@
 The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
-%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
 The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
@@
 3 in Ref.~\cite{Abelev:2012di}).
-%(see further discussions in Sec.~\ref{sec:ptdepsc})
-%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
-%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).
 
@@
 In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$.
-%We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
-%While these product are reconstructed and normalized directly for NSC calculations,
 The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
@@
 Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
-%The detailed quantitative comparisons of the measured $v_n$ to the model calculations are provided in Appendix~\ref{sec:vn}.
 
-%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
 Even though thermalization could be achieved shortly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime.
@@
 It was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-%However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
-%This observation helps us to better understand the fluctuations in initial energy density.
 The model calculations for NSC(4,2) observable show that it has better sensitivity for different $\eta/s(T)$ parameterizations but they cannot
@@
 The discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
-%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
 The measurement of SC($m$,$n$) and NSC($m$,$n$) can provide new constraints for the detailed modeling of fluctuating initial conditions.
-%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
 
@@
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-%As shown in Fig.~\ref{fig:Figure_4}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
 While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
-%For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
-%providing further independent constraints for the models.
-%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
 In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and fail similarly for the anti-correlation between $v_3$ and $v_2$.
-%Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.
 
@@
 Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
-%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_5} is opposite to that in data in 5--10\% central collisions.
-%NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
-%The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, but it is clear that this model does not describe them quantitatively.
 
@@
 The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
-%Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. 
 The SC(4,3) results clearly favor smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
@@
 For SC(3,2), the calculation with the default AMPT settings is closest to the data, but none of the AMPT configurations can describe the data fully. 
-%The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations fail to describe either of them in the most central collisions.
-%Interestingly, the string melting AMPT configuration cannot reproduce the data, and the resulting correlations are weaker than in data.
 The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
@@
 The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
-% interesting AMPT String Melting OFF, Rescattering ON < AMPT String Melting ON, Rescattering OFF
 In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
@@
 	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
-	%\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce it.
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to describe the centrality dependence of the correlations regardless of the initial conditions.
@@
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
-	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
 	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
@@
 
-%Finally, we perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} and the resulting ${\chi}^2$ values are discussed in Appendix~\ref{sec:chisq}.
 The agreement of various model calculations with the data is quantified by calculating the $\chisqndf$:
@@
 \end{figure*}
-% The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively.
@@
 
-%This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
-%Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$).
-Furthermore we observe a clear separation of two parameterizations for SC(5,3) which is even larger than SC(4,2).
-%These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.
-
 Even though the calculations from event-by-event EKRT+viscous hydrodynamics give the best $\chisqndf$ values for both SC($m$,$n$) and NSC($m$,$n$), the $\chisqndf$
@@
 \label{sec:ptdepsc}
-%It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$~30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$~30\% centrality range.
-%NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases. 
 \begin{figure}[p]
@@
 Comparison of the string melting AMPT configuration with and without hadronic rescattering suggests that a very strong $p_{\rm T}$ dependence as well as the correlation strength are weakened by the hadronic rescattering.
-%This might imply that hadronic interactions are the source of this observed $p_{\rm T}$ dependence even though the relative contributions from the partonic and hadronic stages in the final state particle distributions should be studied further.
 Consequently, the observed weak $p_{\rm T}$ dependence may be due to hadronic rescattering.
@@
 However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parameterizations in most centralities is rather small.
-%While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.
 
@@
 The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
-%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
 
@@
 Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
-%The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
-%In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role.
-This observation might help to understand the details of the fluctuations in the initial stage.
 The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to describe the centrality dependence of higher order correlations. 
@@
 The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered. 
-%Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
 Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
@@
 Together with the measurements of individual harmonics the new results for SC($m$,$n$) and NSC($m$,$n$) can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
-
-%\section{Outlooks}
-%\label{sec:outlook}
-%Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge.
-The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events.
-This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow.
-To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases.
-However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected.
-Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow.
-Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
-%%Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
-%%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

### 2017-08-28 makediff.sh
remove convert

@@ -7,5 +7,6 @@
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 CR-Round1
 #../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1 CR-Round1.EB
 #../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1.EB CR-Round1.EB.final
-../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
-../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
+#../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
+#../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
+../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 

### 2017-08-29 fa_2017-08-29.tex
final version submitted, via constantin

% Version: 2017-08-29

The ALICE Collaboration would like to thank all its engineers and technicians for their invaluable contributions to the construction of the experiment and the CERN accelerator teams for the outstanding performance of the LHC complex.
%
The ALICE Collaboration gratefully acknowledges the resources and support provided by all Grid centres and the Worldwide LHC Computing Grid (WLCG) collaboration.
%
The ALICE Collaboration acknowledges the following funding agencies for their support in building and running the ALICE detector:
%
A. I. Alikhanyan National Science Laboratory (Yerevan Physics Institute) Foundation (ANSL), State Committee of Science and World Federation of Scientists (WFS), Armenia;
%
Austrian Academy of Sciences and Nationalstiftung f\"{u}r Forschung, Technologie und Entwicklung, Austria;
%
Ministry of Communications and High Technologies, National Nuclear Research Center, Azerbaijan;
%
Conselho Nacional de Desenvolvimento Cient\'{\i}fico e Tecnol\'{o}gico (CNPq), Universidade Federal do Rio Grande do Sul (UFRGS), Financiadora de Estudos e Projetos (Finep) and Funda\c{c}\~{a}o de Amparo \`{a} Pesquisa do Estado de S\~{a}o Paulo (FAPESP), Brazil;
%
Ministry of Science \& Technology of China (MSTC), National Natural Science Foundation of China (NSFC) and Ministry of Education of China (MOEC) , China;
%
Ministry of Science, Education and Sport and Croatian Science Foundation, Croatia;
%
Ministry of Education, Youth and Sports of the Czech Republic, Czech Republic;
%
The Danish Council for Independent Research | Natural Sciences, the Carlsberg Foundation and Danish National Research Foundation (DNRF), Denmark;
%
Helsinki Institute of Physics (HIP), Finland;
%
Commissariat \`{a} l'Energie Atomique (CEA) and Institut National de Physique Nucl\'{e}aire et de Physique des Particules (IN2P3) and Centre National de la Recherche Scientifique (CNRS), France;
%
Bundesministerium f\"{u}r Bildung, Wissenschaft, Forschung und Technologie (BMBF) and GSI Helmholtzzentrum f\"{u}r Schwerionenforschung GmbH, Germany;
%
General Secretariat for Research and Technology, Ministry of Education, Research and Religions, Greece;
%
National Research, Development and Innovation Office, Hungary;
%
Department of Atomic Energy Government of India (DAE) and Council of Scientific and Industrial Research (CSIR), New Delhi, India;
%
Indonesian Institute of Science, Indonesia;
%
Centro Fermi - Museo Storico della Fisica e Centro Studi e Ricerche Enrico Fermi and Istituto Nazionale di Fisica Nucleare (INFN), Italy;
%
Institute for Innovative Science and Technology , Nagasaki Institute of Applied Science (IIST), Japan Society for the Promotion of Science (JSPS) KAKENHI and Japanese Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan;
%
Consejo Nacional de Ciencia (CONACYT) y Tecnolog\'{i}a, through Fondo de Cooperaci\'{o}n Internacional en Ciencia y Tecnolog\'{i}a (FONCICYT) and Direcci\'{o}n General de Asuntos del Personal Academico (DGAPA), Mexico;
%
Nederlandse Organisatie voor Wetenschappelijk Onderzoek (NWO), Netherlands;
%
The Research Council of Norway, Norway;
%
Commission on Science and Technology for Sustainable Development in the South (COMSATS), Pakistan;
%
Pontificia Universidad Cat\'{o}lica del Per\'{u}, Peru;
%
Ministry of Science and Higher Education and National Science Centre, Poland;
%
Korea Institute of Science and Technology Information and National Research Foundation of Korea (NRF), Republic of Korea;
%
Ministry of Education and Scientific Research, Institute of Atomic Physics and Romanian National Agency for Science, Technology and Innovation, Romania;
%
Joint Institute for Nuclear Research (JINR), Ministry of Education and Science of the Russian Federation and National Research Centre Kurchatov Institute, Russia;
%
Ministry of Education, Science, Research and Sport of the Slovak Republic, Slovakia;
%
National Research Foundation of South Africa, South Africa;
%
Centro de Aplicaciones Tecnol\'{o}gicas y Desarrollo Nuclear (CEADEN), Cubaenerg\'{\i}a, Cuba, Ministerio de Ciencia e Innovacion and Centro de Investigaciones Energ\'{e}ticas, Medioambientales y Tecnol\'{o}gicas (CIEMAT), Spain;
%
Swedish Research Council (VR) and Knut \& Alice Wallenberg Foundation (KAW), Sweden;
%
European Organization for Nuclear Research, Switzerland;
%
National Science and Technology Development Agency (NSDTA), Suranaree University of Technology (SUT) and Office of the Higher Education Commission under NRU project of Thailand, Thailand;
%
Turkish Atomic Energy Agency (TAEK), Turkey;
%
National Academy of  Sciences of Ukraine, Ukraine;
%
Science and Technology Facilities Council (STFC), United Kingdom;
%
National Science Foundation of the United States of America (NSF) and United States Department of Energy, Office of Nuclear Physics (DOE NP), United States of America.

### 2017-11-10 longSC.tex
for PRC

@@
 
-\begin{figure*}[h]
+\begin{figure*}[t!]
             \begin{center}
@@
 
-\begin{figure*}
+\begin{figure}[t!]
 	\begin{center}
@@
         \end{center}   
-\end{figure*}
+\end{figure}
 
@@
 The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
-The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
+The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality percentile or $p_{\rm T, min}$ increases. 
 The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
-In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$.
+In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
 The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
@@
 The {KLN} model assumes that the initial energy density is proportional to that of the initial gluons calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In Monte Carlo versions {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah} of these models an additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
+In Monte Carlo versions {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah} of these models additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy distribution of individual partons, which fluctuate in both momentum and coordinate space.
@@
 
-Even though thermalization could be achieved shortly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime.
+Even though thermalization could be achieved quickly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime.
 To address such non-equilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
@@
 The model calculations for NSC(4,2) observable show that it has better sensitivity for different $\eta/s(T)$ parameterizations but they cannot
-describe neither the centrality dependence nor the absolute values.
+describe either the centrality dependence or the absolute values.
 The discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
@@
 
-\begin{figure*}[!]
+\begin{figure}[t!]
             \begin{center}
@@
         \label{fig:Figure_4}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[!]
+\begin{figure}[t!]
 	\begin{center}
@@
         \end{center}   
- \end{figure*}
+ \end{figure}
 
@@
 
- \begin{figure*}[!]
+ \begin{figure}[t!]
 	\begin{center}
@@
 where $y_i$ ($f_i$) is a measurement (model) value in a centrality bin $i$.
-The systematical and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
+The systematical and statistical errors from the data are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2 + \sigma_{f_i, stat}^2}$ together with the statistical errors of the model calculations.
 The total number of data samples $N_{\rm dof}$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
@@
 
-\begin{figure*}[h]
+\begin{figure}[t!]
             \begin{center}
@@
               \end{center}
-\end{figure*}
+\end{figure}
 The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively.
@@
 \label{sec:ptdepsc}
-\begin{figure}[p]
+\begin{figure}[t!]
              \begin{center}
@@
 
-\begin{figure}[p]
+\begin{figure}[t!]
              \begin{center}

### 2017-11-10 makediff.sh
final to PC for PRC

@@ -9,4 +9,5 @@
 #../git-latexdiff/git-latexdiff --main paper.tex  CR-Round1.EB CR-Round1.EB.final
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
 #../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
-../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 
+#../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 
+../git-latexdiff/git-latexdiff --main paper.tex   master  PRC

### 2017-11-13 longSC.tex
eps to pdf

@@
             \begin{center}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
-                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC}}\hspace{-0.67cm}
+                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC}}
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC.eps}}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC}}
         \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels.
@@
 	\begin{center}
-        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt.eps}}
+        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt}}
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
@@
             \begin{center}
-                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_EKRT.eps}}
+                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_EKRT}}
               \end{center}
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_VISH.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_VISH}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
 	\begin{center}
-        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig6_ModelComparison_AMPT.eps}}
+        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig6_ModelComparison_AMPT}}
         \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV.
@@
             \begin{center}
-                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad.eps}}
+                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad}}
         \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig8_pt_NSC32_Models.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig8_pt_NSC32_Models}}
               \end{center}
@@
              \begin{center}
-              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig9_pt_NSC42_Models.eps}}
+              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig9_pt_NSC42_Models}}
               \end{center}

### 2017-11-13 makediff.sh

@@ -10,4 +10,4 @@
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
 #../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
 #../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 
-../git-latexdiff/git-latexdiff --main paper.tex   master  PRC
+../git-latexdiff/git-latexdiff --main paper.tex   PRC master

### 2017-11-13 makediff.sh
for IRC

@@ -10,4 +10,4 @@
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
 #../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
 #../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 
-../git-latexdiff/git-latexdiff --main paper.tex   PRC master
+../git-latexdiff/git-latexdiff --main paper.tex   master PRC

### 2017-11-14 longSC.tex
IRC

@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
-In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
+In this paper we denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
 The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.

### 2017-11-23 longSC.tex
final figures

@@
                        \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC}}
-        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
+        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for $m$ = 3--5 and $n$ = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
 The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
@@
 This demonstrates the advantage of using the normalized SC observables in which the correlation strength between flow harmonics is not hindered by the differences in magnitudes of different flow harmonics.
-The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality range 20--50\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
+The NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for the centrality range 20--50\% within the errors as shown in Fig.~\ref{fig:Figure_1}(b).
 The SC(5,2) magnitude is larger than SC(5,3), but the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$. 
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range 0--30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the 30--50\% centrality.
+The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range 0--30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the 30--50\% centrality range.
 The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
@@
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
+While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in the 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
 In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and fail similarly for the anti-correlation between $v_3$ and $v_2$.
@@
 	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
-	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
+	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality percentile ranges $>~20\%$ within the errors.
+This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
 \end{enumerate}
@@
 where $y_i$ ($f_i$) is a measurement (model) value in a centrality bin $i$.
-The systematical and statistical errors from the data are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2 + \sigma_{f_i, stat}^2}$ together with the statistical errors of the model calculations.
+The systematic and statistical errors from the data are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2 + \sigma_{f_i, stat}^2}$ together with the statistical errors of the model calculations.
 The total number of data samples $N_{\rm dof}$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
@@
 The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
-As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range 30--50\%.
+As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centrality range and underestimate it in the centrality range 30--50\%.
 However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parameterizations in most centralities is rather small.

### 2017-11-23 paper.tex
adding ack
removed comment-out
remove convert
recommit
into svn
final to PRC

@@
 \documentclass[ALICE,manyauthors]{cernphprep}
+\pdfoutput=1
 \usepackage[comma,square,numbers,sort&compress]{natbib}
@@
 %\usepackage{refcheck}
-\linenumbers
+%\linenumbers
 
@@
 \PHyear{2017}
-\PHnumber{xxx}                 % required, obtained from PH
+\PHnumber{215}                 % required, obtained from PH
 \PHdate{21 August}              % required, will be obtained from PH
@@
 %%% Put your own title + short title here:
-\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV}
+\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV}
 \ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers
@@
 \section*{Acknowledgements}
-%\input{acknowledgements_jan2015.tex}    %%%%%%% get the lates version before submitting
+\input{fa_2017-08-29.tex}    %%%%%%% get the lates version before submitting
 \end{acknowledgement}
-%
-%
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{apsrev4-1}   % Put here the style file name for the paper, i.e.apsrev4-1
-%\bibliography{biblio}
-%\input {bibliography.tex}  
-%
 
-%\nocite{*}
-
-% \bibliographystyle{mybibstyle}
-%\bibliographystyle{utphys}
-%\bibliography{paper}
 \bibliographystyle{utphys}
@@
 \label{app:collab}
-%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
+\input{Alice_Authorlist_2017-Aug-21.tex}  %%%%%%% done by webmaster team
 %\input{}              %%%%%%%%%%%% put the references here

### 2017-11-23 abstract.tex

--- 2017-08-20 abstract.tex
@@
 The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
-have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
+have been measured in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV with the ALICE detector at the Large Hadron Collider. 
 The results are reported in terms of multiparticle correlation observables dubbed Symmetric Cumulants.

### 2017-11-23 appendix.tex
removed comment-out

@@
 $v_n$ results presented in this section are for charged particles in the pseudorapidity range $|\eta| < 0.8$ and the transverse momentum range $0.2 < p_{\rm T} < 5.0$ GeV/$c$ as a function of collision centrality~\cite{Adam:2016izf}.
-%The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.
 
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT}}
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH}}
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT}}
         \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
@@
             \begin{center}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v2_modelcomparisonBest.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v3_modelcomparisonBest.eps}}\hspace{-0.27cm}
-                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest.eps}}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v2_modelcomparisonBest}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v3_modelcomparisonBest}}\hspace{-0.27cm}
+                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA4_v4_modelcomparisonBest}}
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
@@
 Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
-
-%\newpage
-%\section{Chi-Square test for SC observables}
-%\label{sec:chisq}
-%We perform a least-square test to the models for each SC observable via a log-likelihood or least squares-${\chi}^2$ method~\cite{PDBook} as following,
-%
-%\begin{equation}
-%\chi^{2} = \sum_{i=1}^{N} \frac{{(y_i-f_i)}^{2}}{{\sigma_i}^{2}},
-%\label{Eq:chisq}
-%\end{equation}
-%
-%where $y_i$ ($f_i$) is a measurement (model) in a centrality bin, and the systematic and statistical errors  are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2}$.
-%The centrality range is restricted in 10--50\% bins, corresponding the total number of data sets in each observable (N) is 4.
-%The resulting ${\chi}^2$ for few selected calculations from three theoretical models which describe the SC observables best is shown in Fig.~\ref{fig:Figure_A5}.
-%\begin{figure*}[h]
-%            \begin{center}
-%                       \resizebox{0.8\textwidth}{!}{\includegraphics{figs/chisq_bestfits.eps}}
-%        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for all SC observables.
-The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
-%        \label{fig:Figure_A5}
-%              \end{center}
-%\end{figure*}
-%
-%We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and default AMPT models, the ${\chi}^2$ values for SC($m$,$n$) is larger than those for NSC($m$,$n$).
-This can be explained by the fact that the individual flow harmonics $v_n$ is not well described by those models compared to event-by-event EKRT+viscous hydrodynamics as shown in Fig.~\ref{fig:Figure_A4}.
-%Even though the calculations from event-by-event EKRT+viscous hydrodynamics give best ${\chi}^2$ values both for SC($m$,$n$) and NSC($m$,$n$), the ${\chi}^2$
-%values are large especially for the observables related with $v_3$. 
-%Even with the best model calculations from three theoretical models, the ${\chi}^2$ value varies a lot depending both on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties used in the model calculations.
-%
-%
-%

### 2018-01-15 abstract.tex
main part wo funding and ref

@@
 have been measured in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV with the ALICE detector at the Large Hadron Collider. 
-The results are reported in terms of multiparticle correlation observables dubbed Symmetric Cumulants.
+The results are reported in terms of multiparticle correlation observables dubbed symmetric cumulants.
 These observables are robust against biases originating from nonflow effects. 
 The centrality dependence of correlations between the higher order harmonics (the quadrangular $v_4$ and pentagonal $v_5$ flow) and the lower order harmonics (the elliptic $v_2$ and triangular $v_3$ flow)
-is presented. The transverse momentum dependence of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ is also reported. 
-The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
+is presented. The transverse momentum dependences of correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$ are also reported. 
+The results are compared to calculations from viscous hydrodynamics and  a multi-phase transport ({AMPT}) model calculations.
 The comparisons to viscous hydrodynamic models demonstrate that
@@
 The calculations with the AMPT initial conditions yield results closest to the measurements.
-Correlations between the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
+Correlations among the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.

### 2018-01-15 longSC.tex
main part wo funding and ref

@@
 \label{sec:intro}
-The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the Quark-Gluon Plasma (QGP).
+The main emphasis of the ultrarelativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the quark-gluon plasma (QGP).
 The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
@@
 It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature.
-Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}.
+Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using anti-de sitter/conformal field theory (AdS/CFT) correspondence~\cite{Kovtun:2004de}.
 Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
@@
 
-Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
+Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:
 
 \begin{equation}
-E\frac{\mathrm{d}^3N}{\mathrm{d^3}{p}} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
+E\frac{{d}^3N}{{d^3}{p}} = \frac{1}{2\pi}\frac{{d}^2N}{p_{\mathrm{T}}{d}p_{\mathrm{T}}{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
 \label{Eq:Fourier}
@@
 
-\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic.
+\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n{\mathrm{th}}$-order harmonic.
 Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
@@
 where the curly brackets denote the average over the transverse plane, i.e.
-$\{\cdots\}$ = $\int$ d$x$d$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $\phi$ is azimuthal angle, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
-There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g.
-$v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
+$\{\cdots\}$ = $\int$ $d$$x$$d$$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $\phi$ is azimuthal angle, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
+There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g., $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
 Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
@@
 
-The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
+The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{symmetric cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
 The new observables are particularly robust against few-particle nonflow correlations~\cite{Aamodt:2010pa} and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}.
 It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
-In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
+In this article, we have extended the analysis of SC observables to higher order harmonics (up to fifth order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).
 We also present a systematic comparison to hydrodynamic and AMPT model calculations.
@@
 What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$).
-The temperature dependence of $\eta/s$ of the QGP was discussed in~\cite{Csernai:2006zz}.
-The effects on hadron spectra and elliptic flow were studied in~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.
-A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
+The temperature dependence of $\eta/s$ of the QGP was discussed in Ref.~\cite{Csernai:2006zz}.
+The effects on hadron spectra and elliptic flow were studied in Ref.~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.
+A more systematic study with event-by-event Eskola-Kajantie-Ruuskanen-Tuominen (EKRT) + viscous hydrodynamic calculations was recently initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein).
 The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
-It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics.
+It was already demonstrated in Ref.~\cite{Niemi:2015qia} that different $\eta/s(T)$ parametrizations can lead to the same centrality dependence of individual flow harmonics.
 In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between amplitudes of two different harmonics $v_m$ and $v_n$.
@@
 
-For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the set of observables introduced in \cite{Niemi:2012aj}.
-Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced.
+For reasons discussed in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the set of observables introduced in Ref.~\cite{Niemi:2012aj}.
+Based on Ref.~\cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{symmetric cumulants}~(SC), were introduced.
 
@@
 %
-with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
+with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in Ref.~\cite{Bilandzic:2013kga}).
 In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
@@
 In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations.
-For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable.
-This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.
+For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}), the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable.
+This was verified by HIJING model simulations in Ref.~\cite{ALICE:2016kpq}.
 
-The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}.
-It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}.
+The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anticorrelated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}.
+It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (midcentral) regimes~\cite{ALICE:2016kpq}.
 The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role.
-These results were also used to discriminate between different parameterizations of initial conditions.
-It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
-The first theoretical studies of SC observables can be found in \cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
+These results were also used to discriminate between different parametrizations of initial conditions.
+It was demonstrated that in the fluctuation-dominated regime (central collisions), Monte Carlo (MC)-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.
 
@@
 \label{sec:experiment}
-The data sample of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
+The data sample of $\PbPb$ collisions at the center-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
 Detailed descriptions of the ALICE detector can be found
-in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
-Projection Chamber (TPC) was used to reconstruct charged particle
+in Refs.~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The time
+projection chamber (TPC) was used to reconstruct charged particle
 tracks and measure their momenta with full azimuthal coverage in the
@@
 and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
-described in~\cite{Aamodt:2010pa} were applied to minimize
+described in Ref.~\cite{Aamodt:2010pa} were applied to minimize
 contamination from secondary charged particles and fake tracks.
@@
 below 1\% for $p_{\rm T}>1$~GeV/$c$.
-The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
+The $p_{\rm T}$ cutoff of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
 at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
@@
 The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed.
-The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
+The systematic uncertainty from the centrality determination was evaluated by using the TPC and silicon pixel detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
 The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
-As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
+As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$ vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
 The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.
@@
 The systematic uncertainty due to the track reconstruction procedure was estimated from comparisons between results for the so-called standalone TPC tracks with the 
-same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
+same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the inner tracking system (ITS) detectors with tighter selection criteria.
 To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
@@
 Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the reconstruction efficiency.
-In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which has a uniform distribution in azimuthal angle.
+In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}), which has a uniform distribution in azimuthal angle.
 Detector inefficiencies were introduced to mimic the non-uniform azimuthal distribution in the data.
-For the observables SC(5,2), SC(5,3) and SC(4,3) the variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
+For the observables SC(5,2), SC(5,3), and SC(4,3), the variation due to non-uniform acceptance is about 9\%, 17\%, and 11\%, respectively.
 Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
@@
 \label{sec:results}
-The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)) which were published in \cite{ALICE:2016kpq}.
+The centrality dependence of the higher order harmonic correlations [SC(4,3), SC(5,2), and SC(5,3)] are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations [SC(3,2) and SC(4,2)], which were published in Ref.~\cite{ALICE:2016kpq}.
 The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
@@
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for $m$ = 3--5 and $n$ = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands.
+The lower order harmonic correlations [SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)] are taken from Ref.~\cite{ALICE:2016kpq} and shown as bands.
 The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations.
@@
 The higher order flow harmonic correlations are much smaller compared to the lower order harmonic correlations.
-In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).
+In particular, SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller than SC(3,2).
 
@@
 
-It can be seen in Fig.~\ref{fig:Figure_1}(a) that the lower order harmonic correlations as well as SC(5,2) increase non-linearly towards peripheral collisions.
+It can be seen in Fig.~\ref{fig:Figure_1}(a) that the lower order harmonic correlations as well as SC(5,2) increase nonlinearly toward peripheral collisions.
 In the case of SC(5,3) and SC(4,3), the centrality dependence is weaker than for the other harmonic correlations.
 The NSC(5,3) observable shows the strongest normalized correlation among all harmonics while NSC(5,2) shows the weakest centrality dependence.
-Both NSC(3,2) and NSC(4,3) are getting more anti-correlated toward peripheral collisions and have the similar magnitude.
+Both NSC(3,2) and NSC(4,3) are getting more anticorrelated toward peripheral collisions and have similar magnitudes.
 
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC}}
-        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels.
-The NSC(3,2) and NSC(4,2) ((b) and (d)) are shown in the right panels.
+        \caption{SC(3,2) and SC(4,2) [panels (a) and (c)] as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels.
+The NSC(3,2) and NSC(4,2) [panels (b) and (d)] are shown in the right panels.
 Systematic uncertainties are represented with boxes.}         \label{fig:Figure_2}
@@
 
-To study the $p_{\rm T}$ dependence of SC$(m,n)$, we present the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results.
+To study the $p_{\rm T}$ dependence of SC$(m,n)$, we present the results as a function of the low $p_{\rm T}$ cutoff ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results.
 Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
-The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
+The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}(a) and \ref{fig:Figure_2}(c).
 The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
 The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality percentile or $p_{\rm T, min}$ increases. 
-The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
+The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}(b) and \ref{fig:Figure_2}(d).
 The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
@@
         	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt}}
-        \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)).
-$v_4$ and $v_5$ are shown in the same panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)).}
+        \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels [(a), (b), and (c)].
+$v_4$ and $v_5$ are shown in the same panel (c).
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels [(d), (e), and (f)].}
         \label{fig:Figure_3}
@@
 These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
-In this paper we denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
+In this paper, we denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
 The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
-The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_3}.
-The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}.
-The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C).
-The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_3} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
+The centrality dependence of $v_n$ for $n$ = 2--5 is shown in Figs.~\ref{fig:Figure_3}(a)--\ref{fig:Figure_3}(c).
+The $v_n$ values ($n < 5$) are equivalent to those in Ref.~\cite{Adam:2016izf}.
+The fifth-order flow harmonic $v_5$ is shown in Fig.~\ref{fig:Figure_3}(c).
+The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in Figs.~\ref{fig:Figure_3}(d)--\ref{fig:Figure_3}(f) in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
 
@@
 We have performed a systematic comparison of the centrality and transverse momentum dependence of the SC($m$,$n$) and NSC($m$,$n$) to the event-by-event  EKRT+viscous hydrodynamics~\cite{Niemi:2015qia}, VISH2+1~\cite{Shen:2010uy,Shen:2014vra}, and the AMPT~\cite{Qian:2016pau,Lin:2004en,Lin:2014tya} models.
-Comparisons for $v_n$ coefficients with the model calculations are presented in Appendix~\ref{sec:vn}.
+Comparisons for $v_n$ coefficients with the model calculations are presented in the appendix.
 
 In the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
-The subsequent space-time evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
-This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia} and Appendix~\ref{sec:vn}).
+The subsequent space-time evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
+This model gives a good description of the charged hadron multiplicity and the low-$p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11--13 in Ref.~\cite{Niemi:2015qia}).
+Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in Ref.~\cite{Niemi:2015qia} and our appendix).
 
@@
 By tuning transport coefficients and decoupling temperature for a given scenario of initial conditions, it can describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya} energies.
-Three different types of initial conditions~\cite{Zhu:2016puf} ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values have been used for our data to model comparisons.
+Three different types of initial conditions~\cite{Zhu:2016puf} ({MC-Glauber}, Monte Carlo Kharzeev-Levin-Nardi ({MC-KLN}), and {AMPT}) along with different constant $\eta/s$ values have been used for our data to model comparisons.
 Traditionally, the Glauber model constructs the initial entropy density from the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}.
@@
 The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
-For the data comparisons three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering.
-The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb.
+For the data comparisons, three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering.
+The input parameters used in all configurations are $\alpha_s = 0.33$ and a partonic cross section of 1.5~mb.
 In the default configuration, partons are recombined with their parent strings when they stop interacting.
@@
 The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-In the string melting configuration, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}.
+In the string melting configuration, the initial strings are melted into partons whose interactions are described by the zipping parton cascade (ZPC) model~\cite{Zhang:1997ej}.
 These partons are then combined into the final state hadrons via a quark coalescence model.
-In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
+In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a relativistic transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
 The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$, and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}.
-The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.
+The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons, and protons to the data can be found in Ref.~\cite{Adam:2016nfo}.
 
-\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
+\subsection{Centrality dependence of SC($m$,$n$) and NSC($m$,$n$)}
 \label{sec:theory_allorder}
-Comparison to event-by-event EKRT+viscous hydrodynamic predictions with various parameterizations of the temperature dependence of $\eta/s(T)$ was shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
-It was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
-The model calculations for NSC(4,2) observable show that it has better sensitivity for different $\eta/s(T)$ parameterizations but they cannot
+Comparison to event-by-event EKRT+viscous hydrodynamic predictions with various parametrizations of the temperature dependence of $\eta/s(T)$ was shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
+It was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from Ref.~\cite{Niemi:2012aj}.
+The model calculations for NSC(4,2) observable show that it has better sensitivity for different $\eta/s(T)$ parametrizations but they cannot
 describe either the centrality dependence or the absolute values.
@@
 Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.
-The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations.
+The lines are hydrodynamic predictions with two different $\eta/s(T)$ parametrizations.
 Left (right) panels show SC($m$,$n$) (NSC($m$,$n$)).}
@@
 The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_4}. 
-As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
-This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
+As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parametrization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV.
+This parametrization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
 The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
-While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in the 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
-In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and fail similarly for the anti-correlation between $v_3$ and $v_2$.
+While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in the 0--40\% centrality range and deviate by about one $\sigma$ for 40--50\% centrality.
+In the case of $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly in mid-central collisions and fail similarly for the anticorrelation between $v_3$ and $v_2$.
 
@@
 
-However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
+However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parametrizations used in the models.
 Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
@@
 We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
-The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
+The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
 The SC(4,3) results clearly favor smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.
@@
 Results are compared to various AMPT models.
-Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
+Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$)).}
         \label{fig:Figure_6}
@@
 By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, it was possible to recover the difference in SC(3,2) between the data and the model.
-The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in \cite{Adam:2016nfo} in all centrality ranges.
+The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values as reported in Ref.~\cite{Adam:2016nfo} in all centrality ranges.
 
@@
 The NSC(4,2) observable is slightly overestimated by the string melting setting which can describe SC(4,2) but the default AMPT configuration can describe the data better.
-The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)). The hadronic rescattering makes NSC(4,2) slightly smaller.
+The influence of the hadronic rescattering phase on NSC(4,2) is opposite to other observables [SC(3,2), NSC(3,2), and SC(4,2)]. The hadronic rescattering makes NSC(4,2) slightly smaller.
 It should be noted that the agreement with SC($m$,$n$) should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
@@
 The NSC(4,3) observable is well described by the default AMPT model but cannot be reproduced by the string melting AMPT model.
-In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(3,2) and NSC(5,2) and predicts a very weak correlation both for NSC(3,2) and NSC(4,3).
+In summary, the default AMPT model describes well the normalized symmetric cumulants [NSC($m$,$n$)] from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(3,2) and NSC(5,2) and predicts a very weak correlation both for NSC(3,2) and NSC(4,3).
 
@@
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
-	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
+	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ [SC(3,2), SC(4,2), NSC(3,2), and NSC(4,3)] is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to describe the centrality dependence of the correlations regardless of the initial conditions.
 	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively, but not quantitively for most of the centrality ranges.
-	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
+	\item The default AMPT model can describe the normalized symmetric cumulants [NSC($m$,$n$)] quantitively for most centralities while the string melting AMPT model fails to describe them.
 	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality percentile ranges $>~20\%$ within the errors.
@@
 
-The agreement of various model calculations with the data is quantified by calculating the $\chisqndf$:
+The agreement of various model calculations with the data is quantified by calculating the $\chisqndf$,
 
@@
 The systematic and statistical errors from the data are combined in quadrature $\sigma_i = \sqrt{\sigma_{i, stat}^2 + \sigma_{i, syst}^2 + \sigma_{f_i, stat}^2}$ together with the statistical errors of the model calculations.
-The total number of data samples $N_{\rm dof}$ in Eq.~\ref{Eq:chisq} is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
-The $\chisqndf$ for model calculations which are best in describing the SC observables for each of the three different types of models is shown in Fig.~\ref{fig:Figure_7}.
+The total number of data samples $N_{\rm dof}$ in Eq.~(\ref{Eq:chisq}) is 4, which corresponds to the number of bins in the centrality range 10--50\% used in $\chisqndf$ calculations.
+The $\chisqndf$ for model calculations which are best in describing the SC observables for each of the three different types of models are shown in Fig.~\ref{fig:Figure_7}.
 
@@
                        \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad}}
-        \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).
+        \caption{The $\chisqndf$ values calculated by Eq.~(\ref{Eq:chisq}) are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b), and individual harmonics $v_n$ (c).
 Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
@@
 \end{figure}
-The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively.
-The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_7}c.
-We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
+The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Figs.~\ref{fig:Figure_7}(a) and \ref{fig:Figure_7}(b), respectively.
+The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$ = 2--4 are shown in Fig.~\ref{fig:Figure_7}(c).
+We found that in the case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$).
 This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics.
-This is quantified in Fig.~\ref{fig:Figure_7}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
+This is quantified in Fig.~\ref{fig:Figure_7}(c), where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
 The default configuration of the AMPT model gives the best $\chisqndf$ values for NSC($m$,$n$), especially for NSC(3,2).
-However the $\chisqndf$ values of this model are largest for $v_n$ among the models especially for $v_2$.
+However, the $\chisqndf$ values of this model are largest for $v_n$ among the models especially for $v_2$.
 
@@
 The $\chisqndf$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
-The $\chisqndf$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
+The $\chisqndf$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parametrization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
 This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.
@@
 Even though the calculations from event-by-event EKRT+viscous hydrodynamics give the best $\chisqndf$ values for both SC($m$,$n$) and NSC($m$,$n$), the $\chisqndf$
-values are large especially for the observables which include $v_3$. 
+values are large, especially for the observables which include $v_3$. 
 Even with the best model calculations, the $\chisqndf$ value varies a lot depending on the model parameters and/or different order SC observables, which implies that the different order harmonic correlations have different sensitivity to the initial conditions and the system properties.
 
-\subsection{Transverse Momentum Dependence of Correlations between $v_2$ and $v_3$ and between $v_2$ and $v_4$}
+\subsection{Transverse momentum dependence of correlations between $v_2$ and $v_3$ and between $v_2$ and $v_4$}
 \label{sec:ptdepsc}
@@
 
-The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}, respectively.
+The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}, respectively.
 The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
@@
 Consequently, the observed weak $p_{\rm T}$ dependence may be due to hadronic rescattering.
-The relative contributions to the final state particle distributions from partonic and hadronic stages need further study.
+The relative contributions to the final-state particle distributions from partonic and hadronic stages need further study.
 
-The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Fig.~\ref{fig:Figure_8} and Fig.~\ref{fig:Figure_9}.
+The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.
 In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
-The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models.
-The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small.
+The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\%, where the data show stronger $p_{\rm T}$ dependence than the models.
+The difference between the model calculations with the two different parametrizations of $\eta/s(T)$ is very small.
 As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centrality range and underestimate it in the centrality range 30--50\%.
-However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parameterizations in most centralities is rather small.
+However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges, while the difference of the model results for the two parametrizations in most centralities is rather small.
 
-The observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in ~\cite{Niemi:2012aj}.
-The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
+The observed moderate $p_{\rm T}$ dependence in midcentral collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in Ref.~\cite{Niemi:2012aj}.
+The comparisons to hydrodynamic models can further help us to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
 
@@
 In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
-The results are presented in terms of the Symmetric Cumulants SC($m$,$n$).
-It was demonstrated earlier in \cite{ALICE:2016kpq} that SC($m$,$n$) is insensitive to nonflow effects and independent of symmetry plane correlations.
+The results are presented in terms of the symmetric cumulants SC($m$,$n$).
+It was demonstrated earlier in Ref.~\cite{ALICE:2016kpq} that SC($m$,$n$) is insensitive to nonflow effects and independent of symmetry plane correlations.
 
 We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
-These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
+These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
 It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties.
-Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
+Therefore, they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final-state particle anisotropies.
 The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to describe the centrality dependence of higher order correlations. 
@@
 A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order.
-The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered. 
+The default configuration of the AMPT model describes well the normalized symmetric cumulants [NSC($m$,$n$)] for most centralities and for most combinations of harmonics which were considered. 
 Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
-Together with the measurements of individual harmonics the new results for SC($m$,$n$) and NSC($m$,$n$) can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+Together with the measurements of individual harmonics, the new results for SC($m$,$n$) and NSC($m$,$n$) can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultrarelativistic heavy-ion collisions.

### 2018-01-15 makediff.sh
git diff

@@ -10,4 +10,5 @@
 #../git-latexdiff/git-latexdiff --main paper.tex  EB-R1 master 
 #../git-latexdiff/git-latexdiff --main paper.tex   f3edf67 3a440fe
 #../git-latexdiff/git-latexdiff --main paper.tex   master CR-final 
-../git-latexdiff/git-latexdiff --main paper.tex   master PRC
+#../git-latexdiff/git-latexdiff --main paper.tex   master PRC
+../git-latexdiff/git-latexdiff --main paper.tex   master PRC-Proof

### 2018-01-15 longSC.tex
few comma  missing

@@
 This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc.
-Tracks with kinks (i.e.
-tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
+Tracks with kinks (i.e., tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.
 
@@
 Detector inefficiencies were introduced to mimic the non-uniform azimuthal distribution in the data.
-For the observables SC(5,2), SC(5,3), and SC(4,3), the variation due to non-uniform acceptance is about 9\%, 17\%, and 11\%, respectively.
+For the observables SC(5,2), SC(5,3), and SC(4,3), the variation due to nonuniform acceptance is about 9\%, 17\%, and 11\%, respectively.
 Overall, the systematic uncertainties are larger for SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
@@
 The default configuration of the AMPT reproduces NSC(3,2), while the other AMPT configurations predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
-In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for 40--50\% where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
+In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for 40--50\%, where the model underestimates the data and shows a stronger $p_{\rm T}$ dependence than the data.
 As for  NSC(4,2), the default AMPT configuration which describes NSC(3,2) can also reproduce the data well except for the 10--20\% and 40--50\% centralities.

### 2018-01-15 appendix.tex
adding the appendix

@@
         \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}.
-Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} for two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
+Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} for two different $\eta/s(T)$ parametrizations, labeled in the same way as in Ref.~\cite{Niemi:2015qia}.}
         \label{fig:Figure_A1}
@@
 The measured $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}.
-In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
+In these calculations, the initial conditions and $\eta/s$ parametrizations are chosen to reproduce the LHC $v_n$ data.
 The calculations capture the centrality dependence of $v_n$ in the central and mid-central collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
@@
 Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are shown in different colors.
+Three initial conditions from AMPT, MC-KLN, and MC-Glauber are shown in different colors.
 The results for different $\eta/s$ values are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber and, 0.16 for AMPT) are drawn as dashed lines.}
@@
 The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
-Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$.
+Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$, and $v_4$.
 In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to mid-central collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges.
 For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions.
-The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3 and 4).
+The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3, and 4).
 The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$.
@@
                        \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT}}
-        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
+        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3, and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
         \label{fig:Figure_A3}
@@
 The default version of AMPT underestimates $v_n$ for $n$ = 2--4 by $\approx$ 20\%.
-It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
+It should be noted that the default AMPT model can describe the normalized symmetric cumulants [NSC($m$,$n$)] quantitively for most centralities while the string melting AMPT model fails to describe them.
 

### 2018-01-15 longSC.tex
Monte Carlo (MC)--Glauber

@@
 These results were also used to discriminate between different parametrizations of initial conditions.
-It was demonstrated that in the fluctuation-dominated regime (central collisions), Monte Carlo (MC)-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
+It was demonstrated that in the fluctuation-dominated regime (central collisions), Monte Carlo (MC)--Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}.
 The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.

### 2018-01-15 fa_2017-08-29.tex
fa update

@@
 %
-The ALICE Collaboration gratefully acknowledges the resources and support provided by all Grid centres and the Worldwide LHC Computing Grid (WLCG) collaboration.
+The ALICE Collaboration gratefully acknowledges the resources and support provided by all grid centers and the Worldwide LHC Computing Grid (WLCG) collaboration.
 %
@@
 %
-Ministry of Science \& Technology of China (MSTC), National Natural Science Foundation of China (NSFC) and Ministry of Education of China (MOEC) , China;
+Ministry of Science and Technology of China (MSTC), National Natural Science Foundation of China (NSFC), and Ministry of Education of China (MOEC) , China;
 %
-Ministry of Science, Education and Sport and Croatian Science Foundation, Croatia;
+Ministry of Science, Education, and Sport and Croatian Science Foundation, Croatia;
 %
-Ministry of Education, Youth and Sports of the Czech Republic, Czech Republic;
+Ministry of Education, Youth, and Sports of the Czech Republic, Czech Republic;
 %
-The Danish Council for Independent Research | Natural Sciences, the Carlsberg Foundation and Danish National Research Foundation (DNRF), Denmark;
+the Danish Council for Independent Research--Natural Sciences, the Carlsberg Foundation and Danish National Research Foundation (DNRF), Denmark;
 %
@@
 %
-Commissariat \`{a} l'Energie Atomique (CEA) and Institut National de Physique Nucl\'{e}aire et de Physique des Particules (IN2P3) and Centre National de la Recherche Scientifique (CNRS), France;
+Commissariat \`{a} l'Energie Atomique (CEA), Institut National de Physique Nucl\'{e}aire et de Physique des Particules (IN2P3), and Centre National de la Recherche Scientifique (CNRS), France;
 %
@@
 %
-The Research Council of Norway, Norway;
+the Research Council of Norway, Norway;
 %
@@
 %
-Swedish Research Council (VR) and Knut \& Alice Wallenberg Foundation (KAW), Sweden;
+Swedish Research Council (VR) and Knut and Alice Wallenberg Foundation (KAW), Sweden;
 %
@@
 %
-National Science Foundation of the United States of America (NSF) and United States Department of Energy, Office of Nuclear Physics (DOE NP), United States of America.
+and National Science Foundation of the United States of America (NSF) and United States Department of Energy, Office of Nuclear Physics (DOE NP), United States of America.

### 2018-01-15 abstract.tex
fix snn and missing part dj

@@
 The correlations between event-by-event fluctuations of anisotropic flow harmonic amplitudes
-have been measured in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV with the ALICE detector at the Large Hadron Collider. 
+have been measured in Pb-Pb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV with the ALICE detector at the Large Hadron Collider. 
 The results are reported in terms of multiparticle correlation observables dubbed symmetric cumulants.
@@
 The calculations with the AMPT initial conditions yield results closest to the measurements.
-Correlations among the magnitudes of $v_2$, $v_3$ and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
+Correlations among the magnitudes of $v_2$, $v_3$, and $v_4$ show moderate $p_{\rm T}$ dependence in mid-central collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, which might help to understand the possible contribution of bulk viscosity in the hadronic phase of the system.

### 2018-01-15 longSC.tex
fix snn and missing part dj

@@
 NSC($m$,$n$) correlators increase with larger $\eta/s$ in hydrodynamic calculations in the 0--30\% centrality range in the same way as the event plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}.
-In semi-peripheral collisions ($>$~40\%), the opposite trend is observed.
+In semiperipheral collisions ($>$~40\%), the opposite trend is observed.
 
@@
 	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
-	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ [SC(3,2), SC(4,2), NSC(3,2), and NSC(4,3)] is significantly underestimated in hydrodynamic model calculations in mid-central collisions.
+	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ [SC(3,2), SC(4,2), NSC(3,2), and NSC(4,3)] is significantly underestimated in hydrodynamic model calculations in midcentral collisions.
 	\item All the VISH2+1 model calculations with large $\eta/s$ fail to describe the centrality dependence of the correlations regardless of the initial conditions.
-	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively, but not quantitively for most of the centrality ranges.
+	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but not quantitively for most of the centrality ranges.
 	\item The default AMPT model can describe the normalized symmetric cumulants [NSC($m$,$n$)] quantitively for most centralities while the string melting AMPT model fails to describe them.

### 2018-01-15 appendix.tex
fixing comma's and midcentral

@@
 In these calculations, the initial conditions and $\eta/s$ parametrizations are chosen to reproduce the LHC $v_n$ data.
-The calculations capture the centrality dependence of $v_n$ in the central and mid-central collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
+The calculations capture the centrality dependence of $v_n$ in the central and midcentral collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.
 
@@
 Finally, few selected calculations from three theoretical models which describe the $v_n$ data best are shown in Fig.~\ref{fig:Figure_A4}.
-The calculations from event-by-event EKRT+viscous hydrodynamics, VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) with an accuracy of 5--20\%.
+The calculations from event-by-event EKRT+viscous hydrodynamics, VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ ($n$ = 2, 3, and 4) with an accuracy of 5--20\%.
 The centrality dependence differs in the three models as well as in the different order flow harmonics.
-Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
+Together with SC$(m,n)$ and NSC$(m,n)$, the simultaneous description of individual flow harmonics $v_n$ at all orders is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultrarelativistic heavy-ion collisions.

### 2018-01-15 longSC.tex
fixing comma's and midcentral

@@
 
-\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n{\mathrm{th}}$-order harmonic.
+\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$, and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle, and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n{\mathrm{th}}$-order harmonic.
 Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
 The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
-This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
+This profile fluctuates event by event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
 The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
@@
 These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}.
-Therefore their measurement would provide experimental constraints on theoretical parameters used to describe the individual stages of the heavy-ion system evolution.
+Therefore, their measurement would provide experimental constraints on theoretical parameters used to describe the individual stages of the heavy-ion system evolution.
 In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.
@@
 with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in Ref.~\cite{Bilandzic:2013kga}).
-In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
+In this article, SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
 %
@@
 conditions and the event selection criteria are identical to those
-described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
+described in Refs.~\cite{Aamodt:2010pa, Aamodt:2010cz}.
 Approximately $10^7$ minimum-bias $\PbPb$ events with
@@
 The systematic uncertainty from the centrality determination was evaluated by using the TPC and silicon pixel detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors.
-The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
+The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3) and 8\% for  SC(5,3).
 As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$ vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$.
@@
 same parameters as described in Sec.~\ref{sec:experiment}, and tracks from a combination of the TPC and the inner tracking system (ITS) detectors with tighter selection criteria.
-To avoid non-uniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
+To avoid nonuniform azimuthal acceptance due to dead zones in the SPD, and to get the best transverse momentum resolution, a hybrid track selection utilizing SPD hits and/or ITS refit tracks combined with TPC information was used.
 Then each track reconstruction strategy was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
@@
 
-Another large contribution to the systematic uncertainty originates from azimuthal non-uniformities in the reconstruction efficiency.
+Another large contribution to the systematic uncertainty originates from azimuthal nonuniformities in the reconstruction efficiency.
 In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}), which has a uniform distribution in azimuthal angle.
-Detector inefficiencies were introduced to mimic the non-uniform azimuthal distribution in the data.
+Detector inefficiencies were introduced to mimic the nonuniform azimuthal distribution in the data.
 For the observables SC(5,2), SC(5,3), and SC(4,3), the variation due to nonuniform acceptance is about 9\%, 17\%, and 11\%, respectively.
@@
 The centrality dependence of the higher order harmonic correlations [SC(4,3), SC(5,2), and SC(5,3)] are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations [SC(3,2) and SC(4,2)], which were published in Ref.~\cite{ALICE:2016kpq}.
-The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated like $v_3$ and $v_2$.
+The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$ as well as $v_3$ and $v_5$ are correlated like $v_2$ and $v_4$, while $v_3$ and $v_4$ are anticorrelated like $v_3$ and $v_2$.
 
@@
         \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for $m$ = 3--5 and $n$ = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV.
-The lower order harmonic correlations [SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)] are taken from Ref.~\cite{ALICE:2016kpq} and shown as bands.
+The lower order harmonic correlations [SC(3,2), SC(4,2), NSC(3,2), and NSC(4,2)] are taken from Ref.~\cite{ALICE:2016kpq} and shown as bands.
 The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations.
@@
 This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
-The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range 0--30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the 30--50\% centrality range.
+The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range 0--30\%, while showing a moderate increase of anticorrelation with increasing $p_{\rm T, min}$ for the 30--50\% centrality range.
 The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases.
@@
 
-In the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
+In the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD + saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}.
 The subsequent space-time evolution is described by relativistic dissipative fluid dynamics with different parametrizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$.
 This model gives a good description of the charged hadron multiplicity and the low-$p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11--13 in Ref.~\cite{Niemi:2015qia}).
-Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in Ref.~\cite{Niemi:2015qia} and our appendix).
+Each of the $\eta/s(T)$ parametrizations is adjusted to reproduce the measured $v_n$ from central to midperipheral collisions (see Fig.~15 in Ref.~\cite{Niemi:2015qia} and our appendix).
 
@@
 The {KLN} model assumes that the initial energy density is proportional to that of the initial gluons calculated from the corresponding $k_{\rm T}$ factorization formula~\cite{Kharzeev:2000ph}.
-In Monte Carlo versions {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah} of these models additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
+In Monte Carlo versions {MC-Glauber} and {MC-KLN}~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah} of these models, additional initial state fluctuations are introduced through position fluctuations of individual nucleons inside the colliding nuclei.
 For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy distribution of individual partons, which fluctuate in both momentum and coordinate space.
-Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
+Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to nonvanishing initial local flow velocities~\cite{Pang:2012he}.
 
 Even though thermalization could be achieved quickly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime.
-To address such non-equilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
+To address such nonequilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
 The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
@@
 In the string melting configuration, the initial strings are melted into partons whose interactions are described by the zipping parton cascade (ZPC) model~\cite{Zhang:1997ej}.
-These partons are then combined into the final state hadrons via a quark coalescence model.
+These partons are then combined into the final-state hadrons via a quark coalescence model.
 In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a relativistic transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
 The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
-Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$, and $v_5$) at $\snn=2.76$~TeV.
+Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and midcentral $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$, and $v_5$) at $\snn=2.76$~TeV.
 It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}.
@@
 While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in the 0--40\% centrality range and deviate by about one $\sigma$ for 40--50\% centrality.
-In the case of $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly in mid-central collisions and fail similarly for the anticorrelation between $v_3$ and $v_2$.
+In the case of $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly in midcentral collisions and fail similarly for the anticorrelation between $v_3$ and $v_2$.
 
@@
 Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}.
-Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers.
+Three initial conditions from AMPT, MC-KLN, and MC-Glauber are drawn as different colors and markers.
 The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber and 0.16 for AMPT) are drawn as dashed lines.
@@
 It should be noted that the agreement with SC($m$,$n$) should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as was demonstrated for SC(3,2).
-Hence the simultaneous description of SC($m$,$n$) and NSC($m$,$n$) should give better constraints on the parameters in AMPT models.
+Hence, the simultaneous description of SC($m$,$n$) and NSC($m$,$n$) should give better constraints on the parameters in AMPT models.
 The string melting AMPT model describes SC(5,3) and NSC(5,3) well. However, the same setting overestimates SC(5,2) and NSC(5,2). 
-The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as in the case of NSC(3,2) and NSC(4,2).
+The default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well, as in the case of NSC(3,2) and NSC(4,2).
 In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model comes the closest to the data. 
@@
 The $\chisqndf$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$.
-The $\chisqndf$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parametrization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
+The $\chisqndf$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature-dependent $\eta/s$ parametrization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3).
 This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.
@@
 The NSC(3,2) and NSC(4,2) observables as a function of $p_{\rm T, min}$ are compared to the {AMPT} simulations in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}, respectively.
-The observed $p_{\rm T}$ dependence for NSC(3,2) in mid-central collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
+The observed $p_{\rm T}$ dependence for NSC(3,2) in midcentral collisions is also seen in AMPT simulations for higher $p_{\rm T, min}$.
 The default configuration of the AMPT reproduces NSC(3,2), while the other AMPT configurations predict a very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitudes of both NSC(3,2) and NSC(4,2) simultaneously.
@@
 
-We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
+We have found that fluctuations of SC(3,2) and SC(4,3) are anticorrelated in all centralities while fluctuations of SC(4,2), SC(5,2), and SC(5,3) are correlated for all centralities. 
 These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
@@
 The default configuration of the AMPT model describes well the normalized symmetric cumulants [NSC($m$,$n$)] for most centralities and for most combinations of harmonics which were considered. 
-Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions.
+Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in midcentral collisions.
 This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.

### 2018-01-15 Alice_Authorlist_2017-Aug-21.tex
author list USA

@@
 \item \Adef{orgI}Dipartimento DET del Politecnico di Torino, Turin, Italy
-\item \Adef{orgII}Georgia State University, Atlanta, Georgia, United States
+\item \Adef{orgII}Georgia State University, Atlanta, Georgia, USA
 \item \Adef{orgIII}M.V. Lomonosov Moscow State University, D.V. Skobeltsyn Institute of Nuclear, Physics, Moscow, Russia
@@
 \item \Idef{org5}Budker Institute for Nuclear Physics, Novosibirsk, Russia
-\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, United States
+\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, USA
 \item \Idef{org7}Central China Normal University, Wuhan, China
@@
 \item \Idef{org11}Centro Fermi - Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi', Rome, Italy
-\item \Idef{org12}Chicago State University, Chicago, Illinois, United States
+\item \Idef{org12}Chicago State University, Chicago, Illinois, USA
 \item \Idef{org13}China Institute of Atomic Energy, Beijing, China
@@
 \item \Idef{org15}Department of Physics, Aligarh Muslim University, Aligarh, India
-\item \Idef{org16}Department of Physics, Ohio State University, Columbus, Ohio, United States
+\item \Idef{org16}Department of Physics, Ohio State University, Columbus, Ohio, USA
 \item \Idef{org17}Department of Physics, Pusan National University, Pusan, Republic of Korea
@@
 \item \Idef{org80}Laboratoire de Physique Subatomique et de Cosmologie, Universit\'{e} Grenoble-Alpes, CNRS-IN2P3, Grenoble, France
-\item \Idef{org81}Lawrence Berkeley National Laboratory, Berkeley, California, United States
+\item \Idef{org81}Lawrence Berkeley National Laboratory, Berkeley, California, USA
 \item \Idef{org82}Moscow Engineering Physics Institute, Moscow, Russia
@@
 \item \Idef{org93}Nuclear Physics Institute, Academy of Sciences of the Czech Republic, \v{R}e\v{z} u Prahy, Czech Republic
-\item \Idef{org94}Oak Ridge National Laboratory, Oak Ridge, Tennessee, United States
+\item \Idef{org94}Oak Ridge National Laboratory, Oak Ridge, Tennessee, USA
 \item \Idef{org95}Petersburg Nuclear Physics Institute, Gatchina, Russia
-\item \Idef{org96}Physics Department, Creighton University, Omaha, Nebraska, United States
+\item \Idef{org96}Physics Department, Creighton University, Omaha, Nebraska, USA
 \item \Idef{org97}Physics department, Faculty of science, University of Zagreb, Zagreb, Croatia
@@
 \item \Idef{org104}Physik Department, Technische Universit\"{a}t M\"{u}nchen, Munich, Germany
-\item \Idef{org105}Purdue University, West Lafayette, Indiana, United States
+\item \Idef{org105}Purdue University, West Lafayette, Indiana, USA
 \item \Idef{org106}Research Division and ExtreMe Matter Institute EMMI, GSI Helmholtzzentrum f\"ur Schwerionenforschung GmbH, Darmstadt, Germany
@@
 \item \Idef{org118}The Henryk Niewodniczanski Institute of Nuclear Physics, Polish Academy of Sciences, Cracow, Poland
-\item \Idef{org119}The University of Texas at Austin, Physics Department, Austin, Texas, United States
+\item \Idef{org119}The University of Texas at Austin, Physics Department, Austin, Texas, USA
 \item \Idef{org120}Universidad Aut\'{o}noma de Sinaloa, Culiac\'{a}n, Mexico
@@
 \item \Idef{org123}Universidade Federal do ABC, Santo Andre, Brazil
-\item \Idef{org124}University of Houston, Houston, Texas, United States
+\item \Idef{org124}University of Houston, Houston, Texas, USA
 \item \Idef{org125}University of Jyv\"{a}skyl\"{a}, Jyv\"{a}skyl\"{a}, Finland
 \item \Idef{org126}University of Liverpool, Liverpool, United Kingdom
-\item \Idef{org127}University of Tennessee, Knoxville, Tennessee, United States
+\item \Idef{org127}University of Tennessee, Knoxville, Tennessee, USA
 \item \Idef{org128}University of the Witwatersrand, Johannesburg, South Africa
@@
 \item \Idef{org138}Warsaw University of Technology, Warsaw, Poland
-\item \Idef{org139}Wayne State University, Detroit, Michigan, United States
+\item \Idef{org139}Wayne State University, Detroit, Michigan, USA
 \item \Idef{org140}Wigner Research Centre for Physics, Hungarian Academy of Sciences, Budapest, Hungary
-\item \Idef{org141}Yale University, New Haven, Connecticut, United States
+\item \Idef{org141}Yale University, New Haven, Connecticut, USA
 \item \Idef{org142}Yonsei University, Seoul, Republic of Korea

### 2018-01-18 longSC.tex
final to EB

@@
 The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
-In the string melting configuration, the initial strings are melted into partons whose interactions are described by the zipping parton cascade (ZPC) model~\cite{Zhang:1997ej}.
+In the string melting configuration, the initial strings are melted into partons whose interactions are described by the Zhang's parton cascade (ZPC) model~\cite{Zhang:1997ej}.
 These partons are then combined into the final-state hadrons via a quark coalescence model.
